### 2020-11-25 Research Report - Boverhof/main.tex

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{apacite}
\usepackage{caption} 
\usepackage{setspace}

\captionsetup[table]{skip=4pt}
\onehalfspacing
\pagestyle{myheadings}

\begin{document}
\begin{titlepage}
\begin{center}
\LARGE{\textbf{The Realtime Assesment of Mental Workload by Means of Multiple Bio-Signals}}\\
\vspace*{2\baselineskip}
\Large{\textbf{Masterthesis Report}}\\
Methodology and Statistics for the Behavioural, Biomedical and Social Sciences\\
\vspace*{1\baselineskip}
Utrecht University\\
\vspace*{4\baselineskip}
{Bart-Jan Boverhof, 6000142}\\
\vspace*{1\baselineskip}
{\textbf{Thesis Supervisor}}\\
Prof.dr.ir. B.P. Veldkamp\\
\vspace*{1\baselineskip}
{\textbf{Date}}\\
October 14, 2020\\
\vspace*{1\baselineskip}
\end{center}
\end{titlepage}

\section{Introduction}
The topic of mental workload (MWL) has received widespread attention across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
A simple definition of MWL is the demand placed upon humans whilst carrying out a certain task. As pointed out by de Waard (1996), such a definition is too shallow, for it defines workload solely in external sense. It is of importance to acknowledge that MWL is person-specific, for the amount of experienced MWL ushered by a given task may differ across people \cite{de1996measurement}. When referring to MWL throughout this research, person-specific MWL is meant specifically.

A commonly employed measure of workload is the NASA-Task Load Index (or TLX) questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}. A potential problem arousing with such measurements, is that they are conducted post-experiment, posing the risk of jeopardizing the quality of the data by introducing subjectivity. An example of such a danger resides in the observer bias, proving that actors participating in an experiment tend to over-exaggerate the treatment effect when having to report it themselves post-experiment \cite{mahtani2018catalogue}. An inherently more objective method for the assessment of MWL is to gather bio-signals during the experiment, and use these to classify the degree of perceived MWL. Examples of such bio-signals (hereafter modalities) include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc. The advantage of an approach like this is that complementary information streams, each stemming from a different modality can be interpreted simultaneously \cite{ramachandram2017deep}. This yields an objective and rich multifaceted classification of a mental construct, such as MWL. This approach comes however at the cost of an increase in complexity. This complexity mainly resides in the proper designing of a complex framework that inputs the data from the utilized modalities, and outputs a single classification outcome.

The current research directly builds upon previous research conducted by Dolmans and colleagues, who proposed a framework for multi-modal deep-learning classification of MWL \cite{dolmans2020perceived}. The current research will explore the feasibility of a similar framework, but by adding to this a real-time component. This implies that classification is done whilst the experiment takes place, enabling the possibilities to alter the state of the experiment in real-time. Such an approach could enable a wide range of possibilities: consider for example a flight-simulation with the objective of training pilots. The possibility for such a simulation to play out dynamically could enhance the learning-experience, namely by catering the state of the simulation towards the the individual, based on a real-time classification of for example their MWL.

A real-time approach will be contrasted with a non-real-time approach. Special focus will be placed upon the justification of using a real-time approach, given the increment in complexity such an approach is likely to cause. Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, and which can be altered by the researches in real-time.

In order to build both frameworks, three of the (arguably) most widely utilized modalities will be included. These modalities include the techniques of electroencephalogram (EEG), galvanic skin response (GSR) and photoplethysmography (PPG). It is important to stress again that the objective of the current research is not to gain insight into the most optimal model for analyzing data stemming from the previously delineated modalities. It is rather to build a (real-time) framework researchers can utilize, and to which they can flexibly add modalities conform their own research goals. Consequently, one of two design principles on which the architecture of the framework reclines is the concept of modularity. Modularity refers the extent to which different modalities can freely be added and/or removed, without the necessity to re-architect and rebuild the entire framework. The second adhered design principle is the principle generalizability, prescribing that the framework should not solely be utilizable in the context of MWL, but also for the measurement of other mental constructs.

\newpage
\section{Methods}

\subsection{Related Work}
The current section will provide an overview of previous research on the most optimal model for each modality and the most feasible framework architectures.

\subsubsection{Electroencephalogram (EEG)}
The first utilized modality is a technique  called EEG, which detects electrical activity in the brain using electrodes. EEG is a widely utilized method for classifying MWL during experiments. With a review of the complete literature on EEG classification with deep learning, Craik and colleagues found a total of 16 \% of all available papers to deal with MWL, lending credence to the widely employed phenomenon of EEG for investigating MWL \cite{craik2019deep}. Additionally, this review aimed to map the feasibility of using deep neural learning for a range of different EEG application separately. Summarizing the findings, Craik and colleagues report that studies mostly found deep belief networks and ConvNets to perform best when aiming to classify MWL, and advice one of these approaches consequently.\cite{craik2019deep}

Research by Schirrmeister and colleagues contrasted several differently designed convolutional neural networks (ConvNets) against the baseline method for EEG data (FBCSP) in order to decode imagined or executed tasks. The investigated networks included deep, shallow, deep-shallow hybrid and residual ConvNets. Both the deep and shallow ConvNets were found to reach at least similar, and in some regard better classification results, as compared with the FBCSP baseline model. Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, displaying an accuracy of 92.4 \% \cite{schirrmeister2017deep}. The appropriate design choices were found to be of importance in order to be able to reach this accuracy, including the employment of techniques such as batch normalization, dropout and the usage of the ELU activation function.

\subsubsection{Galvanic Skin Response (GSR)}
The second utilized modality is GSR, measuring sweat gland on the hands and hereby inferring arousal. GSR readings have been found to significantly increase as a consequence of an increase in task cognitive load, hence constituting to be an objective predictor \cite{shi2007galvanic}.

Sun and colleagues explored the most optimal deep-learning model for classifying six different emotional states by means of GSR data. Several models were investigated, amongst others the support vector machine, the ConvNet, the long-short-term-memory (LSTM) model and a hybrid model combining the ConvNet and LSTM approaches. The hybrid model was found to perform best, exhibiting an accuracy of 74\%. Additionally, data augmentation was found to be able to substantially increase classification results \cite{sun2019hybrid}.

A variant on the CovNet LSTM model was employed by Dolmans and colleagues, who aimed to classify MWL by means of amongst other modalities GSR (equally so as the current research) \cite{dolmans2020perceived}. The performance of this model was contrasted with a network consisting solely of fully connected dense layers. Conform with findings by Sun and colleagues, the hybrid model was found to perform best \cite{dolmans2020perceived}. The model architecture as utilized by Dolmans and colleagues deployed 2 convolutional layers, after each of which batch normalisation was performed. Subsequently, max pooling was performed, after which the network feeds into two LSTM layers, followed by a dense layer.

\subsubsection{Photoplethysmography (PPG)}
The third modality constitutes PPG, which is a technique utilized to measure heart rate. PPG is, not undeservedly, a widely deployed technique within the field of MWL classification. Zhang and colleagues investigated several approaches for measuring MWL, amongst three others the technique of PPG. Out of these four approaches, PPG was found to display both the highest sensitivity and reliability for measuring MWL, lending credence to the feasibility of PPG as a method for classifying MWL \cite{zhang2018evaluating}.

Work by Biswas and colleagues investigated a deep learning approach to PPG data, with the objective to perform both bio-metric identification and heart rate information. Exceptional results were attained with a neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}. This performance was managed with a hybrid model, incorporating two convolutional, followed with two LSTM layers. After each of two convolutional layers, batch normalisation and max pooling was applied.

The previously delineated model as proposed by Biswas and colleagues was adopted by Dolmans and colleagues, and subsequently applied towards the MWL case. This neural network was contrasted with a network of two fully connected dense layers. Batch normalisation and max pooling was performed in both contrasted networks. Surprisingly, the more sophisticated network constituting of the convolutional and LSTM layers was found to perform worse in the context of MLW classification, as compared with the simpler model, solely build from two dense layers \cite{dolmans2020perceived}.

\subsubsection{Framework Architecture - Data Fusion} 
When architecting a multi-model framework, it is of importance to realize that the information stemming from the different modalities are required to be combined (i.e. fused) in order to result in a single classification. Fusion can be done at different time-points within the framework. Several fusion strategies as proposed by Ramachandram and colleagues will be considered \cite{ramachandram2017deep}.

Early (or data-level) fusion focuses on how to optimally combine data sources, before being fed into the classification model. Techniques that realize this include for example principle component analysis or factor analysis. Early fusing is usually very challenging, due to the fact that data stemming from different modalities differ substantially in terms of dimensionality and sampling rate. Another disadvantage of early fusing, is that usually the oversimplified assumption of conditional independence is made. This assumption is unrealistic in practice, for data stemming from different modalities are expected to be correlated \cite{ramachandram2017deep}.

Late (or decision level) fusion on the other hand, refers to the process of aggregating the decisions from multiple models, each individually trained on all modalities. In case the data sources stemming from the various modalities are either correlated or measured within a deviant dimensionality, late fusion is a much more feasible approach \cite{ramachandram2017deep}.

Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modal deep-learning problems. Modalities are fused by simply adding a higher order layer, to which the individual deep-learning models separately defined for each modality feed into. This need not be a single layer, but could also be multiple layers, as long as each modality ultimately feeds into the highest order output layer \cite{ramachandram2017deep}.

\subsubsection{Framework Architecture - Real-time component}
bla bla

\subsection{Experimental Setup}
The experimental setting for data collection is the spaceship bridge simulator videogame Empty Epsilon, in which respondents are required to carry out tasks on a virtual spaceship bridge \cite{daid2016empty}. This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab hosted by the University of Twente (UT) and carried out in cooperation with Thales. The data is currently in the process of being collected. Ethical approval has been attained at the UT, and will be requested at the UU in the near future.\\  
\textit{Note on this paragraph: I will soon participate in the experiment, after which this paragraph will be extended.}

\subsection{Hyper Parameter Optimization}

\subsection{Model Evaluation}
The performance of the real-time framework will be assessed by contrasting it with a regular, non-real-time framework. Specifically, the quality of performance for each modality individually will be compared across both frameworks. This validation will be endeavored by means of six widely used performance measures, all constructed from the confusion matrix, as depicted below:

\bgroup
\def\arraystretch{1.6}%  
\begin{table}[h]
\centering
\caption{Confusion matrix}
\label{tab:my-table}
\begin{tabular}{lll}
                                        & True Positive          & True Negative          \\ \cline{2-3} 
\multicolumn{1}{l|}{Predicted Positive} & \multicolumn{1}{l|}{a} & \multicolumn{1}{l|}{b} \\ \cline{2-3} 
\multicolumn{1}{l|}{Predicted Negative} & \multicolumn{1}{l|}{c} & \multicolumn{1}{l|}{d} \\ \cline{2-3} 
\end{tabular}
\end{table}
\egroup

The measures accuracy, sensitivity, specificity, PPV, NPV and F1 will be utilized in order to asses model performance. The framework that performs best across these measures is considered to be the superior performing framework. Table two depicts the constitution of these performance measures by partly referring to confusion matrix depicted as table 1. 
\bgroup
\def\arraystretch{1.8}%  
\begin{table}[h]
\centering
\caption{Performance Metrics}
\label{tab:my-table}
\begin{tabular}{ll}
\hline
Accuracy:                       & \(\frac{\!\!\!\!\!\!\!\!\!\!\!\!\!\!a+d}{a+b+c+d}\) \\
Sensitivity:                    & \(\frac{a}{a+c}\)                                   \\
Specificity:                    & \(\frac{d}{b+d}\)                                   \\
Positive Predicted Value (PPV): & \(\frac{a}{a+b}\)                                   \\
Negative Predicted Value:       & \(\frac{d}{c+d}\)                                   \\
F1-measure:                     & \(\frac{2*Sensitivity*PPV}{Sensitivity+PPV}\)       \\ \hline
\end{tabular}
\end{table}
\egroup

\newpage
\bibliographystyle{apacite}
\bibliography{References}
\end{document}

### 2020-11-25 Research Proposal - Boverhof/Research Proposal - Boverhof /main.tex

\documentclass{article}
\pagestyle{myheadings}

\usepackage[utf8]{inputenc}
\usepackage{apacite}

\begin{document}
\begin{titlepage}
\begin{center}
\LARGE{\textbf{The Realtime Assesment of Mental Workload by Means of Multiple Bio-Signals}}\\
\vspace*{2\baselineskip}
\Large{\textbf{Masterthesis Report}}\\
Methodology and Statistics for the Behavioural, Biomedical and Social Sciences\\
\vspace*{1\baselineskip}
Utrecht University\\
\vspace*{8\baselineskip}
{Bart-Jan Boverhof, 6000142}\\
\vspace*{1\baselineskip}
{\textbf{Thesis Supervisor}}\\
Prof.dr.ir. B.P. Veldkamp\\
\vspace*{1\baselineskip}
{\textbf{Date}}\\
October 14, 2020\\
\vspace*{1\baselineskip}
{\textbf{Word count}}\\
747\\
\vspace*{1\baselineskip}
\end{center}
\end{titlepage}

\section{Introduction}
The topic of mental workload (MWL) has received widespread attention across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}. A simple definition of MWL is the demand placed upon humans whilst conducting a specific task. As pointed out by de Waard (1996), such a definition is too shallow, for it defines workload solely externally. It is of importance to acknowledge that MWL is person-specific, for the amount of experienced MWL ushered by a given task differs across people \cite{de1996measurement}.

A commonly employed measure of workload is the NASA-Task Load Index questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}. A potential problem arousing with such measurements, is that they are conducted post-experiment, posing the risk of jeopardizing the quality of the data by introducing subjectivity. An example of such a danger resides in the observer bias, proving that actors participating in an experiment tend to over-exaggerate the treatment effect when having to report it themselves post-experiment \cite{mahtani2018catalogue}. An approach inherently less prone towards such biases is the employment of bio-signals during an experiment.

The main objective of the current research is to provide a flexible framework with which researchers can measure MWL using the specific bio-signals (hereafter modalities) that are most feasible within their context.  The latter framework will aim to classify MWL in real-time, i.e. whilst the experiment takes place. Ultimately, this line of research pursues the ability to conduct a dynamic experiment, the development of which can be altered by in real-time. The following research question is delineated: \\ 
Which type of framework is most feasible for analyzing MWL in real-time by means of various bio-signals?

\newpage
\section{Data and Methods}
In order to answer the aforementioned question, data will be collected utilizing three different modalities, surrounding which the framework will be build. In order to attempt this in real-time, a technique called Lab Streaming Layer (LSL) is utilized during the data collection process. This enables data streams from all modalities to be properly synchronized, whilst satisfying the principle of modularity (i.e. the possibility to add various modalities) \cite{kothe2018lab}. More elaborate explorations of the appropriate architecture of this real-time framework are currently being endeavoured, but fall outside the scope (and word limit) of this proposal. The framework will be created in Python, by utilizing the machine learning toolbox Pytorch \cite{paszke2017automatic}

\subsection{Data}
The experimental setting for data collection is the spaceship bridge simulator videogame Empty Epsilon, in which respondents are required to carry out tasks on a virtual spaceship bridge \cite{daid2016empty}. This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab hosted by the University of Twente (UT) and carried out in cooperation with Thales. Ethical approval has been attained at the UT, and will be requested at the UU in the near future.

\subsection{Methods}
\subsubsection{Electroencephalogram (EEG)}
The first modality is a technique  called electroencephalogram (EEG), which detects electrical activity in the brain using electrodes. Research by \cite{schirrmeister2017deep} contrasted several differently designed convolutional neural networks (ConvNets) against the baseline method for EEG data (FBCSP). Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform well, and will be utilized consequently \cite{schirrmeister2017deep}.

\subsubsection{Galvanic Skin Response (GSR)}
The second modality is the technique called Galvanic Skin Response (GSR), measuring sweat gland on the hands and hereby inferring arousal. This technique was found to be an objective predictor of MWL \cite{shi2007galvanic}. For analyzing GSR data, a hybrid model combining a convolutional neural network (CNN) with a long-short-term memory (LSTM) model is proposed \cite{sun2019hybrid}. Such a model hybrid model was contrasted with a regular CNN (2 layers), after which the hybrid model was found to perform best \cite{dolmans2020perceived}. Consequently, a model stacking 2 convolutional layers with 2 LSTM layers will be utilized.

\subsubsection{Photoplethysmography (PPG)}
The third modality constitutes Photoplethysmography (PPG), which is a technique utilized to measure heart rate, and is also proven to be a suitable indicator of MWL \cite{zhang2018evaluating}. A hybrid model, stacking two convolutional layers and two LSTM was found to perform best, for which this model will be utilized \cite{biswas2019cornet}.

\subsection{Model Evaluation}
The performance of the real-time framework will be assessed by contrasting it with a non-real-time framework. Specifically, the quality of performance for each modality individually will be assessed. This validation will be endeavored by means of six widely utilized performance measures within the fields of deep and machine learning: accuracy, sensitivity, specificity, PPV, NPV and F1. The framework that performs best across these measures will be considered the optimal framework.

\newpage
\bibliographystyle{apacite}
\bibliography{References}
\end{document}

### 2020-11-26 Research Report - Boverhof/Tex report/main.tex
Multiple changes
- Changed structure of the repo
- Added latex table files
- Added the following parts to the report:
    * Data paragraph
    * Restructure of the report
    * Reformulation of several paragraphs

--- 2020-11-25 Research Report - Boverhof/main.tex
@@
 
+%Required packages
 \usepackage[utf8]{inputenc}
@@
 
-\captionsetup[table]{skip=4pt}
-\onehalfspacing
+%Prerequisite statements
+\captionsetup[table]{skip=4pt} %Line indent after table title
+\captionsetup{labelfont={bf}} %Bold label font for tables
+\onehalfspacing %Document line spacing
 \pagestyle{myheadings}
@@
 \begin{document}
+
+%Title page 
 \begin{titlepage}
@@
 
-\section{Introduction}
+\section{Introduction} \label{Introduction}
 The topic of mental workload (MWL) has received widespread attention across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
@@
 
-A real-time approach will be contrasted with a non-real-time approach.
+A real-time classification approach will be contrasted with a non-real-time approach.
 Special focus will be placed upon the justification of using a real-time approach, given the increment in complexity such an approach is likely to cause.
@@
 
-\subsection{Related Work}
-The current section will provide an overview of previous research on the most optimal model for each modality and the most feasible framework architectures.
+\subsection{Related Work} \label{Relatedwork}
+The current section will provide an overview of previous research on the model design for each seperate modality.
+Additionally,  the most feasible architecture for a multi-modular framework will be explored.
+In particular, attention is placed upon the data fusion, the real-time component and several model optimization techniques.
 
-\subsubsection{Electroencephalogram (EEG)}
+\subsubsection{First modality: Electroencephalogram (EEG)}
 The first utilized modality is a technique  called EEG, which detects electrical activity in the brain using electrodes.
@@
 
-\subsubsection{Galvanic Skin Response (GSR)}
+\subsubsection{Second modality: Galvanic Skin Response (GSR)}
 The second utilized modality is GSR, measuring sweat gland on the hands and hereby inferring arousal.
@@
 
-\subsubsection{Photoplethysmography (PPG)}
+\subsubsection{Third modality: Photoplethysmography (PPG)}
 The third modality constitutes PPG, which is a technique utilized to measure heart rate.
@@
 
-\subsubsection{Framework Architecture - Data Fusion} 
+\subsubsection{Framework Architecture}
+
+\paragraph{Data fusion.}  
 When architecting a multi-model framework, it is of importance to realize that the information stemming from the different modalities are required to be combined (i.e.
-fused) in order to result in a single classification.
+fused) in order to ultimately result in a single classification.
 Fusion can be done at different time-points within the framework.
@@
 
-\subsubsection{Framework Architecture - Real-time component}
+\paragraph{Real-time component}
 bla bla
 
-\subsection{Experimental Setup}
-The experimental setting for data collection is the spaceship bridge simulator videogame Empty Epsilon, in which respondents are required to carry out tasks on a virtual spaceship bridge \cite{daid2016empty}.
-This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab hosted by the University of Twente (UT) and carried out in cooperation with Thales.
-The data is currently in the process of being collected.
-Ethical approval has been attained at the UT, and will be requested at the UU in the near future.\\
-\textit{Note on this paragraph: I will soon participate in the experiment, after which this paragraph will be extended.}
+\subsection{Data}
+The current section will provide an overview of the utilized data.
+Special attention is placed on the experimental setup, the description of the participants and the data collection / synchronization process.
 
-\subsection{Hyper Parameter Optimization}
+\subsubsection{Experimental setup}
+The experimental setting for data collection is the spaceship videogame Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}.
+This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente (UT) and carried out in cooperation with Thales.
+The experiment constituted three different segments, during each of which respondents had to carry out different tasks, all aiming to measure workload.
+Each segment consists of six small sessions of roughly 5-10 minutes.
+These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment.
+A schematic overview of the experimental structure is depicted as table \ref{table:expsetup}.
+After each of the 18 segments, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires.
+Each questionnaire inquired upon the degree to which the respondent experienced workload during the previous session.
+These ratings will be used as labels in later training.
+Within each segment, the order in which the sessions (varying in difficulty) were presented have been randomized.
+The order in which the segments were administrated were not random.
+Between every three sessions, respondents were requested to take a short 2 minute break.
+\bgroup
+\def\arraystretch{1.6}%  
+\begin{table}[h]
+\centering
+\caption{Experimental setup: Number of sessions per segment and difficulty setting}
+\label{table:expsetup}
+\begin{tabular}{llll}
+                               & Easy                   & Intermediate           & Hard                   \\ \cline{2-4} 
+\multicolumn{1}{l|}{Segment 1} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
+\multicolumn{1}{l|}{Segment 2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
+\multicolumn{1}{l|}{Segment 3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
+\end{tabular}
+\end{table}
+\egroup
+
+The first segment emulated a scenario in which hostile spaceships approach the respondents spaceship.
+The respondent is required to  quickly react, and defuse hostile spaceships in order to survive.
+The increment in difficulty caused the process of defusing hostile spaceships to be more challenging and hereby to take longer,  aiming to increase workload consequently.
+The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible.
+Obstacles around which the respondent had to carefully navigate were introduced in the intermediate difficult scenario, and hostile spaceships the respondent had to decimate were introduced in the hard scenario.
+Both increase difficulty, and hereby aim to increase workload consequently.
+The third and final segment emulated a machine room, in which respondents had to control the power based on random requests generated by the video-game.
+Variables that could overheat the spaceship  were introduced as a consequence of an increase in difficulty, demanding the respondent multi-task, hereby aiming to increase workload.
+
+\subsubsection{Participants}
+In total, \# respondents have participated in the study.
+
+\subsubsection{Data collection and Synchronization}
+About streaming to LSL, and the utilized devices.
+
+\subsection{Framework}
+The architecture for the proposed framework is constructed by combining insights from the literature, as delineated in paragraph \ref{Relatedwork} with the formulated design principles in section \ref{Introduction} (i.e.
+the principles of molecularity and generalizability).
+
+The utilized network for the EEG modality will be a ConvNet with four convolutional max-pooling blocks. The utilized network for the GSR modality will be a hybrid LSTM ConvNet hybrid.
 
@@
 Specifically, the quality of performance for each modality individually will be compared across both frameworks.
-This validation will be endeavored by means of six widely used performance measures, all constructed from the confusion matrix, as depicted below:
-
+This validation will be endeavored by means of six widely used performance measures, all constructed from the confusion matrix, depicted as table  \ref{table:confusion}
+\bigskip
 \bgroup
@@
 \caption{Confusion matrix}
-\label{tab:my-table}
+\label{table:confusion}
 \begin{tabular}{lll}
@@
 The framework that performs best across these measures is considered to be the superior performing framework.
-Table two depicts the constitution of these performance measures by partly referring to confusion matrix depicted as table 1.
+Table \ref{table:metrics} depicts the constitution of these performance measures by partly referring to confusion matrix depicted as table \ref{table:confusion}.
+\bigskip
 \bgroup
@@
 \caption{Performance Metrics}
-\label{tab:my-table}
+\label{table:metrics}
 \begin{tabular}{ll}
@@
 \newpage
+
 \bibliographystyle{apacite}
 \bibliography{References}
+
 \end{document}

### 2020-11-29 Research Report - Boverhof/Tex report/main.tex

@@
 \usepackage{setspace}
+\usepackage{amsmath}
 
@@
 A commonly employed measure of workload is the NASA-Task Load Index (or TLX) questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}.
-A potential problem arousing with such measurements, is that they are conducted post-experiment, posing the risk of jeopardizing the quality of the data by introducing subjectivity.
-An example of such a danger resides in the observer bias, proving that actors participating in an experiment tend to over-exaggerate the treatment effect when having to report it themselves post-experiment \cite{mahtani2018catalogue}.
-An inherently more objective method for the assessment of MWL is to gather bio-signals during the experiment, and use these to classify the degree of perceived MWL.
+Such measurements are usually conducted post experiment, which could introduce some bias.
+An example of such a bias is the observer bias, prescribing that actors participating in an experiment tend to over-exaggerate the treatment effect when having to report it themselves post-experiment \cite{mahtani2018catalogue}.
+
+An alternative method for assessing MWL is by measuring bio-signals during the experiment, and use these to classify the degree of perceived MWL.
 Examples of such bio-signals (hereafter modalities) include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
+When training such classification models, administration of a questionnaire such as the TLX is usually utilized for labeling.
 The advantage of an approach like this is that complementary information streams, each stemming from a different modality can be interpreted simultaneously \cite{ramachandram2017deep}.
 This yields an objective and rich multifaceted classification of a mental construct, such as MWL.
+Additionally, a separate model for each respondent individually can be fitted, catering towards the individual perception of MWL.
 This approach comes however at the cost of an increase in complexity.
-This complexity mainly resides in the proper designing of a complex framework that inputs the data from the utilized modalities, and outputs a single classification outcome.
+This complexity resides in the construction of a complex framework that inputs the data from the utilized modalities, and outputs a single classification outcome.
 
 The current research directly builds upon previous research conducted by Dolmans and colleagues, who proposed a framework for multi-modal deep-learning classification of MWL \cite{dolmans2020perceived}.
-The current research will explore the feasibility of a similar framework, but by adding to this a real-time component.
+The current research will explore the feasibility of a similar framework, but by utilizing different modalities and data.
+Additionally, the current research will aim to incorporate a real-time component.
 This implies that classification is done whilst the experiment takes place, enabling the possibilities to alter the state of the experiment in real-time.
@@
 These modalities include the techniques of electroencephalogram (EEG), galvanic skin response (GSR) and photoplethysmography (PPG).
-It is important to stress again that the objective of the current research is not to gain insight into the most optimal model for analyzing data stemming from the previously delineated modalities.
+It is important to stress that the objective of the current research is not to gain insight into the most optimal model for analyzing data stemming from the previously delineated modalities individually.
 It is rather to build a (real-time) framework researchers can utilize, and to which they can flexibly add modalities conform their own research goals.
@@
 Additionally, this review aimed to map the feasibility of using deep neural learning for a range of different EEG application separately.
-Summarizing the findings, Craik and colleagues report that studies mostly found deep belief networks and ConvNets to perform best when aiming to classify MWL, and advice one of these approaches consequently.\cite{craik2019deep}
+Summarizing the findings, Craik and colleagues report that studies mostly found deep belief networks and ConvNets to perform best when aiming to classify MWL, and advice one of these approaches consequently \cite{craik2019deep}.
 
-Research by Schirrmeister and colleagues contrasted several differently designed convolutional neural networks (ConvNets) against the baseline method for EEG data (FBCSP) in order to decode imagined or executed tasks.
+Research by \citeA{schirrmeister2017deep} contrasted several differently designed convolutional neural networks (ConvNets) against the baseline method for EEG data (FBCSP) in order to decode imagined or executed tasks.
 The investigated networks included deep, shallow, deep-shallow hybrid and residual ConvNets.
@@
 The appropriate design choices were found to be of importance in order to be able to reach this accuracy, including the employment of techniques such as batch normalization, dropout and the usage of the ELU activation function.
+
+A different approach is proposed by \citeA{tabar2016novel}, combining a ConvNet with a Stacked auto-encoder network (SAE).
+Within this network, the input layer feeds into a convolutional layer with the objective of learning the filters and network parameters.
+The output of this convolutional layer subsequently feeds into SAE part of the network, constituting an input layer, 6 hidden layers and an output layer.
+A classification accuracy of 90 \% was acquired with this model \cite{tabar2016novel} .
 
@@
 
-A variant on the CovNet LSTM model was employed by Dolmans and colleagues, who aimed to classify MWL by means of amongst other modalities GSR (equally so as the current research) \cite{dolmans2020perceived}.
+A variant on the CovNet LSTM model was employed by \citeA{dolmans2020perceived}, who aimed to classify MWL by means of amongst other modalities GSR (equally so as the current research).
 The performance of this model was contrasted with a network consisting solely of fully connected dense layers.
-Conform with findings by Sun and colleagues, the hybrid model was found to perform best \cite{dolmans2020perceived}.
-The model architecture as utilized by Dolmans and colleagues deployed 2 convolutional layers, after each of which batch normalisation was performed.
+Conform with findings by Sun and colleagues, the hybrid model was found to perform best \cite{dolmans2020perceived}, displaying an accuracy of 82 \%.
+The model architecture as utilized by Dolmans and colleagues deployed 2 convolutional layers, after each of which batch normalization was performed.
 Subsequently, max pooling was performed, after which the network feeds into two LSTM layers, followed by a dense layer.
@@
 
-\subsubsection{Framework Architecture}
-
-\paragraph{Data fusion.}  
+\subsubsection{Fusion strategy}  
 When architecting a multi-model framework, it is of importance to realize that the information stemming from the different modalities are required to be combined (i.e.
@@
 Techniques that realize this include for example principle component analysis or factor analysis.
-Early fusing is usually very challenging, due to the fact that data stemming from different modalities differ substantially in terms of dimensionality and sampling rate.
+Early fusing is usually challenging, especially in a multimodal scenario such as the current.
+This resides in the fact that data stemming from different modalities differ substantially in terms of dimensionality and sampling rate.
 Another disadvantage of early fusing, is that usually the oversimplified assumption of conditional independence is made.
-This assumption is unrealistic in practice, for data stemming from different modalities are expected to be correlated \cite{ramachandram2017deep}.
+This assumption is unrealistic, for data stemming from different modalities are expected to be correlated in practice \cite{ramachandram2017deep}.
 
@@
 Modalities are fused by simply adding a higher order layer, to which the individual deep-learning models separately defined for each modality feed into.
-This need not be a single layer, but could also be multiple layers, as long as each modality ultimately feeds into the highest order output layer \cite{ramachandram2017deep}.
+This need not be a single layer, but could also be multiple layers, as long as each modality ultimately feeds into the highest order output layer.
+The depth of the fusion (i.e.
+the amount of fusion layers) can be chosen conform the specific situation, posing intermediate fusion to be the most flexible, and therefore the most widely used fusion method \cite{ramachandram2017deep}.
 
-\paragraph{Real-time component}
+\subsubsection{Real-time component}
 bla bla
+
+\subsubsection{Model optimization}
+The technique of batch normalization was proposed by  \citeA{ioffe2015batch},  and is often applied in deep learning with the objective of enhancing the stability of a network.
+This is endeavored by including a batch normalization layer after each convolutional layer, re-centering and re-scaling the input feeding into this layer.
+If incorporating a batch normalization layer, it is recommended to do so before feeding into the activation function \cite{ioffe2015batch}.
+An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived},  \citeA{schirrmeister2017deep} by specifying a batch normalization layer after each convolutional layer.
+Equally so, the best performing model for PPG data as proposed by \citeA{biswas2019cornet} included a batch normalization layer after each convolutional layer.
+
+Pooling layers are often used in ConvNets, following a convolutional layer with the attempt to decrease the dimensionality.
+The objective of such layers are to merge similar features into one (for a more extensive elaboration see: \cite{lecun2015deep}).
+Considering the EEG ConvNets, both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer.
+The model proposed for GSR data by \citeA{sun2019hybrid} incorporate a max-pooling layer after each, but one of the convolutional layers.
+Lastly, the model as proposed for PPG data by \cite{biswas2019cornet}  specified a max pooling layer after each convolutional layer.
+
+Hyper-parameter optimization (HPO) is a technique that can be used to optimize hyper-parameter including learning rate, dropout probability and momentum.
+The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled \cite{akiba2019optuna}.
+
+\subsection{Framework Architecture}
+The architecture for the proposed framework is constructed by combining insights from the literature whilst keeping in mind the previously delineated design principles (i.e.
+the principles of modularity and generalizability).
+
+The utilized network for the EEG modality is a ConvNet as proposed by \citeA{schirrmeister2017deep}.
+The network is designed to include four convolutional layers, each follow by a max pooling layer of stride $1* 3$.
+Ultimately, these blocks are followed up with a softmax layer in order end up with a classification.
+The Exponential Linear Unit (ELU) function is utilized as activation function, defined as:
+
+\begin{equation}
+R(x)= 
+\begin{Bmatrix}
+x & x \geq0 \\ 
+\alpha (e^x -1) & x<0
+\end{Bmatrix}
+\bigskip
+\end{equation}
+
+The utilized network for the GSR modality is a LSTM ConvNet hybrid.
 
@@
 
-\subsection{Framework}
-The architecture for the proposed framework is constructed by combining insights from the literature, as delineated in paragraph \ref{Relatedwork} with the formulated design principles in section \ref{Introduction} (i.e.
-the principles of molecularity and generalizability).
-
-The utilized network for the EEG modality will be a ConvNet with four convolutional max-pooling blocks. The utilized network for the GSR modality will be a hybrid LSTM ConvNet hybrid.
-
 \subsection{Model Evaluation}

### 2020-11-30 Research Report - Boverhof/Tex report/main.tex

@@
 
-\subsection{Framework Architecture}
-The architecture for the proposed framework is constructed by combining insights from the literature whilst keeping in mind the previously delineated design principles (i.e.
-the principles of modularity and generalizability).
-
-The utilized network for the EEG modality is a ConvNet as proposed by \citeA{schirrmeister2017deep}.
-The network is designed to include four convolutional layers, each follow by a max pooling layer of stride $1* 3$.
-Ultimately, these blocks are followed up with a softmax layer in order end up with a classification.
-The Exponential Linear Unit (ELU) function is utilized as activation function, defined as:
-
-\begin{equation}
-R(x)= 
-\begin{Bmatrix}
-x & x \geq0 \\ 
-\alpha (e^x -1) & x<0
-\end{Bmatrix}
-\bigskip
-\end{equation}
-
-The utilized network for the GSR modality is a LSTM ConvNet hybrid.
-
 \subsection{Data}
@@
 The experimental setting for data collection is the spaceship videogame Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}.
-This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente (UT) and carried out in cooperation with Thales.
+This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente (UT) and carried out in cooperation with Thales group Hengelo.
 The experiment constituted three different segments, during each of which respondents had to carry out different tasks, all aiming to measure workload.
@@
 \subsubsection{Participants}
-In total, \# respondents have participated in the study.
+In total, twenty-five respondents are participating in the study.
+Currently, the data is still in the process of being collected, for which no additional descriptive statistics can be presented in the prevailing section.
+The respondents are students, recruited from the University of Twente.
+Recruitment has been conducted with Sona, which is a cloud-based participant management system.
+Requirements were that respondents didn't have constraints that might interfere with the utilized sensors, such as for example a pacemaker.
+This is assessed by means of a short demographic questionnaire prior to the experiment.
+Additionally, the respondents are made aware of ethical consent prior to the experiment, with the objective to ensure completely voluntary participation.
+Respondents were able to draw back from the experiment at any time.
 
 \subsubsection{Data collection and Synchronization}
-About streaming to LSL, and the utilized devices.
+Data streams stemming from the different modalities are measured on different frequencies, and consequently need to be properly synchronized.
+This is accomplished by means of a technique called Lab-Streaming Layer (LSL), to which different data streams are streamed during the experiment.
+LSL properly synchronizes these data streams, records all data into a single file per participant \cite{kothe2018lab}.
+
+\subsection{Framework Architecture}
+The architecture for the proposed framework is constructed by combining insights from the literature whilst keeping in mind the previously delineated design principles (i.e.
+the principles of modularity and generalizability).
+
+The utilized network for the EEG modality is a ConvNet as proposed by \citeA{schirrmeister2017deep}.
+The network is designed to include four convolutional layers, each follow by a max pooling layer of stride $1* 3$.
+Ultimately, these blocks are followed up with a softmax layer in order end up with a classification.
+The Exponential Linear Unit (ELU) function is utilized as activation function, defined as:
+
+\begin{equation}
+R(x)= 
+\begin{Bmatrix}
+x & x \geq0 \\ 
+\alpha (e^x -1) & x<0
+\end{Bmatrix}
+\bigskip
+\end{equation}
+
+The utilized network for the GSR modality is a LSTM ConvNet hybrid.
 

### 2020-12-01 Research Report - Boverhof/Tex report/main.tex

@@
 
-\subsubsection{Data collection and Synchronization}
+\subsubsection{Devices and Synchronization}
+The Shimmer3 GSR+ sensor is used for both PPG and GSR measurements.
+The device is worn on the wrist, and communicates the signals wirelessly.
+An ear-clip is utilized for measuring the PPG, and converting this to estimate heart rate.
+Skin conductivity (GSR) is monitored between two electrodes attached to two fingers \cite{shimmer}.
+Both PPG and GSR are measured on a sample rate of 256 Hz.
+EEG measurement is conducted with the shimmer 2, equally so on a sampling rate of 256 Hz.
+
 Data streams stemming from the different modalities are measured on different frequencies, and consequently need to be properly synchronized.
-This is accomplished by means of a technique called Lab-Streaming Layer (LSL), to which different data streams are streamed during the experiment.
-LSL properly synchronizes these data streams, records all data into a single file per participant \cite{kothe2018lab}.
+This is accomplished by means of an application called Lab-Streaming Layer (LSL), to which different data streams are streamed during the experiment.
+LSL properly synchronizes these data streams such that they refer to the same points in time, and records all data into a single file per participant \cite{kothe2018lab}.
 
@@
 the principles of modularity and generalizability).
+Figure \# visualizes the entire framework \textit{Still has to be made but didnt figure out yet how}.
 
 The utilized network for the EEG modality is a ConvNet as proposed by \citeA{schirrmeister2017deep}.
-The network is designed to include four convolutional layers, each follow by a max pooling layer of stride $1* 3$.
-Ultimately, these blocks are followed up with a softmax layer in order end up with a classification.
+The network is designed to include four convolutional layers, each follow by a max pooling layer of stride 3.
 The Exponential Linear Unit (ELU) function is utilized as activation function, defined as:
@@
 \begin{equation}
-R(x)= 
+f(x)= 
 \begin{Bmatrix}
@@
 
-The utilized network for the GSR modality is a LSTM ConvNet hybrid.
+The utilized network for the GSR modality is a LSTM ConvNet hybrid model, inspired by the work of \citeA{sun2019hybrid} and  \citeA{dolmans2020perceived}.
+The network is designed to include two convolutional blocks, each consisting of a convolutional layer, followed by a batch normalization layer and closed with a max-pooling layer of stride 4.
+Following these blocks are two LTSM layers.
+The Rectified Linear Unit (ReLU) function is utilized as activation function, defined as:
+
+\begin{equation} 
+\label{eqn:relu}
+f(x)=max(0,x)
+\bigskip
+\end{equation}
+
+Lastly, the PPG modality is analyzed by means of the model as proposed by \citeA{biswas2019cornet}.
+The nework starts with two convolutional blocks, each consisting of a convolutional layer, batch normalization layer and closed with a max pooling layer of stride 4.
+Following these blocks are two LTSM layers, equal to the GSR model.
+The utilized activation function is the ReLU, depicted as equation \ref{eqn:relu}.
+
+The network for each of the modalities are finally closed with one fully connected dense layer before feeding into the head network, such that all inputs are flattened in a lower dimensional space.
+All outputs from these dense layers are concatenated.
+The head network consists of Four dense layers, alternated with some batch normalization and max-pooling layers with the objective of stabilization.
+The entire network and its  size, is summarized in table \ref{table:networksummary}.
+\bigskip
+
+\bgroup
+\def\arraystretch{1.6}%  
+\begin{table}[h]
+\centering
+\caption{Network summary	}
+\label{table:networksummary}
+\begin{tabular}{llll}
+EEG        & GSR        & PPG        & Head       \\ \hline
+Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
+Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
+Conv3: 100 & LSTM1: 256 & LSTM1: 256 & Dense: 128 \\
+Conv4: 200 & LSTM1: 256 & LSTM2: 256 &            \\
+Dense: 200 & Dense: 256 & Dense: 256 &            \\ \hline
+\end{tabular}
+\vspace{2ex}
+
+{\raggedright \textit{Note that for convolutional layers the number reflects the amount of filters, whereas for all other layers it refers to the amount of nodes.} \par}
+\end{table}
+\egroup
 

### 2020-12-07 Research Report - Boverhof/Tex report/main.tex
Report changes
- Changed document margins/sizes
- Added figure
- Rewrote part of introduction to include realtime assesment by 2 paragraphs
- Added "model variations" paragraph

@@
-\documentclass{article}
+\documentclass[12pt]{article}
 
@@
 \usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage[textwidth=160mm, textheight=210mm, hmarginratio=1:1]{geometry}
 
@@
 \onehalfspacing %Document line spacing
-\pagestyle{myheadings}
+\pagestyle{myheadings} %Heading style
+\graphicspath{ {./figures/} } %Defining image path
 
@@
 \begin{center}
-\LARGE{\textbf{The Realtime Assesment of Mental Workload by Means of Multiple Bio-Signals}}\\
+\LARGE{\textbf{The Realtime Assessment of Mental Workload by Means of Multiple Bio-Signals}}\\
 \vspace*{2\baselineskip}
-\Large{\textbf{Masterthesis Report}}\\
-Methodology and Statistics for the Behavioural, Biomedical and Social Sciences\\
+\Large{\textbf{Master thesis Report}}\\
+Methodology and Statistics for the Behavioral, Biomedical and Social Sciences\\
 \vspace*{1\baselineskip}
@@
 Examples of such bio-signals (hereafter modalities) include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
-When training such classification models, administration of a questionnaire such as the TLX is usually utilized for labeling.
 The advantage of an approach like this is that complementary information streams, each stemming from a different modality can be interpreted simultaneously \cite{ramachandram2017deep}.
@@
 The current research will explore the feasibility of a similar framework, but by utilizing different modalities and data.
-Additionally, the current research will aim to incorporate a real-time component.
-This implies that classification is done whilst the experiment takes place, enabling the possibilities to alter the state of the experiment in real-time.
-Such an approach could enable a wide range of possibilities: consider for example a flight-simulation with the objective of training pilots.
-The possibility for such a simulation to play out dynamically could enhance the learning-experience, namely by catering the state of the simulation towards the the individual, based on a real-time classification of for example their MWL.
-
-A real-time classification approach will be contrasted with a non-real-time approach.
-Special focus will be placed upon the justification of using a real-time approach, given the increment in complexity such an approach is likely to cause.
-Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, and which can be altered by the researches in real-time.
+Additionally a realtime component will be introduced.
+This implies that classification can done in realtime, that is whilst the experiment takes place, opening the possibility for the researcher to alter the state of the experiment in realtime.
+Such an approach could enable a wide range of possibilities: consider for example a flight simulation with the objective of educating pilots.
+The possibility for such a simulation to be altered dynamically could substantially enhance the learning-experience, namely by catering the state of the simulation towards the the individual, for example based on their perceived workload.
 
@@
 These modalities include the techniques of electroencephalogram (EEG), galvanic skin response (GSR) and photoplethysmography (PPG).
-It is important to stress that the objective of the current research is not to gain insight into the most optimal model for analyzing data stemming from the previously delineated modalities individually.
-It is rather to build a (real-time) framework researchers can utilize, and to which they can flexibly add modalities conform their own research goals.
+It is important to stress that the objective of the current research is not to gain insight into the most optimal model design for each of the previously delineated modalities.
+It is rather to construct a framework with which realtime classification can be managed, and to which modalities of choice can easily be added.
 Consequently, one of two design principles on which the architecture of the framework reclines is the concept of modularity.
-Modularity refers the extent to which different modalities can freely be added and/or removed, without the necessity to re-architect and rebuild the entire framework.
+Modularity refers the extent to which different modalities can freely be added and/or removed, without the necessity to re-architect and rebuild the framework.
 The second adhered design principle is the principle generalizability, prescribing that the framework should not solely be utilizable in the context of MWL, but also for the measurement of other mental constructs.
+
+Considering the relative complexity of a multi-modular deep neural network, an important point of attention is model optimization.
+In order for realtime classification to be a feasible, an optimized and swift neural network is required.
+The problem in realtime classification with deep learning is often not the quality of classification, but rather the speed of classification.
+The focus of the current research is therefore to architect and optimize a multi-modular deep neural network, which is capable of realtime classification, whilst still ensuring ample accuracy in classification.
+Several networks will be investigated upon in order to asses this.
+Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, the state of which can be altered in real-time.
 
@@
 \subsubsection{First modality: Electroencephalogram (EEG)}
-The first utilized modality is a technique  called EEG, which detects electrical activity in the brain using electrodes.
+The first utilized modality is EEG, which detects electrical activity in the brain using electrodes.
 EEG is a widely utilized method for classifying MWL during experiments.
-With a review of the complete literature on EEG classification with deep learning, Craik and colleagues found a total of 16 \% of all available papers to deal with MWL, lending credence to the widely employed phenomenon of EEG for investigating MWL \cite{craik2019deep}.
-Additionally, this review aimed to map the feasibility of using deep neural learning for a range of different EEG application separately.
-Summarizing the findings, Craik and colleagues report that studies mostly found deep belief networks and ConvNets to perform best when aiming to classify MWL, and advice one of these approaches consequently \cite{craik2019deep}.
+With their review of the complete literature on EEG classification with deep learning, \citeA{craik2019deep} found a total of 16 \% of all available papers to deal with MWL, lending credence to the ability of EEG for classifying MWL.
+Additionally, the usage of deep learning for a range of different EEG application was mapped.
+Summarizing, it was reported that studies mostly found deep belief networks and convolutional neural networks (ConvNets) to perform best when classifying workload, and advice one of these approaches consequently \cite{craik2019deep}.
 
-Research by \citeA{schirrmeister2017deep} contrasted several differently designed convolutional neural networks (ConvNets) against the baseline method for EEG data (FBCSP) in order to decode imagined or executed tasks.
+Research by \citeA{schirrmeister2017deep} contrasted the performance of several ConvNets against the widely acknowledged baseline method for EEG data, being FBCSP.
 The investigated networks included deep, shallow, deep-shallow hybrid and residual ConvNets.
-Both the deep and shallow ConvNets were found to reach at least similar, and in some regard better classification results, as compared with the FBCSP baseline model.
+Both the deep and shallow ConvNets were found to reach at least similar, and in some regard better classification results, as compared with the FBCSP baseline.
 Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, displaying an accuracy of 92.4 \% \cite{schirrmeister2017deep}.
@@
 
-\subsubsection{Real-time component}
-bla bla
+Indeed, when consulting the literature, intermediate fusion strategies are the most prevailing for multimodal deep neural networks.
+When taking such an approach, one is required to design the architecture of these fusion layers.
+\citeA{rastgoo2019automatic} utilize a multimodal ConvNet approach, and fuse the modalities by concatenation followed by two LTSM layers, 2 dense layers and a softmax layer.
+A simpler approach is utilized by	\citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers, ended with a soft-max layer.
+Lastly, \citeA{dolmans2020perceived} used a much more deeper intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.
 
@@
 Between every three sessions, respondents were requested to take a short 2 minute break.
+\bigskip
 \bgroup
@@
 \egroup
+\bigskip
 
@@
 Skin conductivity (GSR) is monitored between two electrodes attached to two fingers \cite{shimmer}.
-Both PPG and GSR are measured on a sample rate of 256 Hz.
+Both PPG and GSR are measured on a sample rate of 256 Hz, i.e.
+256 measured data points per second.
 EEG measurement is conducted with the shimmer 2, equally so on a sampling rate of 256 Hz.
@@
 \subsection{Framework Architecture}
+
+\subsubsection{Universal Framework Architecture}
 The architecture for the proposed framework is constructed by combining insights from the literature whilst keeping in mind the previously delineated design principles (i.e.
 the principles of modularity and generalizability).
-Figure \# visualizes the entire framework \textit{Still has to be made but didnt figure out yet how}.
+No variations based on the general framework architecture will be made, for deviating from the architecture as verified in the literature is likely to be detrimental towards classification accuracy.
 
@@
 The head network consists of Four dense layers, alternated with some batch normalization and max-pooling layers with the objective of stabilization.
-The entire network and its  size, is summarized in table \ref{table:networksummary}.
+A visual representation of the utilized model is depicted as figure \ref{fig:architecture}.
+
+\begin{figure}
+\caption{Framework Architecture}
+\bigskip
+\includegraphics[scale=0.725]{model_architecture}
+\label{fig:architecture}
+\end{figure}
+
+\subsubsection{Model Variations}
+Multi-modular classification in realtime by means of deep-learning requires an optimized network, as was elaborated upon in the introduction.
+Speed is a potential bottleneck for realtime classification with deep learning, especially given the fact the proposed framework architecture is multi-modular, and consequently very complex.
+Different model variations will be investigated upon as a consequence of this.
+The aim is to propose a model that is fast enough for realtime classification, whilst ensuring the maximum amount of accuracy.
+Variations on two different parameters of the previously delineated model will therefore be considered, resulting in four different models.
+
+The first variation reflects the sample rates for each of the included modalities.
+As was elaborated on before, the data collection for each modality was on a sampling rate of 256Hz.
+Naturally, an increase in speed can be attained by feeding less data into the model, i.e.
+decreasing the sampling rate.
+Two out of the four models will consequently model based on a sampling rate of 256Hz, whilst the other two models will model based on sampling rate of 128Hz.
+
+The second variation reflects the amount of utilized filters for convolutional layers, and the amount of neurons for all utilized layers.
+A decrease in the amount of filters / neurons equals a decrease in network size, and consequently an increase in speed.
+Two out of the four models will be the full sized network, whilst the other two models will be halved in size.
+An overview of all four models and their size is provided in table \ref{table:modelvariations}.
 \bigskip
@@
 \centering
-\caption{Network summary	}
-\label{table:networksummary}
-\begin{tabular}{llll}
-EEG        & GSR        & PPG        & Head       \\ \hline
-Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
-Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
-Conv3: 100 & LSTM1: 256 & LSTM1: 256 & Dense: 128 \\
-Conv4: 200 & LSTM1: 256 & LSTM2: 256 &            \\
-Dense: 200 & Dense: 256 & Dense: 256 &            \\ \hline
+\caption{Model variations	}
+\label{table:modelvariations}
+\begin{tabular}{lllll}
+\hline
+                   & EEG        & GSR        & PPG        & Head       \\ \hline
+Model 1: 128Hz \&  & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
+Model 2: 256Hz     & Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
+                   & Conv3: 100 & LSTM1: 256 & LSTM1: 256 & Dense: 178 \\
+                   & Conv4: 200 & LSTM1: 256 & LSTM2: 256 &            \\
+                   \vspace{3ex}
+                   & Dense: 200 & Dense: 256 & Dense: 256 &            \\
+Model 3: 128 Hz \& & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
+Model 4: 256Hz     & Conv2: 25  & Conv2: 64  & Conv2: 64  & Dense: 178 \\
+                   & Conv3: 50  & LSTM1: 128 & LSTM1: 128 & Dense: 89  \\
+                   & Conv4: 100 & LSTM1: 128 & LSTM2: 128 &            \\
+                   & Dense: 100 & Dense: 128 & Dense: 128 &            \\ \hline
 \end{tabular}
@@
 
-{\raggedright \textit{Note that for convolutional layers the number reflects the amount of filters, whereas for all other layers it refers to the amount of nodes.} \par}
+{\raggedright \textit{Note: for convolutional layers the provided number reflects the amount of filters, whereas for all other layers it refers to the amount of nodes.} \par}
 \end{table}

### 2020-12-09 Research Report - Boverhof/Tex report/main.tex

--- 2020-11-30 Research Report - Boverhof/Tex report/main.tex
@@
 \usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage[textwidth=160mm, textheight=210mm, hmarginratio=1:1]{geometry}
 
 %Prerequisite statements
-\captionsetup[table]{skip=4pt} %Line indent after table title
+\DeclareCaptionLabelSeparator*{spaced}{\\[2ex]} %Declare the caption and title seperator spacing
+\captionsetup[table]{,textfont=it,format=plain,justification=justified,
+  singlelinecheck=false,labelsep=spaced,skip=2ex} %Setting up caption for table titles
+ \captionsetup[figure]{,textfont=it,format=plain,justification=justified,
+  singlelinecheck=false,labelsep=spaced,skip=2ex} %Setting up caption for figure titles
 \captionsetup{labelfont={bf}} %Bold label font for tables
 \onehalfspacing %Document line spacing
-\pagestyle{myheadings}
+\pagestyle{myheadings} %Heading style
+\graphicspath{ {./figures/} } %Defining image path
 
@@
 \section{Introduction} \label{Introduction}
-The topic of mental workload (MWL) has received widespread attention across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
-A simple definition of MWL is the demand placed upon humans whilst carrying out a certain task.
+The topic of mental workload has received widespread attention across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
+A commonly utilized definition of mental workload, hereafter referred to as simply workload, is the demand placed upon humans whilst carrying out a certain task.
 As pointed out by de Waard (1996), such a definition is too shallow, for it defines workload solely in external sense.
-It is of importance to acknowledge that MWL is person-specific, for the amount of experienced MWL ushered by a given task may differ across people \cite{de1996measurement}.
-When referring to MWL throughout this research, person-specific MWL is meant specifically.
+It is of importance to acknowledge that workload is person-specific construct, for the amount of experienced workload ushered by a given task may differ across people \cite{de1996measurement}.
+Hence, when referring to workload throughout this research, workload in its person-specific sense is meant.
 
-A commonly employed measure of workload is the NASA-Task Load Index (or TLX) questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}.
-Such measurements are usually conducted post experiment, which could introduce some bias.
+A commonly employed method for assessing workload is the NASA-Task Load Index (or TLX) questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}.
+Such measurements are usually conducted post experiment, which might be unpractical in certain situations.
+For example, consider an experiment with the objective of the assessing workload for pilots during a flight.
+Only well after the flight a measurement in the form of a questionnaire can occur, potentially generating bias.
 An example of such a bias is the observer bias, prescribing that actors participating in an experiment tend to over-exaggerate the treatment effect when having to report it themselves post-experiment \cite{mahtani2018catalogue}.
 
-An alternative method for assessing MWL is by measuring bio-signals during the experiment, and use these to classify the degree of perceived MWL.
-Examples of such bio-signals (hereafter modalities) include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
-When training such classification models, administration of a questionnaire such as the TLX is usually utilized for labeling.
-The advantage of an approach like this is that complementary information streams, each stemming from a different modality can be interpreted simultaneously \cite{ramachandram2017deep}.
-This yields an objective and rich multifaceted classification of a mental construct, such as MWL.
-Additionally, a separate model for each respondent individually can be fitted, catering towards the individual perception of MWL.
-This approach comes however at the cost of an increase in complexity.
-This complexity resides in the construction of a complex framework that inputs the data from the utilized modalities, and outputs a single classification outcome.
+An alternative method for assessing workload is the measurement of bio-signals during the experiment, and use these to classify the degree workload.
+Examples of such bio-signals, hereafter referred to as modalities, include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
+The advantage of this approach is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}.
+This yields an objective and rich multifaceted classification of a mental construct, such as workload.
+Additionally, a separate model for each individual can be trained, catering towards the personal perception of workload for that specific individual.
+This approach comes however at the cost of an increase in complexity, residing in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a single classification outcome.
 
-The current research directly builds upon previous research conducted by Dolmans and colleagues, who proposed a framework for multi-modal deep-learning classification of MWL \cite{dolmans2020perceived}.
-The current research will explore the feasibility of a similar framework, but by utilizing different modalities and data.
-Additionally, the current research will aim to incorporate a real-time component.
-This implies that classification is done whilst the experiment takes place, enabling the possibilities to alter the state of the experiment in real-time.
-Such an approach could enable a wide range of possibilities: consider for example a flight-simulation with the objective of training pilots.
-The possibility for such a simulation to play out dynamically could enhance the learning-experience, namely by catering the state of the simulation towards the the individual, based on a real-time classification of for example their MWL.
+The current research builds upon previous research conducted by \citeA{dolmans2020perceived}, who proposed a framework for multi-modular classification of workload with deep-learning.
+The current research differs from this previous endeavor in that it utilizes different modalities and data, but most importantly because it investigates the feasibility of a real-time approach.
+Real-time in this sense reflects the real-time classification of workload, that is classification whilst the experiment takes place.
+Doing so enables the possibility to alter the state of the experiment whilst it takes place, by responding towards the perceived workload of a participant.
+Such an approach may enable a wide range of possibilities: consider for example a flight simulation with the objective of educating pilots.
+Altering an experiment dynamically after the individual could substantially enhance the learning-experience, namely by anticipating on the perceived workload during a certain segment.
 
-A real-time classification approach will be contrasted with a non-real-time approach.
-Special focus will be placed upon the justification of using a real-time approach, given the increment in complexity such an approach is likely to cause.
-Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, and which can be altered by the researches in real-time.
+In order to build both frameworks, three modalities are included.
+These modalities include the techniques of electroencephalogram hereafter referred to as EEG, galvanic skin response hereafter referred to as GSR and photoplethysmography hereafter referred to as PPG.
+It is important to stress that the objective of the current research is not to gain insight into the most optimal model design for each of the previously delineated modalities.
+It is rather to construct a framework with which real-time classification can be managed, and to which modalities of choice can easily be added.
+Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity.
+Modularity refers the extent to which different modalities can freely be added and/or removed towards the framework, without the necessity to re-architect and rebuild it entirely.
+The second adhered design principle is the principle generalizability, prescribing that the framework should not solely be utilizable in the context of workload, but also for the measurement of other mental constructs.
 
-In order to build both frameworks, three of the (arguably) most widely utilized modalities will be included.
-These modalities include the techniques of electroencephalogram (EEG), galvanic skin response (GSR) and photoplethysmography (PPG).
-It is important to stress that the objective of the current research is not to gain insight into the most optimal model for analyzing data stemming from the previously delineated modalities individually.
-It is rather to build a (real-time) framework researchers can utilize, and to which they can flexibly add modalities conform their own research goals.
-Consequently, one of two design principles on which the architecture of the framework reclines is the concept of modularity.
-Modularity refers the extent to which different modalities can freely be added and/or removed, without the necessity to re-architect and rebuild the entire framework.
-The second adhered design principle is the principle generalizability, prescribing that the framework should not solely be utilizable in the context of MWL, but also for the measurement of other mental constructs.
+A deep-learning approach towards the construction of the real-time multi-modular framework is endeavored.
+Considering the complexity and sheer size of such a deep neural network, an important point of attention is speed.
+In order for real-time classification to be a possible, a swift and thus optimized network is required.
+The problem in real-	time classification with deep learning is often not the accuracy of classification, but rather the speed of classification.
+Deep neural networks easily involve thousands of calculations to be made simultaneously, which is even more true for a multi-modular approach as the current.
+In order for real-time classification to work, these calculations cannot take to long, for if they do the purpose of conducting a real-time approach in general renders redundant.
+The focus of the current research is therefore to architect and optimize a multi-modular deep neural network, which is capable of real-time classification, whilst still ensuring ample accuracy in classification.
+A total of four different network variations, each inhibiting a different degree of complexity, are assessed in their ability to classify in real-time, as well as their performance.
+Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, the state of which can be altered in real-time.
 
-\newpage
 \section{Methods}
@@
 \subsection{Related Work} \label{Relatedwork}
-The current section will provide an overview of previous research on the model design for each seperate modality.
-Additionally,  the most feasible architecture for a multi-modular framework will be explored.
+The current section will provide an overview of previous research on the network architecture for each modality separately.
+Additionally,  the most feasible architecture for the multi-modular framework in is entirety will be explored.
 In particular, attention is placed upon the data fusion, the real-time component and several model optimization techniques.
@@
 \subsubsection{First modality: Electroencephalogram (EEG)}
-The first utilized modality is a technique  called EEG, which detects electrical activity in the brain using electrodes.
-EEG is a widely utilized method for classifying MWL during experiments.
-With a review of the complete literature on EEG classification with deep learning, Craik and colleagues found a total of 16 \% of all available papers to deal with MWL, lending credence to the widely employed phenomenon of EEG for investigating MWL \cite{craik2019deep}.
-Additionally, this review aimed to map the feasibility of using deep neural learning for a range of different EEG application separately.
-Summarizing the findings, Craik and colleagues report that studies mostly found deep belief networks and ConvNets to perform best when aiming to classify MWL, and advice one of these approaches consequently \cite{craik2019deep}.
+The first utilized modality is EEG, which constitutes a technique that detects electrical activity in the brain using electrodes.
+EEG is a widely utilized method for classifying workload.
+An overview of the complete literature on EEG classification with deep learning has been made by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to constitute with workload, lending credence to the ability of EEG as classifier of workload.
+Additionally, the usage of deep learning techniques for a range of different EEG application was investigated upon.
+Summarizing, it was reported that studies mostly found deep belief networks and convolutional neural networks to perform best when classifying workload, and advice one of these approaches as a consequence \cite{craik2019deep}.
 
-Research by \citeA{schirrmeister2017deep} contrasted several differently designed convolutional neural networks (ConvNets) against the baseline method for EEG data (FBCSP) in order to decode imagined or executed tasks.
-The investigated networks included deep, shallow, deep-shallow hybrid and residual ConvNets.
-Both the deep and shallow ConvNets were found to reach at least similar, and in some regard better classification results, as compared with the FBCSP baseline model.
+Research by \citeA{schirrmeister2017deep} contrasted the performance of several convolutional neural networks, hereafter referred to as "ConvNets", against the widely acknowledged baseline method for EEG classification, filter bank common spatial pattern, hereafter referred to as "FBCSP".
+The investigated networks included a deep, a shallow, a deep-shallow hybrid and a residual ConvNet.
+Both the deep and shallow ConvNets were found to reach at least similar, and in some regard better classification results, as compared with the FBCSP baseline.
 Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, displaying an accuracy of 92.4 \% \cite{schirrmeister2017deep}.
-The appropriate design choices were found to be of importance in order to be able to reach this accuracy, including the employment of techniques such as batch normalization, dropout and the usage of the ELU activation function.
 
-A different approach is proposed by \citeA{tabar2016novel}, combining a ConvNet with a Stacked auto-encoder network (SAE).
+A different approach is proposed by \citeA{tabar2016novel}, combining a ConvNet with a Stacked auto-encoder network, hereafter referred to as "SAE".
 Within this network, the input layer feeds into a convolutional layer with the objective of learning the filters and network parameters.
@@
 The second utilized modality is GSR, measuring sweat gland on the hands and hereby inferring arousal.
-GSR readings have been found to significantly increase as a consequence of an increase in task cognitive load, hence constituting to be an objective predictor \cite{shi2007galvanic}.
+GSR readings have been found to significantly increase as a consequence of an increase in task workload, hence constituting to be an objective predictor \cite{shi2007galvanic}.
 
-Sun and colleagues explored the most optimal deep-learning model for classifying six different emotional states by means of GSR data.
-Several models were investigated, amongst others the support vector machine, the ConvNet, the long-short-term-memory (LSTM) model and a hybrid model combining the ConvNet and LSTM approaches.
-The hybrid model was found to perform best, exhibiting an accuracy of 74\%.
-Additionally, data augmentation was found to be able to substantially increase classification results \cite{sun2019hybrid}.
+Sun and colleagues explored the most optimal deep learning network for classifying six different emotional states by means of GSR data.
+Several models were investigated upon, amongst others a support vector machine, a ConvNet, a long-short-term-memory model and a hybrid model combining the ConvNet and long-short-term-memory, herefater referred to as "LSTM", approaches.
+The hybrid model was found to perform best, exhibiting an accuracy of 74\% \cite{sun2019hybrid}.
 
-A variant on the CovNet LSTM model was employed by \citeA{dolmans2020perceived}, who aimed to classify MWL by means of amongst other modalities GSR (equally so as the current research).
+A variant on the CovNet LSTM model was employed by \citeA{dolmans2020perceived}, who aimed to classify workload by means of, amongst other modalities, also GSR.
 The performance of this model was contrasted with a network consisting solely of fully connected dense layers.
-Conform with findings by Sun and colleagues, the hybrid model was found to perform best \cite{dolmans2020perceived}, displaying an accuracy of 82 \%.
-The model architecture as utilized by Dolmans and colleagues deployed 2 convolutional layers, after each of which batch normalization was performed.
-Subsequently, max pooling was performed, after which the network feeds into two LSTM layers, followed by a dense layer.
+Conform with findings by  \citeA{sun2019hybrid}, the hybrid model was found to perform best, displaying an accuracy of 82 \% \cite{dolmans2020perceived}.
+The model architecture as utilized by \citeA{dolmans2020perceived} deployed two convolutional max-pooling blocks and two LSTM layers.
 
@@
 The third modality constitutes PPG, which is a technique utilized to measure heart rate.
-PPG is, not undeservedly, a widely deployed technique within the field of MWL classification.
-Zhang and colleagues investigated several approaches for measuring MWL, amongst three others the technique of PPG.
-Out of these four approaches, PPG was found to display both the highest sensitivity and reliability for measuring MWL, lending credence to the feasibility of PPG as a method for classifying MWL \cite{zhang2018evaluating}.
+PPG is, not undeservedly, a widely deployed technique within the field of workload classification.
+Zhang and colleagues investigated several approaches for measuring workload, comparing in total four modalities, out of which one was PPG.
+PPG was found to display both the highest sensitivity and reliability for measuring workload, lending credence to the feasibility of PPG as a method for classifying workload \cite{zhang2018evaluating}.
 
-Work by Biswas and colleagues investigated a deep learning approach to PPG data, with the objective to perform both bio-metric identification and heart rate information.
+Work by \citeA{biswas2019cornet} investigated upon a deep learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
 Exceptional results were attained with a neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
-This performance was managed with a hybrid model, incorporating two convolutional, followed with two LSTM layers.
-After each of two convolutional layers, batch normalisation and max pooling was applied.
+This performance was managed with a hybrid model, incorporating two convolutional max-pooling blocks, followed with two LSTM layers.
 
-The previously delineated model as proposed by Biswas and colleagues was adopted by Dolmans and colleagues, and subsequently applied towards the MWL case.
-This neural network was contrasted with a network of two fully connected dense layers.
-Batch normalisation and max pooling was performed in both contrasted networks.
-Surprisingly, the more sophisticated network constituting of the convolutional and LSTM layers was found to perform worse in the context of MLW classification, as compared with the simpler model, solely build from two dense layers \cite{dolmans2020perceived}.
+The previously delineated model as proposed by \citeA{biswas2019cornet} was adopted by \citeA{dolmans2020perceived}, and subsequently applied towards the MWL case.
+Batch normalisation and max pooling was performed in both contrasted networks \cite{dolmans2020perceived}.
 
 \subsubsection{Fusion strategy}  
-When architecting a multi-model framework, it is of importance to realize that the information stemming from the different modalities are required to be combined (i.e.
-fused) in order to ultimately result in a single classification.
-Fusion can be done at different time-points within the framework.
-Several fusion strategies as proposed by Ramachandram and colleagues will be considered \cite{ramachandram2017deep}.
+When architecting a multi-modular network, information streams stemming from different modalities are required to be combined, i.e.
+"fused", at one point in the network in order to ultimately result in a single classification.
+Fusion can be done at different locations, and in different ways.
+Several fusion strategies as proposed by \citeA{ramachandram2017deep} will be considered.
 
-Early (or data-level) fusion focuses on how to optimally combine data sources, before being fed into the classification model.
+Early, or data-level, fusion focuses on how to optimally combine data sources, before being fed into the network.
 Techniques that realize this include for example principle component analysis or factor analysis.
-Early fusing is usually challenging, especially in a multimodal scenario such as the current.
-This resides in the fact that data stemming from different modalities differ substantially in terms of dimensionality and sampling rate.
+Early fusing is usually challenging, especially for a multi-modular situation such as the current.
+This resides in the fact that data stemming from different modalities often differ with regards to dimensionality and sampling rate.
 Another disadvantage of early fusing, is that usually the oversimplified assumption of conditional independence is made.
-This assumption is unrealistic, for data stemming from different modalities are expected to be correlated in practice \cite{ramachandram2017deep}.
+This assumption is unrealistic in practice, for data stemming from different modalities are expected to be correlated \cite{ramachandram2017deep}.
 
-Late (or decision level) fusion on the other hand, refers to the process of aggregating the decisions from multiple models, each individually trained on all modalities.
-In case the data sources stemming from the various modalities are either correlated or measured within a deviant dimensionality, late fusion is a much more feasible approach \cite{ramachandram2017deep}.
+Late, or decision level, fusion on the other hand refers to the process of aggregating the decisions from multiple models, each separately applied on each modalitiy separately.
+In case the data sources stemming from the various modalities are either correlated or inhibit a different dimensionality, late fusion is a much more feasible approach \cite{ramachandram2017deep}.
 
-Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modal deep-learning problems.
-Modalities are fused by simply adding a higher order layer, to which the individual deep-learning models separately defined for each modality feed into.
-This need not be a single layer, but could also be multiple layers, as long as each modality ultimately feeds into the highest order output layer.
+Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modal deep learning problems.
+Modalities are fused by concatenation and adding a higher order layer, to which the individual networks, separately defined for each modality, feed into.
+This need not be a single layer, but could be multiple layers, as long as each modality ultimately feeds into the highest order output layer.
 The depth of the fusion (i.e.
-the amount of fusion layers) can be chosen conform the specific situation, posing intermediate fusion to be the most flexible, and therefore the most widely used fusion method \cite{ramachandram2017deep}.
+the amount of fusion layers) can be chosen conform the specific situation, posing intermediate fusion to be the most flexible, and therefore the most widely utilized fusion strategy \cite{ramachandram2017deep}.
 
-\subsubsection{Real-time component}
-bla bla
+Indeed, when consulting the literature, intermediate fusion strategies are the most prevailing for multi-modular deep neural networks.
+When taking such an approach, one is required to consider the design of this higher order network.
+\citeA{rastgoo2019automatic} utilize a multi-modular ConvNet approach, and fuse the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer.
+A simpler approach is utilized by	\citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers, and ending with a soft-max layer.
+Lastly, \citeA{dolmans2020perceived} used a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.
 
@@
 If incorporating a batch normalization layer, it is recommended to do so before feeding into the activation function \cite{ioffe2015batch}.
-An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived},  \citeA{schirrmeister2017deep} by specifying a batch normalization layer after each convolutional layer.
+An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived} and \citeA{schirrmeister2017deep} by specifying a batch normalization layer after each convolutional layer.
 Equally so, the best performing model for PPG data as proposed by \citeA{biswas2019cornet} included a batch normalization layer after each convolutional layer.
@@
 Pooling layers are often used in ConvNets, following a convolutional layer with the attempt to decrease the dimensionality.
-The objective of such layers are to merge similar features into one (for a more extensive elaboration see: \cite{lecun2015deep}).
-Considering the EEG ConvNets, both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer.
-The model proposed for GSR data by \citeA{sun2019hybrid} incorporate a max-pooling layer after each, but one of the convolutional layers.
-Lastly, the model as proposed for PPG data by \cite{biswas2019cornet}  specified a max pooling layer after each convolutional layer.
+The objective of such layers are to merge similar features into one (for a more extensive elaboration see: \citeA{lecun2015deep}).
+Considering the earlier delineated EEG ConvNets, both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer.
+The network as proposed for GSR by \citeA{sun2019hybrid} incorporated a max-pooling layer after each, but one of the convolutional layers.
+Lastly, the network as proposed for PPG by \cite{biswas2019cornet}  specified a max pooling layer after each convolutional layer.
 
-Hyper-parameter optimization (HPO) is a technique that can be used to optimize hyper-parameter including learning rate, dropout probability and momentum.
-The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled \cite{akiba2019optuna}.
+Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be used to optimize hyper-parameter, such as for example learning rate, dropout probability and momentum.
+Substantial advancements within the deep learning community have been attained by utilizing HPO, especially considering the performance of ConvNets \cite{bergstra2012random}.
+The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled, and thus HPO can be performed \cite{akiba2019optuna}.
 
@@
 \subsubsection{Experimental setup}
-The experimental setting for data collection is the spaceship videogame Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}.
+The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}.
 This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente (UT) and carried out in cooperation with Thales group Hengelo.
-The experiment constituted three different segments, during each of which respondents had to carry out different tasks, all aiming to measure workload.
+The experiment constituted three different segments, during each of which the respondent had to carry out different tasks, all of which constructed to entail varying degrees of perceived workload.
 Each segment consists of six small sessions of roughly 5-10 minutes.
 These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment.
-A schematic overview of the experimental structure is depicted as table \ref{table:expsetup}.
-After each of the 18 segments, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires.
+A schematic overview of the experimental structure is delineated as table \ref{table:expsetup}.
+After each of the 18 sessions, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires.
 Each questionnaire inquired upon the degree to which the respondent experienced workload during the previous session.
-These ratings will be used as labels in later training.
+These ratings have been use as labels in later training of the network.
 Within each segment, the order in which the sessions (varying in difficulty) were presented have been randomized.
@@
 \egroup
+\bigskip
 
-The first segment emulated a scenario in which hostile spaceships approach the respondents spaceship.
-The respondent is required to  quickly react, and defuse hostile spaceships in order to survive.
-The increment in difficulty caused the process of defusing hostile spaceships to be more challenging and hereby to take longer,  aiming to increase workload consequently.
+The first segment emulated a scenario in which hostile spaceships approach the respondent's spaceship.
+The respondent is required to  quickly react by defusing hostile spaceships in order to survive.
+The increment in difficulty caused the process of defusing hostile spaceships to be more challenging, and hereby to take longer,  aiming to increase workload as a consequence.
 The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible.
 Obstacles around which the respondent had to carefully navigate were introduced in the intermediate difficult scenario, and hostile spaceships the respondent had to decimate were introduced in the hard scenario.
-Both increase difficulty, and hereby aim to increase workload consequently.
-The third and final segment emulated a machine room, in which respondents had to control the power based on random requests generated by the video-game.
-Variables that could overheat the spaceship  were introduced as a consequence of an increase in difficulty, demanding the respondent multi-task, hereby aiming to increase workload.
+Both increase difficulty, and hereby aim to increase workload as a consequence.
+The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests.
+Variables that could overheat the spaceship  were introduced as a consequence of an increase in difficulty, demanding the respondent to multi-task, hereby aiming to increase workload.
 
@@
 In total, twenty-five respondents are participating in the study.
-Currently, the data is still in the process of being collected, for which no additional descriptive statistics can be presented in the prevailing section.
+Currently, the data is still in the process of being collected, for which no additional descriptive statistics can be presented in the this section as of yet.
 The respondents are students, recruited from the University of Twente.
 Recruitment has been conducted with Sona, which is a cloud-based participant management system.
-Requirements were that respondents didn't have constraints that might interfere with the utilized sensors, such as for example a pacemaker.
-This is assessed by means of a short demographic questionnaire prior to the experiment.
-Additionally, the respondents are made aware of ethical consent prior to the experiment, with the objective to ensure completely voluntary participation.
+Requirements were that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker.
+This was assessed by means of a short demographic questionnaire prior to the experiment.
+Additionally, the respondents were made aware of ethical consent prior to the experiment, with the objective to ensure completely voluntary participation.
 Respondents were able to draw back from the experiment at any time.
 
-\subsubsection{Data collection and Synchronization}
-Data streams stemming from the different modalities are measured on different frequencies, and consequently need to be properly synchronized.
-This is accomplished by means of a technique called Lab-Streaming Layer (LSL), to which different data streams are streamed during the experiment.
-LSL properly synchronizes these data streams, records all data into a single file per participant \cite{kothe2018lab}.
+\subsubsection{Devices and Synchronization}
+The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
+The device is worn on the wrist, and is able to communicate the signal wirelessly.
+An ear-clip was utilized for measuring PPG, and converting this to estimate heart rate.
+Skin conductivity, or GSR, was monitored by two electrodes attached to the fingers \cite{shimmer}.
+Both PPG and GSR were measured on a sample rate of 256 Hz.
+EEG measurement is conducted with the shimmer 2, equally so on a sampling rate of 256 Hz.
+
+Data streams stemming from the different modalities were required to be properly synchronized such that they are parallel.
+This was accomplished by means of an application called Lab-Streaming Layer, hereafter refered to as "LSL", to which the different data are streamed during the experiment.
+LSL properly synchronized these data streams, such that they refer to the same points in time, and subsequently record all data into a single file per participant \cite{kothe2018lab}.
 
 \subsection{Framework Architecture}
-The architecture for the proposed framework is constructed by combining insights from the literature whilst keeping in mind the previously delineated design principles (i.e.
+As was elaborated on in the introduction, several networks will be compared in their ability to classify workload in real-time, and the performance with which this is managed.
+The upcoming section firstly describes the universal architecture that all networks variants have in common.
+Subsequently, the distinctions in each of the four varying networks are delineated.
+
+\subsubsection{Universal Framework Architecture}
+The architecture for the proposed framework is constructed by combining insights from the literature, whilst keeping in mind the previously delineated design principles (i.e.
 the principles of modularity and generalizability).
+No variations based on the general framework architecture will be made, for deviating from the architectures as verified in the literature could be detrimental with regards to classification accuracy.
+A visual representation of the complete network is depicted as figure \ref{fig:architecture}.
 
-The utilized network for the EEG modality is a ConvNet as proposed by \citeA{schirrmeister2017deep}.
-The network is designed to include four convolutional layers, each follow by a max pooling layer of stride $1* 3$.
-Ultimately, these blocks are followed up with a softmax layer in order end up with a classification.
-The Exponential Linear Unit (ELU) function is utilized as activation function, defined as:
+\begin{figure}
+\caption{Full Network Architecture}
+\bigskip
+\includegraphics[scale=0.725]{model_architecture}
+\label{fig:architecture}
+\end{figure}
+
+The utilized network for the EEG modality is a ConvNet, as proposed by \citeA{schirrmeister2017deep}.
+The network is designed to include four convolutional blocks, each constituting a convolutional layer, followed by a batch normalisation layer.
+The Exponential Linear Unit, hereafter referred to as "ELU", function is utilized as activation function, and is defined as equation \ref{eqn:elu}.
+Lastly, each block is closed with a max pooling layer of stride three.
 
 \begin{equation}
-R(x)= 
+\label{eqn:elu}
+f(x)= 
 \begin{Bmatrix}
@@
 
-The utilized network for the GSR modality is a LSTM ConvNet hybrid.
+The utilized network for the GSR modality is a LSTM ConvNet network, inspired by the work of \citeA{sun2019hybrid} and  \citeA{dolmans2020perceived}.
+The network is designed to include two convolutional blocks, each constituting a convolutional layer, followed by a batch normalization layer, an activation layer and closed with a max-pooling layer of stride four.
+The Rectified Linear Unit, hereafter referred to as "ReLU", function is utilized as activation function, defined as equation \ref{eqn:relu}.
+Following these two convolutional blocks are two LTSM layers.
 
+\begin{equation} 
+\label{eqn:relu}
+f(x)=max(0,x)
+\bigskip
+\end{equation}
+
+Lastly, the PPG modality is analyzed by means of the network as proposed by \citeA{biswas2019cornet}.
+The nework opens with two convolutional blocks, each consisting of a convolutional layer, batch normalization layer, activation layer and closed with a max pooling layer of stride four.
+The utilized activation function is the ReLU, depicted as equation \ref{eqn:relu}.
+Following these convolutional blocks are two LTSM layers, equal to the GSR model.
+
+The networks for each of the modalities are finally closed with one fully connected dense layer, before feeding into the head network.
+This is done in order to flatten all inputs into a lower dimensional space, such that concatenation is possible.
+The head network consists of Four dense layers, alternated with some batch normalization and max-pooling layers, with the objective of stabilization.
+
+\subsubsection{Model Variations}
+Multi-modular classification in real-time by means of deep-learning requires an optimized network, as was elaborated upon in the introduction.
+Speed is a potential bottleneck, especially given the proposed network architecture is multi-modular, and substantially  complex.
+Different network variations will be investigated upon as a consequence of this.
+The aim is to propose a network that is fast enough for proper real-time classification, whilst ensuring the maximum amount of accuracy.
+Variations based on two different parameters of the network as depicted in figure \ref{fig:architecture} will therefore be considered, resulting in a total of four variations.
+
+The first parameter constitutes the sampling rate for each of the included modalities.
+As was elaborated on earlier, data collection for each modality was conducted on a sampling rate of 256Hz.
+Naturally, an increase in classification speed can be attained by feeding less data into the network, i.e.
+decreasing the sampling rate.
+Two out of the four networks will consequently be fed data measured on a sampling rate of 256Hz, whilst the other two networks will input based on a sampling rate of 128Hz.
+
+The second parameter reflects the amount of utilized filters for convolutional layers, and the amount of neurons for all utilized layers.
+A decrease in the amount of filters / neurons constitutes a decrease in network size, and consequently an increase in speed.
+Two out of the four models will be the full sized network, whilst the other two models will be halved in size.
+An overview of all four network variations is provided in table \ref{table:modelvariations}.
+
+\bgroup
+\def\arraystretch{1.6}%  
+\begin{table}[h]
+\centering
+\caption{Model variation sizes}
+\label{table:modelvariations}
+\begin{tabular}{lllll}
+\hline
+                   & EEG        & GSR        & PPG        & Head       \\ \hline
+Model 1: 128Hz \&  & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
+Model 2: 256Hz     & Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
+                   & Conv3: 100 & LSTM1: 256 & LSTM1: 256 & Dense: 178 \\
+                   & Conv4: 200 & LSTM1: 256 & LSTM2: 256 &            \\
+                   \vspace{3ex}
+                   & Dense: 200 & Dense: 256 & Dense: 256 &            \\ \hline
+Model 3: 128 Hz \& & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
+Model 4: 256Hz     & Conv2: 25  & Conv2: 64  & Conv2: 64  & Dense: 178 \\
+                   & Conv3: 50  & LSTM1: 128 & LSTM1: 128 & Dense: 89  \\
+                   & Conv4: 100 & LSTM1: 128 & LSTM2: 128 &            \\
+                   & Dense: 100 & Dense: 128 & Dense: 128 &            \\ \hline
+\end{tabular}
+\vspace{2ex}
+
+\begin{doublespacing}
+{\raggedright \textit{Note:} For all convolutional layers the depicted number reflects the amount of utilized filters, whereas for LTSM layers it reflects the amount  of nodes. \par}
+\end{doublespacing}
+\end{table}
+\egroup
+
+\clearpage
 \subsection{Model Evaluation}
-The performance of the real-time framework will be assessed by contrasting it with a regular, non-real-time framework.
-Specifically, the quality of performance for each modality individually will be compared across both frameworks.
-This validation will be endeavored by means of six widely used performance measures, all constructed from the confusion matrix, depicted as table  \ref{table:confusion}
+The performance of the four network variations will be contrasted by means of several performance metrics.
+The utilized metrics constitute six well known and widely applied metrics, all constructed from the confusion matrix, depicted as table \ref{table:confusion}.
+
 \bigskip
@@
 
-The measures accuracy, sensitivity, specificity, PPV, NPV and F1 will be utilized in order to asses model performance.
-The framework that performs best across these measures is considered to be the superior performing framework.
-Table \ref{table:metrics} depicts the constitution of these performance measures by partly referring to confusion matrix depicted as table \ref{table:confusion}.
+The measures accuracy, sensitivity, specificity, PPV, NPV and F1 will be utilized in order to asses network performance.
+The network that performs best across these measures is considered to be the superior performing network.
+Table \ref{table:metrics} depicts the constitution of these performance metrics, by partly referring to confusion matrix depicted as table \ref{table:confusion}.
 \bigskip

### 2020-12-19 Research Report - Boverhof/Tex report/main.tex

@@
 
+%Introduction section
 \section{Introduction} \label{Introduction}
@@
 As pointed out by de Waard (1996), such a definition is too shallow, for it defines workload solely in external sense.
-It is of importance to acknowledge that workload is person-specific construct, for the amount of experienced workload ushered by a given task may differ across people \cite{de1996measurement}.
+It is of importance to acknowledge that workload is a person-specific construct, for the amount of experienced workload ushered by a given task may differ across people \cite{de1996measurement}.
 Hence, when referring to workload throughout this research, workload in its person-specific sense is meant.
@@
 A commonly employed method for assessing workload is the NASA-Task Load Index (or TLX) questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}.
-Such measurements are usually conducted post experiment, which might be unpractical in certain situations.
+Such an assessment is usually conducted post experiment, which in certain situations could be unpractical.
 For example, consider an experiment with the objective of the assessing workload for pilots during a flight.
 Only well after the flight a measurement in the form of a questionnaire can occur, potentially generating bias.
-An example of such a bias is the observer bias, prescribing that actors participating in an experiment tend to over-exaggerate the treatment effect when having to report it themselves post-experiment \cite{mahtani2018catalogue}.
+An example of such a bias is the observer bias, prescribing that actors participating in an experiment tend to over-exaggerate the treatment effect, i.e.
+the degree if perceived workload, when having to report it themselves post-experiment \cite{mahtani2018catalogue}.
 
-An alternative method for assessing workload is the measurement of bio-signals during the experiment, and use these to classify the degree workload.
+An alternative method for assessing workload is the measurement of bio-signals during the experiment, with which the degree workload is being classified.
 Examples of such bio-signals, hereafter referred to as modalities, include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
@@
 The current research builds upon previous research conducted by \citeA{dolmans2020perceived}, who proposed a framework for multi-modular classification of workload with deep-learning.
-The current research differs from this previous endeavor in that it utilizes different modalities and data, but most importantly because it investigates the feasibility of a real-time approach.
-Real-time in this sense reflects the real-time classification of workload, that is classification whilst the experiment takes place.
-Doing so enables the possibility to alter the state of the experiment whilst it takes place, by responding towards the perceived workload of a participant.
-Such an approach may enable a wide range of possibilities: consider for example a flight simulation with the objective of educating pilots.
-Altering an experiment dynamically after the individual could substantially enhance the learning-experience, namely by anticipating on the perceived workload during a certain segment.
+This research differs from this previous endeavor in that it utilizes different modalities and thus different data.
+However most importantly, the current research differs in that it investigates the feasibility of a real-time approach.
+Real-time in this sense considers the real-time classification of workload, that is classification whilst the experiment takes place.
+Doing so enables the possibility conduct a dynamic experiment, the state of which can be altered by responding towards the classified degree of workload for a participant.
+Consider a simulation with the objective of educating its participant, such as a flight simulator with the objective of educating trainee pilots.
+In such a situation, the ability to alter the state of the experiment dynamically, that is based on the amount of perceived workload, could substantially enhance the learning experience of a single session.
+Operations with which the trainee perceives high workload possibly require more practice, which could be dynamically integrated in the remainder of the experiment.
+Doing so has the potential of dramatically increasing the effectiveness of a single simulation session, hereby possibly entailing a more efficient learning process.
 
@@
 These modalities include the techniques of electroencephalogram hereafter referred to as EEG, galvanic skin response hereafter referred to as GSR and photoplethysmography hereafter referred to as PPG.
-It is important to stress that the objective of the current research is not to gain insight into the most optimal model design for each of the previously delineated modalities.
+It is important to stress that the objective of the current research is not to gain insight into the most optimal model design for each of these previously delineated modalities.
 It is rather to construct a framework with which real-time classification can be managed, and to which modalities of choice can easily be added.
 Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity.
-Modularity refers the extent to which different modalities can freely be added and/or removed towards the framework, without the necessity to re-architect and rebuild it entirely.
-The second adhered design principle is the principle generalizability, prescribing that the framework should not solely be utilizable in the context of workload, but also for the measurement of other mental constructs.
+Modularity refers to the extent to which different modalities can freely be added and/or removed to the framework, without the necessity to re-architect and rebuild it entirely.
+The second adhered design principle is the principle of generalizability, prescribing that the framework should not solely be utilizable in the context of workload, but also for the measurement of other mental constructs.
 
 A deep-learning approach towards the construction of the real-time multi-modular framework is endeavored.
-Considering the complexity and sheer size of such a deep neural network, an important point of attention is speed.
-In order for real-time classification to be a possible, a swift and thus optimized network is required.
-The problem in real-	time classification with deep learning is often not the accuracy of classification, but rather the speed of classification.
-Deep neural networks easily involve thousands of calculations to be made simultaneously, which is even more true for a multi-modular approach as the current.
-In order for real-time classification to work, these calculations cannot take to long, for if they do the purpose of conducting a real-time approach in general renders redundant.
-The focus of the current research is therefore to architect and optimize a multi-modular deep neural network, which is capable of real-time classification, whilst still ensuring ample accuracy in classification.
-A total of four different network variations, each inhibiting a different degree of complexity, are assessed in their ability to classify in real-time, as well as their performance.
-Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, the state of which can be altered in real-time.
+Considering the complexity and sheer size of such a network, an important point of attention is speed.
+In order for real-time classification to be possible, a swiftly classifying and hence optimized network is requisited.
+The challenge in real-time classification with deep-learning is often not reaching adequate performance, but rather to attain adequate speed of classification.
+Deep neural networks easily constitute thousands of calculations made simultaneously, which is even more so for a multi-modular approach.
+In order for real-time classification to work, classification cannot take too long, for if it does it is not real-time anymore.
+Firstly, for each of the three modalities a single-modular network is constructed and assessed in terms of speed and performance.
+Secondly, a multi-modular network is architected, and also assessed in terms of speed and performance.
+Additionally, several variations to this multi-modular framework are considered.
+These variations differ in their size, e.g.
+the amount of neurons and filters.
+The objective of the current research is to explore the circumstances in which a multi-modular approach by means of deep learning is capable of real-time classification, whilst still ensuring ample performance with respect to classification accuracy.
+Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, of which the state can be altered in real-time.
 
@@
 \subsection{Related Work} \label{Relatedwork}
-The current section will provide an overview of previous research on the network architecture for each modality separately.
-Additionally,  the most feasible architecture for the multi-modular framework in is entirety will be explored.
-In particular, attention is placed upon the data fusion, the real-time component and several model optimization techniques.
+The current section will provide an overview of previous research on the most optimal network architecture for each modality separately.
+Additionally,  the most feasible architecture for the multi-modular framework in its entirety will be explored.
+In particular, attention is placed upon the data fusion strategy, the real-time component and several model optimization techniques.
 
@@
 The second utilized modality is GSR, measuring sweat gland on the hands and hereby inferring arousal.
-GSR readings have been found to significantly increase as a consequence of an increase in task workload, hence constituting to be an objective predictor \cite{shi2007galvanic}.
+GSR activity have been found to significantly increase as a consequence of an increase in task workload, hence constituting to be an objective predictor \cite{shi2007galvanic}.
 
@@
 
-The previously delineated model as proposed by \citeA{biswas2019cornet} was adopted by \citeA{dolmans2020perceived}, and subsequently applied towards the MWL case.
-Batch normalisation and max pooling was performed in both contrasted networks \cite{dolmans2020perceived}.
-
 \subsubsection{Fusion strategy}  
@@
 Fusion can be done at different locations, and in different ways.
-Several fusion strategies as proposed by \citeA{ramachandram2017deep} will be considered.
+Several fusion strategies as proposed by \citeA{ramachandram2017deep} have been considered.
 
@@
 Late, or decision level, fusion on the other hand refers to the process of aggregating the decisions from multiple models, each separately applied on each modalitiy separately.
-In case the data sources stemming from the various modalities are either correlated or inhibit a different dimensionality, late fusion is a much more feasible approach \cite{ramachandram2017deep}.
+In case the data sources stemming from the various modalities are either correlated or ultimately inhibit a different dimensionality, late fusion is a much more feasible approach \cite{ramachandram2017deep}.
 
@@
 The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}.
-This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente (UT) and carried out in cooperation with Thales group Hengelo.
+This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
 The experiment constituted three different segments, during each of which the respondent had to carry out different tasks, all of which constructed to entail varying degrees of perceived workload.
@@
 The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests.
-Variables that could overheat the spaceship  were introduced as a consequence of an increase in difficulty, demanding the respondent to multi-task, hereby aiming to increase workload.
+Variables that could overheat the spaceship were introduced, demanding the respondent to multi-task, hence increasing difficulty.
 
@@
 This was assessed by means of a short demographic questionnaire prior to the experiment.
-Additionally, the respondents were made aware of ethical consent prior to the experiment, with the objective to ensure completely voluntary participation.
+Additionally, the respondents were made aware of informed consent prior to the experiment, with the objective to ensure completely voluntary participation.
 Respondents were able to draw back from the experiment at any time.
@@
 
-\subsubsection{Universal Framework Architecture}
-The architecture for the proposed framework is constructed by combining insights from the literature, whilst keeping in mind the previously delineated design principles (i.e.
-the principles of modularity and generalizability).
-No variations based on the general framework architecture will be made, for deviating from the architectures as verified in the literature could be detrimental with regards to classification accuracy.
-A visual representation of the complete network is depicted as figure \ref{fig:architecture}.
+\subsubsection{Single-modular Network Architectures}
+The architecture of each of the single-modular networks is determined by combining insights from the literature.
+Each network utilizes only a single modality.
+No variations from this network architecture will be made, for deviating from the architectures as verified in the literature could be detrimental with regards to performance.
+These separate networks are all depicted as figure \ref{fig:singlearchitecture}.
 
 \begin{figure}
-\caption{Full Network Architecture}
+\caption{Three Single-modular Network Architectures}
 \bigskip
-\includegraphics[scale=0.725]{model_architecture}
-\label{fig:architecture}
+\includegraphics[scale=0.725]{single_model_architecture}
+\label{fig:singlearchitecture}
 \end{figure}
@@
 
-The networks for each of the modalities are finally closed with one fully connected dense layer, before feeding into the head network.
+\subsubsection{Multi-modular Network Architecture}
+The architecture for multi-modular approach is constructed by combining the single-modular networks as derived from the literature, whilst keeping in mind the previously delineated design principles (i.e.
+the principles of modularity and generalizability).
+A visual representation of the complete network is depicted as figure \ref{fig:multiarchitecture}.
+
+\begin{figure}
+\caption{Multi-modular Network Architecture}
+\bigskip
+\includegraphics[scale=0.725]{multi_model_architecture}
+\label{fig:multiarchitecture}
+\end{figure}
+
+In order to combine the previously delineated single-modular networks, each of these distinct parts are closed with one fully connected dense layer before feeding into the head network.
 This is done in order to flatten all inputs into a lower dimensional space, such that concatenation is possible.
-The head network consists of Four dense layers, alternated with some batch normalization and max-pooling layers, with the objective of stabilization.
+The head network consists of Four dense layers, alternated with a batch normalization and max-pooling layers, with the objective of stabilization.
 
-\subsubsection{Model Variations}
+\subsubsection{Multi-modular Network Variations}
 Multi-modular classification in real-time by means of deep-learning requires an optimized network, as was elaborated upon in the introduction.
-Speed is a potential bottleneck, especially given the proposed network architecture is multi-modular, and substantially  complex.
-Different network variations will be investigated upon as a consequence of this.
-The aim is to propose a network that is fast enough for proper real-time classification, whilst ensuring the maximum amount of accuracy.
-Variations based on two different parameters of the network as depicted in figure \ref{fig:architecture} will therefore be considered, resulting in a total of four variations.
+Speed is a potential bottleneck, especially given the proposed network architecture is multi-modular, and thus substantially complex.
+Consequently, different variations of the delineated network will be investigated upon.
+The aim is to propose a network that is fast enough for real-time classification, whilst ensuring the maximum amount of accuracy.
+Three different variations with regards to size of the network as depicted in figure \ref{fig:multiarchitecture} will therefore be considered.
 
-The first parameter constitutes the sampling rate for each of the included modalities.
-As was elaborated on earlier, data collection for each modality was conducted on a sampling rate of 256Hz.
-Naturally, an increase in classification speed can be attained by feeding less data into the network, i.e.
-decreasing the sampling rate.
-Two out of the four networks will consequently be fed data measured on a sampling rate of 256Hz, whilst the other two networks will input based on a sampling rate of 128Hz.
-
-The second parameter reflects the amount of utilized filters for convolutional layers, and the amount of neurons for all utilized layers.
-A decrease in the amount of filters / neurons constitutes a decrease in network size, and consequently an increase in speed.
-Two out of the four models will be the full sized network, whilst the other two models will be halved in size.
-An overview of all four network variations is provided in table \ref{table:modelvariations}.
+Network size constitutes the amount of utilized filters for convolutional layers, and the amount of neurons for all other utilized layers.
+A decrease in the amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of calculations.
+This is likely to bring about an increase in speed.
+An overview of all three multi-modular network variations, and the amount of utilized neurons/filters is provided in table \ref{table:modelvariations}.
+Network 1 is referred to as the full network, and is the biggest in terms of size.
+The size of network 2 constitutes of 75 \% of the size of the full network.
+Network 3 constitutes of 50 \% of the size of the full network.
 
@@
         & EEG        & GSR        & PPG        & Head       \\ \hline
-Model 1: 128Hz \&  & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
-Model 2: 256Hz     & Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
+Model 1 & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
+        & Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
         & Conv3: 100 & LSTM1: 256 & LSTM1: 256 & Dense: 178 \\
@@
         & Dense: 200 & Dense: 256 & Dense: 256 &            \\ \hline
-Model 3: 128 Hz \& & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
-Model 4: 256Hz     & Conv2: 25  & Conv2: 64  & Conv2: 64  & Dense: 178 \\
+Model 2 & Conv1: 18  & Conv1: 96  & Conv1: 96  & Dense: 534 \\
+        & Conv2: 34  & Conv2: 96  & Conv2: 96  & Dense: 267 \\
+        & Conv3: 75  & LSTM1: 192 & LSTM1: 192 & Dense: 134 \\
+        & Conv4: 150 & LSTM1: 192 & LSTM1: 192 &            \\
+        \vspace{3ex}
+        & Dense: 150 & Dense: 192 & Dense: 192 &            \\ \hline
+Model 3 & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
+        & Conv2: 25  & Conv2: 64  & Conv2: 64  & Dense: 178 \\
         & Conv3: 50  & LSTM1: 128 & LSTM1: 128 & Dense: 89  \\

### 2020-12-27 Research Report - Boverhof/Tex report/main.tex

@@
 Skin conductivity, or GSR, was monitored by two electrodes attached to the fingers \cite{shimmer}.
-Both PPG and GSR were measured on a sample rate of 256 Hz.
-EEG measurement is conducted with the shimmer 2, equally so on a sampling rate of 256 Hz.
+EEG measurement is conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}.
+The Shimmer3 GSR+ is able to read and output data signals on a sampling rate of 256 Hz, whereas the Muse 2 is able to sample at 220 Hz.
+
+As was already touched upon in the introduction, real-time classification requires a swift network.
+A higher sampling rate entails more data traveling through the network, decelerating classification speed.
+As a consequence, it is beneficial to input data on the minimum required sampling rate with which the key features can be detected for each modality separately.
+\citeA{fujita2019evaluation} investigated the minimum required sampling rate for the PPG modality.
+The extent to which features were detected have been contrasted for several sampling rates.
+A sampling rate of 60 Hz was found to be the absolute minimum required sampling rate for extracting features stably \cite{fujita2019evaluation}.
+A slightly higher sampling rate might be the safer option, however.
+\citeA{shimmer} recommend a sampling rate of 100 Hz for the PPG modality, and stable feature extraction was observed on this rate by \citeA{fujita2019evaluation} as well.
+Hence, a sampling rate of 100 Hz is utilized for the PPG modality.
+The recommended sampling rate for GSR data is determined to range between 0.03 and 5 Hz \cite{shimmer}.
+A sampling rate of 5 Hz will be utilized consequently.
+For the EEG modality, different features require a widely different sampling rate in order to be detected.
+Frequency bands for traditional EEG features are defined on about 0.5-4 Hz for delta, and at most on about 16-24 Hz for beta.
+The gamma frequency band recently gained in popularity within the field of EEG, and is defined on a frequency ranging up to 80 Hz \cite{weiergraeber2016sampling}.
+In order to detect a feature residing on the 80 Hz frequency band, a substantially higher sampling rate is required to record the signal without aliasing.
+The required sampling rate can be determined by means of the Nyquist criterion for practical EEG sampling, defined as equation \ref{eqn:nyquist}.
+
+\begin{equation}
+\label{eqn:nyquist}
+f_{samp} > 2.5 * f_{max}
+\end{equation}
+where $f_{sam}$ reflects the required sampling rate and $f_{max}$ reflects the frequency range of a particular modality \cite{srinivasan1998estimating}.
+Hence, in order to be able to detect the gamma frequency band, a sampling rate of 200 is utilized for the EEG modality.
+A summary of the utilized sampling rates per modality is depicted as table \ref{table:samplingrate}.
+
+\bgroup
+\def\arraystretch{1.6}%  
+\begin{table}[h]
+\centering
+\caption{Sampling rate per modality}
+\label{table:samplingrate}
+\begin{tabular}{ll}
+    & Utilized sampling rate (Hz) \\ \hline
+ Electroencephalogram (EEG) & 200                         \\
+Galvanic Skin Response (GSR) & 5                           \\
+Photoplethysmography (PPG) & 100                         \\ \hline
+\end{tabular}
+\end{table}
+\egroup
 
@@
 As was elaborated on in the introduction, several networks will be compared in their ability to classify workload in real-time, and the performance with which this is managed.
-The upcoming section firstly describes the universal architecture that all networks variants have in common.
-Subsequently, the distinctions in each of the four varying networks are delineated.
+The upcoming section opens with the description of the network architectures solely utilizing one of the three modalities each.
+Subsequently, the multi-modular architecture will be elaborated on.
+Lastly, several variations based on this multi-modular architecture are delineated.
 
@@
 The architecture of each of the single-modular networks is determined by combining insights from the literature.
-Each network utilizes only a single modality.
-No variations from this network architecture will be made, for deviating from the architectures as verified in the literature could be detrimental with regards to performance.
-These separate networks are all depicted as figure \ref{fig:singlearchitecture}.
+Each of the three network merely utilizes a single modality with which workload is classified.
+These networks and their architecture are all depicted as figure \ref{fig:singlearchitecture}.
 
 \begin{figure}
-\caption{Three Single-modular Network Architectures}
+\caption{The Three Single-modular Network Architectures}
 \bigskip
@@
 The Exponential Linear Unit, hereafter referred to as "ELU", function is utilized as activation function, and is defined as equation \ref{eqn:elu}.
-Lastly, each block is closed with a max pooling layer of stride three.
+Each convolutional block is closed with a max pooling layer of stride three.
 
@@
 
-Lastly, the PPG modality is analyzed by means of the network as proposed by \citeA{biswas2019cornet}.
+Lastly, the utilized network for the PPG modality is inspired upon the network as proposed by \citeA{biswas2019cornet}.
 The nework opens with two convolutional blocks, each consisting of a convolutional layer, batch normalization layer, activation layer and closed with a max pooling layer of stride four.
@@
 
-\subsubsection{Multi-modular Network Architecture}
-The architecture for multi-modular approach is constructed by combining the single-modular networks as derived from the literature, whilst keeping in mind the previously delineated design principles (i.e.
-the principles of modularity and generalizability).
-A visual representation of the complete network is depicted as figure \ref{fig:multiarchitecture}.
+\subsubsection{Multi-modular Network: Architecture}
+The network architecture that is utilized for the multi-modular approach is determined by a combination of the single-modular networks, as derived from the literature.
+The previously delineated design principles (i.e.
+the principles of modularity and generalizability) are taken into account when doing so.
+A visual representation of the multi-modular network is depicted as figure \ref{fig:multiarchitecture}.
 
@@
 This is done in order to flatten all inputs into a lower dimensional space, such that concatenation is possible.
-The head network consists of Four dense layers, alternated with a batch normalization and max-pooling layers, with the objective of stabilization.
+The head network consists of four dense layers.
+These layers are alternated with a batch normalization and max-pooling layer with the objective of stabilization.
 
-\subsubsection{Multi-modular Network Variations}
+\subsubsection{Multi-modular Network: Variations}
 Multi-modular classification in real-time by means of deep-learning requires an optimized network, as was elaborated upon in the introduction.
-Speed is a potential bottleneck, especially given the proposed network architecture is multi-modular, and thus substantially complex.
-Consequently, different variations of the delineated network will be investigated upon.
-The aim is to propose a network that is fast enough for real-time classification, whilst ensuring the maximum amount of accuracy.
+Speed is a potential bottleneck, for a multi-modular network such as presented is substantially complex in nature.
+Therefore, several variations of the delineated network will be investigated upon, differing in their complexity.
+These variations are not made by changing the network architecture, whereas deviating from the proven network architecure is likely to be detrimental with regards to model performance.
+The aim is to propose a network that is fast enough for real-time classification, whilst maintaining the highest amount of accuracy as possible.
 Three different variations with regards to size of the network as depicted in figure \ref{fig:multiarchitecture} will therefore be considered.
 
-Network size constitutes the amount of utilized filters for convolutional layers, and the amount of neurons for all other utilized layers.
-A decrease in the amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of calculations.
+Network size is understood as the amount of utilized filters for convolutional layers, and the amount of neurons for all other utilized layers.
+A decrease in the amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of required calculations.
 This is likely to bring about an increase in speed.
@@
         & EEG        & GSR        & PPG        & Head       \\ \hline
-Model 1 & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
+Network 1 & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
         & Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
@@
         & Dense: 200 & Dense: 256 & Dense: 256 &            \\ \hline
-Model 2 & Conv1: 18  & Conv1: 96  & Conv1: 96  & Dense: 534 \\
+Network 2 & Conv1: 18  & Conv1: 96  & Conv1: 96  & Dense: 534 \\
         & Conv2: 34  & Conv2: 96  & Conv2: 96  & Dense: 267 \\
@@
         & Dense: 150 & Dense: 192 & Dense: 192 &            \\ \hline
-Model 3 & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
+Network 3 & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
         & Conv2: 25  & Conv2: 64  & Conv2: 64  & Dense: 178 \\

### 2020-12-30 Research Report - Boverhof/Tex report/main.tex

@@
 These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment.
-A schematic overview of the experimental structure is delineated as table \ref{table:expsetup}.
+A schematic overview of the experimental structure is depicted as figure \ref{fig:experimental}.
 After each of the 18 sessions, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires.
@@
 Between every three sessions, respondents were requested to take a short 2 minute break.
+
+\begin{figure}
+\caption{Experimental setup}
 \bigskip
-\bgroup
-\def\arraystretch{1.6}%  
-\begin{table}[h]
-\centering
-\caption{Experimental setup: Number of sessions per segment and difficulty setting}
-\label{table:expsetup}
-\begin{tabular}{llll}
-                               & Easy                   & Intermediate           & Hard                   \\ \cline{2-4} 
-\multicolumn{1}{l|}{Segment 1} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
-\multicolumn{1}{l|}{Segment 2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
-\multicolumn{1}{l|}{Segment 3} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} & \multicolumn{1}{l|}{2} \\ \cline{2-4} 
-\end{tabular}
-\end{table}
-\egroup
-\bigskip
+\includegraphics[scale=0.4]{experimental_setup}
+\label{fig:experimental}
+\end{figure}
 
@@
 
-\subsubsection{Devices and Synchronization}
+\subsubsection{Devices and Sampling Rate}
 The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
@@
 EEG measurement is conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}.
-The Shimmer3 GSR+ is able to read and output data signals on a sampling rate of 256 Hz, whereas the Muse 2 is able to sample at 220 Hz.
+The Shimmer3 GSR+ is able to read and output data signals on a sampling rate of 256 Hz, whereas the Muse 2 is able to sample at a maximum of 220 Hz.
 
@@
 A higher sampling rate entails more data traveling through the network, decelerating classification speed.
-As a consequence, it is beneficial to input data on the minimum required sampling rate with which the key features can be detected for each modality separately.
+As a consequence, it is beneficial to input data on the minimum required sampling rate with which the key features can be detected for each modality in a consistent manner.
 \citeA{fujita2019evaluation} investigated the minimum required sampling rate for the PPG modality.
 The extent to which features were detected have been contrasted for several sampling rates.
-A sampling rate of 60 Hz was found to be the absolute minimum required sampling rate for extracting features stably \cite{fujita2019evaluation}.
+A sampling rate of 60 Hz was found to be the absolute minimum required sampling rate for extracting all commonly utilized features stably \cite{fujita2019evaluation}.
 A slightly higher sampling rate might be the safer option, however.
-\citeA{shimmer} recommend a sampling rate of 100 Hz for the PPG modality, and stable feature extraction was observed on this rate by \citeA{fujita2019evaluation} as well.
+\citeA{shimmer} recommend a sampling rate of 100 Hz for the PPG modality, and stable feature extraction was naturally observed on this rate by \citeA{fujita2019evaluation} as well.
 Hence, a sampling rate of 100 Hz is utilized for the PPG modality.
-The recommended sampling rate for GSR data is determined to range between 0.03 and 5 Hz \cite{shimmer}.
+The required sampling rate for the GSR modality is substantially lower as compared with both PPG and EEG.
+Shimmer recommended the necessary sampling rate to range between 0.03 and 5 Hz \cite{shimmer}.
 A sampling rate of 5 Hz will be utilized consequently.
@@
 In order to detect a feature residing on the 80 Hz frequency band, a substantially higher sampling rate is required to record the signal without aliasing.
-The required sampling rate can be determined by means of the Nyquist criterion for practical EEG sampling, defined as equation \ref{eqn:nyquist}.
+The required sampling rate can be determined by means of the Nyquist criterion for practical EEG sampling, defined as equation \ref{eqn:nyquist},
 
@@
 \end{equation}
-where $f_{sam}$ reflects the required sampling rate and $f_{max}$ reflects the frequency range of a particular modality \cite{srinivasan1998estimating}.
+where $f_{sam}$ reflects the required sampling rate and $f_{max}$ reflects the frequency range around which the feature to be detected resides\cite{srinivasan1998estimating}.
 Hence, in order to be able to detect the gamma frequency band, a sampling rate of 200 is utilized for the EEG modality.
@@
 
+\subsubsection{Synchronization}
 Data streams stemming from the different modalities were required to be properly synchronized such that they are parallel.
@@
 \begin{figure}
-\caption{The Three Single-modular Network Architectures}
+\caption{Three single-modular network architectures}
 \bigskip

### 2021-01-01 Research Report - Boverhof/Tex report/main.tex

@@
 {\textbf{Date}}\\
-October 14, 2020\\
+January 11, 2020\\
 \vspace*{1\baselineskip}
@@
 \section{Introduction} \label{Introduction}
-The topic of mental workload has received widespread attention across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
-A commonly utilized definition of mental workload, hereafter referred to as simply workload, is the demand placed upon humans whilst carrying out a certain task.
-As pointed out by de Waard (1996), such a definition is too shallow, for it defines workload solely in external sense.
-It is of importance to acknowledge that workload is a person-specific construct, for the amount of experienced workload ushered by a given task may differ across people \cite{de1996measurement}.
-Hence, when referring to workload throughout this research, workload in its person-specific sense is meant.
+The topic of mental workload is a widely studied 
+phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
+A commonly utilized definition for mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst they carry out a particular task.
+As pointed out by \citeA{de1996measurement}, the aforementioned definition is too simplistic, for it defines workload solely as an external phenomenon.
+Workload is, however, a person-specific construct, for the amount of perceived workload ushered by a given task may differ across individuals \cite{de1996measurement}.
+Hence, when referring to workload throughout this research, person-specific workload is implied specifically.
 
-A commonly employed method for assessing workload is the NASA-Task Load Index (or TLX) questionnaire, operationalizing workload in clusters of six different dimensions \cite{hart2006nasa}.
-Such an assessment is usually conducted post experiment, which in certain situations could be unpractical.
-For example, consider an experiment with the objective of the assessing workload for pilots during a flight.
-Only well after the flight a measurement in the form of a questionnaire can occur, potentially generating bias.
-An example of such a bias is the observer bias, prescribing that actors participating in an experiment tend to over-exaggerate the treatment effect, i.e.
-the degree if perceived workload, when having to report it themselves post-experiment \cite{mahtani2018catalogue}.
+A commonly employed method for assessing workload is the well established NASA-Task Load Index questionnaire.
+This questionnaire inquires the respondent on the amount of perceived workload, and is constructed from six subjective sub-scales \cite{hart2006nasa}.
+Such an assessment is usually conducted post-experiment, which can in certain situations be deemed undesirable.
+Consider an experiment in which is aimed to assess workload of a pilot in flight.
+An evident approach towards such an experiment is that we wish to measure the degree of perceived workload during different phases of the flight.
+However, only after the simulation is concluded, a measurement in the form of a questionnaire can be administrated.
+In such a situation, utilizing a post-experiment assessment is prone to generate bias.
+A widely recognized bias is the observer-bias, advocating that participants in an experiment tend to overexaggerate the treatment effect when having to report it post-experiment \cite{mahtani2018catalogue}.
+In the light of the aforementioned example, pilots are expected to overexaggerate the degree of perceived workload when having to report it post-experiment.
 
-An alternative method for assessing workload is the measurement of bio-signals during the experiment, with which the degree workload is being classified.
-Examples of such bio-signals, hereafter referred to as modalities, include techniques such as electroencephalogram, eye tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
-The advantage of this approach is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}.
-This yields an objective and rich multifaceted classification of a mental construct, such as workload.
-Additionally, a separate model for each individual can be trained, catering towards the personal perception of workload for that specific individual.
-This approach comes however at the cost of an increase in complexity, residing in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a single classification outcome.
+An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these to classify workload.
+Examples of such bio-signals, hereafter referred to as "modalities", include techniques as electroencephalogram, eye-tracking, galvanic skin response, functional near-infrared spectroscopy etc.
+The advantage of such an approach is that complementary information streams, each stemming from a different modality, may all be interpreted simultaneously \cite{ramachandram2017deep}.
+This has the potential of yielding a rich and multifaceted classification of construct such as workload.
+Additionally, it is possible to train a separate model for each individual, catering towards the individual perception of workload for that specific person.
+This approach, however, comes at the cost of an increase in complexity.
+This resides in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a single classification outcome.
 
-The current research builds upon previous research conducted by \citeA{dolmans2020perceived}, who proposed a framework for multi-modular classification of workload with deep-learning.
-This research differs from this previous endeavor in that it utilizes different modalities and thus different data.
-However most importantly, the current research differs in that it investigates the feasibility of a real-time approach.
-Real-time in this sense considers the real-time classification of workload, that is classification whilst the experiment takes place.
-Doing so enables the possibility conduct a dynamic experiment, the state of which can be altered by responding towards the classified degree of workload for a participant.
-Consider a simulation with the objective of educating its participant, such as a flight simulator with the objective of educating trainee pilots.
-In such a situation, the ability to alter the state of the experiment dynamically, that is based on the amount of perceived workload, could substantially enhance the learning experience of a single session.
-Operations with which the trainee perceives high workload possibly require more practice, which could be dynamically integrated in the remainder of the experiment.
-Doing so has the potential of dramatically increasing the effectiveness of a single simulation session, hereby possibly entailing a more efficient learning process.
+The current research builds upon research conducted by \citeA{dolmans2020perceived}, who proposed a deep-learning approach to multi-modular classification of workload.
+The current research differs from this previous endeavor in that it utilizes different modalities, and hence different data.
+In addition, the current research investigates upon the feasibility of a real-time approach.
+Real-time in this sense reflects the real-time classification of workload, i.e.
+the classification of workload whilst the experiment takes place.
+Doing so enables the possibility to conduct a dynamic experiment, the state of which can be altered by responding towards the classified degree of workload at a certain moment in time.
+Consider a simulation with the objective of educating its participant, such as a surgical simulation for educating surgeons-in-training.
+The learning experience of a single session could be dramatically enhanced when the state of the experiment is catered towards the individual learning process dynamically.
+For example, in case it is recognized early on in the simulation that a surgeon-in-training has difficulty with a specific procedure, the remainder of the experiment can be catered towards focusing on this specific procedure.
+By enhancing the learning experience in this way, the effectiveness of a single simulation session can be improved dramatically, entailing a more efficient learning process.
 
-In order to build both frameworks, three modalities are included.
-These modalities include the techniques of electroencephalogram hereafter referred to as EEG, galvanic skin response hereafter referred to as GSR and photoplethysmography hereafter referred to as PPG.
-It is important to stress that the objective of the current research is not to gain insight into the most optimal model design for each of these previously delineated modalities.
-It is rather to construct a framework with which real-time classification can be managed, and to which modalities of choice can easily be added.
+Three different modalities are utilized in the current research.
+Firstly the technique of electroencephalogram, hereafter referred to as "EEG", secondly the technique of galvanic skin response, hereafter referred to as "GSR" and thirdly the technique photoplethysmography, hereafter referred to as "PPG".
+It is of importance to recognize that the objective of the current research is not to gain insight into the most optimal model design for each of the previously delineated modalities.
+The objective is rather to construct a framework with which real-time classification can be managed, and to which modalities of choice can easily be added in future research endeavors.
 Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity.
 Modularity refers to the extent to which different modalities can freely be added and/or removed to the framework, without the necessity to re-architect and rebuild it entirely.
-The second adhered design principle is the principle of generalizability, prescribing that the framework should not solely be utilizable in the context of workload, but also for the measurement of other mental constructs.
+The second design principle is the principle of generalizability, prescribing that the framework should not merely be utilizable in the context of workload, but also for the measurement of other mental constructs.
 
-A deep-learning approach towards the construction of the real-time multi-modular framework is endeavored.
-Considering the complexity and sheer size of such a network, an important point of attention is speed.
-In order for real-time classification to be possible, a swiftly classifying and hence optimized network is requisited.
+A deep-learning approach towards the construction of a real-time multi-modular framework is realized.
+Considering the complexity and sheer size of such a deep-neural network, an important point of attention is classification speed.
 The challenge in real-time classification with deep-learning is often not reaching adequate performance, but rather to attain adequate speed of classification.
-Deep neural networks easily constitute thousands of calculations made simultaneously, which is even more so for a multi-modular approach.
-In order for real-time classification to work, classification cannot take too long, for if it does it is not real-time anymore.
-Firstly, for each of the three modalities a single-modular network is constructed and assessed in terms of speed and performance.
-Secondly, a multi-modular network is architected, and also assessed in terms of speed and performance.
-Additionally, several variations to this multi-modular framework are considered.
-These variations differ in their size, e.g.
+Deep neural networks easily constitute thousands of calculations to be made simultaneously, which is even more true for a multi-modular approach such as the current.
+In order for real-time classification to work, classification cannot take too long, for otherwise it is not real-time anymore and the previously delineated benefit of a real-time approach dissipates.
+As a consequence, multiple networks are considered and contrasted in terms of performance and ability to classify in real-time.
+Firstly, for each of the three modalities separately, a single-modular network is constructed.
+Secondly, a multi-modular network is architected.
+Additionally, several variations to this multi-modular framework are considered and contrasted.
+These variations are specified to differ in size, i.e.
 the amount of neurons and filters.
-The objective of the current research is to explore the circumstances in which a multi-modular approach by means of deep learning is capable of real-time classification, whilst still ensuring ample performance with respect to classification accuracy.
-Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, of which the state can be altered in real-time.
+
+The objective of the current research is to explore the circumstances in which a multi-modular approach by means of deep learning is capable of real-time classification, whilst still ensuring ample and adequate performance.
+Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, and of which the state can be altered in real-time.
 

### 2021-01-03 Research Report - Boverhof/Tex report/main.tex

@@
 %Introduction section
-\section{Introduction} \label{Introduction}
+\section{Introduction}
 The topic of mental workload is a widely studied 
@@
 
+%Method section
 \section{Methods}
 
-\subsection{Related Work} \label{Relatedwork}
-The current section will provide an overview of previous research on the most optimal network architecture for each modality separately.
-Additionally,  the most feasible architecture for the multi-modular framework in its entirety will be explored.
-In particular, attention is placed upon the data fusion strategy, the real-time component and several model optimization techniques.
+\subsection{Related Work} 
+The following section will provide an overview of preceding research on the most optimal network architecture for each single-modular network.
+Subsequently, the most feasible architecture for the multi-modular framework in its entirety will be explored, with particular attention on the data fusion strategy and a range model optimization techniques.
 
-\subsubsection{First modality: Electroencephalogram (EEG)}
+\subsubsection{Electroencephalogram (EEG)}
 The first utilized modality is EEG, which constitutes a technique that detects electrical activity in the brain using electrodes.
-EEG is a widely utilized method for classifying workload.
-An overview of the complete literature on EEG classification with deep learning has been made by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to constitute with workload, lending credence to the ability of EEG as classifier of workload.
-Additionally, the usage of deep learning techniques for a range of different EEG application was investigated upon.
-Summarizing, it was reported that studies mostly found deep belief networks and convolutional neural networks to perform best when classifying workload, and advice one of these approaches as a consequence \cite{craik2019deep}.
+EEG is a commonly utilized method within the field of workload investigation.
+An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to cope with workload classification.
+With regards to these EEG applications, \citeA{craik2019deep} reported that studies mostly found deep belief networks and convolutional neural networks, hereafter referred to as "ConvNets", to perform best when classifying workload, and advice one of these approaches as a consequence.
 
-Research by \citeA{schirrmeister2017deep} contrasted the performance of several convolutional neural networks, hereafter referred to as "ConvNets", against the widely acknowledged baseline method for EEG classification, filter bank common spatial pattern, hereafter referred to as "FBCSP".
-The investigated networks included a deep, a shallow, a deep-shallow hybrid and a residual ConvNet.
-Both the deep and shallow ConvNets were found to reach at least similar, and in some regard better classification results, as compared with the FBCSP baseline.
-Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, displaying an accuracy of 92.4 \% \cite{schirrmeister2017deep}.
+\citeA{tabar2016novel} proposed combining a ConvNet with a Stacked auto-encoder network, hereafter referred to as "SAE".
+The input layer was specified to feed into a convolutional layer with the objective of learning the filters and network parameters.
+The output of this convolutional layer was subsequently specified to feed into the SAE part, architected to include an input layer, 6 hidden layers and an output layer.
+A classification accuracy of 90 \% was acquired with this network \cite{tabar2016novel}.
 
-A different approach is proposed by \citeA{tabar2016novel}, combining a ConvNet with a Stacked auto-encoder network, hereafter referred to as "SAE".
-Within this network, the input layer feeds into a convolutional layer with the objective of learning the filters and network parameters.
-The output of this convolutional layer subsequently feeds into SAE part of the network, constituting an input layer, 6 hidden layers and an output layer.
-A classification accuracy of 90 \% was acquired with this model \cite{tabar2016novel} .
+Research by \citeA{schirrmeister2017deep} contrasted the performance of several ConvNets against the widely utilized baseline method for EEG classification, filter bank common spatial pattern, hereafter referred to as "FBCSP".
+A deep ConvNet, a shallow ConvNet, a deep-shallow hybrid ConvNet and a residual ConvNet were contrasted with an FBCSP.
+Both the deep and shallow ConvNets were found to reach at least similar, and in some regard better classification results as compared with the FBCSP baseline approach.
+Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, exhibiting an accuracy of 92.4 \% \cite{schirrmeister2017deep}.
 
-\subsubsection{Second modality: Galvanic Skin Response (GSR)}
+\subsubsection{Galvanic Skin Response (GSR)}
 The second utilized modality is GSR, measuring sweat gland on the hands and hereby inferring arousal.
-GSR activity have been found to significantly increase as a consequence of an increase in task workload, hence constituting to be an objective predictor \cite{shi2007galvanic}.
+GSR activity is known to be significantly correlated with workload, as was demonstrated amongst others by \citeA{shi2007galvanic}.
+As a consequence, GSR poses a widely utilized modality within the field of workload detection.
 
-Sun and colleagues explored the most optimal deep learning network for classifying six different emotional states by means of GSR data.
-Several models were investigated upon, amongst others a support vector machine, a ConvNet, a long-short-term-memory model and a hybrid model combining the ConvNet and long-short-term-memory, herefater referred to as "LSTM", approaches.
-The hybrid model was found to perform best, exhibiting an accuracy of 74\% \cite{sun2019hybrid}.
+\citeA{sun2019hybrid} explored the architecture for the most suitable deep-learning approach to the classification of several emotional states by means of GSR.
+Several model were explored, amongst others a support vector machine, a ConvNet, a long-short-term-memory, hereafter referred to as "LSTM", network.
+Additionally, a hybrid model combining the ConvNet and LSTM approaches was explored.
+This aforementioned hybrid model was found to perform best, exhibiting an accuracy of 74\% \cite{sun2019hybrid}.
 
-A variant on the CovNet LSTM model was employed by \citeA{dolmans2020perceived}, who aimed to classify workload by means of, amongst other modalities, also GSR.
+\citeA{dolmans2020perceived} took a multi-modular approach to workload classification, and architected a variant on the previously delineated CovNet-LSTM approach for the GSR modality specifically.
 The performance of this model was contrasted with a network consisting solely of fully connected dense layers.
@@
 
-\subsubsection{Third modality: Photoplethysmography (PPG)}
-The third modality constitutes PPG, which is a technique utilized to measure heart rate.
-PPG is, not undeservedly, a widely deployed technique within the field of workload classification.
-Zhang and colleagues investigated several approaches for measuring workload, comparing in total four modalities, out of which one was PPG.
-PPG was found to display both the highest sensitivity and reliability for measuring workload, lending credence to the feasibility of PPG as a method for classifying workload \cite{zhang2018evaluating}.
+\subsubsection{Photoplethysmography (PPG)}
+The third modality constitutes PPG, which is a technique utilized to measure volumetric changes in blood in peripheral circulation.
+\citeA{zhang2018evaluating} contrasted several approaches towards workload classification, out of which PPG was found to perform among the best.
+As a consequence, PPG constitutes one of the most widely utilized approaches towards workload classification.
 
-Work by \citeA{biswas2019cornet} investigated upon a deep learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
-Exceptional results were attained with a neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
-This performance was managed with a hybrid model, incorporating two convolutional max-pooling blocks, followed with two LSTM layers.
+Work by \citeA{biswas2019cornet} investigated upon a deep-learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
+Exceptional results were attained with a deep neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
+This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed with two LSTM layers.
 
-\subsubsection{Fusion strategy}  
-When architecting a multi-modular network, information streams stemming from different modalities are required to be combined, i.e.
-"fused", at one point in the network in order to ultimately result in a single classification.
-Fusion can be done at different locations, and in different ways.
-Several fusion strategies as proposed by \citeA{ramachandram2017deep} have been considered.
+\subsubsection{Fusion Strategy}  
+When taking a multi-modular deep-learning approach, information streams stemming from different modalities are required to be combined, i.e.
+"fused", at a certain point in the network in order to ultimately result in a single classification.
+Fusion can be done conforming different strategies.
+Several strategies as proposed by \citeA{ramachandram2017deep} have been considered.
 
-Early, or data-level, fusion focuses on how to optimally combine data sources, before being fed into the network.
-Techniques that realize this include for example principle component analysis or factor analysis.
-Early fusing is usually challenging, especially for a multi-modular situation such as the current.
-This resides in the fact that data stemming from different modalities often differ with regards to dimensionality and sampling rate.
-Another disadvantage of early fusing, is that usually the oversimplified assumption of conditional independence is made.
-This assumption is unrealistic in practice, for data stemming from different modalities are expected to be correlated \cite{ramachandram2017deep}.
+Early, or data-level, fusion constitutes an approach that fuses data sources before being fed into the network.
+Techniques that manage this include for example principle component analysis and factor analysis.
+Early fusing is usually proven to be challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate.
+In addition, when endeavoring an early fusion approach ,the oversimplified assumption of conditional independence is made implicitly.
+This assumption is unrealistic in nature, for data stemming from different modalities are expected to be correlated in practice \cite{ramachandram2017deep}.
 
-Late, or decision level, fusion on the other hand refers to the process of aggregating the decisions from multiple models, each separately applied on each modalitiy separately.
-In case the data sources stemming from the various modalities are either correlated or ultimately inhibit a different dimensionality, late fusion is a much more feasible approach \cite{ramachandram2017deep}.
+Late, or decision-level, fusion refers to the process of aggregating the decisions of multiple networks, each architected and applied towards each modality separately.
+In case the data sources stemming from the various modalities are either correlated or ultimately inhibit a different dimensionality, late fusion is a much more feasible approach as contrasted with early-fusion \cite{ramachandram2017deep}.
 
-Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modal deep learning problems.
-Modalities are fused by concatenation and adding a higher order layer, to which the individual networks, separately defined for each modality, feed into.
+Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modular deep-learning problems.
+Data streams are usually fused by concatenation of the networks defined for each modality separately, followed by a higher order layer that ultimately results in a classification.
 This need not be a single layer, but could be multiple layers, as long as each modality ultimately feeds into the highest order output layer.
-The depth of the fusion (i.e.
-the amount of fusion layers) can be chosen conform the specific situation, posing intermediate fusion to be the most flexible, and therefore the most widely utilized fusion strategy \cite{ramachandram2017deep}.
+The depth of the fusion, i.e.
+the specified number of fusion layers, can be chosen conform to the specific circumstances, posing intermediate fusion to be the most flexible and therefore the most widely adopted fusion strategy \cite{ramachandram2017deep}.
 
-Indeed, when consulting the literature, intermediate fusion strategies are the most prevailing for multi-modular deep neural networks.
-When taking such an approach, one is required to consider the design of this higher order network.
-\citeA{rastgoo2019automatic} utilize a multi-modular ConvNet approach, and fuse the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer.
+Indeed, when consulting the literature, one is forced to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep neural networks.
+When taking such an approach, the higher order network architecture is required to be established, for which several previous endeavors will be considered.
+\citeA{rastgoo2019automatic} utilize a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer.
 A simpler approach is utilized by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers, and ending with a soft-max layer.
-Lastly, \citeA{dolmans2020perceived} used a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.
+Lastly, \citeA{dolmans2020perceived} took a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.
 
-\subsubsection{Model optimization}
-The technique of batch normalization was proposed by  \citeA{ioffe2015batch},  and is often applied in deep learning with the objective of enhancing the stability of a network.
-This is endeavored by including a batch normalization layer after each convolutional layer, re-centering and re-scaling the input feeding into this layer.
-If incorporating a batch normalization layer, it is recommended to do so before feeding into the activation function \cite{ioffe2015batch}.
-An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived} and \citeA{schirrmeister2017deep} by specifying a batch normalization layer after each convolutional layer.
-Equally so, the best performing model for PPG data as proposed by \citeA{biswas2019cornet} included a batch normalization layer after each convolutional layer.
+\subsubsection{Model Optimization}
+The technique of batch normalization was originally proposed by \citeA{ioffe2015batch}, and is often a applied in deep-learning with the objective of enhancing the stability of a network.
+Especially ConvNets capitalize on this technique.
+It is beneficial to include a batch normalization layer after each convolutional layer, re-centering and re-scaling the input feeding into subsequent layers.
+When incorporating a batch normalization layer, it is recommended to do so before feeding into the activation function \cite{ioffe2015batch}.
+An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived} and \citeA{schirrmeister2017deep} by specifying a batch normalization layer following each convolutional layer.
+Equally so, the best performing network for PPG data as proposed by \citeA{biswas2019cornet} included a batch normalization layer succeeding each convolutional layer.
 
-Pooling layers are often used in ConvNets, following a convolutional layer with the attempt to decrease the dimensionality.
-The objective of such layers are to merge similar features into one (for a more extensive elaboration see: \citeA{lecun2015deep}).
-Considering the earlier delineated EEG ConvNets, both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer.
-The network as proposed for GSR by \citeA{sun2019hybrid} incorporated a max-pooling layer after each, but one of the convolutional layers.
+Pooling layers are commonly employed in ConvNets, often subceeding a convolutional layer with the purpose decreasing dimensionality.
+The objective of such layers are to merge similar features into one: for a more extensive elaboration see \citeA{lecun2015deep}.
+Both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer within their EEG ConvNets.
+The network as proposed for GSR by \citeA{sun2019hybrid} incorporated a max-pooling layer after each but one of the convolutional layers.
 Lastly, the network as proposed for PPG by \cite{biswas2019cornet} specified a max pooling layer after each convolutional layer.
 
-Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be used to optimize hyper-parameter, such as for example learning rate, dropout probability and momentum.
-Substantial advancements within the deep learning community have been attained by utilizing HPO, especially considering the performance of ConvNets \cite{bergstra2012random}.
-The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled, and thus HPO can be performed \cite{akiba2019optuna}.
+Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be used to optimize hyper-parameters such as learning rate, dropout probability and momentum.
+Substantial advancements within the deep learning community have been attained by utilizing HPO, especially with regards to ConvNet performance \cite{bergstra2012random}.
+The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled and optimization can be performed \cite{akiba2019optuna}.
 
 \subsection{Data}
-The current section will provide an overview of the utilized data.
-Special attention is placed on the experimental setup, the description of the participants and the data collection / synchronization process.
+The subsequent section will provide an overview of the utilized data.
+Attention is primarily placed upon the experimental setup, the description of the respondents, the utilized devices and the synchronization process.
 
-\subsubsection{Experimental setup}
-The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which the respondent is required to carry out tasks on a virtual spaceship \cite{daid2016empty}.
-This experiment is instituted by the Brain Computer Interfaces (BCI) testbed lab, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
-The experiment constituted three different segments, during each of which the respondent had to carry out different tasks, all of which constructed to entail varying degrees of perceived workload.
-Each segment consists of six small sessions of roughly 5-10 minutes.
+\subsubsection{Experimental Setup}
+The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which respondents are required to carry out tasks on a virtual spaceship \cite{daid2016empty}.
+This experiment was instituted by the Brain Computer Interfaces testbed lab, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
+The experiment constituted three different segments, in each of which the respondent had to carry out tasks.
+These tasks were constructed to evoke varying degrees of perceived workload.
+Each segment consisted of six small sessions lasting roughly five to ten minutes.
 These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment.
 A schematic overview of the experimental structure is depicted as figure \ref{fig:experimental}.
-After each of the 18 sessions, respondents filled in the TLX questionnaire consisting of 6 questions each, resulting in 18 filled in questionnaires.
-Each questionnaire inquired upon the degree to which the respondent experienced workload during the previous session.
-These ratings have been use as labels in later training of the network.
-Within each segment, the order in which the sessions (varying in difficulty) were presented have been randomized.
-The order in which the segments were administrated were not random.
-Between every three sessions, respondents were requested to take a short 2 minute break.
+
+After each small session, respondents filled in the TLX questionnaire compromising six questions each, resulting in 18 filled in questionnaires per respondent.
+Each questionnaire inquired upon the degree to which the respondent experienced workload during the preceding session.
+These ratings have been utilized to label the data for network training purposes.
+Within each segment, the order in which the sessions were presented was randomized.
+The order in which the three main segments were administrated was not randomized.
+Between every three sessions, respondents were requested to take a short two minute break.
 
@@
 The first segment emulated a scenario in which hostile spaceships approach the respondent's spaceship.
-The respondent is required to  quickly react by defusing hostile spaceships in order to survive.
-The increment in difficulty caused the process of defusing hostile spaceships to be more challenging, and hereby to take longer,  aiming to increase workload as a consequence.
+The respondent is required to quickly react by defusing the hostiles in order to survive.
+The increment in difficulty caused the process of defusing hostile spaceships to become more challenging, hereby aiming to cause an increase in workload.
 The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible.
-Obstacles around which the respondent had to carefully navigate were introduced in the intermediate difficult scenario, and hostile spaceships the respondent had to decimate were introduced in the hard scenario.
-Both increase difficulty, and hereby aim to increase workload as a consequence.
+Obstacles around which the respondent had to carefully navigate and hostile spaceships the respondent had to decimate were introduced in the higher difficulty sessions.
 The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests.
-Variables that could overheat the spaceship were introduced, demanding the respondent to multi-task, hence increasing difficulty.
+In the increased difficulty settings, variables that could overheat the spaceship were introduced, demanding the respondent to multi-task and aiming to increase workload.
 
-\subsubsection{Participants}
-In total, twenty-five respondents are participating in the study.
+\subsubsection{Respondents}
+In total, 25 respondents have participated in the study.
 Currently, the data is still in the process of being collected, for which no additional descriptive statistics can be presented in the this section as of yet.
-The respondents are students, recruited from the University of Twente.
+The respondents are students recruited from the University of Twente.
 Recruitment has been conducted with Sona, which is a cloud-based participant management system.
-Requirements were that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker.
+A requirements for participation was that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker.
 This was assessed by means of a short demographic questionnaire prior to the experiment.
-Additionally, the respondents were made aware of informed consent prior to the experiment, with the objective to ensure completely voluntary participation.
+Additionally, the respondents were made aware of informed consent prior to the experiment with the objective to ensure completely voluntary participation.
 Respondents were able to draw back from the experiment at any time.
@@
 The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
-The device is worn on the wrist, and is able to communicate the signal wirelessly.
+The device is worn on the wrist, and is able to communicate both signals wirelessly.
 An ear-clip was utilized for measuring PPG, and converting this to estimate heart rate.
 Skin conductivity, or GSR, was monitored by two electrodes attached to the fingers \cite{shimmer}.
-EEG measurement is conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}.
+EEG measurement was conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}.
 The Shimmer3 GSR+ is able to read and output data signals on a sampling rate of 256 Hz, whereas the Muse 2 is able to sample at a maximum of 220 Hz.
 
-As was already touched upon in the introduction, real-time classification requires a swift network.
-A higher sampling rate entails more data traveling through the network, decelerating classification speed.
-As a consequence, it is beneficial to input data on the minimum required sampling rate with which the key features can be detected for each modality in a consistent manner.
-\citeA{fujita2019evaluation} investigated the minimum required sampling rate for the PPG modality.
-The extent to which features were detected have been contrasted for several sampling rates.
-A sampling rate of 60 Hz was found to be the absolute minimum required sampling rate for extracting all commonly utilized features stably \cite{fujita2019evaluation}.
-A slightly higher sampling rate might be the safer option, however.
-\citeA{shimmer} recommend a sampling rate of 100 Hz for the PPG modality, and stable feature extraction was naturally observed on this rate by \citeA{fujita2019evaluation} as well.
-Hence, a sampling rate of 100 Hz is utilized for the PPG modality.
+As was set forth in the introduction, real-time classification requires a swiftly classifying network.
+A higher sampling rate equals more data traveling through the network, which decelerates classification speed.
+As a consequence, it is necessary to input data on the minimum required sampling rate with which key features can be detected a consistent manner, for each modality separately.
+
+\citeA{fujita2019evaluation} investigated the required sampling rate for PPG feature detection.
+The extent to which important features were detected was contrasted for several sampling rates.
+A sampling rate of 60 Hz was found to be the absolute minimum required sampling rate for extracting all commonly utilized features in a stable manner \cite{fujita2019evaluation}.
+Utilizing a slightly higher sampling rate might be the safer option, however.
+The Shimmer3 GSR+ manufacturers recommend a sampling rate of 100 Hz for the PPG modality \cite{shimmer}.
+Hence, a sampling rate of 100 Hz was specified for the PPG modality.
+
 The required sampling rate for the GSR modality is substantially lower as compared with both PPG and EEG.
-Shimmer recommended the necessary sampling rate to range between 0.03 and 5 Hz \cite{shimmer}.
-A sampling rate of 5 Hz will be utilized consequently.
+In fact, the Shimmer3 GSR+ manufacturers recommend a sampling rate ranging between 0.03 and 5 Hz \cite{shimmer}.
+A sampling rate of 5 Hz was specified as a consequence.
+
 For the EEG modality, different features require a widely different sampling rate in order to be detected.
-Frequency bands for traditional EEG features are defined on about 0.5-4 Hz for delta, and at most on about 16-24 Hz for beta.
-The gamma frequency band recently gained in popularity within the field of EEG, and is defined on a frequency ranging up to 80 Hz \cite{weiergraeber2016sampling}.
-In order to detect a feature residing on the 80 Hz frequency band, a substantially higher sampling rate is required to record the signal without aliasing.
+Frequency bands for traditionally considered EEG features are defined on about 0.5-4 Hz for delta, and at most on about 16-24 Hz for beta.
+The gamma frequency band recently gained in popularity within the field of EEG however, and is defined on a frequency ranging up to 80 Hz \cite{weiergraeber2016sampling}.
+In order to detect a feature residing on a 80 Hz frequency band, a substantially higher sampling rate is required to record the signal without aliasing.
 The required sampling rate can be determined by means of the Nyquist criterion for practical EEG sampling, defined as equation \ref{eqn:nyquist},
@@
 \end{equation}
-where $f_{sam}$ reflects the required sampling rate and $f_{max}$ reflects the frequency range around which the feature to be detected resides\cite{srinivasan1998estimating}.
-Hence, in order to be able to detect the gamma frequency band, a sampling rate of 200 is utilized for the EEG modality.
-A summary of the utilized sampling rates per modality is depicted as table \ref{table:samplingrate}.
+where $f_{samp}$ reflects the required sampling rate and $f_{max}$ reflects the frequency range around which the feature to be detected resides \cite{srinivasan1998estimating}.
+Hence, in order to be able to detect the gamma frequency band, a sampling rate of $2.5*80=200$ was specified for the EEG modality.
+A summary of the specified sampling rates per modality are depicted in table \ref{table:samplingrate}.
 
@@
 \centering
+\bigskip
 \caption{Sampling rate per modality}
@@
 \begin{tabular}{ll}
-    & Utilized sampling rate (Hz) \\ \hline
+    & Specified sampling rate (Hz) \\ \hline
  Electroencephalogram (EEG) & 200                         \\
@@
 \end{table}
+\bigskip
 \egroup
@@
 \subsubsection{Synchronization}
-Data streams stemming from the different modalities were required to be properly synchronized such that they are parallel.
-This was accomplished by means of an application called Lab-Streaming Layer, hereafter refered to as "LSL", to which the different data are streamed during the experiment.
-LSL properly synchronized these data streams, such that they refer to the same points in time, and subsequently record all data into a single file per participant \cite{kothe2018lab}.
+Data streams stemming from the different modalities were required to be properly synchronized.
+This was accomplished by means of an application called Lab-Streaming Layer, hereafter referred to as "LSL".
+The data streams stemming from the different modalities were all streamed to LSL during the experiment.
+LSL properly synchronized these data streams, such that they are parallel time-wise.
+Subsequently, all data was recorded into a single file per participant \cite{kothe2018lab}.
 
 \subsection{Framework Architecture}
-As was elaborated on in the introduction, several networks will be compared in their ability to classify workload in real-time, and the performance with which this is managed.
-The upcoming section opens with the description of the network architectures solely utilizing one of the three modalities each.
-Subsequently, the multi-modular architecture will be elaborated on.
-Lastly, several variations based on this multi-modular architecture are delineated.
+As was elaborated on in the introduction, several networks have been compared in their ability to classify workload in real-time, and the performance with which this is managed.
+The upcoming section opens with the description of architecture of the three single-modular networks.
+Subsequently, the multi-modular network architecture will be elaborated on.
+Lastly, several variations made on this multi-modular architecture are discussed.
 
@@
 The architecture of each of the single-modular networks is determined by combining insights from the literature.
-Each of the three network merely utilizes a single modality with which workload is classified.
-These networks and their architecture are all depicted as figure \ref{fig:singlearchitecture}.
+Each of the three networks merely utilized a single modality with which workload was classified.
+These networks and their architectures are depicted as figure \ref{fig:singlearchitecture}.
 
@@
 
-The utilized network for the EEG modality is a ConvNet, as proposed by \citeA{schirrmeister2017deep}.
-The network is designed to include four convolutional blocks, each constituting a convolutional layer, followed by a batch normalisation layer.
-The Exponential Linear Unit, hereafter referred to as "ELU", function is utilized as activation function, and is defined as equation \ref{eqn:elu}.
+The utilized network for the EEG modality was a ConvNet as proposed by \citeA{schirrmeister2017deep}.
+The network was designed to include four convolutional blocks, each constituting a convolutional layer, followed by a batch normalization layer.
+The Exponential Linear Unit, hereafter referred to as "ELU", function was utilized as activation function.
 Each convolutional block is closed with a max pooling layer of stride three.
 
-\begin{equation}
-\label{eqn:elu}
-f(x)= 
-\begin{Bmatrix}
-x & x \geq0 \\ 
-\alpha (e^x -1) & x<0
-\end{Bmatrix}
-\bigskip
-\end{equation}
-
-The utilized network for the GSR modality is a LSTM ConvNet network, inspired by the work of \citeA{sun2019hybrid} and  \citeA{dolmans2020perceived}.
-The network is designed to include two convolutional blocks, each constituting a convolutional layer, followed by a batch normalization layer, an activation layer and closed with a max-pooling layer of stride four.
-The Rectified Linear Unit, hereafter referred to as "ReLU", function is utilized as activation function, defined as equation \ref{eqn:relu}.
+The utilized network for the GSR modality was a LSTM ConvNet hybrid, inspired upon by the work of \citeA{sun2019hybrid} and \citeA{dolmans2020perceived}.
+The network was designed to include two convolutional blocks, each constituting a convolutional layer, followed by a batch normalization layer, the activation layer and closed with a max-pooling layer of stride four.
+The Rectified Linear Unit, hereafter referred to as "ReLU", function was utilized as activation function.
 Following these two convolutional blocks are two LTSM layers.
 
-\begin{equation} 
-\label{eqn:relu}
-f(x)=max(0,x)
-\bigskip
-\end{equation}
-
-Lastly, the utilized network for the PPG modality is inspired upon the network as proposed by \citeA{biswas2019cornet}.
+Lastly, the utilized network for the PPG modality was inspired from the network as proposed by \citeA{biswas2019cornet}.
 The nework opens with two convolutional blocks, each consisting of a convolutional layer, batch normalization layer, activation layer and closed with a max pooling layer of stride four.
-The utilized activation function is the ReLU, depicted as equation \ref{eqn:relu}.
-Following these convolutional blocks are two LTSM layers, equal to the GSR model.
+The utilized activation function was the ReLU.
+Following these convolutional blocks are two LTSM layers, equal to the GSR network.
 
@@
 the principles of modularity and generalizability) are taken into account when doing so.
-A visual representation of the multi-modular network is depicted as figure \ref{fig:multiarchitecture}.
+The visual representation of the multi-modular network is depicted as figure \ref{fig:multiarchitecture}.
 
@@
 \subsubsection{Multi-modular Network: Variations}
-Multi-modular classification in real-time by means of deep-learning requires an optimized network, as was elaborated upon in the introduction.
-Speed is a potential bottleneck, for a multi-modular network such as presented is substantially complex in nature.
-Therefore, several variations of the delineated network will be investigated upon, differing in their complexity.
-These variations are not made by changing the network architecture, whereas deviating from the proven network architecure is likely to be detrimental with regards to model performance.
-The aim is to propose a network that is fast enough for real-time classification, whilst maintaining the highest amount of accuracy as possible.
-Three different variations with regards to size of the network as depicted in figure \ref{fig:multiarchitecture} will therefore be considered.
+Speed is a potential bottleneck for a multi-modular network that should be able to classify in real-time.
+The previously delineated network is substantially complex in nature.
+Therefore, several variations of this network have been investigated upon, each differing in their complexity.
+These variations are not made by altering the network architecture, for deviating from the distinguished architecture might be detrimental towards performance.
+The goal is to propose a network that is fast enough for real-time classification, whilst maintaining the highest amount of accuracy as possible.
+Three different variations with regards to size of the network as depicted in figure \ref{fig:multiarchitecture} have therefore been considered.
 
-Network size is understood as the amount of utilized filters for convolutional layers, and the amount of neurons for all other utilized layers.
+Network size can be understood as the amount of specified filters for convolutional layers, and the amount of specified neurons for all other utilized layers.
 A decrease in the amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of required calculations.
-This is likely to bring about an increase in speed.
-An overview of all three multi-modular network variations, and the amount of utilized neurons/filters is provided in table \ref{table:modelvariations}.
+Doing so brings about an increase in speed.
+An overview of all three multi-modular network variations, and the amount of specified neurons/filters per layer, is provided in table \ref{table:modelvariations}.
 Network 1 is referred to as the full network, and is the biggest in terms of size.
@@
 \subsection{Model Evaluation}
-The performance of the four network variations will be contrasted by means of several performance metrics.
+The network performances have been assessed and contrasted by means of several performance metrics.
 The utilized metrics constitute six well known and widely applied metrics, all constructed from the confusion matrix, depicted as table \ref{table:confusion}.
@@
 
-The measures accuracy, sensitivity, specificity, PPV, NPV and F1 will be utilized in order to asses network performance.
-The network that performs best across these measures is considered to be the superior performing network.
+The measures accuracy, sensitivity, specificity, PPV, NPV and F1 have been utilized in order to asses network performance.
+The network that performs best across these measures was considered to be the superior performing network.
 Table \ref{table:metrics} depicts the constitution of these performance metrics, by partly referring to confusion matrix depicted as table \ref{table:confusion}.

### 2021-01-04 Research Report - Boverhof/Tex report/main.tex

@@
 {\textbf{Date}}\\
-January 11, 2020\\
+January 11, 2021\\
 \vspace*{1\baselineskip}
@@
 \section{Introduction}
-The topic of mental workload is a widely studied 
+The topic of mental workload is a commonly investigated 
 phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
-A commonly utilized definition for mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst they carry out a particular task.
-As pointed out by \citeA{de1996measurement}, the aforementioned definition is too simplistic, for it defines workload solely as an external phenomenon.
-Workload is, however, a person-specific construct, for the amount of perceived workload ushered by a given task may differ across individuals \cite{de1996measurement}.
-Hence, when referring to workload throughout this research, person-specific workload is implied specifically.
+A widely utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst they carry out a certain task.
+As pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual.
+Workload is, however, a person-specific construct.
+The amount of perceived workload ushered by a given task may differ across individuals due to how well one is able to cope with that particular task \cite{de1996measurement}.
+Hence, when referring to workload throughout this research, the person-specific nature of workload is acknowledged.
 
-A commonly employed method for assessing workload is the well established NASA-Task Load Index questionnaire.
-This questionnaire inquires the respondent on the amount of perceived workload, and is constructed from six subjective sub-scales \cite{hart2006nasa}.
-Such an assessment is usually conducted post-experiment, which can in certain situations be deemed undesirable.
-Consider an experiment in which is aimed to assess workload of a pilot in flight.
-An evident approach towards such an experiment is that we wish to measure the degree of perceived workload during different phases of the flight.
-However, only after the simulation is concluded, a measurement in the form of a questionnaire can be administrated.
-In such a situation, utilizing a post-experiment assessment is prone to generate bias.
-A widely recognized bias is the observer-bias, advocating that participants in an experiment tend to overexaggerate the treatment effect when having to report it post-experiment \cite{mahtani2018catalogue}.
-In the light of the aforementioned example, pilots are expected to overexaggerate the degree of perceived workload when having to report it post-experiment.
+A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire.
+This questionnaire inquires into the amount of perceived workload, and rests on six subjective sub-scales \cite{hart2006nasa}.
+This assessment is usually conducted post-experiment, which can in certain situations be considered undesirable.
+Consider for example an experiment in which it is aimed to assess workload of a pilot in flight.
+An insightful learning approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight.
+However, only after the flight is concluded a measurement in the form of a questionnaire can be administrated.
+In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate bias.
+A widely recognized type of bias is the observer-bias, advocating that participants in an experiment tend to overexaggerate the treatment effect, i.e.
+the amount of perceived workload in our case, when having to report it post-experiment \cite{mahtani2018catalogue}.
 
-An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these to classify workload.
-Examples of such bio-signals, hereafter referred to as "modalities", include techniques as electroencephalogram, eye-tracking, galvanic skin response, functional near-infrared spectroscopy etc.
-The advantage of such an approach is that complementary information streams, each stemming from a different modality, may all be interpreted simultaneously \cite{ramachandram2017deep}.
-This has the potential of yielding a rich and multifaceted classification of construct such as workload.
-Additionally, it is possible to train a separate model for each individual, catering towards the individual perception of workload for that specific person.
+An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs in order to classify workload.
+Examples of such bio-signals, hereafter referred to as "modalities", include techniques as electroencephalogram, eye-tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
+The advantage of such an approach is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}.
+Doing so poses the potential to yield a rich and multifaceted classification of a mental construct such as workload.
+However most importantly, it is possible to train a separate model for each individual, catering towards the person-specific nature inherent to workload as was touched upon before.
 This approach, however, comes at the cost of an increase in complexity.
@@
 In addition, the current research investigates upon the feasibility of a real-time approach.
-Real-time in this sense reflects the real-time classification of workload, i.e.
+Real-time in this sense constitutes the real-time classification of workload, i.e.
 the classification of workload whilst the experiment takes place.
-Doing so enables the possibility to conduct a dynamic experiment, the state of which can be altered by responding towards the classified degree of workload at a certain moment in time.
-Consider a simulation with the objective of educating its participant, such as a surgical simulation for educating surgeons-in-training.
-The learning experience of a single session could be dramatically enhanced when the state of the experiment is catered towards the individual learning process dynamically.
-For example, in case it is recognized early on in the simulation that a surgeon-in-training has difficulty with a specific procedure, the remainder of the experiment can be catered towards focusing on this specific procedure.
-By enhancing the learning experience in this way, the effectiveness of a single simulation session can be improved dramatically, entailing a more efficient learning process.
+Taking such an approach enables the possibility to conduct a dynamic experiment, the state of which can be altered by responding towards the classified degree of workload in real-time.
+Consider a simulation with the objective of educating its partakers, such as a surgical simulation for educating surgeons-in-training.
+The learning experience of a single session could be dramatically enhanced when the state of the experiment is catered towards the individual learning process.
+For example, in case it is recognized at the start of the session that a surgeon-in-training has difficulty with a specific procedure, the remainder of the session can be catered towards focusing on this specific procedure.
+By enhancing the learning experience in this manner, the effectiveness of a single simulation session can be improved upon dramatically, entailing a substantially more efficient learning process.
 
-Three different modalities are utilized in the current research.
-Firstly the technique of electroencephalogram, hereafter referred to as "EEG", secondly the technique of galvanic skin response, hereafter referred to as "GSR" and thirdly the technique photoplethysmography, hereafter referred to as "PPG".
+Three modalities are utilized in the current research.
+The first of which is the technique of electroencephalogram, hereafter referred to as "EEG".
+The second is the technique of galvanic skin response, hereafter referred to as "GSR".
+Lastly, the third technique is called photoplethysmography, hereafter referred to as "PPG".
 It is of importance to recognize that the objective of the current research is not to gain insight into the most optimal model design for each of the previously delineated modalities.
-The objective is rather to construct a framework with which real-time classification can be managed, and to which modalities of choice can easily be added in future research endeavors.
+The objective is rather to construct a framework with which real-time classification of a mental construct such as workload can be managed, and to which modalities of choice can easily be added in future research endeavors.
 Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity.
-Modularity refers to the extent to which different modalities can freely be added and/or removed to the framework, without the necessity to re-architect and rebuild it entirely.
-The second design principle is the principle of generalizability, prescribing that the framework should not merely be utilizable in the context of workload, but also for the measurement of other mental constructs.
+Modularity refers to the extent to which different modalities can freely be added and/or removed towards the framework, without the necessity of re-architecting and rebuilding it entirely.
+The second design principle is the principle of generalizability, prescribing that the framework should not merely be utilizable for the classification of workload, but also for the classification of other mental constructs.
 
-A deep-learning approach towards the construction of a real-time multi-modular framework is realized.
+A deep-learning approach towards the construction of a real-time multi-modular framework is adopted.
 Considering the complexity and sheer size of such a deep-neural network, an important point of attention is classification speed.
@@
 In order for real-time classification to work, classification cannot take too long, for otherwise it is not real-time anymore and the previously delineated benefit of a real-time approach dissipates.
-As a consequence, multiple networks are considered and contrasted in terms of performance and ability to classify in real-time.
-Firstly, for each of the three modalities separately, a single-modular network is constructed.
-Secondly, a multi-modular network is architected.
-Additionally, several variations to this multi-modular framework are considered and contrasted.
-These variations are specified to differ in size, i.e.
-the amount of neurons and filters.
+As a consequence, multiple networks are considered and contrasted in terms of performance and their ability to classify in real-time.
+Firstly, for each of the three modalities individually, a single-modular network is constructed.
+Secondly, a multi-modular network is architected combining all three modalities.
+Additionally, several variations on this multi-modular framework are considered and contrasted.
+These variations are specified to differ in network size, i.e.
+the amount of specified neurons and filters.
 
-The objective of the current research is to explore the circumstances in which a multi-modular approach by means of deep learning is capable of real-time classification, whilst still ensuring ample and adequate performance.
+The objective of the current research is to explore the circumstances under which a multi-modular approach by means of deep-learning is capable of real-time classification, whilst still ensuring ample and adequate performance.
 Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, and of which the state can be altered in real-time.
@@
 %Method section
+\newpage
 \section{Methods}
@@
 \subsection{Related Work} 
-The following section will provide an overview of preceding research on the most optimal network architecture for each single-modular network.
-Subsequently, the most feasible architecture for the multi-modular framework in its entirety will be explored, with particular attention on the data fusion strategy and a range model optimization techniques.
+The following section provides an overview of preceding research on the most optimal network architecture for each single-modular network.
+Subsequently, the most feasible architecture for the multi-modular framework in its entirety is explored, with particular attention placed upon the data fusion strategy and a range model optimization techniques.
 
 \subsubsection{Electroencephalogram (EEG)}
-The first utilized modality is EEG, which constitutes a technique that detects electrical activity in the brain using electrodes.
-EEG is a commonly utilized method within the field of workload investigation.
-An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to cope with workload classification.
-With regards to these EEG applications, \citeA{craik2019deep} reported that studies mostly found deep belief networks and convolutional neural networks, hereafter referred to as "ConvNets", to perform best when classifying workload, and advice one of these approaches as a consequence.
+EEG constitutes a technique that detects electrical activity in the brain by using electrodes.
+EEG is a commonly utilized method within the field of workload assessment.
+An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to investigate workload specifically.
+With regards to these EEG applications, it was reported that studies mostly found deep belief networks and convolutional neural networks, hereafter referred to as "ConvNets", to perform best in workload classification.
+One of these approaches is advised consequently \cite{craik2019deep}.
 
-\citeA{tabar2016novel} proposed combining a ConvNet with a Stacked auto-encoder network, hereafter referred to as "SAE".
+For EEG classification, \citeA{tabar2016novel} proposed combining a ConvNet with a Stacked auto-encoder network, hereafter referred to as "SAE".
 The input layer was specified to feed into a convolutional layer with the objective of learning the filters and network parameters.
-The output of this convolutional layer was subsequently specified to feed into the SAE part, architected to include an input layer, 6 hidden layers and an output layer.
+The output of this convolutional layer was subsequently specified to feed into the SAE part of the network, designed to include an input layer, 6 hidden layers and an output layer.
 A classification accuracy of 90 \% was acquired with this network \cite{tabar2016novel}.
@@
 \subsubsection{Galvanic Skin Response (GSR)}
-The second utilized modality is GSR, measuring sweat gland on the hands and hereby inferring arousal.
-GSR activity is known to be significantly correlated with workload, as was demonstrated amongst others by \citeA{shi2007galvanic}.
-As a consequence, GSR poses a widely utilized modality within the field of workload detection.
+GSR is a technique that measures sweat gland on the hands, hereby inferring arousal.
+GSR activity is known to be strongly correlated with an increase in perceived workload, as was demonstrated amongst others by \citeA{shi2007galvanic}.
+Hence, GSR poses a widely utilized modality within the field of workload classification.
 
-\citeA{sun2019hybrid} explored the architecture for the most suitable deep-learning approach to the classification of several emotional states by means of GSR.
-Several model were explored, amongst others a support vector machine, a ConvNet, a long-short-term-memory, hereafter referred to as "LSTM", network.
-Additionally, a hybrid model combining the ConvNet and LSTM approaches was explored.
+\citeA{sun2019hybrid} explored the most suitable model design for the classification of several emotional states with GSR.
+Various models were explored, amongst others a support vector machine, a ConvNet and long-short-term-memory network, hereafter referred to as "LSTM network".
+Additionally, the feasibility of a hybrid network, combining both the ConvNet and LSTM approaches, was explored.
 This aforementioned hybrid model was found to perform best, exhibiting an accuracy of 74\% \cite{sun2019hybrid}.
 
-\citeA{dolmans2020perceived} took a multi-modular approach to workload classification, and architected a variant on the previously delineated CovNet-LSTM approach for the GSR modality specifically.
+\citeA{dolmans2020perceived} took a multi-modular approach to workload classification, and architected a variant on the previously delineated CovNet-LSTM approach for the GSR modality.
 The performance of this model was contrasted with a network consisting solely of fully connected dense layers.
@@
 \subsubsection{Photoplethysmography (PPG)}
-The third modality constitutes PPG, which is a technique utilized to measure volumetric changes in blood in peripheral circulation.
-\citeA{zhang2018evaluating} contrasted several approaches towards workload classification, out of which PPG was found to perform among the best.
-As a consequence, PPG constitutes one of the most widely utilized approaches towards workload classification.
+PPG is a technique utilized to measure volumetric changes in blood in peripheral circulation from which heart-rate is derived.
+\citeA{zhang2018evaluating} contrasted several approaches, utilizing different modalities, towards workload classification, out of which PPG was found to perform among the best.
+As a consequence, PPG constitutes one of the most widely utilized modalities for workload classification.
 
-Work by \citeA{biswas2019cornet} investigated upon a deep-learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
+Work by \citeA{biswas2019cornet} explored a deep-learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
 Exceptional results were attained with a deep neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
-This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed with two LSTM layers.
+This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed by two LSTM layers.
 
-\subsubsection{Fusion Strategy}  
-When taking a multi-modular deep-learning approach, information streams stemming from different modalities are required to be combined, i.e.
-"fused", at a certain point in the network in order to ultimately result in a single classification.
+\subsubsection{Multi-modular Fusion Strategy}  
+For the multi-modular deep-learning approach, the information streams stemming the three modalities are required to be combined, i.e.
+"fused", at a certain point in the network in order to ultimately result in a single classification of workload.
 Fusion can be done conforming different strategies.
@@
 Early fusing is usually proven to be challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate.
-In addition, when endeavoring an early fusion approach ,the oversimplified assumption of conditional independence is made implicitly.
+In addition, when taking an early fusion approach ,the oversimplified assumption of conditional independence is made implicitly.
 This assumption is unrealistic in nature, for data stemming from different modalities are expected to be correlated in practice \cite{ramachandram2017deep}.
 
-Late, or decision-level, fusion refers to the process of aggregating the decisions of multiple networks, each architected and applied towards each modality separately.
-In case the data sources stemming from the various modalities are either correlated or ultimately inhibit a different dimensionality, late fusion is a much more feasible approach as contrasted with early-fusion \cite{ramachandram2017deep}.
+Late, or decision-level, fusion refers to the process of aggregating the decisions of multiple separate networks, each applied towards every modality separately.
+In case the data sources stemming from the various modalities are either correlated or ultimately differ in their dimensionality, late fusion is a much more feasible approach as contrasted with early-fusion \cite{ramachandram2017deep}.
 
 Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modular deep-learning problems.
-Data streams are usually fused by concatenation of the networks defined for each modality separately, followed by a higher order layer that ultimately results in a classification.
-This need not be a single layer, but could be multiple layers, as long as each modality ultimately feeds into the highest order output layer.
+Data streams are usually fused by a concatenation layer, joining the outputs of the networks defined for each modality separately, resulting in a single joint deep neural network.
+Classification is managed based on the outputs from each of the single-modular network parts.
+Several "higher-order layers" are usually defined in between the concatenation layer and the ultimate classification.
 The depth of the fusion, i.e.
-the specified number of fusion layers, can be chosen conform to the specific circumstances, posing intermediate fusion to be the most flexible and therefore the most widely adopted fusion strategy \cite{ramachandram2017deep}.
+the specified number of higher-order layers, can be chosen conform to the specific circumstances, posing intermediate fusion to be the most flexible and therefore the most widely adopted fusion strategy \cite{ramachandram2017deep}.
 
-Indeed, when consulting the literature, one is forced to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep neural networks.
-When taking such an approach, the higher order network architecture is required to be established, for which several previous endeavors will be considered.
-\citeA{rastgoo2019automatic} utilize a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer.
+Indeed, when consulting the literature, one is forced to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep-learning approaches.
+When taking such an approach, the higher-order part of the network needs to be established, for which several previous research endeavors will be considered.
+\citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer.
 A simpler approach is utilized by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers, and ending with a soft-max layer.
@@
 
-\subsubsection{Model Optimization}
-The technique of batch normalization was originally proposed by \citeA{ioffe2015batch}, and is often a applied in deep-learning with the objective of enhancing the stability of a network.
-Especially ConvNets capitalize on this technique.
+\subsubsection{Model Optimization Strategies}
+The technique of batch normalization was originally proposed by \citeA{ioffe2015batch}, and is often a applied in deep-learning with the objective of stabilizing a network.
+Especially ConvNets are able to capitalize on this technique.
 It is beneficial to include a batch normalization layer after each convolutional layer, re-centering and re-scaling the input feeding into subsequent layers.
-When incorporating a batch normalization layer, it is recommended to do so before feeding into the activation function \cite{ioffe2015batch}.
-An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived} and \citeA{schirrmeister2017deep} by specifying a batch normalization layer following each convolutional layer.
+When incorporating a batch normalization layer, it is recommended to do so before the specification of the activation function \cite{ioffe2015batch}.
+An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived} and \citeA{schirrmeister2017deep} through specifying a batch normalization layer following each convolutional layer.
 Equally so, the best performing network for PPG data as proposed by \citeA{biswas2019cornet} included a batch normalization layer succeeding each convolutional layer.
 
-Pooling layers are commonly employed in ConvNets, often subceeding a convolutional layer with the purpose decreasing dimensionality.
-The objective of such layers are to merge similar features into one: for a more extensive elaboration see \citeA{lecun2015deep}.
-Both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer within their EEG ConvNets.
+Pooling layers are commonly employed in ConvNets, often succeeding a convolutional layer with the purpose decreasing the dimensionality.
+The objective of such layers are to merge similar features into one.
+For a more extensive elaboration on pooling, please consult \citeA{lecun2015deep}.
+In their EEG ConvNets, both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer.
 The network as proposed for GSR by \citeA{sun2019hybrid} incorporated a max-pooling layer after each but one of the convolutional layers.
@@
 
-Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be used to optimize hyper-parameters such as learning rate, dropout probability and momentum.
-Substantial advancements within the deep learning community have been attained by utilizing HPO, especially with regards to ConvNet performance \cite{bergstra2012random}.
+Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be used to optimize hyper-parameters such as learning rate and dropout.
+Substantial advancements in deep-learning have been attained by utilizing HPO, especially for ConvNet.
+\cite{bergstra2012random}.
 The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled and optimization can be performed \cite{akiba2019optuna}.
@@
 The subsequent section will provide an overview of the utilized data.
-Attention is primarily placed upon the experimental setup, the description of the respondents, the utilized devices and the synchronization process.
+Attention is primarily placed upon the experimental setup, the description of the respondents, the utilized devices for data collection and the synchronization process.
 
 \subsubsection{Experimental Setup}
-The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which respondents are required to carry out tasks on a virtual spaceship \cite{daid2016empty}.
-This experiment was instituted by the Brain Computer Interfaces testbed lab, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
+The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which respondents were asked to carry out tasks on a virtual spaceship \cite{daid2016empty}.
+This experiment was instituted by the Brain Computer Interfaces testbed, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
 The experiment constituted three different segments, in each of which the respondent had to carry out tasks.
-These tasks were constructed to evoke varying degrees of perceived workload.
+These tasks are designed to evoke varying degrees of workload.
 Each segment consisted of six small sessions lasting roughly five to ten minutes.
@@
 
-After each small session, respondents filled in the TLX questionnaire compromising six questions each, resulting in 18 filled in questionnaires per respondent.
+After each of the 18 sessions, respondents were asked to fill in the TLX questionnaire, compromising of six questions each.
+This resulted in 18 filled in questionnaires per respondent.
 Each questionnaire inquired upon the degree to which the respondent experienced workload during the preceding session.
@@
 The order in which the three main segments were administrated was not randomized.
-Between every three sessions, respondents were requested to take a short two minute break.
+Between every three sessions, respondents given a short two minute break.
 
@@
 The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests.
-In the increased difficulty settings, variables that could overheat the spaceship were introduced, demanding the respondent to multi-task and aiming to increase workload.
+In the increased difficulty settings, variables that could overheat the spaceship were introduced, demanding the respondent to multi-task and aiming to increase workload as a consequence.
 
@@
 Recruitment has been conducted with Sona, which is a cloud-based participant management system.
-A requirements for participation was that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker.
+A requirement for participation was that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker.
 This was assessed by means of a short demographic questionnaire prior to the experiment.
-Additionally, the respondents were made aware of informed consent prior to the experiment with the objective to ensure completely voluntary participation.
-Respondents were able to draw back from the experiment at any time.
+Additionally, the respondents were made aware of informed consent prior to the experiment, with the objective to ensure completely voluntary participation.
+Respondents were able to draw back from the experiment at any given time.
 
@@
 The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
-The device is worn on the wrist, and is able to communicate both signals wirelessly.
+This device is worn on the wrist.
+Signals were communicated wirelessly.
 An ear-clip was utilized for measuring PPG, and converting this to estimate heart rate.
@@
 EEG measurement was conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}.
-The Shimmer3 GSR+ is able to read and output data signals on a sampling rate of 256 Hz, whereas the Muse 2 is able to sample at a maximum of 220 Hz.
+The Shimmer3 GSR+ is able to read and output data signals on a sampling rate of 256 Hz, whereas the Muse 2 is able to sample at a maximum rate of 220 Hz.
 
 As was set forth in the introduction, real-time classification requires a swiftly classifying network.
-A higher sampling rate equals more data traveling through the network, which decelerates classification speed.
-As a consequence, it is necessary to input data on the minimum required sampling rate with which key features can be detected a consistent manner, for each modality separately.
+A higher sampling rate equals more data traveling through the network, decelerating classification speed.
+As a consequence, it is necessary to input data on the minimum required sampling rate with which key features can be detected consistently.
 
-\citeA{fujita2019evaluation} investigated the required sampling rate for PPG feature detection.
+\citeA{fujita2019evaluation} explored the required sampling rate for PPG feature detection.
 The extent to which important features were detected was contrasted for several sampling rates.
@@
 Utilizing a slightly higher sampling rate might be the safer option, however.
-The Shimmer3 GSR+ manufacturers recommend a sampling rate of 100 Hz for the PPG modality \cite{shimmer}.
+The Shimmer3 GSR+ manufacturers recommend a sampling rate of 100 Hz for PPG \cite{shimmer}.
 Hence, a sampling rate of 100 Hz was specified for the PPG modality.
@@
 For the EEG modality, different features require a widely different sampling rate in order to be detected.
-Frequency bands for traditionally considered EEG features are defined on about 0.5-4 Hz for delta, and at most on about 16-24 Hz for beta.
-The gamma frequency band recently gained in popularity within the field of EEG however, and is defined on a frequency ranging up to 80 Hz \cite{weiergraeber2016sampling}.
-In order to detect a feature residing on a 80 Hz frequency band, a substantially higher sampling rate is required to record the signal without aliasing.
+Frequency bands for traditionally considered EEG features are defined on about 0.5-4 Hz for the delta feature, and at most on about 16-24 Hz for the beta feature.
+The gamma feature recently gained in popularity within the field of EEG, and is defined on a frequency band ranging up to 80 Hz \cite{weiergraeber2016sampling}.
+In order to be able to detect an EEG feature residing on a 80 Hz frequency band, a substantially higher sampling rate is required to record the signal without aliasing.
 The required sampling rate can be determined by means of the Nyquist criterion for practical EEG sampling, defined as equation \ref{eqn:nyquist},
@@
 \end{equation}
-where $f_{samp}$ reflects the required sampling rate and $f_{max}$ reflects the frequency range around which the feature to be detected resides \cite{srinivasan1998estimating}.
-Hence, in order to be able to detect the gamma frequency band, a sampling rate of $2.5*80=200$ was specified for the EEG modality.
+where $f_{samp}$ reflects the required sampling rate and $f_{max}$ reflects the frequency band around which the feature to be detected resides \cite{srinivasan1998estimating}.
+Hence, in order to be able to detect the gamma feature stably, a sampling rate of $2.5*80=200$ was specified for the EEG modality.
 A summary of the specified sampling rates per modality are depicted in table \ref{table:samplingrate}.
@@
 \begin{table}[h]
-\centering
 \bigskip
@@
 The data streams stemming from the different modalities were all streamed to LSL during the experiment.
-LSL properly synchronized these data streams, such that they are parallel time-wise.
+LSL properly synchronized these data streams, such that they are parallel.
 Subsequently, all data was recorded into a single file per participant \cite{kothe2018lab}.
 
+\newpage
 \subsection{Framework Architecture}
 As was elaborated on in the introduction, several networks have been compared in their ability to classify workload in real-time, and the performance with which this is managed.
-The upcoming section opens with the description of architecture of the three single-modular networks.
-Subsequently, the multi-modular network architecture will be elaborated on.
+The upcoming section opens with the description of the architecture of the three single-modular networks.
+Subsequently, the multi-modular network architecture is elaborated upon.
 Lastly, several variations made on this multi-modular architecture are discussed.
@@
 \subsubsection{Single-modular Network Architectures}
-The architecture of each of the single-modular networks is determined by combining insights from the literature.
-Each of the three networks merely utilized a single modality with which workload was classified.
-These networks and their architectures are depicted as figure \ref{fig:singlearchitecture}.
+The appropriate architecture for each of the single-modular networks is determined by combining insights from the literature.
+The three single-modular networks and their architectures are depicted as figure \ref{fig:singlearchitecture}.
 
@@
 The Exponential Linear Unit, hereafter referred to as "ELU", function was utilized as activation function.
-Each convolutional block is closed with a max pooling layer of stride three.
+Each convolutional block was closed with a max pooling layer of stride three.
 
-The utilized network for the GSR modality was a LSTM ConvNet hybrid, inspired upon by the work of \citeA{sun2019hybrid} and \citeA{dolmans2020perceived}.
+The utilized network for the GSR modality was a LSTM ConvNet hybrid, inspired from the work of \citeA{sun2019hybrid} and \citeA{dolmans2020perceived}.
 The network was designed to include two convolutional blocks, each constituting a convolutional layer, followed by a batch normalization layer, the activation layer and closed with a max-pooling layer of stride four.
 The Rectified Linear Unit, hereafter referred to as "ReLU", function was utilized as activation function.
-Following these two convolutional blocks are two LTSM layers.
+Following these two convolutional blocks were two LTSM layers.
 
@@
 The utilized activation function was the ReLU.
-Following these convolutional blocks are two LTSM layers, equal to the GSR network.
+Following these convolutional blocks were two LTSM layers.
 
+\newpage
 \subsubsection{Multi-modular Network: Architecture}
-The network architecture that is utilized for the multi-modular approach is determined by a combination of the single-modular networks, as derived from the literature.
+The network architecture utilized for the multi-modular approach was determined by a combination of the single-modular networks, as derived from the literature.
 The previously delineated design principles (i.e.
-the principles of modularity and generalizability) are taken into account when doing so.
-The visual representation of the multi-modular network is depicted as figure \ref{fig:multiarchitecture}.
+the principles of modularity and generalizability) were considered when doing so.
+A visual representation of the multi-modular network is depicted as figure \ref{fig:multiarchitecture}.
 
@@
 
-In order to combine the previously delineated single-modular networks, each of these distinct parts are closed with one fully connected dense layer before feeding into the head network.
-This is done in order to flatten all inputs into a lower dimensional space, such that concatenation is possible.
+An intermediate fusion strategy is adopted.
+The architecture for the single-modular parts of the network remained unchanged.
+In order to fuse the previously delineated single-modular parts, each of these is closed with one fully connected dense layer before feeding into the head network.
+This is done in order to flatten all inputs towards a lower dimensional space, such that concatenation is possible.
 The head network consists of four dense layers.
@@
 \subsubsection{Multi-modular Network: Variations}
-Speed is a potential bottleneck for a multi-modular network that should be able to classify in real-time.
-The previously delineated network is substantially complex in nature.
-Therefore, several variations of this network have been investigated upon, each differing in their complexity.
-These variations are not made by altering the network architecture, for deviating from the distinguished architecture might be detrimental towards performance.
+Speed is a potential bottleneck for a multi-modular approach that is destined to classify in real-time.
+The previously delineated network is substantially complex in nature, hence running the risk of not classifying fast enough.
+Therefore, several variations on this network architecture have been designed.
+These variations are not made by altering the network architecture, for deviating from the validated architecture could be detrimental with regards to performance.
+Hence, three variations with regards to network size as depicted in figure \ref{fig:multiarchitecture} have been considered.
 The goal is to propose a network that is fast enough for real-time classification, whilst maintaining the highest amount of accuracy as possible.
-Three different variations with regards to size of the network as depicted in figure \ref{fig:multiarchitecture} have therefore been considered.
 
 Network size can be understood as the amount of specified filters for convolutional layers, and the amount of specified neurons for all other utilized layers.
-A decrease in the amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of required calculations.
-Doing so brings about an increase in speed.
+A decrease in the specified amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of required calculations.
+Doing so is likely to bring about an increase in speed.
 An overview of all three multi-modular network variations, and the amount of specified neurons/filters per layer, is provided in table \ref{table:modelvariations}.
-Network 1 is referred to as the full network, and is the biggest in terms of size.
+Network 1 is referred to as the full network.
 The size of network 2 constitutes of 75 \% of the size of the full network.
@@
 \begin{table}[h]
-\centering
 \caption{Model variation sizes}
@@
 The network performances have been assessed and contrasted by means of several performance metrics.
-The utilized metrics constitute six well known and widely applied metrics, all constructed from the confusion matrix, depicted as table \ref{table:confusion}.
+The utilized metrics constitute six well known and widely applied metrics, all constructed from the confusion matrix, theoretically depicted as table \ref{table:confusion}.
 
@@
 \begin{table}[h]
-\centering
 \caption{Confusion matrix}
@@
 Table \ref{table:metrics} depicts the constitution of these performance metrics, by partly referring to confusion matrix depicted as table \ref{table:confusion}.
+
 \bigskip
@@
 \begin{table}[h]
-\centering
 \caption{Performance Metrics}

### 2021-01-06 Research Report - Boverhof/Tex report/main.tex

@@
 \section{Introduction}
-The topic of mental workload is a commonly investigated 
-phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
+The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
 A widely utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst they carry out a certain task.
-As pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual.
-Workload is, however, a person-specific construct.
-The amount of perceived workload ushered by a given task may differ across individuals due to how well one is able to cope with that particular task \cite{de1996measurement}.
+As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual.
+Workload needs to be recognized as a person-specific construct however.
+The amount of perceived workload ushered by a given task may differ across individuals, due to how well one is able to cope with that particular task \cite{de1996measurement}.
 Hence, when referring to workload throughout this research, the person-specific nature of workload is acknowledged.
@@
 This assessment is usually conducted post-experiment, which can in certain situations be considered undesirable.
-Consider for example an experiment in which it is aimed to assess workload of a pilot in flight.
+Consider for example an experiment in which is aimed to assess workload of a pilot in flight.
 An insightful learning approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight.
-However, only after the flight is concluded a measurement in the form of a questionnaire can be administrated.
+However, only after the flight is concluded, a measurement in the form of a questionnaire can be administrated.
 In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate bias.
@@
 Doing so poses the potential to yield a rich and multifaceted classification of a mental construct such as workload.
-However most importantly, it is possible to train a separate model for each individual, catering towards the person-specific nature inherent to workload as was touched upon before.
+However most importantly, it is possible to train a separate model for each individual, catering towards the person-specific nature inherent to workload, as was pointed out by \citeA{de1996measurement}.
 This approach, however, comes at the cost of an increase in complexity.
@@
 For example, in case it is recognized at the start of the session that a surgeon-in-training has difficulty with a specific procedure, the remainder of the session can be catered towards focusing on this specific procedure.
-By enhancing the learning experience in this manner, the effectiveness of a single simulation session can be improved upon dramatically, entailing a substantially more efficient learning process.
+By enhancing the learning experience in this manner, the effectiveness of a single session can be improved upon dramatically, entailing a substantially more efficient learning process.
 
@@
 Lastly, the third technique is called photoplethysmography, hereafter referred to as "PPG".
-It is of importance to recognize that the objective of the current research is not to gain insight into the most optimal model design for each of the previously delineated modalities.
+It is of importance to recognize that the objective of the current research is not to gain insight into the most optimal model design for each of these previously delineated modalities.
 The objective is rather to construct a framework with which real-time classification of a mental construct such as workload can be managed, and to which modalities of choice can easily be added in future research endeavors.
@@
 Modularity refers to the extent to which different modalities can freely be added and/or removed towards the framework, without the necessity of re-architecting and rebuilding it entirely.
-The second design principle is the principle of generalizability, prescribing that the framework should not merely be utilizable for the classification of workload, but also for the classification of other mental constructs.
+The second design principle is the principle of generalizability, prescribing that the framework should not merely be utilizable for the classification of workload, but for the classification of other mental constructs as well.
 
@@
 Additionally, several variations on this multi-modular framework are considered and contrasted.
-These variations are specified to differ in network size, i.e.
+These networks are specified to vary in size, i.e.
 the amount of specified neurons and filters.
 
-The objective of the current research is to explore the circumstances under which a multi-modular approach by means of deep-learning is capable of real-time classification, whilst still ensuring ample and adequate performance.
+The aim of the current research is to explore the circumstances under which a multi-modular approach by means of deep-learning is capable of real-time classification, whilst still ensuring ample and adequate performance.
+The objective is to provide a framework with which the previously delineated is possible, whilst satisfying the principles of modularity and generalizability.
 Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, and of which the state can be altered in real-time.
@@
 \subsection{Related Work} 
-The following section provides an overview of preceding research on the most optimal network architecture for each single-modular network.
+The following sections provide an overview of preceding research on the most optimal network architecture for each single-modular network.
 Subsequently, the most feasible architecture for the multi-modular framework in its entirety is explored, with particular attention placed upon the data fusion strategy and a range model optimization techniques.
@@
 An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to investigate workload specifically.
-With regards to these EEG applications, it was reported that studies mostly found deep belief networks and convolutional neural networks, hereafter referred to as "ConvNets", to perform best in workload classification.
+With regards to these EEG applications, it was reported that studies mostly used deep belief networks and convolutional neural networks, hereafter referred to as "ConvNets".
 One of these approaches is advised consequently \cite{craik2019deep}.
@@
 A deep ConvNet, a shallow ConvNet, a deep-shallow hybrid ConvNet and a residual ConvNet were contrasted with an FBCSP.
-Both the deep and shallow ConvNets were found to reach at least similar, and in some regard better classification results as compared with the FBCSP baseline approach.
+Both the deep and shallow ConvNets were found to reach at least similar, and in some regards better classification results as compared with the FBCSP baseline approach.
 Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, exhibiting an accuracy of 92.4 \% \cite{schirrmeister2017deep}.
@@
 GSR is a technique that measures sweat gland on the hands, hereby inferring arousal.
-GSR activity is known to be strongly correlated with an increase in perceived workload, as was demonstrated amongst others by \citeA{shi2007galvanic}.
+GSR activity is known to be strongly correlated with perceived workload, as was demonstrated amongst others by \citeA{shi2007galvanic}.
 Hence, GSR poses a widely utilized modality within the field of workload classification.
@@
 \citeA{sun2019hybrid} explored the most suitable model design for the classification of several emotional states with GSR.
-Various models were explored, amongst others a support vector machine, a ConvNet and long-short-term-memory network, hereafter referred to as "LSTM network".
+Various models were explored, amongst others a support vector machine, a ConvNet and a long-short-term-memory network, hereafter referred to as "LSTM network".
 Additionally, the feasibility of a hybrid network, combining both the ConvNet and LSTM approaches, was explored.
@@
 
-\citeA{dolmans2020perceived} took a multi-modular approach to workload classification, and architected a variant on the previously delineated CovNet-LSTM approach for the GSR modality.
+\citeA{dolmans2020perceived} took a multi-modular approach to workload classification, and designed a variant based on the previously delineated CovNet-LSTM approach for GSR.
 The performance of this model was contrasted with a network consisting solely of fully connected dense layers.
@@
 \subsubsection{Photoplethysmography (PPG)}
-PPG is a technique utilized to measure volumetric changes in blood in peripheral circulation from which heart-rate is derived.
-\citeA{zhang2018evaluating} contrasted several approaches, utilizing different modalities, towards workload classification, out of which PPG was found to perform among the best.
-As a consequence, PPG constitutes one of the most widely utilized modalities for workload classification.
+PPG is a technique utilized to measure volumetric changes in blood peripheral circulation from which heart-rate is derived.
+\citeA{zhang2018evaluating} contrasted several approaches, each utilizing a different modality, towards workload classification, out of which PPG was found to perform among the best.
+It is for this reason that PPG constitutes one of the most widely utilized modalities in workload classification.
 
-Work by \citeA{biswas2019cornet} explored a deep-learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
-Exceptional results were attained with a deep neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
+Work by \citeA{biswas2019cornet} explored a deep-learning approach on PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
+Exceptional results were realized with a deep neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
 This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed by two LSTM layers.
@@
 \subsubsection{Multi-modular Fusion Strategy}  
-For the multi-modular deep-learning approach, the information streams stemming the three modalities are required to be combined, i.e.
+When conducting a multi-modular deep-learning approach, the information streams stemming the three modalities are required to be combined, i.e.
 "fused", at a certain point in the network in order to ultimately result in a single classification of workload.
@@
 Early, or data-level, fusion constitutes an approach that fuses data sources before being fed into the network.
-Techniques that manage this include for example principle component analysis and factor analysis.
-Early fusing is usually proven to be challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate.
-In addition, when taking an early fusion approach ,the oversimplified assumption of conditional independence is made implicitly.
+Techniques that manage this include for example principle-component analysis and factor analysis.
+Early fusing is usually proven to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate.
+In addition, when taking an early fusion approach, the oversimplified assumption of conditional independence is made implicitly.
 This assumption is unrealistic in nature, for data stemming from different modalities are expected to be correlated in practice \cite{ramachandram2017deep}.
@@
 Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modular deep-learning problems.
-Data streams are usually fused by a concatenation layer, joining the outputs of the networks defined for each modality separately, resulting in a single joint deep neural network.
+Data streams are usually fused by a concatenation layer, joining the outputs of the separately defined network parts of each modality.
+This results in a single joint deep neural network.
 Classification is managed based on the outputs from each of the single-modular network parts.
@@
 Indeed, when consulting the literature, one is forced to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep-learning approaches.
-When taking such an approach, the higher-order part of the network needs to be established, for which several previous research endeavors will be considered.
+When taking an intermediate fusion approach, the higher-order part of the network needs to be designed and established, for which several previous research endeavors are considered.
 \citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer.
@@
 An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived} and \citeA{schirrmeister2017deep} through specifying a batch normalization layer following each convolutional layer.
-Equally so, the best performing network for PPG data as proposed by \citeA{biswas2019cornet} included a batch normalization layer succeeding each convolutional layer.
+Equally so, the best performing network for PPG as proposed by \citeA{biswas2019cornet} included a batch normalization layer succeeding each convolutional layer.
 
-Pooling layers are commonly employed in ConvNets, often succeeding a convolutional layer with the purpose decreasing the dimensionality.
+Pooling layers are commonly employed in ConvNets, often succeeding a convolutional layer with the purpose of decreasing the dimensionality.
 The objective of such layers are to merge similar features into one.
@@
 Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be used to optimize hyper-parameters such as learning rate and dropout.
-Substantial advancements in deep-learning have been attained by utilizing HPO, especially for ConvNet.
-\cite{bergstra2012random}.
+Substantial advancements in deep-learning have been attained by utilizing HPO, especially for ConvNets \cite{bergstra2012random}.
 The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled and optimization can be performed \cite{akiba2019optuna}.
+\bigskip
 
@@
 \subsubsection{Experimental Setup}
-The experimental setting for data collection is the open-source spaceship video-game Empty Epsilon, in which respondents were asked to carry out tasks on a virtual spaceship \cite{daid2016empty}.
+The experimental setting in which the data collection took place is the open-source spaceship video-game Empty Epsilon, in which respondents were asked to carry out tasks on a virtual spaceship \cite{daid2016empty}.
 This experiment was instituted by the Brain Computer Interfaces testbed, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
 The experiment constituted three different segments, in each of which the respondent had to carry out tasks.
-These tasks are designed to evoke varying degrees of workload.
+These tasks were designed to evoke varying degrees of workload.
 Each segment consisted of six small sessions lasting roughly five to ten minutes.
 These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment.
-A schematic overview of the experimental structure is depicted as figure \ref{fig:experimental}.
+Within each segment, the order in which the sessions were presented was randomized.
+The order in which the three main segments were administrated was not randomized.
+Between every three sessions, respondents were given a short two minute break.
+A schematic overview of the experimental structure is depicted as Figure \ref{fig:experimental}.
 
@@
 Each questionnaire inquired upon the degree to which the respondent experienced workload during the preceding session.
-These ratings have been utilized to label the data for network training purposes.
-Within each segment, the order in which the sessions were presented was randomized.
-The order in which the three main segments were administrated was not randomized.
-Between every three sessions, respondents given a short two minute break.
+These measurements have been utilized to label the data for network training purposes.
 
 \begin{figure}
-\caption{Experimental setup}
+\caption{Experimental Setup}
 \bigskip
@@
 
-The first segment emulated a scenario in which hostile spaceships approach the respondent's spaceship.
-The respondent is required to quickly react by defusing the hostiles in order to survive.
+The first segment emulated a scenario in which hostile spaceships approached the respondent's spaceship.
+The respondent was required to quickly react by defusing the hostiles in order to survive.
 The increment in difficulty caused the process of defusing hostile spaceships to become more challenging, hereby aiming to cause an increase in workload.
 The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible.
-Obstacles around which the respondent had to carefully navigate and hostile spaceships the respondent had to decimate were introduced in the higher difficulty sessions.
+Obstacles around which the respondent had to navigate carefully, as well as hostile spaceships the respondent had to decimate, were introduced in the higher difficulty sessions.
 The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests.
@@
 In total, 25 respondents have participated in the study.
-Currently, the data is still in the process of being collected, for which no additional descriptive statistics can be presented in the this section as of yet.
+No additional descriptive statistics can be presented in the this section as of yet.
 The respondents are students recruited from the University of Twente.
-Recruitment has been conducted with Sona, which is a cloud-based participant management system.
+Recruitment has been conducted by means of Sona, which is a cloud-based participant management system.
 A requirement for participation was that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker.
 This was assessed by means of a short demographic questionnaire prior to the experiment.
-Additionally, the respondents were made aware of informed consent prior to the experiment, with the objective to ensure completely voluntary participation.
-Respondents were able to draw back from the experiment at any given time.
+Additionally, the respondents were made aware of informed consent prior to the experiment in order to ensure completely voluntary participation.
+Respondents were able to draw back from the experiment at any time.
 
@@
 Signals were communicated wirelessly.
-An ear-clip was utilized for measuring PPG, and converting this to estimate heart rate.
-Skin conductivity, or GSR, was monitored by two electrodes attached to the fingers \cite{shimmer}.
+An ear-clip is utilized for measuring PPG, and converting this to estimate heart rate.
+Skin conductivity, or GSR, is monitored by two electrodes attached to the fingers \cite{shimmer}.
 EEG measurement was conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}.
@@
 A higher sampling rate equals more data traveling through the network, decelerating classification speed.
-As a consequence, it is necessary to input data on the minimum required sampling rate with which key features can be detected consistently.
+As a consequence, it is highly beneficial to input data on the minimum required sampling rate with which key features can be detected consistently.
 
@@
 A sampling rate of 60 Hz was found to be the absolute minimum required sampling rate for extracting all commonly utilized features in a stable manner \cite{fujita2019evaluation}.
-Utilizing a slightly higher sampling rate might be the safer option, however.
+Utilizing a slightly higher sampling rate is the safer option, however.
 The Shimmer3 GSR+ manufacturers recommend a sampling rate of 100 Hz for PPG \cite{shimmer}.
@@
 
-The required sampling rate for the GSR modality is substantially lower as compared with both PPG and EEG.
+The required sampling rate for the GSR modality is substantially lower as compared with both PPG and EEG measurement.
 In fact, the Shimmer3 GSR+ manufacturers recommend a sampling rate ranging between 0.03 and 5 Hz \cite{shimmer}.
@@
 For the EEG modality, different features require a widely different sampling rate in order to be detected.
-Frequency bands for traditionally considered EEG features are defined on about 0.5-4 Hz for the delta feature, and at most on about 16-24 Hz for the beta feature.
-The gamma feature recently gained in popularity within the field of EEG, and is defined on a frequency band ranging up to 80 Hz \cite{weiergraeber2016sampling}.
+Frequency bands for traditionally considered EEG features reside on about 0.5-4 Hz for the delta feature, and at most on about 16-24 Hz for the beta feature.
+The gamma feature recently gained in popularity, and resides on a frequency band ranging up to 80 Hz \cite{weiergraeber2016sampling}.
 In order to be able to detect an EEG feature residing on a 80 Hz frequency band, a substantially higher sampling rate is required to record the signal without aliasing.
-The required sampling rate can be determined by means of the Nyquist criterion for practical EEG sampling, defined as equation \ref{eqn:nyquist},
+The required sampling rate can be determined by means of the Nyquist criterion for practical EEG sampling, defined as Equation \ref{eqn:nyquist},
 
@@
 Hence, in order to be able to detect the gamma feature stably, a sampling rate of $2.5*80=200$ was specified for the EEG modality.
-A summary of the specified sampling rates per modality are depicted in table \ref{table:samplingrate}.
+A summary of the specified sampling rates per modality are depicted in Table \ref{table:samplingrate}.
 
@@
 \bigskip
-\caption{Sampling rate per modality}
+\caption{Sampling Rate per Modality}
 \label{table:samplingrate}
@@
 Subsequently, all data was recorded into a single file per participant \cite{kothe2018lab}.
+\bigskip
 
-\newpage
 \subsection{Framework Architecture}
-As was elaborated on in the introduction, several networks have been compared in their ability to classify workload in real-time, and the performance with which this is managed.
 The upcoming section opens with the description of the architecture of the three single-modular networks.
@@
 
-\subsubsection{Single-modular Network Architectures}
+\subsubsection{Single-modular Network: Architectures}
 The appropriate architecture for each of the single-modular networks is determined by combining insights from the literature.
-The three single-modular networks and their architectures are depicted as figure \ref{fig:singlearchitecture}.
+The three single-modular network architectures are depicted as Figure \ref{fig:singlearchitecture}.
 
 \begin{figure}
-\caption{Three single-modular network architectures}
+\caption{The Three Single-modular Network Architectures}
 \bigskip
@@
 
-\newpage
 \subsubsection{Multi-modular Network: Architecture}
@@
 The previously delineated design principles (i.e.
-the principles of modularity and generalizability) were considered when doing so.
-A visual representation of the multi-modular network is depicted as figure \ref{fig:multiarchitecture}.
+the principles of modularity and generalizability) were taken into account when doing so.
+A visual representation of the multi-modular network is depicted as Figure \ref{fig:multiarchitecture}.
 
 \begin{figure}
-\caption{Multi-modular Network Architecture}
+\caption{The Multi-modular Network Architecture}
 \bigskip
@@
 
-An intermediate fusion strategy is adopted.
+An intermediate fusion strategy is adopted due to its highly flexible nature as compared with other fusion strategies.
 The architecture for the single-modular parts of the network remained unchanged.
-In order to fuse the previously delineated single-modular parts, each of these is closed with one fully connected dense layer before feeding into the head network.
+In order to fuse the  single-modular parts of the network, each of these is closed with one fully connected dense layer before feeding into the head network.
 This is done in order to flatten all inputs towards a lower dimensional space, such that concatenation is possible.
@@
 Speed is a potential bottleneck for a multi-modular approach that is destined to classify in real-time.
-The previously delineated network is substantially complex in nature, hence running the risk of not classifying fast enough.
+The previously delineated network is substantially complex in nature, hence posing the risk of not being able to classify fast enough.
 Therefore, several variations on this network architecture have been designed.
 These variations are not made by altering the network architecture, for deviating from the validated architecture could be detrimental with regards to performance.
-Hence, three variations with regards to network size as depicted in figure \ref{fig:multiarchitecture} have been considered.
+Hence, three variations with regards to size of the network as depicted in Figure \ref{fig:multiarchitecture} have been considered.
 The goal is to propose a network that is fast enough for real-time classification, whilst maintaining the highest amount of accuracy as possible.
@@
 Doing so is likely to bring about an increase in speed.
-An overview of all three multi-modular network variations, and the amount of specified neurons/filters per layer, is provided in table \ref{table:modelvariations}.
+An overview of all three multi-modular network variations, and the amount of specified neurons/filters per layer, is provided in Table \ref{table:modelvariations}.
 Network 1 is referred to as the full network.
-The size of network 2 constitutes of 75 \% of the size of the full network.
-Network 3 constitutes of 50 \% of the size of the full network.
+The size of this network is determined from the literature.
+This implies that the size for each of the sub-parts (i.e.
+the EEG, PPG and GSR sub-parts) are roughly adopted from the research that proposed these designs initially.
+The size of Network 2 constitutes of 75 \% of the size of the full network.
+Lastly, Network 3 constitutes of 50 \% of the size of the full network.
 
@@
 \begin{table}[h]
-\caption{Model variation sizes}
+\caption{Model Variations Based on Size}
 \label{table:modelvariations}
@@
 The network performances have been assessed and contrasted by means of several performance metrics.
-The utilized metrics constitute six well known and widely applied metrics, all constructed from the confusion matrix, theoretically depicted as table \ref{table:confusion}.
+When assessing performance in deep/machine-learning, it is of importance to realize that each performance metric may favor one approach over the other, simply and solely due to the mathematical nature in which both the metric and the model are defined \cite{gunawardana2009survey}.
+For this reason, we deemed it of importance to not merely evaluate performance based on one or two metrics.
+The approach we adopted is rather to consider a conglomerate of different metrics, and evaluate performance based on the whole span of these.
+The utilized metrics constitute six well known and widely utilized metrics within the fields of deep/machine-learning.
+All six metrics are constructed from the confusion matrix, the theoretical format of which is depicted as Table \ref{table:confusion}.
 
@@
 \begin{table}[h]
-\caption{Confusion matrix}
+\caption{Confusion Matrix}
 \label{table:confusion}
@@
 
-The measures accuracy, sensitivity, specificity, PPV, NPV and F1 have been utilized in order to asses network performance.
-The network that performs best across these measures was considered to be the superior performing network.
-Table \ref{table:metrics} depicts the constitution of these performance metrics, by partly referring to confusion matrix depicted as table \ref{table:confusion}.
+The six metrics include the metric of accuracy, sensitivity, specificity, positive predicted value hereafter referred to as "PPV, negative predicted value hereafter referred to as "NPV" and F1.
+Table \ref{table:metrics} depicts mathematical the constitution of these performance metrics, by partly referring to confusion matrix depicted as Table \ref{table:confusion}.
+In substantive terms, accuracy can simply be understood as the proportion of correct classifications.
+Sensitivity is understood as the proportion true positives, whereas specificity is understood of as the proportion of true negatives.
+PPV reflects the proportion of predicted positives that are correctly predicted as positive.
+NPV on the other hand reflects the proportion of predicted negatives that are correctly predicted to be negative.
+Lastly, F1-score is a function of both sensitivity and PPV, seeking balance between the latter two.
 
-\bigskip
 \bgroup
@@
 \begin{table}[h]
-\caption{Performance Metrics}
+\caption{Utilized Performance Metrics}
 \label{table:metrics}
@@
 Positive Predicted Value (PPV): & \(\frac{a}{a+b}\)                                   \\
-Negative Predicted Value:       & \(\frac{d}{c+d}\)                                   \\
-F1-measure:                     & \(\frac{2*Sensitivity*PPV}{Sensitivity+PPV}\)       \\ \hline
+Negative Predicted Value (NPV):       & \(\frac{d}{c+d}\)                                   \\
+F1-score:                     & \(\frac{2*Sensitivity*PPV}{Sensitivity+PPV}\)       \\ \hline
 \end{tabular}
@@
 
+For each of the three single-modular networks, as well as each of the three multi-modular network variants, these six metrics have been constructed and reported.
+The network that performed best across the range of these metrics was considered to be the superior performing network.
+In case of contradictory interpretations, a reference will be made back to the mathematical definition and substantive interpretation of the previously delineated performance metrics.
+Summarizing, with the described assessment approach it is aimed to gain insight into multiple dimension of network performance, resulting in a broad and complete assessment of network performance altogether.
+
 \newpage
-
 \bibliographystyle{apacite}

### 2021-01-15 1.latex_report/main.tex
Several changes/additions
- Updates to internal folder structure
- Added descriptive R scripts

--- 2021-01-06 Research Report - Boverhof/Tex report/main.tex
@@
 {\textbf{Date}}\\
-January 11, 2021\\
+January 7, 2021\\
 \vspace*{1\baselineskip}
@@
 As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual.
-Workload needs to be recognized as a person-specific construct however.
+Workload needs to be recognized as a person-specific construct.
 The amount of perceived workload ushered by a given task may differ across individuals, due to how well one is able to cope with that particular task \cite{de1996measurement}.
@@
 This assessment is usually conducted post-experiment, which can in certain situations be considered undesirable.
-Consider for example an experiment in which is aimed to assess workload of a pilot in flight.
+Consider for example an experiment in which it is aimed to assess workload of a pilot in flight.
 An insightful learning approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight.
@@
 An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs in order to classify workload.
-Examples of such bio-signals, hereafter referred to as "modalities", include techniques as electroencephalogram, eye-tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
+Examples of such bio-signals, hereafter referred to as "modalities", include techniques as electroencephalography, eye-tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
 The advantage of such an approach is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}.
-Doing so poses the potential to yield a rich and multifaceted classification of a mental construct such as workload.
-However most importantly, it is possible to train a separate model for each individual, catering towards the person-specific nature inherent to workload, as was pointed out by \citeA{de1996measurement}.
+Doing so poses the potential of yielding a rich and multifaceted classification of a mental construct such as workload.
+However most importantly, it is possible to train a separate model for each individual.
+It renders possible to cater towards the person-specific nature inherent to workload, the importance of which was pointed out by \citeA{de1996measurement}.
 This approach, however, comes at the cost of an increase in complexity.
@@
 The learning experience of a single session could be dramatically enhanced when the state of the experiment is catered towards the individual learning process.
-For example, in case it is recognized at the start of the session that a surgeon-in-training has difficulty with a specific procedure, the remainder of the session can be catered towards focusing on this specific procedure.
+For example, in case it is recognized at the start of the session that a partaker has difficulty with a specific procedure, the remainder of the session can be catered towards focusing on this specific procedure.
 By enhancing the learning experience in this manner, the effectiveness of a single session can be improved upon dramatically, entailing a substantially more efficient learning process.
 
-Three modalities are utilized in the current research.
-The first of which is the technique of electroencephalogram, hereafter referred to as "EEG".
+Three modalities are utilized in the current research. The first of which is the technique of electroencephalography
+, hereafter referred to as "EEG".
 The second is the technique of galvanic skin response, hereafter referred to as "GSR".
@@
 the amount of specified neurons and filters.
+These networks were created in Python, by utilizing the deep/machine-learning toolbox Pytorch \cite{paszke2017automatic}
 
-The aim of the current research is to explore the circumstances under which a multi-modular approach by means of deep-learning is capable of real-time classification, whilst still ensuring ample and adequate performance.
+The aim of the current research is to explore the circumstances under which a multi-modular approach by means of deep-learning is capable of real-time classification of workload, whilst still ensuring ample and adequate performance.
 The objective is to provide a framework with which the previously delineated is possible, whilst satisfying the principles of modularity and generalizability.
@@
 
-\subsubsection{Electroencephalogram (EEG)}
+\subsubsection{Electroencephalography (EEG)}
 EEG constitutes a technique that detects electrical activity in the brain by using electrodes.
 EEG is a commonly utilized method within the field of workload assessment.
-An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to investigate workload specifically.
+An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to deal with workload specifically.
 With regards to these EEG applications, it was reported that studies mostly used deep belief networks and convolutional neural networks, hereafter referred to as "ConvNets".
@@
 
-For EEG classification, \citeA{tabar2016novel} proposed combining a ConvNet with a Stacked auto-encoder network, hereafter referred to as "SAE".
+For EEG classification, \citeA{tabar2016novel} proposed a combination of a ConvNet with a stacked auto-encoder network, hereafter referred to as "SAE network".
 The input layer was specified to feed into a convolutional layer with the objective of learning the filters and network parameters.
-The output of this convolutional layer was subsequently specified to feed into the SAE part of the network, designed to include an input layer, 6 hidden layers and an output layer.
+The output of this convolutional layer was subsequently specified to feed into the SAE part of the network, designed to include an input layer, six hidden layers and an output layer.
 A classification accuracy of 90 \% was acquired with this network \cite{tabar2016novel}.
@@
 GSR is a technique that measures sweat gland on the hands, hereby inferring arousal.
-GSR activity is known to be strongly correlated with perceived workload, as was demonstrated amongst others by \citeA{shi2007galvanic}.
-Hence, GSR poses a widely utilized modality within the field of workload classification.
+GSR activity is known to be strongly correlated with perceived workload, indicating the utility of GSR for workload classification \cite{shi2007galvanic}.
 
@@
 \subsubsection{Photoplethysmography (PPG)}
-PPG is a technique utilized to measure volumetric changes in blood peripheral circulation from which heart-rate is derived.
-\citeA{zhang2018evaluating} contrasted several approaches, each utilizing a different modality, towards workload classification, out of which PPG was found to perform among the best.
-It is for this reason that PPG constitutes one of the most widely utilized modalities in workload classification.
+PPG is a technique utilized to measure volumetric changes in blood peripheral circulation, from which it is possible to derive heart-rate.
+\citeA{zhang2018evaluating} contrasted several approaches towards workload classification, each utilizing a different modality.
+PPG was found to perform among the best, explaining why PPG constitutes one of the most widely utilized modalities in workload classification.
 
-Work by \citeA{biswas2019cornet} explored a deep-learning approach on PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
+Work by \citeA{biswas2019cornet} explored a deep-learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
 Exceptional results were realized with a deep neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
@@
 \subsubsection{Multi-modular Fusion Strategy}  
-When conducting a multi-modular deep-learning approach, the information streams stemming the three modalities are required to be combined, i.e.
-"fused", at a certain point in the network in order to ultimately result in a single classification of workload.
+When conducting a multi-modular deep-learning approach, the information streams stemming from the three modalities are required to be combined, i.e.
+"fused", at a certain point in the network, in order to ultimately result in a single classification of workload.
 Fusion can be done conforming different strategies.
@@
 Techniques that manage this include for example principle-component analysis and factor analysis.
-Early fusing is usually proven to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate.
+Early fusing is usually proven to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in dimensionality and sampling rate.
 In addition, when taking an early fusion approach, the oversimplified assumption of conditional independence is made implicitly.
@@
 Late, or decision-level, fusion refers to the process of aggregating the decisions of multiple separate networks, each applied towards every modality separately.
-In case the data sources stemming from the various modalities are either correlated or ultimately differ in their dimensionality, late fusion is a much more feasible approach as contrasted with early-fusion \cite{ramachandram2017deep}.
+In case the data sources stemming from the various modalities are either correlated or ultimately differ in their dimensionality, late fusion is a much more feasible approach as contrasted with early fusion \cite{ramachandram2017deep}.
 
@@
 \citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer.
-A simpler approach is utilized by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers, and ending with a soft-max layer.
+A simpler approach is adopted by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers, and ending with a soft-max layer.
 Lastly, \citeA{dolmans2020perceived} took a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.
@@
 
-Pooling layers are commonly employed in ConvNets, often succeeding a convolutional layer with the purpose of decreasing the dimensionality.
+Pooling layers are commonly employed in ConvNets, usually succeeding a convolutional layer with the purpose of decreasing the dimensionality.
 The objective of such layers are to merge similar features into one.
@@
 
-Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be used to optimize hyper-parameters such as learning rate and dropout.
+Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be utilized to optimize hyper-parameters such as learning rate and dropout.
 Substantial advancements in deep-learning have been attained by utilizing HPO, especially for ConvNets \cite{bergstra2012random}.
@@
 This was assessed by means of a short demographic questionnaire prior to the experiment.
-Additionally, the respondents were made aware of informed consent prior to the experiment in order to ensure completely voluntary participation.
+Additionally, respondents were made aware of informed consent prior to the experiment in order to ensure completely voluntary participation.
 Respondents were able to draw back from the experiment at any time.
@@
 The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
-This device is worn on the wrist.
+This device was worn on the wrist.
 Signals were communicated wirelessly.
-An ear-clip is utilized for measuring PPG, and converting this to estimate heart rate.
-Skin conductivity, or GSR, is monitored by two electrodes attached to the fingers \cite{shimmer}.
+An ear-clip was utilized for measuring PPG, and converting this to estimate heart rate.
+Skin conductivity, or GSR, was monitored by two electrodes attached to the fingers \cite{shimmer}.
 EEG measurement was conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}.
@@
 Lastly, the utilized network for the PPG modality was inspired from the network as proposed by \citeA{biswas2019cornet}.
-The nework opens with two convolutional blocks, each consisting of a convolutional layer, batch normalization layer, activation layer and closed with a max pooling layer of stride four.
+The network opens with two convolutional blocks, each consisting of a convolutional layer, a batch normalization layer, the activation layer and closed with a max pooling layer of stride four.
 The utilized activation function was the ReLU.
@@
 In order to fuse the  single-modular parts of the network, each of these is closed with one fully connected dense layer before feeding into the head network.
-This is done in order to flatten all inputs towards a lower dimensional space, such that concatenation is possible.
+This is done in order to flatten all inputs towards a lower dimensional space, such that concatenation was possible.
 The head network consists of four dense layers.
@@
 Hence, three variations with regards to size of the network as depicted in Figure \ref{fig:multiarchitecture} have been considered.
-The goal is to propose a network that is fast enough for real-time classification, whilst maintaining the highest amount of accuracy as possible.
+The goal was to propose a network that is fast enough for real-time classification, whilst maintaining the highest amount of accuracy as possible.
 
@@
 A decrease in the specified amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of required calculations.
-Doing so is likely to bring about an increase in speed.
+Doing so was expected to bring about an increase in speed.
 An overview of all three multi-modular network variations, and the amount of specified neurons/filters per layer, is provided in Table \ref{table:modelvariations}.
 Network 1 is referred to as the full network.
-The size of this network is determined from the literature.
-This implies that the size for each of the sub-parts (i.e.
-the EEG, PPG and GSR sub-parts) are roughly adopted from the research that proposed these designs initially.
+The size of this network was determined by consulting the literature.
+The sizes of each of the sub-parts, i.e.
+the EEG, PPG and GSR sub-parts, were roughly adopted from the research that proposed these designs initially.
 The size of Network 2 constitutes of 75 \% of the size of the full network.
@@
 \subsection{Model Evaluation}
-The network performances have been assessed and contrasted by means of several performance metrics.
+The performance of the networks has been assessed and contrasted by means of several performance metrics.
 When assessing performance in deep/machine-learning, it is of importance to realize that each performance metric may favor one approach over the other, simply and solely due to the mathematical nature in which both the metric and the model are defined \cite{gunawardana2009survey}.
 For this reason, we deemed it of importance to not merely evaluate performance based on one or two metrics.
-The approach we adopted is rather to consider a conglomerate of different metrics, and evaluate performance based on the whole span of these.
-The utilized metrics constitute six well known and widely utilized metrics within the fields of deep/machine-learning.
-All six metrics are constructed from the confusion matrix, the theoretical format of which is depicted as Table \ref{table:confusion}.
+The adopted approach is rather to consider a conglomerate of different metrics, and evaluate performance based on the whole span of those.
+The utilized metrics constitute six well known and widely deployed metrics in the field of deep/machine-learning.
+All six metrics are constructed from the confusion matrix.
+The theoretical format of the confusion matrix is depicted as Figure \ref{fig:confusion}.
 
@@
 \def\arraystretch{1.6}%  
-\begin{table}[h]
+\begin{figure}[h]
 \caption{Confusion Matrix}
-\label{table:confusion}
+\label{fig:confusion}
 \begin{tabular}{lll}
@@
 \end{tabular}
-\end{table}
+\end{figure}
 \egroup
@@
 
-The six metrics include the metric of accuracy, sensitivity, specificity, positive predicted value hereafter referred to as "PPV, negative predicted value hereafter referred to as "NPV" and F1.
-Table \ref{table:metrics} depicts mathematical the constitution of these performance metrics, by partly referring to confusion matrix depicted as Table \ref{table:confusion}.
+The six metrics include accuracy, sensitivity, specificity, positive predicted value hereafter referred to as "PPV, negative predicted value hereafter referred to as "NPV" and F1.
+Table \ref{table:metrics} depicts the mathematical composition of these performance metrics, by partly referring to confusion matrix depicted as Figure \ref{fig:confusion}.
 In substantive terms, accuracy can simply be understood as the proportion of correct classifications.
-Sensitivity is understood as the proportion true positives, whereas specificity is understood of as the proportion of true negatives.
+Sensitivity is understood as the proportion true positives, whereas specificity is understood as the proportion of true negatives.
 PPV reflects the proportion of predicted positives that are correctly predicted as positive.
@@
 The network that performed best across the range of these metrics was considered to be the superior performing network.
-In case of contradictory interpretations, a reference will be made back to the mathematical definition and substantive interpretation of the previously delineated performance metrics.
-Summarizing, with the described assessment approach it is aimed to gain insight into multiple dimension of network performance, resulting in a broad and complete assessment of network performance altogether.
+In case of contradictory interpretations, a reference was made back to the mathematical definition and substantive interpretation of the previously delineated performance metrics.
+To summarize, with the described assessment approach it was aimed to gain insight into multiple dimension of network performance, resulting in a broad and complete assessment of performance altogether.
 

### 2021-01-15 2.descriptives/2.create_figure.R

@@ -1,0 +1,38 @@
+######################################################
+################## 0. PREREQUISITES ##################
+######################################################
+#Setting seed
+set.seed(7931)
+
+#Loading libraries
+require(rstudioapi) #Utilized for automatically setting wd
+require(ggplot2)  #Utilized for plotting
+
+#Setting working directory
+setwd(dirname(getActiveDocumentContext()$path)) 
+
+#Loading data
+data <- readRDS("./data/data.rds")
+
+######################################################
+################# 2. DATA PREPARATION ################
+######################################################
+
+#Create ordinal age variable
+data$age_cat <- cut(data$age, breaks = c(14,19,24,29,34,39,44,49,54,59,64), labels = c("15-19","20-24","25-29","30-34","35-39","40-44","45-49","50-54","55-59","60-64"))
+
+#Drop unused factor levels
+data$gender <-  droplevels(data$gender)
+
+######################################################
+################### 3. CREATING PLOT #################
+######################################################
+
+#Creating plots
+#Histogram
+ggplot(data, aes(x = age_cat, fill=gender, color = gender))+
+  geom_histogram(alpha=0.5, stat = "count",position="identity")+
+  xlab("Age")+
+  ylab("Count")
+
+                 

### 2021-01-18 1.latex_manuscript/manuscript.tex
Changes
- Updated latex report with descriptives.
- Updated and added README files in subfolders.
- Created the `main analysis` folder.

--- 2021-01-15 1.latex_report/main.tex
@@
 \vspace*{2\baselineskip}
-\Large{\textbf{Master thesis Report}}\\
+\Large{\textbf{Masterthesis Report}}\\
 Methodology and Statistics for the Behavioral, Biomedical and Social Sciences\\
@@
 In total, 25 respondents have participated in the study.
-No additional descriptive statistics can be presented in the this section as of yet.
+Demographic information of the respondents is set forth in Table \ref{table:demographics}.
 The respondents are students recruited from the University of Twente.
@@
 Respondents were able to draw back from the experiment at any time.
+
+\bgroup
+\def\arraystretch{1.6}  
+\begin{table}[h]
+\bigskip
+\caption{Demographic Overview Respondents}
+\label{table:demographics}
+\begin{tabular}{rrrr}
+  \hline
+ & Female & Male \\ 
+  \hline
+10-19 &   7 &   0 &  \hspace{1cm} \\ 
+  20-29 &  13 &   4 &   \\ 
+  30-39 &   1 &   1  &   \\ 
+  40-49 &   0 &   8  &   \\ 
+  50-59 &   0 &   0 &   \\ 
+  60-69 &   0 &   4 &   \\ 
+   \hline
+   \bigskip
+\end{tabular}
+\end{table}
+\egroup
 
@@
 Photoplethysmography (PPG) & 100                         \\ \hline
+   \bigskip
 \end{tabular}
 \end{table}
-\bigskip
 \egroup

### 2021-01-19 3.main_analysis/singe_modular/main.py
Small changes
- Changes to README files
- Small change of structure in the 3.main_analysis subfolder
- Setup of the 3.main_analysis folder

@@ -1,0 +1,9 @@
+################### 0. Prerequisites ###################
+
+#Loading packages
+import torch
+
+
+x = torch.rand(5,3)
+print(x)
+

### 2021-01-20 3.main_analysis/multi_modular/main.py
Added some usefull packages in python scrips

@@ -1,8 +1,15 @@
+"""
+Single-modular deep neural network
+"""
+
 ################### 0. Prerequisites ###################
 
 #Loading packages
-import torch
+import torch #PyTorch deep-learning library
+from torch import nn #PyTorch additionals
+from torch import optim #PyTorch optimizer for network training
+import torch.nn.functional as F #PyTorch pre specified function library
 
-x = torch.rand(5,3)
+
+x = torch.randn(10, 10)
 print(x)
-

### 2021-01-20 3.main_analysis/singe_modular/main.py

@@ -1,9 +1,15 @@
+"""
+Single-modular deep neural network
+"""
+
 ################### 0. Prerequisites ###################
 
 #Loading packages
-import torch
+import torch #PyTorch deep-learning library
+from torch import nn #PyTorch additionals
+from torch import optim #PyTorch optimizer for network training
+import torch.nn.functional as F #PyTorch pre specified function library
 
 
-x = torch.rand(5,3)
+x = torch.randn(10, 10)
 print(x)
-

### 2021-01-21 3.singe_modular_analysis/eeg_net.py
Multiple changes (see description)
- Change of structure
- Outline neural networks first code
- Explanding readme files

@@ -1,0 +1,59 @@
+"""
+Single-modular deep neural network EEG modality.
+"""
+
+
+
+################### 0. Prerequisites ###################
+#Loading packages
+import torch #PyTorch deep-learning library
+from torch import nn, optim #PyTorch additionals and training optimizer
+import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
+
+
+
+################### 1. Loading data ###################
+#Load the training data
+train_dat = 
+train_loader = torch.utils.data.DataLoader(train_dat, batch_size = 64, shuffle = True)
+
+#Load the test data
+test_dat = 
+test_loader = torch.utils.data.Dataloader(test_dat, batch_size = 64, shuffle = True)
+
+
+
+################### 2. Define Network architecture ###################
+class Net(nn.Module):
+    def __init__(self):
+        super(Net, self).__init__()
+        #Convolutional layers
+        self.conv1 = nn.Conv1d(784, 256)
+        self.conv2 = nn.Conv1d(784, 256)
+        self.conv3 = nn.Conv1d(784, 256)
+        self.conv4 = nn.Conv1d(784, 256)
+
+        #Max pooling layer (3x1)
+        self.pool = nn.MaxPool1d(kernel_size = 3, stride = 1) 
+
+        #Batch normalization
+        self.batch1 = nn.BatchNorm1d(num_features = 1)
+        self.batch2 = nn.BatchNorm1d(num_features = 1)
+        self.batch3 = nn.BatchNorm1d(num_features = 1)
+        self.batch4 = nn.BatchNorm1d(num_features = 1)
+
+        #Dense layer
+        self.dense = nn.Linear(100,10) 
+        
+    def forward(self, x): 
+        x = self.pool(F.elu(self.batch1(self.conv1(x)))) #First block
+        x = self.pool(F.elu(self.batch2(self.conv2(x)))) #Second block
+        x = self.pool(F.elu(self.batch3(self.conv3(x)))) #Third block
+        x = self.pool(F.elu(self.batch4(self.conv4(x)))) #Fourth block
+        x = F.softmax(self.dense(x)) #Classification block
+        return x
+
+#Display network
+Net()
+
+

### 2021-01-21 3.singe_modular_analysis/ppg_net.py

@@ -1,0 +1,57 @@
+"""
+Single-modular deep neural network PPG modality
+"""
+
+
+
+################### 0. Prerequisites ###################
+#Loading packages
+import torch #PyTorch deep-learning library
+from torch import nn, optim #PyTorch additionals and training optimizer
+import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
+
+
+
+################### 1. Loading data ###################
+#Load the training data
+train_dat = 
+train_loader = torch.utils.data.DataLoader(train_dat, batch_size = 64, shuffle = True)
+
+#Load the test data
+test_dat = 
+test_loader = torch.utils.data.Dataloader(test_dat, batch_size = 64, shuffle = True)
+
+
+
+################### 2. Define Network architecture ###################
+class Net(nn.Module):
+    def __init__(self):
+        super(Net, self).__init__()
+        #Convolutional layers
+        self.conv1 = nn.Conv1d(784, 256)
+        self.conv2 = nn.Conv1d(784, 256)
+
+        #Max pooling layer (3x1)
+        self.pool = nn.MaxPool1d(kernel_size = 4, stride = 1) 
+
+        #Batch normalization
+        self.batch1 = nn.BatchNorm1d(num_features = 1)
+        self.batch2 = nn.BatchNorm1d(num_features = 1)
+
+        #LSTM layers
+        self.lstm = nn.LSTM(10)
+
+        #Dense layer
+        self.dense = nn.Linear(100,10) 
+        
+        
+    def forward(self, x): 
+        x = self.pool(F.relu(self.batch1(self.conv1(x)))) #First block
+        x = self.pool(F.relu(self.batch2(self.conv2(x)))) #Second block
+        x = self.lstm(x) #Third block
+        x = self.lstm(x) #Fourth block
+        x = F.softmax(self.dense(x)) #Classification block
+        return x
+
+#Display network
+Net()

### 2021-01-21 3.single_modular_analysis/eeg_net.py
Added data + data-readme file
Added data + data-readme file

@@ -1,5 +1,7 @@
 """
-Single-modular deep neural network EEG modality.
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description Single-modular deep neural network design for the EEG-modality.
 """
 
 
@@ -12,19 +14,8 @@ import torch.nn.functional as F #PyTorch library providing a lot of pre-specifie
 
 
 
-################### 1. Loading data ###################
-#Load the training data
-train_dat = 
-train_loader = torch.utils.data.DataLoader(train_dat, batch_size = 64, shuffle = True)
-
-#Load the test data
-test_dat = 
-test_loader = torch.utils.data.Dataloader(test_dat, batch_size = 64, shuffle = True)
-
-
-
-################### 2. Define Network architecture ###################
-class Net(nn.Module):
+################### 1. Define Network architecture ###################
+class EegNet(nn.Module):
     def __init__(self):
         super(Net, self).__init__()
         #Convolutional layers
@@ -54,6 +45,6 @@ class Net(nn.Module):
         return x
 
 #Display network
-Net()
+EegNet()
 
 

### 2021-01-21 3.single_modular_analysis/gsr_net.py

@@ -1,5 +1,7 @@
 """
-Single-modular deep neural network GSR modality
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description Single-modular deep neural network design for the GSR-modality.
 """
 
 
@@ -12,19 +14,8 @@ import torch.nn.functional as F #PyTorch library providing a lot of pre-specifie
 
 
 
-################### 1. Loading data ###################
-#Load the training data
-train_dat = 
-train_loader = torch.utils.data.DataLoader(train_dat, batch_size = 64, shuffle = True)
-
-#Load the test data
-test_dat = 
-test_loader = torch.utils.data.Dataloader(test_dat, batch_size = 64, shuffle = True)
-
-
-
-################### 2. Define Network architecture ###################
-class Net(nn.Module):
+################### 1. Define Network architecture ###################
+class GsrNet(nn.Module):
     def __init__(self):
         super(Net, self).__init__()
         #Convolutional layers
@@ -54,4 +45,4 @@ class Net(nn.Module):
         return x
 
 #Display network
-Net()
+GsrNet()

### 2021-01-21 3.single_modular_analysis/ppg_net.py

@@ -1,5 +1,7 @@
 """
-Single-modular deep neural network PPG modality
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description Single-modular deep neural network design for the PPG-modality.
 """
 
 
@@ -12,19 +14,8 @@ import torch.nn.functional as F #PyTorch library providing a lot of pre-specifie
 
 
 
-################### 1. Loading data ###################
-#Load the training data
-train_dat = 
-train_loader = torch.utils.data.DataLoader(train_dat, batch_size = 64, shuffle = True)
-
-#Load the test data
-test_dat = 
-test_loader = torch.utils.data.Dataloader(test_dat, batch_size = 64, shuffle = True)
-
-
-
-################### 2. Define Network architecture ###################
-class Net(nn.Module):
+################### 1. Define Network architecture ###################
+class PpgNet(nn.Module):
     def __init__(self):
         super(Net, self).__init__()
         #Convolutional layers
@@ -54,4 +45,4 @@ class Net(nn.Module):
         return x
 
 #Display network
-Net()
+PpgNet()

### 2021-01-21 3.single_modular_analysis/train.py

@@ -1,0 +1,23 @@
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description Loading the data and training all networks.
+"""
+
+
+
+################### 0. Prerequisites ###################
+#Loading packages
+import torch #PyTorch deep-learning library
+from torch import nn, optim #PyTorch additionals and training optimizer
+import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
+
+
+
+################### 1. Loading data ###################
+#Training data
+train_dat_eeg = 
+train_dat_ppg =
+train_dat_gsr = 
+
+train_loader = torch.utils.data.DataLoader(train_dat, batch_size = 64, shuffle = True)

### 2021-01-22 5.data/data_writer.py
added xdf to csv first part

@@ -1,6 +1,0 @@
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description Writers the data from a .xdf extenstion to a usable extension (TFRECORD).
-"""
-

### 2021-01-22 5.data/xdf_to_csv.py

@@ -1,0 +1,53 @@
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description: Creates .csv files based on the desired markers.
+"""
+
+
+
+################### 0. Prerequisites ###################
+import pyxdf
+import numpy as np
+import matplotlib.pyplot as plt
+
+#Load xdf file
+data, header = pyxdf.load_xdf('5.data/bc10/bci10 operations.xdf')
+
+print(data)
+
+for stream in data:
+    y = stream['time_series']
+
+    if isinstance(y, list):
+        # list of strings, draw one vertical line for each marker
+        for timestamp, marker in zip(stream['time_stamps'], y):
+            plt.axvline(x=timestamp)
+            print(f'Marker "{marker[0]}" @ {timestamp:.2f}s')
+    elif isinstance(y, np.ndarray):
+        # numeric data, draw as lines
+        plt.plot(stream['time_stamps'], y)
+    else:
+        raise RuntimeError('Unknown stream format')
+
+plt.show()
+
+
+
+
+
+'''
+def xdf2csv(x, output_location,
+            epoch_length = 10, 
+            data_col = "time_series", time_col = "time_stamps"):
+    """
+    FUNCTION DESCRIPTION:
+        The purpose of this function is to read in the .xdf files, and return csv files. 
+
+    FUNCTION ARGUMENTS:
+        x             The dictionary obtained from the "load_xdf" function.
+        epoc_lenght   The length of the selected data window in seconds.
+        data_col      Name of the column from which to select data. Current default is "time series".
+        time_col      Name of the column to base the selected data window on. 
+    """
+'''

### 2021-03-08 hpo/hpo.py
ds

@@ -1,651 +1,0 @@
-# -*- coding: utf-8 -*-
-"""HPO.ipynb
-
-Automatically generated by Colaboratory.
-
-Original file is located at
-    https://colab.research.google.com/drive/1sFV5wSyxqKG4ZLP76tj8p6RrVbeK1waq
-"""
-
-#!pip install optuna
-#!pip install pickle5
-import numpy as np
-import torch
-import os
-import torch 
-from torch import optim #PyTorch additionals and training optimizer
-import torch.nn as nn
-import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
-import os
-import matplotlib.pyplot as plt
-from torch.utils.data import Dataset, DataLoader, SubsetRandomSampler
-from torch import optim
-from torch.nn.utils.rnn import pad_sequence
-import numpy as np
-import optuna 
-import pickle5 as pickle
-
-"""# Dataprep"""
-
-class PytorchDataset(Dataset):
-    
-    def __init__(self, path, modality):
-        """
-        Purpose: 
-            Load pickle object and save only specified data. 
-        """
-        dat = pickle.load(open("/content/drive/MyDrive/thesis/data/bci12.pickle", "rb")) #Open pickle
-        key = "labels_"+modality #Determining right dict key
-        self.labels = dat[key] #Saving labels
-        self.dat = dat[modality] #Saving only modality of interest
-        self.modality = modality
-
-        #Determining the longest window for later use
-        lengths = []
-        for i in self.dat:
-            lengths.append(len(i))
-        longest_window = max(lengths)
-
-
-    def __len__(self):
-        """
-        Purpose: 
-            Obtain the length of the data
-        """
-        return len(self.dat)
-
-
-    def __getitem__(self, idx):
-        """
-        Purpose:
-            Iterater to select windows
-        """
-        windows = self.dat[idx]
-        labels = self.labels[idx]
-
-        return windows, labels
-    
-
-    def __PaddingLength__(self):
-        """
-        Purpose:
-            Determine padding length
-        """
-        lengths = []
-        for i in self.dat:
-            lengths.append(i.shape[0])
-        
-        return max(lengths)
-
-    def __ObtainModality__(self):
-        """
-        Purpose:
-            Print modality
-        """
-        
-        return self.modality
-
-
-#Batch transformation class
[…]

### 2021-03-08 hpo/hpo_eeg.py

@@ -1,0 +1,421 @@
+# -*- coding: utf-8 -*-
+"""hpo_eeg.ipynb
+
+Automatically generated by Colaboratory.
+
+Original file is located at
+    https://colab.research.google.com/drive/1sFV5wSyxqKG4ZLP76tj8p6RrVbeK1waq
+"""
+
+#pip install optuna
+#pip install pickle5
+import numpy as np
+import torch
+import os
+import torch 
+from torch import optim #PyTorch additionals and training optimizer
+import torch.nn as nn
+import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
+import os
+from torch.utils.data import Dataset, DataLoader, SubsetRandomSampler
+from torch import optim
+from torch.nn.utils.rnn import pad_sequence
+import numpy as np
+import optuna 
+import pickle
+
+"""# Dataprep"""
+
+class PytorchDataset(Dataset):
+    
+    def __init__(self, path, modality):
+        """
+        Purpose: 
+            Load pickle object and save only specified data. 
+        """
+        dat = pickle.load(open("pipeline/prepared_data/"+participant+".pickle", "rb")) #Open pickle
+        key = "labels_"+modality #Determining right dict key
+        self.labels = dat[key] #Saving labels
+        self.dat = dat[modality] #Saving only modality of interest
+        self.modality = modality
+
+        #Determining the longest window for later use
+        lengths = []
+        for i in self.dat:
+            lengths.append(len(i))
+        longest_window = max(lengths)
+
+
+    def __len__(self):
+        """
+        Purpose: 
+            Obtain the length of the data
+        """
+        return len(self.dat)
+
+
+    def __getitem__(self, idx):
+        """
+        Purpose:
+            Iterater to select windows
+        """
+        windows = self.dat[idx]
+        labels = self.labels[idx]
+
+        return windows, labels
+    
+
+    def __PaddingLength__(self):
+        """
+        Purpose:
+            Determine padding length
+        """
+        lengths = []
+        for i in self.dat:
+            lengths.append(i.shape[0])
+        
+        return max(lengths)
+
+    def __ObtainModality__(self):
+        """
+        Purpose:
+            Print modality
+        """
+        
+        return self.modality
+
+
+#Batch transformation class
+class BatchTransformation():
+    def __call__(self, batch):
+        """
+        Purpose:   
+            Transformation of windows per batch (padding & normalizing labels & transposing)
+        """
+
+        padding_length = self.padding_length
+        modality = self.modality
+
+        #PADDING
[…]

### 2021-03-08 manuscript/manuscript.tex

--- 2021-01-18 1.latex_manuscript/manuscript.tex
@@
 Workload needs to be recognized as a person-specific construct.
-The amount of perceived workload ushered by a given task may differ across individuals, due to how well one is able to cope with that particular task \cite{de1996measurement}.
-Hence, when referring to workload throughout this research, the person-specific nature of workload is acknowledged.
+The amount of perceived workload ushered by a given task may vary across individuals due to how well one is able to cope with that particular task \cite{de1996measurement}.
 
-A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire.
-This questionnaire inquires into the amount of perceived workload, and rests on six subjective sub-scales \cite{hart2006nasa}.
-This assessment is usually conducted post-experiment, which can in certain situations be considered undesirable.
+A commonly employed method for the assessment of person-specific workload is the well established NASA-Task Load Index questionnaire.
+This questionnaire inquires into the amount of perceived workload,  and embodies six different dimensions \cite{hart2006nasa}.
+Such an assessment is usually conducted post-experiment, which might in certain situations be undesirable.
 Consider for example an experiment in which it is aimed to assess workload of a pilot in flight.
@@
 However, only after the flight is concluded, a measurement in the form of a questionnaire can be administrated.
-In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate bias.
-A widely recognized type of bias is the observer-bias, advocating that participants in an experiment tend to overexaggerate the treatment effect, i.e.
-the amount of perceived workload in our case, when having to report it post-experiment \cite{mahtani2018catalogue}.
+In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate biases, such as for example the observer-bias, which advocates that participants in an experiment tend to overexaggerate the treatment effect, i.e.
+the amount of perceived workload, when having to report it post-experiment \cite{mahtani2018catalogue}.
 
-An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs in order to classify workload.
-Examples of such bio-signals, hereafter referred to as "modalities", include techniques as electroencephalography, eye-tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
-The advantage of such an approach is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}.
-Doing so poses the potential of yielding a rich and multifaceted classification of a mental construct such as workload.
-However most importantly, it is possible to train a separate model for each individual.
-It renders possible to cater towards the person-specific nature inherent to workload, the importance of which was pointed out by \citeA{de1996measurement}.
+An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs to predict the degree of experienced workload.
+Examples of such bio-signals, hereafter referred to as "modalities", include techniques such as electroencephalography, eye-tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
+The advantage of utilizing multiple bio-signals is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}.
+Doing so poses the potential of yielding a rich and multifaceted prediction of a mental construct such as workload.
+However most importantly, it is renders possible to train a separate model for each individual, with which can be catered towards the person-specific nature inherent to workload, the importance of which was pointed out by \citeA{de1996measurement}.
 This approach, however, comes at the cost of an increase in complexity.
-This resides in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a single classification outcome.
-
-The current research builds upon research conducted by \citeA{dolmans2020perceived}, who proposed a deep-learning approach to multi-modular classification of workload.
-The current research differs from this previous endeavor in that it utilizes different modalities, and hence different data.
-In addition, the current research investigates upon the feasibility of a real-time approach.
-Real-time in this sense constitutes the real-time classification of workload, i.e.
-the classification of workload whilst the experiment takes place.
-Taking such an approach enables the possibility to conduct a dynamic experiment, the state of which can be altered by responding towards the classified degree of workload in real-time.
-Consider a simulation with the objective of educating its partakers, such as a surgical simulation for educating surgeons-in-training.
-The learning experience of a single session could be dramatically enhanced when the state of the experiment is catered towards the individual learning process.
-For example, in case it is recognized at the start of the session that a partaker has difficulty with a specific procedure, the remainder of the session can be catered towards focusing on this specific procedure.
-By enhancing the learning experience in this manner, the effectiveness of a single session can be improved upon dramatically, entailing a substantially more efficient learning process.
+This resides in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a prediction
 
@@
 Lastly, the third technique is called photoplethysmography, hereafter referred to as "PPG".
-It is of importance to recognize that the objective of the current research is not to gain insight into the most optimal model design for each of these previously delineated modalities.
-The objective is rather to construct a framework with which real-time classification of a mental construct such as workload can be managed, and to which modalities of choice can easily be added in future research endeavors.
+The objective of the current study is to construct a framework with which real-time prediction of a mental construct such as workload can be managed, and to which modalities of choice can easily be added in future research endeavors.
 Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity.
@@
 A deep-learning approach towards the construction of a real-time multi-modular framework is adopted.
-Considering the complexity and sheer size of such a deep-neural network, an important point of attention is classification speed.
-The challenge in real-time classification with deep-learning is often not reaching adequate performance, but rather to attain adequate speed of classification.
+Considering the complexity and sheer size of such a deep-neural network, an important point of attention is prediction speed.
+The challenge in real-time prediction with deep-learning is often not reaching adequate performance, but rather to attain adequate speed of prediction.
 Deep neural networks easily constitute thousands of calculations to be made simultaneously, which is even more true for a multi-modular approach such as the current.
-In order for real-time classification to work, classification cannot take too long, for otherwise it is not real-time anymore and the previously delineated benefit of a real-time approach dissipates.
-As a consequence, multiple networks are considered and contrasted in terms of performance and their ability to classify in real-time.
+In order for real-time prediction to work, prediction cannot take too long, for otherwise it is not real-time anymore and the previously delineated benefit of a real-time approach dissipates.
+As a consequence, multiple networks are considered and contrasted in terms of performance and their ability to predict in real-time.
 Firstly, for each of the three modalities individually, a single-modular network is constructed.
-Secondly, a multi-modular network is architected combining all three modalities.
-Additionally, several variations on this multi-modular framework are considered and contrasted.
-These networks are specified to vary in size, i.e.
-the amount of specified neurons and filters.
-These networks were created in Python, by utilizing the deep/machine-learning toolbox Pytorch \cite{paszke2017automatic}
+and assessed.
+Secondly, a multi-modular network is architected combining all three modalities into one.
+These networks were created in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}
 
@@
 \subsubsection{Respondents}
-In total, 25 respondents have participated in the study.
+In total, 38 respondents have participated in the study.
 Demographic information of the respondents is set forth in Table \ref{table:demographics}.
@@
   50-59 &   0 &   0 &   \\ 
-  60-69 &   0 &   4 &   \\ 
-   \hline
-   \bigskip
+  60-69 &   0 &   4 &   \\ \hline
+  Total    &  21 &  17 & \\ \hline
 \end{tabular}

### 2021-03-10 hpo/combine.py
small structure change

@@ -1,0 +1,17 @@
+import pickle
+
+participants = ["bci10", "bci12", "bci13", "bci17", "bci21", "bci22",
+                "bci23", "bci24", "bci26", "bci27", "bci28", "bci29", "bci30", 
+                "bci31", "bci32", "bci33", "bci34", "bci35", "bci36", "bci37", 
+                "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
+
+modality = "EEG"
+
+combination = {}
+
+for i in participants:
+    x = pickle.load(open("hpo/hyper_parameters/"+modality+"_"+i+".pickle", "rb"))
+    combination[i] = x
+
+with open("hpo/hyper_parameters/"+modality+"_"+params+".pickle", 'wb') as handle: #Save as pickle
+    pickle.dump(combination, handle, protocol=pickle.HIGHEST_PROTOCOL)

### 2021-03-10 hpo/hpo_eeg.py

@@ -33,7 +33,7 @@ class PytorchDataset(Dataset):
         Purpose: 
             Load pickle object and save only specified data. 
         """
-        dat = pickle.load(open("pipeline/prepared_data/"+participant+".pickle", "rb")) #Open pickle
+        dat = pickle.load(open("/floyd/input/data/"+participant+".pickle", "rb")) #Open pickle
         key = "labels_"+modality #Determining right dict key
         self.labels = dat[key] #Saving labels
         self.dat = dat[modality] #Saving only modality of interest
@@ -378,8 +378,8 @@ participants = [
                 "bci31", "bci32", "bci33", "bci34", "bci35", "bci36", "bci37", 
                 "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
 
-ntrials = 100
-epochs = 80
+ntrials = 1
+epochs = 1
 batch_size = 10
 np.random.seed(3791)
 torch.manual_seed(3791)
@@ -416,6 +416,6 @@ if __name__ == "__main__":
         for key, value in trial.params.items():
             print("    {}: {}".format(key, value))
 
-        with open("/Users/bart-janb/Documents/GitHub/Masterthesis/hpo/hyperparams"+modality+"_"+participant+".pickle", 'wb') as handle: #Save as pickle
+        with open(modality+"_"+participant+".pickle", 'wb') as handle: #Save as pickle
             pickle.dump(study.best_trial, handle, protocol=pickle.HIGHEST_PROTOCOL)
 

### 2021-03-10 pytorch/old stuff/networks copy.py

@@ -63,9 +63,9 @@ class EEGNet(nn.Module):
 
         return x
 
-class PPGnet(nn.Module):
+class PPGnew(nn.Module):
     def __init__(self, tensor_length, drop = 0.25):
-        super(PPGnet, self).__init__()
+        super(PPGnew, self).__init__()
 
         self.drop = drop
         self.tensor_length = tensor_length
@@ -111,9 +111,9 @@ class PPGnet(nn.Module):
 
         return x
 
-class GSRnet(nn.Module):
+class GSRnew(nn.Module):
     def __init__(self, tensor_length, drop = 0.25):
-        super(GSRnet, self).__init__()
+        super(GSRnew, self).__init__()
 
         self.drop = drop
         self.tensor_length = tensor_length
@@ -158,6 +158,146 @@ class GSRnet(nn.Module):
         x = self.dense2(x)
 
         return x
+
+#Display network
+#eeg_net = EegNet()
+#summary(eeg_net, (1000,1))
+
+################### PPG Net ###################
+class PPGNet(nn.Module):
+
+    def __init__(self, filters = 32, hidden_dim = 64, n_layers =2, drop = 0.25):
+        super(PPGNet, self).__init__()
+        
+        self.ip_dim = filters
+        self.hidden_dim = hidden_dim
+        self.n_layers = n_layers
+        self.drop = drop
+
+        #Convolutional layers
+        self.conv1 = nn.Conv1d(in_channels =  1, out_channels = filters, kernel_size = 3, padding=1)
+        self.conv2 = nn.Conv1d(in_channels = filters, out_channels = filters, kernel_size = 3, padding=1)
+
+        #Max pooling layer (4)
+        self.pool = nn.MaxPool1d(kernel_size = 4, stride = 4) 
+
+        #Batch normalization
+        self.batch1 = nn.BatchNorm1d(num_features = filters)
+        self.batch2 = nn.BatchNorm1d(num_features = filters)
+        self.batch3 = nn.BatchNorm1d(num_features = int(hidden_dim/4))
+
+        #Dense & classification layer 
+        self.fc1 = nn.Linear(hidden_dim, int(hidden_dim/4))
+        self.fc2 = nn.Linear(int(hidden_dim/4), 1)
+
+
+        #LSTM layer
+        self.lstm = nn.LSTM(input_size = filters, 
+                                hidden_size = hidden_dim, 
+                                num_layers = n_layers, 
+                                dropout = drop,
+                                batch_first= True)
+    
[…]

### 2021-03-10 pytorch/train_single.py

@@ -1,0 +1,325 @@
+#!/usr/bin/env python
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description Loading the data and training all networks.
+"""
+
+
+###########################################################################################
+###################################### 0. Prerequisites ###################################
+###########################################################################################
+#Loading packages
+
+import torch 
+from torch import optim #PyTorch additionals and training optimizer
+import torch.nn as nn
+import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
+import os
+import pickle
+import matplotlib.pyplot as plt
+from torch.utils.data import Dataset, DataLoader, SubsetRandomSampler
+from torch import optim
+from torch.nn.utils.rnn import pad_sequence
+import numpy as np
+
+try: #Importing network
+    import dataprep, networks
+except ModuleNotFoundError:
+    wd = os.getcwd()
+    print("Error: please make sure that working directory is set as '~/Masterthesis'")
+    print("Current working directory is:", wd)
+
+
+def TrainLoop(participant, modality, drop, epochs, trainortest, batch_size):
+    
+    ###########################################################################################
+    ########################## 1. Create PyTorch dataset & Loader(s) ##########################
+    ###########################################################################################
+    #Create PyTorch dataset definition class
+    
+    path = "pipeline/prepared_data/"+participant+".pickle"
+    pydata =  dataprep.PytorchDataset(path = path,       #Creating PyTorch dataset
+                                      modality = modality)
+
+    padding_length = dataprep.PytorchDataset.__PaddingLength__(pydata) #Determining the longest window for later use
+    dataprep.BatchTransformation.transfer([padding_length, modality]) #Transfer max padding length & modality vars to BatchTransfor class
+               
+               
+    #Making splits
+    test_split = .1
+    validation_split = .1
+
+    ################
+    ## TEST SPLIT ##
+    ################    
+    indices_traintest = list(range(len(pydata.dat))) #Create list of indices
+    test_indices = indices_traintest[::int(test_split*100)]  
+    train_val_indices = [x for x in indices_traintest if x not in test_indices]
+
+    val_indices = train_val_indices[::int(validation_split*100)]
+    train_indices = [x for x in train_val_indices if x not in val_indices]
+   
+  
+    traindata = [pydata[i] for i in train_indices]
+    valdata = [pydata[i] for i in val_indices]
[…]

### 2021-03-31 hpo/combine.py
Clean-up
- Some code cleaning
- Some restructuring of the repo
- Some extra code commenting

@@ -1,18 +1,29 @@
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description This file combines all files resulting from the hpo search into four pickle file. 
+"""
+
+#Importing packages
 import pickle
 
+#Define participants
 participants = ["bci10", "bci12", "bci13", "bci17", "bci21", "bci22",
                 "bci23", "bci24", "bci26", "bci27", "bci28", "bci29", "bci30", 
                 "bci31", "bci32", "bci33", "bci34", "bci35", "bci36", "bci37", 
                 "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
 
+#Define modalities
 modalities = ["EEG","PPG","GSR"]
 
-
+#Combine hyper-parameters
 for modality in modalities:
     combination = {}
     for i in participants:
         x = pickle.load(open("hpo/hyper_parameters/"+modality+"_"+i+".pickle", "rb"))
         combination[i] = x.params
 
-    with open("pytorch/optimized_parameters/"+modality+".pickle", 'wb') as handle: #Save as pickle
+    with open("hpo/hyper_parameters_combined/"+modality+".pickle", 'wb') as handle: #Save as pickle
         pickle.dump(combination, handle, protocol=pickle.HIGHEST_PROTOCOL)
+
+

### 2021-03-31 hpo/hpo_eeg.py

@@ -1,14 +1,10 @@
-# -*- coding: utf-8 -*-
-"""hpo_eeg.ipynb
-
-Automatically generated by Colaboratory.
-
-Original file is located at
-    https://colab.research.google.com/drive/1sFV5wSyxqKG4ZLP76tj8p6RrVbeK1waq
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description This file conducts the hyper-paramater optimization for sigle-modular EEG networks on GPU.
+BEWARE! Running this code on a machine with NVIDIA GPU is highly recommended. 
 """
 
-#pip install optuna
-#pip install pickle5
 import numpy as np
 import torch
 import os
@@ -24,8 +20,9 @@ import numpy as np
 import optuna 
 import pickle
 
-"""# Dataprep"""
-
+#############################################################################################
+##################################### Data preperation ######################################
+#############################################################################################
 class PytorchDataset(Dataset):
     
     def __init__(self, path, modality):
@@ -33,7 +30,7 @@ class PytorchDataset(Dataset):
         Purpose: 
             Load pickle object and save only specified data. 
         """
-        dat = pickle.load(open("/floyd/input/data/"+participant+".pickle", "rb")) #Open pickle
+        dat = pickle.load(open("...SPECIFY THE LOCATION OF THE DATA HERE..."+participant+".pickle", "rb")) #Open pickle
         key = "labels_"+modality #Determining right dict key
         self.labels = dat[key] #Saving labels
         self.dat = dat[modality] #Saving only modality of interest
@@ -120,23 +117,9 @@ class BatchTransformation():
         BatchTransformation.padding_length = self[0]
         BatchTransformation.modality = self[1]
 
-"""# Networks"""
-
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description Single-modular deep neural network design for the EEG-modality.
-"""
-
-################### 0. Prerequisites ###################
-#Loading packages
-import torch #PyTorch deep-learning library
-from torch import optim #PyTorch additionals and training optimizer
-import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
-import torch.nn as nn
-from torchsummary import summary
-
-################### EEG Net ###################
+#############################################################################################
+######################################### Network ###########################################
+#############################################################################################
 class EEGNet(nn.Module):
     def __init__(self, tensor_length, out_features, drop):
         super(EEGNet, self).__init__()
[…]

### 2021-03-31 hpo/hpo_gsr.py

@@ -1,14 +1,10 @@
-# -*- coding: utf-8 -*-
-"""hpo_ppg.ipynb
-
-Automatically generated by Colaboratory.
-
-Original file is located at
-    https://colab.research.google.com/drive/1uJByrJAe7iu4MaoGMTpZLVMLcmYfIN6S
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description This file conducts the hyper-paramater optimization for sigle-modular GSR networks on GPU.
+BEWARE! Running this code on a machine with NVIDIA GPU is highly recommended. 
 """
 
-#!pip install optuna
-#!pip install pickle5
 import numpy as np
 import torch
 import os
@@ -24,8 +20,9 @@ import numpy as np
 import optuna 
 import pickle5 as pickle
 
-"""# Dataprep"""
-
+#############################################################################################
+##################################### Data preperation ######################################
+#############################################################################################
 class PytorchDataset(Dataset):
     
     def __init__(self, path, modality):
@@ -33,7 +30,7 @@ class PytorchDataset(Dataset):
         Purpose: 
             Load pickle object and save only specified data. 
         """
-        dat = pickle.load(open("/content/drive/MyDrive/thesis/data/"+participant+".pickle", "rb")) #Open pickle
+        dat = pickle.load(open("...SPECIFY THE LOCATION OF THE DATA HERE..."+participant+".pickle", "rb")) #Open pickle
         key = "labels_"+modality #Determining right dict key
         self.labels = dat[key] #Saving labels
         self.dat = dat[modality] #Saving only modality of interest
@@ -120,11 +117,12 @@ class BatchTransformation():
         BatchTransformation.padding_length = self[0]
         BatchTransformation.modality = self[1]
 
-"""# Networks"""
-
-class PPGNet(nn.Module):
+#############################################################################################
+######################################### Network ###########################################
+#############################################################################################
+class GSRNet(nn.Module):
     def __init__(self, tensor_length, out_features, drop):
-        super(PPGNet, self).__init__()
+        super(GSRNet, self).__init__()
 
         self.drop = drop
         self.tensor_length = tensor_length
@@ -170,20 +168,9 @@ class PPGNet(nn.Module):
 
         return x
 
-"""# Train"""
-
-#!/usr/bin/env python
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description Loading the data and training all networks.
-"""
-
-
[…]

### 2021-03-31 hpo/hpo_multi.py

@@ -1,14 +1,10 @@
-# -*- coding: utf-8 -*-
-"""hpo_multi.ipynb
-
-Automatically generated by Colaboratory.
-
-Original file is located at
-    https://colab.research.google.com/drive/1PsSXXPvB7VRytEYDM9fEsZRcL4kDgRPu
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description This file conducts the hyper-paramater optimization for multi-modular networks on GPU.
+BEWARE! Running this code on a machine with NVIDIA GPU is highly recommended. 
 """
 
-#!pip install optuna
-#!pip install pickle5
 import numpy as np
 import torch
 import os
@@ -25,8 +21,9 @@ import optuna
 import pickle5 as pickle
 import math
 
-"""# Dataprep"""
-
+#############################################################################################
+##################################### Data preperation ######################################
+#############################################################################################
 class PytorchDataset(Dataset):
     
     def __init__(self, participant, modality):
@@ -34,7 +31,7 @@ class PytorchDataset(Dataset):
         Purpose: 
             Load pickle object and save only specified data. 
         """
-        dat = pickle.load(open("/content/drive/MyDrive/thesis/data/"+participant+".pickle", "rb")) #Open pickle
+        dat = pickle.load(open("...SPECIFY THE LOCATION OF THE DATA HERE..."+participant+".pickle", "rb")) #Open pickle
         key = "labels_"+modality #Determining right dict key
         self.labels = dat[key] #Saving labels
         self.dat = dat[modality] #Saving only modality of interest
@@ -76,7 +73,6 @@ class PytorchDataset(Dataset):
 
 
 
-#Batch transformation class
 class BatchTransformationEEG():
     def __call__(self, batch):
         """
@@ -108,6 +104,7 @@ class BatchTransformationEEG():
             in the __call__ function.
         """
         BatchTransformationEEG.padding_length = self[0]
+
 
 
 class BatchTransformationPPG():
@@ -189,15 +186,10 @@ def PaddingLength(data):
     
     return max(lengths)
 
-"""# Networks"""
 
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description Single-modular deep neural network design for the EEG-modality.
-"""
-
-################### EEG Net ###################
+#############################################################################################
+######################################## Networks ###########################################
[…]

### 2021-03-31 pipeline/main.py

@@ -1,4 +1,3 @@
-#!/usr/bin/env python
 """
 @Author: Bart-Jan Boverhof
 @Description: Central script with which data is read, windows are created and windows are constructed.

### 2021-03-31 pipeline/transformer.py

@@ -3,6 +3,7 @@
 @Modified by: Bart-Jan Boverhof
 @Description: Creates pandas dataframes based on the desired markers.
 """
+
 #### Prerequisites ####
 #Importing packages
 import pyxdf

### 2021-03-31 pytorch/loop_multi.py

@@ -2,15 +2,13 @@
 """
 @Author: Bart-Jan Boverhof
 @Last Modified by: Bart-Jan Boverhof
-@Description Loading the data and training all networks.
+@Description This file contains the central training-loop function for training the multi-modular network.
 """
-
 
 ###########################################################################################
 ###################################### 0. Prerequisites ###################################
 ###########################################################################################
 #Loading packages
-
 import torch 
 from torch import optim #PyTorch additionals and training optimizer
 import torch.nn as nn
@@ -31,8 +29,17 @@ except ModuleNotFoundError:
     print("Current working directory is:", wd)
 
 
-def TrainLoop(participant, drop, epochs, trainortest, batch_size):
-    
+def MultiTrainLoop(participant, drop, epochs, trainortest, batch_size):
+    """
+    Purpose:
+        Central training loop function for the multi-modal network. 
+    Arguments:
+        participant: particpant to select for training.
+        modality: network variation to train (EEG / PPG / GSR / Multi) 
+        batch_size: utilized batch size for training
+        hpo: objtect containing optimized hyperparamaters to utilize for training
+        trainortest: whether to train, or test the already trained model at hand
+    """
     ###########################################################################################
     ########################## 1. Create PyTorch dataset & Loader(s) ##########################
     ###########################################################################################

### 2021-03-31 pytorch/networks.py

@@ -1,10 +1,8 @@
 """
 @Author: Bart-Jan Boverhof
 @Last Modified by: Bart-Jan Boverhof
-@Description Single-modular deep neural network design for the EEG-modality.
+@Description This file contains utilized all deep-neural network definitions.
 """
-
-
 
 ################### 0. Prerequisites ###################
 #Loading packages
@@ -17,7 +15,7 @@ import math
 
 ################### EEG Net ###################
 class EEGNet(nn.Module):
-    def __init__(self, tensor_length, drop = 0.25, multi = False):
+    def __init__(self, tensor_length, drop, multi, n_units):
         super(EEGNet, self).__init__()
 
         self.multi = multi
@@ -45,8 +43,8 @@ class EEGNet(nn.Module):
         self.batch4 = nn.BatchNorm1d(num_features = 200)
 
         #Dense layer
-        self.dense1 = nn.Linear(dense_input, int(dense_input/8)) 
-        self.dense2 = nn.Linear(int(dense_input/8), 1) 
+        self.dense1 = nn.Linear(dense_input, n_units) 
+        self.dense2 = nn.Linear(n_units, 1) 
         self.dense3 = nn.Linear(dense_input, dense_input) 
 
         #Dropout layer
@@ -71,7 +69,7 @@ class EEGNet(nn.Module):
         return x
 
 class PPGNet(nn.Module):
-    def __init__(self, tensor_length, drop = 0.25, multi = False):
+    def __init__(self, tensor_length, drop , multi, n_units):
         super(PPGNet, self).__init__()
 
         self.multi = multi
@@ -99,8 +97,8 @@ class PPGNet(nn.Module):
         self.batch4 = nn.BatchNorm1d(num_features = 128)
 
         #Dense layer
-        self.dense1 = nn.Linear(dense_input, int(dense_input/8)) 
-        self.dense2 = nn.Linear(int(dense_input/8), 1) 
+        self.dense1 = nn.Linear(dense_input, n_units) 
+        self.dense2 = nn.Linear(n_units, 1) 
         self.dense3 = nn.Linear(dense_input, dense_input) 
 
         #Dropout layer
@@ -124,8 +122,10 @@ class PPGNet(nn.Module):
 
         return x
 
+
+
 class GSRNet(nn.Module):
-    def __init__(self, tensor_length, drop = 0.25, multi = False):
+    def __init__(self, tensor_length, drop, multi, n_units):
[…]

### 2021-03-31 pytorch/old stuff/blaaa/networks copy.py

@@ -1,252 +1,0 @@
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description Single-modular deep neural network design for the EEG-modality.
-"""
-
-
-
-################### 0. Prerequisites ###################
-#Loading packages
-import torch #PyTorch deep-learning library
-from torch import optim #PyTorch additionals and training optimizer
-import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
-import torch.nn as nn
-from torchsummary import summary
-
-################### EEG Net ###################
-class EEGNet(nn.Module):
-    def __init__(self, tensor_length, drop = 0.25, multi = False):
-        super(EEGNet, self).__init__()
-
-        self.multi = multi
-        self.drop = drop
-
-        foo = int(tensor_length /3)
-        foo = int(foo /3)         
-        foo = int(foo /3)
-        foo = int(foo /3)
-        dense_input = 200*foo
-
-        #Convolutional layers
-        self.conv1 = nn.Conv1d(in_channels = 4, out_channels = 25, kernel_size = 3, padding=1)
-        self.conv2 = nn.Conv1d(in_channels = 25, out_channels = 50, kernel_size = 3, padding=1)
-        self.conv3 = nn.Conv1d(in_channels = 50, out_channels = 100, kernel_size = 3, padding=1)
-        self.conv4 = nn.Conv1d(in_channels = 100, out_channels = 200, kernel_size = 3, padding=1)
-
-        #Max pooling layer (3x1)
-        self.pool = nn.MaxPool1d(kernel_size = 3, stride = 3) 
-
-        #Batch normalization
-        self.batch1 = nn.BatchNorm1d(num_features = 25)
-        self.batch2 = nn.BatchNorm1d(num_features = 50)
-        self.batch3 = nn.BatchNorm1d(num_features = 100)
-        self.batch4 = nn.BatchNorm1d(num_features = 200)
-
-        #Dense layer
-        self.dense1 = nn.Linear(dense_input, int(dense_input/8)) 
-        self.dense2 = nn.Linear(int(dense_input/8), 1) 
-        self.dense3 = nn.Linear(dense_input, dense_input) 
-
-        #Dropout layer
-        self.dropout = nn.Dropout(drop)
-
-        
-    def forward(self, x): 
-        x = self.pool(F.elu(self.batch1(self.conv1(x)))) #First block
[…]

### 2021-03-31 pytorch/old stuff/networks copy.py

@@ -1,330 +1,0 @@
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description Single-modular deep neural network design for the EEG-modality.
-"""
-
-
-
-################### 0. Prerequisites ###################
-#Loading packages
-import torch #PyTorch deep-learning library
-from torch import optim #PyTorch additionals and training optimizer
-import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
-import torch.nn as nn
-from torchsummary import summary
-
-################### EEG Net ###################
-class EEGNet(nn.Module):
-    def __init__(self, tensor_length, drop = 0.25):
-        super(EEGNet, self).__init__()
-
-        self.drop = drop
-        self.tensor_length = tensor_length
-        foo = int(tensor_length /3)
-        foo = int(foo /3)         
-        foo = int(foo /3)
-        foo = int(foo /3)
-        dense_input = 200*foo
-
-        #Convolutional layers
-        self.conv1 = nn.Conv1d(in_channels = 4, out_channels = 25, kernel_size = 3, padding=1)
-        self.conv2 = nn.Conv1d(in_channels = 25, out_channels = 50, kernel_size = 3, padding=1)
-        self.conv3 = nn.Conv1d(in_channels = 50, out_channels = 100, kernel_size = 3, padding=1)
-        self.conv4 = nn.Conv1d(in_channels = 100, out_channels = 200, kernel_size = 3, padding=1)
-
-        #Max pooling layer (3x1)
-        self.pool = nn.MaxPool1d(kernel_size = 3, stride = 3) 
-
-        #Batch normalization
-        self.batch1 = nn.BatchNorm1d(num_features = 25)
-        self.batch2 = nn.BatchNorm1d(num_features = 50)
-        self.batch3 = nn.BatchNorm1d(num_features = 100)
-        self.batch4 = nn.BatchNorm1d(num_features = 200)
-
-        #Dense layer
-        self.dense1 = nn.Linear(dense_input, int(dense_input/8)) 
-        self.dense2 = nn.Linear(int(dense_input/8), 1) 
-
-        #Dropout layer
-        self.dropout = nn.Dropout(drop)
-
-        
-    def forward(self, x): 
-        x = self.pool(F.elu(self.batch1(self.conv1(x)))) #First block
-        x = self.pool(F.elu(self.batch2(self.conv2(x)))) #Second block
[…]

### 2021-03-31 pytorch/old stuff/train_cross_val.py

@@ -1,279 +1,0 @@
-#!/usr/bin/env python
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description Loading the data and training all networks.
-"""
-
-
-###########################################################################################
-###################################### 0. Prerequisites ###################################
-###########################################################################################
-#Loading packages
-
-import torch 
-from torch import optim #PyTorch additionals and training optimizer
-import torch.nn as nn
-import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
-import os
-import pickle
-import matplotlib.pyplot as plt
-from torch.utils.data import Dataset, DataLoader, SubsetRandomSampler
-from torch import optim
-from torch.nn.utils.rnn import pad_sequence
-import numpy as np
-from sklearn.model_selection import KFold
-
-
-try: #Importing network
-    import dataprep, networks
-except ModuleNotFoundError:
-    wd = os.getcwd()
-    print("Error: please make sure that working directory is set as '~/Masterthesis'")
-    print("Current working directory is:", wd)
-
-
-def TrainLoop(participant, modality, filters, hidden_dim, n_layers, drop, epochs, trainortest):
-    
-    ###########################################################################################
-    ########################## 1. Create PyTorch dataset & Loader(s) ##########################
-    ###########################################################################################
-    #Create PyTorch dataset definition class
-    path = "pipeline/prepared_data/"+participant+"/data.pickle"
-    pydata =  dataprep.PytorchDataset(path = path,       #Creating PyTorch dataset
-                                      modality = modality)
-
-    padding_length = dataprep.PytorchDataset.__PaddingLength__(pydata) #Determining the longest window for later use
-    dataprep.BatchTransformation.transfer([padding_length, modality]) #Transfer max padding length & modality vars to BatchTransfor class
-               
-               
-    #Making splits
-    batch_size = 10
-    test_split = .1
-
-    ################
-    ## TEST SPLIT ##
-    ################ 
-    
-    indices = list(range(len(pydata.dat))) #Create list of indices
-    train_test_split = int(np.floor(test_split * len(pydata))) #Calculate number of windows to use for train/test
-    np.random.shuffle(indices) #Shuffle indices.
-    train_indices, test_indices = indices[train_test_split:], indices[:train_test_split] #Splitted indices.
-
-    test_sampler = SubsetRandomSampler(test_indices) #Train sampler    
-    testloader = torch.utils.data.DataLoader(pydata, #Test loader 
[…]

### 2021-03-31 pytorch/old stuff/tryout.py

@@ -1,263 +1,0 @@
-#!/usr/bin/env python
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description Loading the data and training all networks.
-"""
-
-
-###########################################################################################
-###################################### 0. Prerequisites ###################################
-###########################################################################################
-#Loading packages
-
-import torch 
-from torch import optim #PyTorch additionals and training optimizer
-import torch.nn as nn
-import torch.nn.functional as F #PyTorch library providing a lot of pre-specified functions
-import os
-import pickle
-import matplotlib.pyplot as plt
-from torch.utils.data import Dataset, DataLoader, SubsetRandomSampler
-from torch import optim
-from torch.nn.utils.rnn import pad_sequence
-import numpy as np
-
-try: #Importing network
-    import dataprep, networks
-except ModuleNotFoundError:
-    wd = os.getcwd()
-    print("Error: please make sure that working directory is set as '~/Masterthesis'")
-    print("Current working directory is:", wd)
-
-
-def TrainLoop(participant, modality, drop, epochs, trainortest, batch_size):
-    
-    ###########################################################################################
-    ########################## 1. Create PyTorch dataset & Loader(s) ##########################
-    ###########################################################################################
-    #Create PyTorch dataset definition class
-    path = "pipeline/prepared_data/"+participant+".pickle"
-    pydata =  dataprep.PytorchDataset(path = path,       #Creating PyTorch dataset
-                                      modality = modality)
-
-    padding_length = dataprep.PytorchDataset.__PaddingLength__(pydata) #Determining the longest window for later use
-    dataprep.BatchTransformation.transfer([padding_length, modality]) #Transfer max padding length & modality vars to BatchTransfor class
-               
-               
-    #Making splits
-    test_split = .1
-    validation_split = .1
-
-    ################
-    ## TEST SPLIT ##
-    ################    
-    """
-    indices_traintest = list(range(len(pydata.dat))) #Create list of indices
-    test_indices = indices_traintest[::int(test_split*100)]  
-    train_val_indices = [x for x in indices_traintest if x not in test_indices]
-
-    val_indices = train_val_indices[::int(validation_split*100)]
-    train_indices = [x for x in train_val_indices if x not in val_indices]
-   
-  
-    traindata = [pydata[i] for i in train_indices]
-    valdata = [pydata[i] for i in val_indices]
[…]

### 2021-03-31 pytorch/train.py

@@ -1,58 +1,76 @@
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description: This file contains the code from which all already trained networks networks are tested
+"""
+
+#############################################################################################
+######################################### Prerequisites #####################################
+#############################################################################################
+#Importing packages
 import numpy as np
 import torch
 import os
+import pickle
 
-try: #Importing network
-    import train_single, train_multi, dataprep
+#Import local files
+try:
+    import loop_single, loop_multi, dataprep
 except ModuleNotFoundError:
     wd = os.getcwd()
     print("Error: please make sure that working directory is set as '~/Masterthesis'.")
     print("Current working directory is:", wd)
 
-
+"""
+#Included participants
 participants = ["bci10", "bci12", "bci13", "bci17", "bci21", "bci22",
                 "bci23", "bci24", "bci26", "bci27", "bci28", "bci29", "bci30", 
                 "bci31", "bci32", "bci33", "bci34", "bci35", "bci36", "bci37", 
                 "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
+"""
 
-modalities = ["EEG","PPG","GSR"]
+#Modalities
+modalities = ["PPG","GSR","EEG"]
+
+#Included participants
+participants = ["bci35", "bci36", "bci37", 
+                "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
+
 
 
 #############################################################################################
+################################ Train Single-modality networks #############################
 #############################################################################################
-################################### Single-modality networks ################################
-#############################################################################################
-#############################################################################################
-
-drop = 0.25
-epochs = 30
-batch_size = 10
-trainortest = "train"
 np.random.seed(3791)
 torch.manual_seed(3791)
+torch.cuda.manual_seed(3791)
+
+epochs = 400
+batch_size = 10
+
+
+for modality in modalities:
+
+    #Select correct hpo file
+    hpo = pickle.load(open("hpo/hyper_parameters/"+modality+".pickle", "rb"))   
+    
+    for i in participants:
+
+        loop_single.SingleTrainLoop(participant = i, modality = modality,
+                        batch_size = batch_size, hpo = hpo,
+                        epochs = epochs, trainortest = "train")
+
 """
-for i in participants:
-    for modality in modalities:
-
-        train_single.TrainLoop(participant = i, modality = modality,
[…]

### 2021-04-01 pytorch/networks.py
Small bug fixes train scripts

@@ -42,13 +42,15 @@ class EEGNet(nn.Module):
         self.batch3 = nn.BatchNorm1d(num_features = 100)
         self.batch4 = nn.BatchNorm1d(num_features = 200)
 
-        #Dense layer
-        self.dense1 = nn.Linear(dense_input, n_units) 
-        self.dense2 = nn.Linear(n_units, 1) 
-        self.dense3 = nn.Linear(dense_input, dense_input) 
+        #Dense and dropout layers
+        if multi == False:
+            self.dense1 = nn.Linear(dense_input, n_units) 
+            self.dense2 = nn.Linear(n_units, 1) 
+            self.dropout = nn.Dropout(drop)
 
-        #Dropout layer
-        self.dropout = nn.Dropout(drop)
+        elif multi == True:
+            self.dense3 = nn.Linear(dense_input, dense_input) 
+
 
         
     def forward(self, x): 
@@ -96,14 +98,14 @@ class PPGNet(nn.Module):
         self.batch3 = nn.BatchNorm1d(num_features = 64)
         self.batch4 = nn.BatchNorm1d(num_features = 128)
 
-        #Dense layer
-        self.dense1 = nn.Linear(dense_input, n_units) 
-        self.dense2 = nn.Linear(n_units, 1) 
-        self.dense3 = nn.Linear(dense_input, dense_input) 
+        #Dense and dropout layers
+        if multi == False:
+            self.dense1 = nn.Linear(dense_input, n_units) 
+            self.dense2 = nn.Linear(n_units, 1) 
+            self.dropout = nn.Dropout(drop)
 
-        #Dropout layer
-        self.dropout = nn.Dropout(drop)
-
+        elif multi == True:
+            self.dense3 = nn.Linear(dense_input, dense_input) 
         
     def forward(self, x): 
         x = self.pool(F.elu(self.batch1(self.conv1(x)))) #First block
@@ -152,13 +154,14 @@ class GSRNet(nn.Module):
         self.batch3 = nn.BatchNorm1d(num_features = 64)
         self.batch4 = nn.BatchNorm1d(num_features = 128)
 
-        #Dense layer
-        self.dense1 = nn.Linear(dense_input, n_units) 
-        self.dense2 = nn.Linear(n_units, 1) 
-        self.dense3 = nn.Linear(dense_input, dense_input) 
+        #Dense and dropout layers
+        if multi == False:
[…]

### 2021-04-01 pytorch/train.py

@@ -27,15 +27,15 @@ participants = ["bci10", "bci12", "bci13", "bci17", "bci21", "bci22",
                 "bci23", "bci24", "bci26", "bci27", "bci28", "bci29", "bci30", 
                 "bci31", "bci32", "bci33", "bci34", "bci35", "bci36", "bci37", 
                 "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
-"""
 
 #Modalities
 modalities = ["PPG","GSR","EEG"]
+"""
 
 #Included participants
-participants = ["bci35", "bci36", "bci37", 
+participants = ["bci10", "bci35", "bci36", "bci37", 
                 "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
-
+modalities = ["GSR"]
 
 
 #############################################################################################
@@ -60,16 +60,22 @@ for modality in modalities:
                         batch_size = batch_size, hpo = hpo,
                         epochs = epochs, trainortest = "train")
 
-"""
+
 #############################################################################################
 #############################################################################################
 ################################### Multi-modality networks #################################
 #############################################################################################
 #############################################################################################
-loop_muilti.MultiTrainLoop(participant = "bci10",
-                drop = drop, batch_size = batch_size, 
-                epochs = epochs, trainortest = trainortest)
-
+"""
+for i in participants:
+    
+    #Select correct hpo file
+    hpo = pickle.load(open("hpo/hyper_parameters/multi.pickle", "rb"))   
+    
+    #Loop
+    loop_multi.MultiTrainLoop(participant = i,
+                    batch_size = batch_size, hpo = hpo,
+                    epochs = epochs, trainortest = "train")
 """
 
 

### 2021-04-01 manuscript/manuscript.tex

@@
 
+\section{Results}
+
+\newpage
+\section{Limitations}
+
+\begin{itemize}
+  \item  More HPO could have been done, to get even better performing models but we had limited computatioal power.   
+  \item This approach costs a lot of computational power to both train and do HPO. Especially since person-specific models are fitted. This upholds mostly for the multi-modal network.
+  \item Due to the sheer size of the trained model and the fact that models are trained person specific, storage sizes of the models are huge.
+This could be unpractical.
+This upholds mostly for the multi-modal network.
+  \item Possibly different window sizes per modality could lead to better results.
+* Insert some of the sources here that suggest different window sizes per modality* .
+This was beyond the scope of this project.
+\end{itemize}
+
 \newpage

### 2021-04-02 pytorch/loop_single.py
Added performance code

@@ -178,14 +178,6 @@ def SingleTrainLoop(participant, modality, batch_size, hpo, epochs, trainortest)
                 valid_loss_min = valid_loss
 
 
-        """
-        plt.plot(list(range(epochs-5)), train_list[5:len(train_list)], label = "train")
-        plt.plot(list(range(epochs-5)), valid_list[5:len(valid_list)], label = "validation")
-        plt.show()
-        """
-
-
-
     ###########################################################################################
     #################################### 4. Test loop #########################################
     ###########################################################################################
@@ -199,8 +191,8 @@ def SingleTrainLoop(participant, modality, batch_size, hpo, epochs, trainortest)
 
         diff = torch.Tensor()
         
-        predictions = torch.Tensor()
-        labelss = torch.Tensor()
+        predictions_concat = torch.Tensor()
+        labels_concat = torch.Tensor()
 
         for windows, labels in testloader:
             
@@ -212,22 +204,7 @@ def SingleTrainLoop(participant, modality, batch_size, hpo, epochs, trainortest)
             foo = (out.squeeze() - labels)
             diff = torch.cat([diff,foo])
 
-            predictions = torch.cat([predictions, out])
-            labelss = torch.cat([labelss, labels])
+            predictions_concat = torch.cat([predictions_concat, out])
+            labels_concat = torch.cat([labels_concat, labels])
 
-        test_loss = test_loss/len(testloader.sampler)
-        print("Test los:",test_loss)
-        average_miss = sum(abs(diff))/len(testloader.sampler)
-
-        print("Average Missclasification:", float(average_miss))
-        print("Or on the orignal scale:", float(average_miss*20))
-
-        corr = np.corrcoef(predictions.squeeze().detach().numpy(), labelss.detach().numpy())
-        print("Correlation predictions and labels:", float(corr[1][0]))
-
-        print(predictions.squeeze()) 
-        print(labelss.squeeze())            
-        
-        plt.hist(diff.detach().numpy(), bins= 50)
-        plt.show()
-        print('dd')
+    return predictions_concat, labels_concat

### 2021-04-02 pytorch/networks.py

@@ -103,6 +103,7 @@ class PPGNet(nn.Module):
             self.dense1 = nn.Linear(dense_input, n_units) 
             self.dense2 = nn.Linear(n_units, 1) 
             self.dropout = nn.Dropout(drop)
+            self.dense3 = nn.Linear(dense_input, dense_input) 
 
         elif multi == True:
             self.dense3 = nn.Linear(dense_input, dense_input) 
@@ -159,6 +160,7 @@ class GSRNet(nn.Module):
             self.dense1 = nn.Linear(dense_input, n_units) 
             self.dense2 = nn.Linear(n_units, 1) 
             self.dropout = nn.Dropout(drop)
+            self.dense3 = nn.Linear(dense_input, dense_input) 
 
         elif multi == True:
             self.dense3 = nn.Linear(dense_input, dense_input) 

### 2021-04-02 pytorch/test.py

@@ -1,7 +1,7 @@
 """
 @Author: Bart-Jan Boverhof
 @Last Modified by: Bart-Jan Boverhof
-@Description: This file contains the code from which all networks networks are tested
+@Description: This file contains the code from which all networks networks are tested.
 """
 #############################################################################################
 ######################################### Prerequisites #####################################
@@ -10,10 +10,13 @@
 import numpy as np
 import torch
 import os
+import pickle
+import math
+import matplotlib.pyplot as plt
 
 #Import local files
 try:
-    import train_single, train_multi, dataprep
+    import loop_single, loop_multi, dataprep
 except ModuleNotFoundError:
     wd = os.getcwd()
     print("Error: please make sure that working directory is set as '~/Masterthesis'.")
@@ -26,56 +29,199 @@ participants = ["bci10", "bci12", "bci13", "bci17", "bci21", "bci22",
                 "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
 
 #Modalities
-modalities = ["EEG","PPG","GSR"]
+modalities = ["PPG"]
 
 
 #############################################################################################
-################################### Train Single-modality networks ################################
+##################################### 1. Obtain results #####################################
 #############################################################################################
 np.random.seed(3791)
 torch.manual_seed(3791)
 torch.cuda.manual_seed(3791)
-
-
-epochs = 30
 batch_size = 10
 
 
-for i in participants:
-    for modality in modalities:
 
-        train_single.TrainLoop(participant = i, modality = "PPG",
-                        drop = drop, batch_size = batch_size, 
-                        epochs = epochs, trainortest = "test")
+def ObtainResults(modality, returndict):
+    """
+    Purpose:
+        Uses test windows to calculate predictions of trained networks.
+    Arguments:
+        modality: network variation to output results for (EEG / PPG / GSR / Multi) 
+        returndict: whether to return the results as dictionary and hereby retain person specific information (True)
+                    or returns results as single numpy arrays (False)
+    Return:
+        If returndict == True: Returns a dict of predictions and a dict of labels wherein keys correspond to participants
[…]

### 2021-04-06 manuscript/manuscript.tex
Finished results plots

@@
 \usepackage[textwidth=160mm, textheight=210mm, hmarginratio=1:1]{geometry}
+\usepackage{geometry}
 
@@
 
+\newgeometry{margin=1.1cm}
+\begin{figure}
+\caption{Mean Absolute Error (MAE) per modality}
+\bigskip
+\includegraphics[scale=0.67]{mae_hist.png}
+\label{fig:mae_hist}
+\end{figure}
+\restoregeometry
+
 \newpage
+
+\newgeometry{margin=1.1cm}
+\begin{figure}
+\caption{Mean Absolute Error (MAE) against label size}
+\bigskip
+\includegraphics[scale=0.67]{mae_scatter.png}
+\label{fig:mae_scatter}
+\end{figure}
+\restoregeometry
+
 \section{Limitations}
@@
 This was beyond the scope of this project.
+   \item How generizable is this to other situations for the same person (since things such as PPG are context dependent (like for example regarding how one ate).
+   \item Long runtimes,  even when testing. This upholds only for the multi network. The reason is likely the sheer size of these networks, which for some persons are blown up due to device lagging. 
 \end{itemize}

### 2021-04-06 pytorch/loop_multi.py

@@ -53,11 +53,7 @@ def MultiTrainLoop(participant, hpo, epochs, trainortest, batch_size):
     gsrdat =  dataprep.PytorchDataset(path = path,       #Creating PyTorch dataset
                                       modality = "GSR")
 
-    same = len(eegdat) == len(ppgdat) == len(gsrdat)
-    if same == True:
-        print("Amount of windows are equal across modalities")
-    else:
-        print("BEWARE AMOUNT OF WINDOWS DIFFER ACROSS MODALITIES!!!")
+    print(participant)
 
     padinglength_eeg = dataprep.PaddingLength(eegdat) #Determining the longest window for later use
     padinglength_ppg = dataprep.PaddingLength(ppgdat) #Determining the longest window for later use
@@ -228,19 +224,13 @@ def MultiTrainLoop(participant, hpo, epochs, trainortest, batch_size):
                 torch.save(multi_model.state_dict(), "pytorch/trained_models/"+participant+".pt")
                 valid_loss_min = valid_loss
 
-        """
-        plt.plot(list(range(epochs-5)), train_list[5:len(train_list)], label = "train")
-        plt.plot(list(range(epochs-5)), valid_list[5:len(valid_list)], label = "validation")
-        plt.show()
-        """
-
 
 
     ###########################################################################################
     ########################## 4. Assessing model performance ##################################
     ###########################################################################################
     elif trainortest == "test":
-        multi_model.load_state_dict(torch.load("pytorch/trained_models/"+participant+".pt"))
+        multi_model.load_state_dict(torch.load("pytorch/trained_models/multi/"+participant+"_multi.pt", map_location= "cpu"))
 
         test_loss = 0.0
 
@@ -248,8 +238,8 @@ def MultiTrainLoop(participant, hpo, epochs, trainortest, batch_size):
         multi_model.eval()
         diff = torch.Tensor()
         
-        predictions = torch.Tensor()
-        labelss = torch.Tensor()
+        predictions_concat = torch.Tensor()
+        labels_concat = torch.Tensor()
 
         for (eeg_windows, labels), (ppg_windows, labels), (gsr_windows, labels) in zip(eeg_testloader, ppg_testloader, gsr_testloader):
             
@@ -261,22 +251,8 @@ def MultiTrainLoop(participant, hpo, epochs, trainortest, batch_size):
             foo = (out.squeeze() - labels)
             diff = torch.cat([diff,foo])
 
[…]

### 2021-04-06 pytorch/loop_single.py

@@ -182,7 +182,7 @@ def SingleTrainLoop(participant, modality, batch_size, hpo, epochs, trainortest)
     #################################### 4. Test loop #########################################
     ###########################################################################################
     elif trainortest == "test":
-        model.load_state_dict(torch.load("pytorch/trained_models/"+modality+"/"+participant+"_"+modality+".pt"))
+        model.load_state_dict(torch.load("pytorch/trained_models/"+modality+"/"+participant+"_"+modality+".pt", map_location = "cpu"))
 
         
         model.eval()

### 2021-04-06 pytorch/test.py

@@ -1,227 +1,0 @@
-"""
-@Author: Bart-Jan Boverhof
-@Last Modified by: Bart-Jan Boverhof
-@Description: This file contains the code from which all networks networks are tested.
-"""
-#############################################################################################
-######################################### Prerequisites #####################################
-#############################################################################################
-#Importing packages
-import numpy as np
-import torch
-import os
-import pickle
-import math
-import matplotlib.pyplot as plt
-
-#Import local files
-try:
-    import loop_single, loop_multi, dataprep
-except ModuleNotFoundError:
-    wd = os.getcwd()
-    print("Error: please make sure that working directory is set as '~/Masterthesis'.")
-    print("Current working directory is:", wd)
-
-#Included participants
-participants = ["bci10", "bci12", "bci13", "bci17", "bci21", "bci22",
-                "bci23", "bci24", "bci26", "bci27", "bci28", "bci29", "bci30", 
-                "bci31", "bci32", "bci33", "bci34", "bci35", "bci36", "bci37", 
-                "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
-
-#Modalities
-modalities = ["PPG"]
-
-
-#############################################################################################
-##################################### 1. Obtain results #####################################
-#############################################################################################
-np.random.seed(3791)
-torch.manual_seed(3791)
-torch.cuda.manual_seed(3791)
-batch_size = 10
-
-
-
-def ObtainResults(modality, returndict):
-    """
-    Purpose:
-        Uses test windows to calculate predictions of trained networks.
-    Arguments:
-        modality: network variation to output results for (EEG / PPG / GSR / Multi) 
-        returndict: whether to return the results as dictionary and hereby retain person specific information (True)
-                    or returns results as single numpy arrays (False)
-    Return:
-        If returndict == True: Returns a dict of predictions and a dict of labels wherein keys correspond to participants
-        If returndict == False: Returns a np array of predictions and a np array of labels
-    """
-
-    #Objects for storing values
[…]

### 2021-04-06 results/model_performance/results.py

@@ -1,0 +1,304 @@
+"""
+@Author: Bart-Jan Boverhof
+@Last Modified by: Bart-Jan Boverhof
+@Description: This file contains the code from which all networks networks are tested.
+"""
+#############################################################################################
+######################################### Prerequisites #####################################
+#############################################################################################
+#Importing packages
+import numpy as np
+import torch
+import os
+import pickle
+import math
+import matplotlib.pyplot as plt
+import pandas as pd
+
+
+def Performance(modality):
+    """
+    Purpose:
+        Calculates and print several performance statistics
+    Arguments:
+        modality: network variation to output results for (EEG / PPG / GSR / Multi) 
+    """
+
+    print("-----------------------------------------------------------------")
+    print("-------------------- Results "+modality+"------------------------")
+    print("-----------------------------------------------------------------")
+
+
+    #Open results
+    results = pickle.load(open("results/model_performance/predictions/"+modality+".pickle", "rb"))  
+    
+    predictions = results["predictions"]
+    labels = results["labels"]
+
+    #Metric 1: Correlation predictions and labels
+    corr = np.corrcoef(predictions, labels)
+    print("Correlation predictions and labels:", round(float(corr[1][0]), 5))  
+
+    #Metric 2: Mean absolute error
+    np.set_printoptions(suppress=True)
+    mae = sum(abs(predictions - labels)) / len(predictions)
+
+    print("Mean asbsolute error "+modality+"_networks:", round(float(mae), 5))
+    print("Mean absolute error "+modality+"_networks on the original scale:", round(float(mae*20), 5))
+    
+    #Metric 3: RMSE
+    rmse = math.sqrt(sum((predictions - labels) **2) / len(predictions))
+    print("Root mean error "+modality+"_networks:", round(float(rmse), 5))
+
+    #Metric 4: SE
+    stdev = np.std(predictions - labels)
+    print("Standard deviation "+modality+"_networks:", round(float(stdev), 5))
+
+
[…]

### 2021-04-07 results/model_performance/results.py
Introduction manuscript revision

@@ -79,7 +79,7 @@ def HistGrid():
     median = x[round(len(predictions)*0.5)]
 
     #Plot
-    ax1.hist(x, bins = 70, color = "dodgerblue")
+    ax1.hist(x, bins = 70, color = "#0092cb")
     ax1.set_title("EEG-Networks", fontsize = 10, fontstyle = "italic") 
     ax1.vlines((lowerbound, median, upperbound), 0, 71, colors= "darkslategray", linestyles= ("dashed", "solid", "dashed"))
     ax1.set(ylabel='Count')
@@ -99,7 +99,7 @@ def HistGrid():
     median = x[round(len(predictions)*0.5)]
 
     #Plot
-    ax2.hist(x, bins = 70, color = "dodgerblue")
+    ax2.hist(x, bins = 70, color = "#0092cb")
     ax2.set_title("PPG-Networks", fontsize = 10, fontstyle = "italic") 
     ax2.vlines((lowerbound, median, upperbound), 0, 68, colors= "darkslategray", linestyles= ("dashed", "solid", "dashed"))
 
@@ -119,7 +119,7 @@ def HistGrid():
     median = x[round(len(predictions)*0.5)]
 
     #Plot
-    ax3.hist(x, bins = 70, color = "dodgerblue")
+    ax3.hist(x, bins = 70, color = "#0092cb")
     ax3.set_title("GSR-Networks", fontsize = 10, fontstyle = "italic") 
     ax3.vlines((lowerbound, median, upperbound), 0, 69, colors= "darkslategray", linestyles= ("dashed", "solid", "dashed"))
     ax3.set(ylabel='Count', xlabel = 'MAE')
@@ -140,7 +140,7 @@ def HistGrid():
     median = x[round(len(predictions)*0.5)]
 
     #Plot
-    ax4.hist(x, bins = 70, color = "dodgerblue")
+    ax4.hist(x, bins = 70, color = "#0092cb")
     ax4.set_title("Multi-Modular Networks", fontsize = 10, fontstyle = "italic") 
     ax4.vlines((lowerbound, median, upperbound), 0, 51, colors= "darkslategray", linestyles= ("dashed", "solid", "dashed"))
     ax4.set(xlabel='MAE')
@@ -300,5 +300,5 @@ modalities = ["PPG", "GSR", "EEG", "multi"]
 for modality in modalities:
     Performance(modality)
 
-#HistGrid()
+HistGrid()
 Scatter()

### 2021-04-07 manuscript/manuscript.tex

@@
 \section{Introduction}
-The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and neurosciences \cite{shuggi2017mental}.
-A widely utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst they carry out a certain task.
+The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and cognitive neurosciences \cite{shuggi2017mental}.
+A commonly utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst carrying out a particular task.
 As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual.
-Workload needs to be recognized as a person-specific construct.
-The amount of perceived workload ushered by a given task may vary across individuals due to how well one is able to cope with that particular task \cite{de1996measurement}.
+Workload requires to be recognized as a person-specific construct, for the amount of perceived workload ushered by a given task may vary substantially across individuals.
+\cite{de1996measurement}.
 
-A commonly employed method for the assessment of person-specific workload is the well established NASA-Task Load Index questionnaire.
-This questionnaire inquires into the amount of perceived workload,  and embodies six different dimensions \cite{hart2006nasa}.
-Such an assessment is usually conducted post-experiment, which might in certain situations be undesirable.
-Consider for example an experiment in which it is aimed to assess workload of a pilot in flight.
-An insightful learning approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight.
-However, only after the flight is concluded, a measurement in the form of a questionnaire can be administrated.
-In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate biases, such as for example the observer-bias, which advocates that participants in an experiment tend to overexaggerate the treatment effect, i.e.
+A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire.
+This method inquires into the amount of perceived workload,  embodying six different dimensions \cite{hart2006nasa}.
+Due to practical considerations such an assessment is usually conducted post-experiment, which can in certain situations be deemed suboptimal.
+Consider for example an experiment, in which is aimed to assess the perceived workload of a pilot in flight.
+An insightful  approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight, such that can be determined which specific manoeuvres tend to embark an increase in perceived workload.
+However, only after the flight is concluded, a questionnaire-based assessment such as the NASA-Task Load Index can be administrated.
+In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate biases.
+One example of such a bias is the observer-bias, which advocates that participants in an experiment tend to overexaggerate the treatment effect, i.e.
 the amount of perceived workload, when having to report it post-experiment \cite{mahtani2018catalogue}.
@@
 An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs to predict the degree of experienced workload.
-Examples of such bio-signals, hereafter referred to as "modalities", include techniques such as electroencephalography, eye-tracking, galvanic skin response, functional near-infrared spectroscopy, etc.
 The advantage of utilizing multiple bio-signals is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}.
-Doing so poses the potential of yielding a rich and multifaceted prediction of a mental construct such as workload.
-However most importantly, it is renders possible to train a separate model for each individual, with which can be catered towards the person-specific nature inherent to workload, the importance of which was pointed out by \citeA{de1996measurement}.
-This approach, however, comes at the cost of an increase in complexity.
-This resides in the need to construct a complex framework that inputs the data from each of the utilized modalities, and ultimately outputs a prediction
+Doing so poses the theoretical potential of yielding a rich and multifaceted assessment of a mental construct such as workload.
+Additionally by taking a physiological bio-signal approach, it renders possible to train a model for each individual separately,  hereby acknowledging the between-personal differences inherent to workload, the importance of which was stressed by \citeA{de1996measurement} and touched upon in the opening paragraph of this research.
 
-Three modalities are utilized in the current research. The first of which is the technique of electroencephalography
-, hereafter referred to as "EEG".
-The second is the technique of galvanic skin response, hereafter referred to as "GSR".
-Lastly, the third technique is called photoplethysmography, hereafter referred to as "PPG".
-The objective of the current study is to construct a framework with which real-time prediction of a mental construct such as workload can be managed, and to which modalities of choice can easily be added in future research endeavors.
-Consequently, one of two design principles on which the architecture of the framework reclines is the principle of modularity.
-Modularity refers to the extent to which different modalities can freely be added and/or removed towards the framework, without the necessity of re-architecting and rebuilding it entirely.
-The second design principle is the principle of generalizability, prescribing that the framework should not merely be utilizable for the classification of workload, but for the classification of other mental constructs as well.
+In the current research we explore the previously delineated approach to workload assessment by means of various physiological bio-signals, that is a multi-modular approach.
+We do so by combining data-streams stemming from three different modalities, being electroencephalography, photoplethysmography and galvanic skin response.
+Electroencephalography,  hereafter referred to as "EEG", is often utilized in the assessment of workload \cite{craik2019deep} and found to amongst the most adequately performing techniques within this field \cite{hogervorst2014combining}.
+Galvanic skin response, hereafter referred to as "GSR", equally so is a widely adopted approach towards workload investigation \cite{nourbakhsh2012using}.
+Lastly, heart-rate is a widely recognized indicator of workload, mostly obtained through photoplethysmography, hereafter referred to as "PPG"\cite{zhang2018evaluating}.
 
-A deep-learning approach towards the construction of a real-time multi-modular framework is adopted.
-Considering the complexity and sheer size of such a deep-neural network, an important point of attention is prediction speed.
-The challenge in real-time prediction with deep-learning is often not reaching adequate performance, but rather to attain adequate speed of prediction.
-Deep neural networks easily constitute thousands of calculations to be made simultaneously, which is even more true for a multi-modular approach such as the current.
-In order for real-time prediction to work, prediction cannot take too long, for otherwise it is not real-time anymore and the previously delineated benefit of a real-time approach dissipates.
-As a consequence, multiple networks are considered and contrasted in terms of performance and their ability to predict in real-time.
-Firstly, for each of the three modalities individually, a single-modular network is constructed.
-and assessed.
-Secondly, a multi-modular network is architected combining all three modalities into one.
-These networks were created in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}
-
-The aim of the current research is to explore the circumstances under which a multi-modular approach by means of deep-learning is capable of real-time classification of workload, whilst still ensuring ample and adequate performance.
-The objective is to provide a framework with which the previously delineated is possible, whilst satisfying the principles of modularity and generalizability.
-Ultimately, this line of research pursues the ability to conduct a dynamic experiment for multiple people simultaneously, and of which the state can be altered in real-time.
+A deep-learning approach towards model construction is utilized.
+A range of four different neural networks are constructed and contrasted in performance: one of which is a multi-modular network combining all three modalities, and three of which are networks solely utilizing either the EEG, GSR or PPG modality.
+With this research we endeavor on the one side to explore which modalities are most adequate predictors of workload in an experimental setting, and whether a multi-modular combination of all three previously delineated modalities is preferable over the three simpler (but much less computationally demanding) single-modular models.
+This assessment will be propelled by model performance, but whilst taking into consideration computational costs.
+All networks were constructed in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}.
 
@@
 
+\newpage
 \section{Results}
+Results EEG networks 
+\begin{itemize}
+\item Correlation predictions and labels: 0.68788.
+\item Mean asbsolute error: 0.11029.
+\item Mean absolute error on the original scale: 2.20586.
+\end{itemize}
+\bigskip
 
-\newgeometry{margin=1.1cm}
+Results PPG networks 
+\begin{itemize}
+\item Correlation predictions and labels: 0.52998.
+\item Mean asbsolute error: 0.13587.
+\item Mean absolute error on the original scale: 2.71747.
+\end{itemize}
+\bigskip
+
+Results GSR networks 
+\begin{itemize}
+\item Correlation predictions and labels: 0.65339.
+\item Mean asbsolute error: 0.11883.
+\item Mean absolute error on the original scale: 2.37665.
+\end{itemize}
+\bigskip
+
+Results Multi-Modality networks 
+\begin{itemize}
+\item Correlation predictions and labels: 0.60864.
+\item Mean asbsolute error: 0.12848.
+\item Mean absolute error on the original scale: 2.56964.
+\end{itemize}
+
+\newgeometry{margin=1.4cm}
 \begin{figure}
@@
 \bigskip
-\includegraphics[scale=0.67]{mae_hist.png}
+\includegraphics[scale=0.7]{mae_hist.png}
 \label{fig:mae_hist}
@@
    \item Long runtimes,  even when testing. This upholds only for the multi network. The reason is likely the sheer size of these networks, which for some persons are blown up due to device lagging. 
+   \item hardware failure?
 \end{itemize}

### 2021-04-13 manuscript/manuscript.tex
Manscrupt: Revision and First part results

@@
 \usepackage{geometry}
+\usepackage[capposition=top]{floatrow}
 
@@
 The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and cognitive neurosciences \cite{shuggi2017mental}.
-A commonly utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon individuals whilst carrying out a particular task.
+A commonly utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon one whilst one carries out a particular task.
 As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual.
-Workload requires to be recognized as a person-specific construct, for the amount of perceived workload ushered by a given task may vary substantially across individuals.
+Workload, however, requires to be recognized as a person-specific construct, for the amount of perceived workload ushered by a given task may vary substantially across individuals.
 \cite{de1996measurement}.
 
-A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire.
+A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire, hereafter referred to as "NASA-TLX".
 This method inquires into the amount of perceived workload,  embodying six different dimensions \cite{hart2006nasa}.
 Due to practical considerations such an assessment is usually conducted post-experiment, which can in certain situations be deemed suboptimal.
-Consider for example an experiment, in which is aimed to assess the perceived workload of a pilot in flight.
-An insightful  approach towards such an experiment would be to measure the degree of perceived workload at different phases of the flight, such that can be determined which specific manoeuvres tend to embark an increase in perceived workload.
-However, only after the flight is concluded, a questionnaire-based assessment such as the NASA-Task Load Index can be administrated.
+Consider for example an experiment in which it is aimed to assess the perceived workload of a pilot in flight.
+An insightful  approach towards such an experiment would be to measure the degree of perceived workload during different phases of the flight, such that can be determined which specific manoeuvres tend to cause an increase in perceived workload.
+However,  a questionnaire-based assessment such as the NASA-TLX can only be administrated after the flight is concluded.
 In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate biases.
-One example of such a bias is the observer-bias, which advocates that participants in an experiment tend to overexaggerate the treatment effect, i.e.
-the amount of perceived workload, when having to report it post-experiment \cite{mahtani2018catalogue}.
+One example of such a bias is the observer-bias, dictating that participants of an experiment tend to overexaggerate the treatment effect, i.e.
+the amount of perceived workload in our case, when having to report it post-experiment \cite{mahtani2018catalogue}.
 
 An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs to predict the degree of experienced workload.
-The advantage of utilizing multiple bio-signals is that complementary information streams, each stemming from a different modality, can all be interpreted simultaneously \cite{ramachandram2017deep}.
+A considerable advantage of such an approach is that it renders possible to cater the method towards the individual,  hereby acknowledging the between-personal perceptual differences inherent to workload, the importance of which was discussed in the first paragraph of this paper and stressed by \citeA{de1996measurement}.
+But taking a physiological bio-signal-approach poses more advantages: e.g.
+one may utilize multiple complementary bio-signals, each stemming from a different physiological source simultaneously \cite{ramachandram2017deep}.
 Doing so poses the theoretical potential of yielding a rich and multifaceted assessment of a mental construct such as workload.
-Additionally by taking a physiological bio-signal approach, it renders possible to train a model for each individual separately,  hereby acknowledging the between-personal differences inherent to workload, the importance of which was stressed by \citeA{de1996measurement} and touched upon in the opening paragraph of this research.
+In addition, with such an approach one may select a variety of the most suitable physiological bio-signals, hereafter referred to as "modalities",  and combine these information streams in order to yield a multifaceted prediction.
 
-In the current research we explore the previously delineated approach to workload assessment by means of various physiological bio-signals, that is a multi-modular approach.
+With the current research endeavor we explore the feasibility of an approach to workload assessment by means of multiple modalities simultaneously, hereafter referred to as "multi-modular approach".
 We do so by combining data-streams stemming from three different modalities, being electroencephalography, photoplethysmography and galvanic skin response.
-Electroencephalography,  hereafter referred to as "EEG", is often utilized in the assessment of workload \cite{craik2019deep} and found to amongst the most adequately performing techniques within this field \cite{hogervorst2014combining}.
-Galvanic skin response, hereafter referred to as "GSR", equally so is a widely adopted approach towards workload investigation \cite{nourbakhsh2012using}.
-Lastly, heart-rate is a widely recognized indicator of workload, mostly obtained through photoplethysmography, hereafter referred to as "PPG"\cite{zhang2018evaluating}.
+Electroencephalography,  hereafter referred to as "EEG", is often utilized in the assessment of workload \cite{craik2019deep} \cite{berka2005evaluation} and found to be amongst the most adequately performing techniques within the field \cite{hogervorst2014combining}.
+Galvanic skin response, hereafter referred to as "GSR", equally so is a widely adopted approach towards workload assessment \cite{nourbakhsh2012using} \cite{zhou2015dynamic}.
+Lastly, heart-rate is a widely recognized indicator of workload, mostly obtained through photoplethysmography, hereafter referred to as "PPG" \cite{zhang2018evaluating} \cite{jimenez2018using}.
 
-A deep-learning approach towards model construction is utilized.
-A range of four different neural networks are constructed and contrasted in performance: one of which is a multi-modular network combining all three modalities, and three of which are networks solely utilizing either the EEG, GSR or PPG modality.
-With this research we endeavor on the one side to explore which modalities are most adequate predictors of workload in an experimental setting, and whether a multi-modular combination of all three previously delineated modalities is preferable over the three simpler (but much less computationally demanding) single-modular models.
-This assessment will be propelled by model performance, but whilst taking into consideration computational costs.
+A deep learning approach towards modeling is adopted.
+A range of four different deep neural networks, hereafter referred to as "DNN's", are constructed and contrasted in performance: three of which are single-modular DNN's, i.e.
+networks each utilizing data from only a single modality.
+Thus,  one DNN solely utilizes the EEG modality,  one solely utilizes GSR and one solely utilizes PPG.
+The fourth network is a multi-modular network combining all three modalities into one.
+With this research we firstly sought to explore which modalities constitute the most adequate predictors of workload in an experimental setting, and secondly whether a multi-modular combination is preferable over the three simpler (but much less computationally demanding) single-modular DNN's.
+This assessment will be propelled by contrasting network performance, however when drawing conclusions, considerations regarding computational costs will be taken into consideration as well.
 All networks were constructed in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}.
@@
 \newpage
-\section{Methods}
+\section{Data \& Methods}
+
+\subsection{Data}
+The subsequent section will provide an overview of the utilized data.
+Attention is placed upon the experimental setup, the description of the respondents, the utilized devices for data collection and the synchronization process.
+
+\subsubsection{Experimental Setup}
+The experimental setting in which data collection befell is the open-source spaceship video-game Empty Epsilon, in which partakers carry out tasks on a virtual spaceship bridge \cite{daid2016empty}.
+This experiment was instituted by the Brain Computer Interfaces testbed, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
+The experiment constituted three different segments, in each of which the respondent had to carry out tasks.
+These tasks were designed to evoke varying degrees of workload.
+Each segment consisted of six small sessions, lasting roughly five to ten minutes.
+These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment.
+Within each segment, the order in which the sessions were presented was randomized.
+Between every three sessions, respondents were given a short two minute break.
+A schematic overview of the experimental structure is depicted as Figure \ref{fig:experimental}.
+
+After each of the 18 sessions, respondents were asked to fill out the NASA-TLX, resulting in 18 filled in questionnaires per respondent.
+Each questionnaire consists out of 6 questions, inquiring upon the degree to which the respondent experienced workload during the preceding session.
+The mean of a subset of four of these items have been utilized to label the data for training purposes.
+Two items were not incorporated into the scale, for they inquired into physical demand specifically, which given the experiment took place on a computer whilst sitting behind a desk was considered to be a redundant factor.
+Each item, and hence the newly constructed scale, ranges from 0-20, wherein 0 reflects low workload and 20 reflects high workload.
+In order to encourage numerical stability, label scores were normalized to reside in-between 0-1.
+
+\begin{figure}
+\caption{Schematic Depiction of the Experimental Setup}
+\bigskip
+\includegraphics[scale=0.35]{experimental_setup}
+\label{fig:experimental}
+\bigskip
+\end{figure}
+
+The first segment emulated a scenario in which hostile spaceships approached the respondent's spaceship.
+The respondent was required to quickly respond by defusing the hostiles in order to survive.
+The increment in difficulty caused the process of defusing hostile spaceships to become more challenging, hereby aiming to cause an increase in workload.
+The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible.
+Obstacles around which the respondent had to navigate carefully, as well as hostile spaceships the respondent had to decimate, were introduced in the higher difficulty sessions.
+The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests.
+In the increased difficulty settings, variables that could overheat the spaceship were introduced, demanding the respondent to multi-task and aiming to increase workload as a consequence.
+
+\subsubsection{Participants}
+After having to omit 7 participants due to hardware failure, 27 respondents were included in the final analysis.
+18 participants are female whereas 9 are male.
+The mean age and standard deviation are $\mu =26, \sigma = 10.31$ respectively.
+The participants are students recruited from the University of Twente, as well as several employees of Thales group Hengelo.
+
+\subsubsection{Devices and Synchronization}
+The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
+This device is worn on the wrist.
+Signals are communicated wirelessly via Bluetooth.
+An ear-clip is utilized for measuring PPG.
+The Shimmer3 GSR+ automatically converts measured PPG signals to heart-rate.
+Skin conductivity, or GSR, is measured by two electrodes attached to the fingers \cite{shimmer}.
+EEG measurement was conducted with the Muse 2, which is a commercially offered multi-sensor headband that provides feedback on brain activity \cite{muse}.
+The Muse 2 headband constitutes five sensors, each monitoring a different brainwave frequency.
+
+The Shimmer3 GSR+ measures signals on a sampling rate of 256 Hz, whereas the Muse 2 measures at a sampling rate of 220 Hz.
+Given that multiple devices are utilized, data streams are required to be properly synchronized.
+This was accomplished by means of an application called Lab-Streaming Layer, hereafter referred to as "LSL", developed by \citeA{kothe2018lab}.
+The three data streams stemming from the two devices were all streamed to LSL during the experiment.
+LSL subsequently properly synchronizes all data streams in real-time,  such that they are parallel, hence all referring to equivalent points in time.
 
 \subsection{Related Work} 
-The following sections provide an overview of preceding research on the most optimal network architecture for each single-modular network.
-Subsequently, the most feasible architecture for the multi-modular framework in its entirety is explored, with particular attention placed upon the data fusion strategy and a range model optimization techniques.
+The following section provides an overview of preceding research regarding the assessment of workload by means of physiological bio-signals, with a focus on deep learning approaches.
+Attention is predominantly placed upon the most feasible network architectures, in addition to a range of model optimization techniques and to the data fusion strategy for the multi-modular DNN.
+The final part of this section will be dedicated to hyperparameter optimization.
 
 \subsubsection{Electroencephalography (EEG)}
-EEG constitutes a technique that detects electrical activity in the brain by using electrodes.
-EEG is a commonly utilized method within the field of workload assessment.
-An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all available papers to deal with workload specifically.
-With regards to these EEG applications, it was reported that studies mostly used deep belief networks and convolutional neural networks, hereafter referred to as "ConvNets".
-One of these approaches is advised consequently \cite{craik2019deep}.
+An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all publications to consider workload assessment specifically.
+The lion's share of these publications utilized either a deep belief networks or convolutional neural network, hereafter referred to as "ConvNet".
+One of these approaches is encouraged by the authors consequently \cite{craik2019deep}.
 
-For EEG classification, \citeA{tabar2016novel} proposed a combination of a ConvNet with a stacked auto-encoder network, hereafter referred to as "SAE network".
-The input layer was specified to feed into a convolutional layer with the objective of learning the filters and network parameters.
-The output of this convolutional layer was subsequently specified to feed into the SAE part of the network, designed to include an input layer, six hidden layers and an output layer.
+\citeA{tabar2016novel} proposed a hybrid of a ConvNet with a stacked auto-encoder network, hereafter referred to as "SAE network".
+Inputs were specified to feed into the convolutional-part with the objective of learning extracting features.
+The output of this part was subsequently specified to feed into the SAE part of the network,  which encompasses a stack of dense-layers, designed specifically as an input layer, six hidden layers and an output layer.
 A classification accuracy of 90 \% was acquired with this network \cite{tabar2016novel}.
@@
 \subsubsection{Galvanic Skin Response (GSR)}
-GSR is a technique that measures sweat gland on the hands, hereby inferring arousal.
-GSR activity is known to be strongly correlated with perceived workload, indicating the utility of GSR for workload classification \cite{shi2007galvanic}.
-
-\citeA{sun2019hybrid} explored the most suitable model design for the classification of several emotional states with GSR.
-Various models were explored, amongst others a support vector machine, a ConvNet and a long-short-term-memory network, hereafter referred to as "LSTM network".
-Additionally, the feasibility of a hybrid network, combining both the ConvNet and LSTM approaches, was explored.
+\citeA{sun2019hybrid} explored the most suitable approach to the classification of several emotional states with GSR.
+Various models were explored, amongst others a support vector machine, a ConvNet and a long-short-term-memory, hereafter referred to as "LSTM", network.
+Additionally, the feasibility of a hybrid DNN, combining both the ConvNet and LSTM approaches, was explored.
 This aforementioned hybrid model was found to perform best, exhibiting an accuracy of 74\% \cite{sun2019hybrid}.
 
-\citeA{dolmans2020perceived} took a multi-modular approach to workload classification, and designed a variant based on the previously delineated CovNet-LSTM approach for GSR.
+\citeA{dolmans2020perceived} took, amongst other approaches to workload prediction,  a GSR approach, and designed a variant based on the previously delineated CovNet-LSTM structure.
 The performance of this model was contrasted with a network consisting solely of fully connected dense layers.
-Conform with findings by  \citeA{sun2019hybrid}, the hybrid model was found to perform best, displaying an accuracy of 82 \% \cite{dolmans2020perceived}.
-The model architecture as utilized by \citeA{dolmans2020perceived} deployed two convolutional max-pooling blocks and two LSTM layers.
+Conform with findings by  \citeA{sun2019hybrid}, the hybrid model was found to perform best, displaying an absolute difference between predicted and true label of 0.197 (scaled on 0-1).
+The model architecture as utilized deployed two convolutional max-pooling blocks and two LSTM layers \cite{dolmans2020perceived}.
 
 \subsubsection{Photoplethysmography (PPG)}
-PPG is a technique utilized to measure volumetric changes in blood peripheral circulation, from which it is possible to derive heart-rate.
-\citeA{zhang2018evaluating} contrasted several approaches towards workload classification, each utilizing a different modality.
-PPG was found to perform among the best, explaining why PPG constitutes one of the most widely utilized modalities in workload classification.
-
-Work by \citeA{biswas2019cornet} explored a deep-learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
-Exceptional results were realized with a deep neural network, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
+Research by \citeA{biswas2019cornet} explored a deep learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
+Exceptional results were realized with a DNN, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
 This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed by two LSTM layers.
@@
 \subsubsection{Multi-modular Fusion Strategy}  
-When conducting a multi-modular deep-learning approach, the information streams stemming from the three modalities are required to be combined, i.e.
-"fused", at a certain point in the network, in order to ultimately result in a single classification of workload.
-Fusion can be done conforming different strategies.
-Several strategies as proposed by \citeA{ramachandram2017deep} have been considered.
+When conducting a multi-modular deep learning approach,  information streams stemming from the different modalities are required to be combined, i.e.
+"fused", at a certain point in the network in order to ultimately result in a single prediction of workload.
+Fusion can be done conforming several strategies.
+Three strategies as proposed by \citeA{ramachandram2017deep} have been considered.
 
 Early, or data-level, fusion constitutes an approach that fuses data sources before being fed into the network.
-Techniques that manage this include for example principle-component analysis and factor analysis.
-Early fusing is usually proven to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in dimensionality and sampling rate.
+Early fusing is usually proven to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate.
 In addition, when taking an early fusion approach, the oversimplified assumption of conditional independence is made implicitly.
@@
 Late, or decision-level, fusion refers to the process of aggregating the decisions of multiple separate networks, each applied towards every modality separately.
-In case the data sources stemming from the various modalities are either correlated or ultimately differ in their dimensionality, late fusion is a much more feasible approach as contrasted with early fusion \cite{ramachandram2017deep}.
+In case the data sources stemming from the various modalities are either correlated or ultimately differ in their dimensionality, late fusion is often a more feasible approach as opposed to early fusion \cite{ramachandram2017deep}.
 
@@
 This results in a single joint deep neural network.
-Classification is managed based on the outputs from each of the single-modular network parts.
 Several "higher-order layers" are usually defined in between the concatenation layer and the ultimate classification.
@@
 
-Indeed, when consulting the literature, one is forced to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep-learning approaches.
+Indeed, when consulting the literature, one is prone to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep learning approaches.
 When taking an intermediate fusion approach, the higher-order part of the network needs to be designed and established, for which several previous research endeavors are considered.
-\citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers, two dense layers and a softmax layer.
-A simpler approach is adopted by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers, and ending with a soft-max layer.
+\citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers and two dense layers.
+A simpler approach is adopted by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers.
 Lastly, \citeA{dolmans2020perceived} took a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.
@@
 \subsubsection{Model Optimization Strategies}
-The technique of batch normalization was originally proposed by \citeA{ioffe2015batch}, and is often a applied in deep-learning with the objective of stabilizing a network.
-Especially ConvNets are able to capitalize on this technique.
-It is beneficial to include a batch normalization layer after each convolutional layer, re-centering and re-scaling the input feeding into subsequent layers.
-When incorporating a batch normalization layer, it is recommended to do so before the specification of the activation function \cite{ioffe2015batch}.
-An increase in accuracy for EEG classification was attained by \citeA{dolmans2020perceived} and \citeA{schirrmeister2017deep} through specifying a batch normalization layer following each convolutional layer.
-Equally so, the best performing network for PPG as proposed by \citeA{biswas2019cornet} included a batch normalization layer succeeding each convolutional layer.
+The technique of batch normalization was initialized by \citeA{ioffe2015batch}, and is widely utilized in DNN's with the objective of stabilization.
+Especially ConvNets benefit from this technique.
+It is beneficial to incorporate a batch normalization layer subsequent to a convolutional layer, but before feeding into the activation function \cite{ioffe2015batch}.
+All previously delineated networks architectures utilize batch normalization layers, in most cases specified subsequent to each convolutional layer \cite{dolmans2020perceived} \cite{tabar2016novel} \cite{schirrmeister2017deep} \cite{biswas2019cornet} \cite{sun2019hybrid}.
 
-Pooling layers are commonly employed in ConvNets, usually succeeding a convolutional layer with the purpose of decreasing the dimensionality.
-The objective of such layers are to merge similar features into one.
+Pooling layers are commonly employed in ConvNets, usually succeeding a convolutional layer with the purpose of reducing dimensionality.
+The objective of such layers are to down-sample features into a more compact space, hereby only retaining indispensable information.
 For a more extensive elaboration on pooling, please consult \citeA{lecun2015deep}.
-In their EEG ConvNets, both \citeA{schirrmeister2017deep} and \citeA{tabar2016novel} specified a max-pooling layer after each convolutional layer.
-The network as proposed for GSR by \citeA{sun2019hybrid} incorporated a max-pooling layer after each but one of the convolutional layers.
-Lastly, the network as proposed for PPG by \cite{biswas2019cornet} specified a max pooling layer after each convolutional layer.
+All previously delineated networks architectures utilize max-pooling layers, usually specified subsequent to the activation layer \cite{dolmans2020perceived} \cite{tabar2016novel} \cite{schirrmeister2017deep} \cite{biswas2019cornet} \cite{sun2019hybrid}.
 
-Hyper-parameter optimization, hereafter referred to as "HPO", is a technique that can be utilized to optimize hyper-parameters such as learning rate and dropout.
-Substantial advancements in deep-learning have been attained by utilizing HPO, especially for ConvNets \cite{bergstra2012random}.
+\subsubsection{Hyper Parameter Optimization}
+Hyper parameter optimization, hereafter referred to as "HPO", is a technique that can be utilized to optimize network hyper-parameters, such as learning rate and dropout rate.
+In theory, one could optimize the entire DNN architecture, including the number of neurons/filters in (convolutional) layers, the number of layers in general, whether to use certain layers etc.
+There is, however, a strong relationship between the amount of parameters to be optimized and the computational resources required to do so, in where many parameters to optimize tends to inflate computational costs by a substantial amount.
+Substantial advancements in DNN performance have been attained by utilizing HPO, especially for ConvNets \cite{bergstra2012random}.
 The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled and optimization can be performed \cite{akiba2019optuna}.
@@
 
-\subsection{Data}
-The subsequent section will provide an overview of the utilized data.
-Attention is primarily placed upon the experimental setup, the description of the respondents, the utilized devices for data collection and the synchronization process.
+\subsection{Deep Neural Network Architectures \& Training} \label{section:DNN}
+Before elaborating on the chosen DNN architectures, we will firstly touch upon several universal truths for all networks.
+Given the person-specific character inherent to physiological data,  networks for each respondent have been trained independently.
+Despite this, all network architectures across persons are similar, except for the specified hyperparamaters: these were optimized for each of the four networks and for each respondents individually as well.
+As a consequence, four DNN's are trained for each of the 27 respondents separately, resulting in a total of 108 trained networks, each one utilizing one of 108 sets of optimized hyperparamaters.
+All networks were
 
-\subsubsection{Experimental Setup}
-The experimental setting in which the data collection took place is the open-source spaceship video-game Empty Epsilon, in which respondents were asked to carry out tasks on a virtual spaceship \cite{daid2016empty}.
-This experiment was instituted by the Brain Computer Interfaces testbed, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
-The experiment constituted three different segments, in each of which the respondent had to carry out tasks.
-These tasks were designed to evoke varying degrees of workload.
-Each segment consisted of six small sessions lasting roughly five to ten minutes.
-These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment.
-Within each segment, the order in which the sessions were presented was randomized.
-The order in which the three main segments were administrated was not randomized.
-Between every three sessions, respondents were given a short two minute break.
-A schematic overview of the experimental structure is depicted as Figure \ref{fig:experimental}.
+\subsubsection{Single-modular Network}
+All single-modular network architectures took inspiration from previously delineated research \cite{schirrmeister2017deep} \cite{dolmans2020perceived} \cite{sun2019hybrid} \cite{biswas2019cornet}.
+In contrast with most of these previous endeavors, we opted for a ConvNet-only approach, i.e.
+without LSTM-layers, for the objective of the current research is not of a time-series-forecasting-kind.
+An experimental scenario wherein the course of actions over the duration of the experiment always unfold in a similar manner are inclined to benefit from acknowledging this time-series-like nature, hence benefiting from LSTM.
+An example of such a scenario would be a pilot in flight: whilst workload arousing phenomena that occur during a flight could differ across takes, the general chronological structure of the scenario always adheres to a similar blueprint.
+I.e., starting with ascend, likely to arouse a peak in workload, and closing with touch down, equally so likely to arouse a peak in workload.
+Our experimental scenario doesn't adhere to such a set in stone unfolding, for the order in which the scenario's with variable difficulty were presented was entirely randomized.
+Hence, for there is no chronologically consistent development of the experimental scenario, we opted for a ConvNet approach without opting to learn from the development over time, thus without LSTM-layers.
 
-After each of the 18 sessions, respondents were asked to fill in the TLX questionnaire, compromising of six questions each.
-This resulted in 18 filled in questionnaires per respondent.
-Each questionnaire inquired upon the degree to which the respondent experienced workload during the preceding session.
-These measurements have been utilized to label the data for network training purposes.
+The three single-modular DNN architectures are depicted alongside one another as Figure \ref{fig:singlearchitecture}.
+Each of the single-modular networks can be distinguished by two separate part, being the convolutional part and the prediction part.
+The objective of the convolutional part is to extract features from the data.
+For each network, this part consists of four convolutional blocks, each compromising a convolutional layer, a batch normalization layer, the Exponential Linear Unit, hereafter referred to as "ELU", activation function, and a max-pooling layer respectively.
+The prediction part compromises a flatten-layer,  with the objective of representing all input into one dimensional shape, followed by a dropout layer, a dense layer, a Rectified linear activation, hereafter referred to as "RELU", closed by another dense layer.
+An overview of the amount of utilized filters / neurons for each layer of each network is provided in Table \ref{table:modelvariations}.
 
+Consistent with training, HPO was equally so done for each respondent individually, resulting in 27 optimized sets of parameters for the EEG networks, 27 for the PPG networks and 27 for the GSR networks.We optimized the learning rate, dropout rate and the amount of neurons for the first dense layer in 50 trials per network.
+For training, a total of 600 epochs have been made through the data for each network independently.
+All training and HPO of the single-modular networks has been done on a V100 GPU,  offered by the GPU cloud service Google Collab.
+Total running time for the single-modular networks was about four days, the most of which was absorbed by HPO.
+
+\newgeometry{margin=2cm}
 \begin{figure}
-\caption{Experimental Setup}
+\caption{The Three Single-modular Network Architectures}
 \bigskip
-\includegraphics[scale=0.4]{experimental_setup}
-\label{fig:experimental}
+\includegraphics[scale=0.7]{single_model_architecture}
+\label{fig:singlearchitecture}
+\floatfoot{\emph{Note:} Each network constitutes a convolutional part of four convolutional blocks, and a classification part of two fully connected dense layers. }
 \end{figure}
+\restoregeometry
 
-The first segment emulated a scenario in which hostile spaceships approached the respondent's spaceship.
-The respondent was required to quickly react by defusing the hostiles in order to survive.
-The increment in difficulty caused the process of defusing hostile spaceships to become more challenging, hereby aiming to cause an increase in workload.
-The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible.
-Obstacles around which the respondent had to navigate carefully, as well as hostile spaceships the respondent had to decimate, were introduced in the higher difficulty sessions.
-The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests.
-In the increased difficulty settings, variables that could overheat the spaceship were introduced, demanding the respondent to multi-task and aiming to increase workload as a consequence.
-
-\subsubsection{Respondents}
-In total, 38 respondents have participated in the study.
-Demographic information of the respondents is set forth in Table \ref{table:demographics}.
-The respondents are students recruited from the University of Twente.
-Recruitment has been conducted by means of Sona, which is a cloud-based participant management system.
-A requirement for participation was that respondents didn't have any constraints that might interfere with the utilized sensors, such as for example a pacemaker.
-This was assessed by means of a short demographic questionnaire prior to the experiment.
-Additionally, respondents were made aware of informed consent prior to the experiment in order to ensure completely voluntary participation.
-Respondents were able to draw back from the experiment at any time.
-
-\bgroup
-\def\arraystretch{1.6}  
-\begin{table}[h]
-\bigskip
-\caption{Demographic Overview Respondents}
-\label{table:demographics}
-\begin{tabular}{rrrr}
-  \hline
- & Female & Male \\ 
-  \hline
-10-19 &   7 &   0 &  \hspace{1cm} \\ 
-  20-29 &  13 &   4 &   \\ 
-  30-39 &   1 &   1  &   \\ 
-  40-49 &   0 &   8  &   \\ 
-  50-59 &   0 &   0 &   \\ 
-  60-69 &   0 &   4 &   \\ \hline
-  Total    &  21 &  17 & \\ \hline
-\end{tabular}
-\end{table}
-\egroup
-
-\subsubsection{Devices and Sampling Rate}
-The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
-This device was worn on the wrist.
-Signals were communicated wirelessly.
-An ear-clip was utilized for measuring PPG, and converting this to estimate heart rate.
-Skin conductivity, or GSR, was monitored by two electrodes attached to the fingers \cite{shimmer}.
-EEG measurement was conducted with the Muse 2, which is a multi-sensor headband that provides feedback on brain activity \cite{muse}.
-The Shimmer3 GSR+ is able to read and output data signals on a sampling rate of 256 Hz, whereas the Muse 2 is able to sample at a maximum rate of 220 Hz.
-
-As was set forth in the introduction, real-time classification requires a swiftly classifying network.
-A higher sampling rate equals more data traveling through the network, decelerating classification speed.
-As a consequence, it is highly beneficial to input data on the minimum required sampling rate with which key features can be detected consistently.
-
-\citeA{fujita2019evaluation} explored the required sampling rate for PPG feature detection.
-The extent to which important features were detected was contrasted for several sampling rates.
-A sampling rate of 60 Hz was found to be the absolute minimum required sampling rate for extracting all commonly utilized features in a stable manner \cite{fujita2019evaluation}.
-Utilizing a slightly higher sampling rate is the safer option, however.
-The Shimmer3 GSR+ manufacturers recommend a sampling rate of 100 Hz for PPG \cite{shimmer}.
-Hence, a sampling rate of 100 Hz was specified for the PPG modality.
-
-The required sampling rate for the GSR modality is substantially lower as compared with both PPG and EEG measurement.
-In fact, the Shimmer3 GSR+ manufacturers recommend a sampling rate ranging between 0.03 and 5 Hz \cite{shimmer}.
-A sampling rate of 5 Hz was specified as a consequence.
-
-For the EEG modality, different features require a widely different sampling rate in order to be detected.
-Frequency bands for traditionally considered EEG features reside on about 0.5-4 Hz for the delta feature, and at most on about 16-24 Hz for the beta feature.
-The gamma feature recently gained in popularity, and resides on a frequency band ranging up to 80 Hz \cite{weiergraeber2016sampling}.
-In order to be able to detect an EEG feature residing on a 80 Hz frequency band, a substantially higher sampling rate is required to record the signal without aliasing.
-The required sampling rate can be determined by means of the Nyquist criterion for practical EEG sampling, defined as Equation \ref{eqn:nyquist},
-
-\begin{equation}
-\label{eqn:nyquist}
-f_{samp} > 2.5 * f_{max}
-\end{equation}
-where $f_{samp}$ reflects the required sampling rate and $f_{max}$ reflects the frequency band around which the feature to be detected resides \cite{srinivasan1998estimating}.
-Hence, in order to be able to detect the gamma feature stably, a sampling rate of $2.5*80=200$ was specified for the EEG modality.
-A summary of the specified sampling rates per modality are depicted in Table \ref{table:samplingrate}.
-
+\newgeometry{margin=1.6cm}
 \bgroup
@@
 \begin{table}[h]
-\bigskip
-\caption{Sampling Rate per Modality}
-\label{table:samplingrate}
-\begin{tabular}{ll}
-    & Specified sampling rate (Hz) \\ \hline
- Electroencephalogram (EEG) & 200                         \\
-Galvanic Skin Response (GSR) & 5                           \\
-Photoplethysmography (PPG) & 100                         \\ \hline
-   \bigskip
+\caption{Network Sizes}
+\label{table:modelvariations}
+\begin{tabular}{lllll}
+\hline
+        & EEG-Net/Part  & GSR-Net/Part  & PPG-Net/Part  & Multi-Modular Head-Net     \\ \hline
+ Single-Modular-Nets & Dense Out: 1 & Dense Out: 1 & Dense Out: 1 &   \\
+        & Dense 1: \emph{hpo} & Dense 1: \emph{hpo} & Dense 1: \emph{hpo} &   \\
+        \vspace{1.5ex}        
+        & Drop out: \emph{hpo} & Drop out: \emph{hpo} & Drop out: \emph{hpo} &   \\
+        & Conv4: 200 & Conv4: 128 & Conv4: 128 &    \\ 
+        & Conv3: 100 & Conv3: 64 & Conv3: 64 &    \\ 
+        & Conv2 50 & Conv2: 32 & Conv2: 32 &    \\ 
+        \vspace{3ex}
+        & Conv1: 25 & Conv1: 16 & Conv1: 16 &  \\         
+  Multi-Modular-Net & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense Out: 1  \\
+        & Conv4: 200 & Conv4: 128 & Conv4: 128  &  Dense 3: \emph{hpo} \\ 
+        & Conv3: 100 & Conv3: 64 & Conv3: 64 & Dense 2: \emph{hpo}  \\ 
+        & Conv2 50 & Conv2: 32 & Conv2: 32 & Drop out: \emph{hpo}    \\ 
+        \vspace{3ex}
+        & Conv1: 25 & Conv1: 16 & Conv1: 16 &    \\   \hline
 \end{tabular}
+\vspace{2ex}
+\begin{doublespacing}
+
+\floatfoot{\textit{Notes:} For all convolutional layers the depicted number reflects the amount of utilized filters, whereas for dense layers it reflects the amount  of nodes.
+All depicted values are the amount of filters/nodes that a respective layer outputs.
+\textit{input} refers to fully connected dense layers, wherein the number of outputting nodes equals the number of inputting nodes.
+\textit{Hpo} implies that the value for the respective layer was optimized (see first paragraph of section \ref{section:DNN})}
+
+\end{doublespacing}
 \end{table}
 \egroup
+\restoregeometry
 
-\subsubsection{Synchronization}
-Data streams stemming from the different modalities were required to be properly synchronized.
-This was accomplished by means of an application called Lab-Streaming Layer, hereafter referred to as "LSL".
-The data streams stemming from the different modalities were all streamed to LSL during the experiment.
-LSL properly synchronized these data streams, such that they are parallel.
-Subsequently, all data was recorded into a single file per participant \cite{kothe2018lab}.
-\bigskip
+\subsubsection{Multi-modular Network}
+The network architecture utilized for the multi-modular approach was determined by combining the previously characterized single-modular networks with insights drawn from previous research, in particular \cite{han2020classification}.
+A visual representation of the multi-modular network is depicted as Figure \ref{fig:multiarchitecture}.
+An overview of the amount of utilized filters and neurons for each layer of the multi-modular network is provided in Table \ref{table:modelvariations}.
 
-\subsection{Framework Architecture}
-The upcoming section opens with the description of the architecture of the three single-modular networks.
-Subsequently, the multi-modular network architecture is elaborated upon.
-Lastly, several variations made on this multi-modular architecture are discussed.
+The network architecture for the single-modular parts of the network are separately defined entities of the multi-modular network, but are highly similar as compared with the previously delineated single-modular networks.
+An intermediate fusion strategy is adopted due to its highly flexible nature as compared with alternative fusion strategies.
+The output of all three distinct parts in the network were flattened, followed by a dense layer and RELU activation.
+Flattening was nescessary such that all inputs were represented in one-dimensional space, after which concatenation was possible.
+The prediction part, also referred to as "Head-Network", consists of three dense layers, alternated with dropout, batch normalization and RELU activation.
 
-\subsubsection{Single-modular Network: Architectures}
-The appropriate architecture for each of the single-modular networks is determined by combining insights from the literature.
-The three single-modular network architectures are depicted as Figure \ref{fig:singlearchitecture}.
+Again, consistent with training, HPO was equally so done for each respondent individually, resulting in 27 optimized sets of parameters each of the 27 multi-modular networks.
+We optimized the learning rate, dropout rate and the amount of neurons for the first and second dense layers in 18 trials per network.
+For training, a total of 250 epochs have been made through the data for each network independently.
+All training and HPO has been done on a Cloud TPU v2,  offered by the GPU cloud service Google Collab Pro.
+Total running time for the multi-modular networks was about 12 days, the most of which absorbed by HPO.
 
-\begin{figure}
-\caption{The Three Single-modular Network Architectures}
-\bigskip
-\includegraphics[scale=0.725]{single_model_architecture}
-\label{fig:singlearchitecture}
-\end{figure}
-
-The utilized network for the EEG modality was a ConvNet as proposed by \citeA{schirrmeister2017deep}.
-The network was designed to include four convolutional blocks, each constituting a convolutional layer, followed by a batch normalization layer.
-The Exponential Linear Unit, hereafter referred to as "ELU", function was utilized as activation function.
-Each convolutional block was closed with a max pooling layer of stride three.
-
-The utilized network for the GSR modality was a LSTM ConvNet hybrid, inspired from the work of \citeA{sun2019hybrid} and \citeA{dolmans2020perceived}.
-The network was designed to include two convolutional blocks, each constituting a convolutional layer, followed by a batch normalization layer, the activation layer and closed with a max-pooling layer of stride four.
-The Rectified Linear Unit, hereafter referred to as "ReLU", function was utilized as activation function.
-Following these two convolutional blocks were two LTSM layers.
-
-Lastly, the utilized network for the PPG modality was inspired from the network as proposed by \citeA{biswas2019cornet}.
-The network opens with two convolutional blocks, each consisting of a convolutional layer, a batch normalization layer, the activation layer and closed with a max pooling layer of stride four.
-The utilized activation function was the ReLU.
-Following these convolutional blocks were two LTSM layers.
-
-\subsubsection{Multi-modular Network: Architecture}
-The network architecture utilized for the multi-modular approach was determined by a combination of the single-modular networks, as derived from the literature.
-The previously delineated design principles (i.e.
-the principles of modularity and generalizability) were taken into account when doing so.
-A visual representation of the multi-modular network is depicted as Figure \ref{fig:multiarchitecture}.
-
+\newgeometry{margin=2cm}
 \begin{figure}
@@
 \bigskip
-\includegraphics[scale=0.725]{multi_model_architecture}
+\includegraphics[scale=0.7]{multi_model_architecture}
 \label{fig:multiarchitecture}
+\floatfoot{\emph{Note:} The network constitutes a convolutional part of four convolutional blocks for each of distinct parts of the networks.
+All three distinct parts were flatenned, after which concatenation was possible.
+The prediction part of the network constitutes several dense layers.}
 \end{figure}
+\restoregeometry
 
-An intermediate fusion strategy is adopted due to its highly flexible nature as compared with other fusion strategies.
-The architecture for the single-modular parts of the network remained unchanged.
-In order to fuse the  single-modular parts of the network, each of these is closed with one fully connected dense layer before feeding into the head network.
-This is done in order to flatten all inputs towards a lower dimensional space, such that concatenation was possible.
-The head network consists of four dense layers.
-These layers are alternated with a batch normalization and max-pooling layer with the objective of stabilization.
-
-\subsubsection{Multi-modular Network: Variations}
-Speed is a potential bottleneck for a multi-modular approach that is destined to classify in real-time.
-The previously delineated network is substantially complex in nature, hence posing the risk of not being able to classify fast enough.
-Therefore, several variations on this network architecture have been designed.
-These variations are not made by altering the network architecture, for deviating from the validated architecture could be detrimental with regards to performance.
-Hence, three variations with regards to size of the network as depicted in Figure \ref{fig:multiarchitecture} have been considered.
-The goal was to propose a network that is fast enough for real-time classification, whilst maintaining the highest amount of accuracy as possible.
-
-Network size can be understood as the amount of specified filters for convolutional layers, and the amount of specified neurons for all other utilized layers.
-A decrease in the specified amount of filters and neurons constitutes a decrease in network size, and consequently a decrease in the amount of required calculations.
-Doing so was expected to bring about an increase in speed.
-An overview of all three multi-modular network variations, and the amount of specified neurons/filters per layer, is provided in Table \ref{table:modelvariations}.
-Network 1 is referred to as the full network.
-The size of this network was determined by consulting the literature.
-The sizes of each of the sub-parts, i.e.
-the EEG, PPG and GSR sub-parts, were roughly adopted from the research that proposed these designs initially.
-The size of Network 2 constitutes of 75 \% of the size of the full network.
-Lastly, Network 3 constitutes of 50 \% of the size of the full network.
-
-\bgroup
-\def\arraystretch{1.6}%  
-\begin{table}[h]
-\caption{Model Variations Based on Size}
-\label{table:modelvariations}
-\begin{tabular}{lllll}
-\hline
-        & EEG        & GSR        & PPG        & Head       \\ \hline
-Network 1 & Conv1: 25  & Conv1: 128 & Conv1: 128 & Dense: 712 \\
-        & Conv2: 50  & Conv2: 128 & Conv2: 128 & Dense: 356 \\
-        & Conv3: 100 & LSTM1: 256 & LSTM1: 256 & Dense: 178 \\
-        & Conv4: 200 & LSTM1: 256 & LSTM2: 256 &            \\ 
-        \vspace{3ex}
-        & Dense: 200 & Dense: 256 & Dense: 256 &            \\ \hline
-Network 2 & Conv1: 18  & Conv1: 96  & Conv1: 96  & Dense: 534 \\
-        & Conv2: 34  & Conv2: 96  & Conv2: 96  & Dense: 267 \\
-        & Conv3: 75  & LSTM1: 192 & LSTM1: 192 & Dense: 134 \\
-        & Conv4: 150 & LSTM1: 192 & LSTM1: 192 &            \\
-        \vspace{3ex}
-        & Dense: 150 & Dense: 192 & Dense: 192 &            \\ \hline
-Network 3 & Conv1: 13  & Conv1: 64  & Conv1: 64  & Dense: 356 \\
-        & Conv2: 25  & Conv2: 64  & Conv2: 64  & Dense: 178 \\
-        & Conv3: 50  & LSTM1: 128 & LSTM1: 128 & Dense: 89  \\
-        & Conv4: 100 & LSTM1: 128 & LSTM2: 128 &            \\
-        & Dense: 100 & Dense: 128 & Dense: 128 &            \\ \hline
-\end{tabular}
-\vspace{2ex}
-
-\begin{doublespacing}
-{\raggedright \textit{Note:} For all convolutional layers the depicted number reflects the amount of utilized filters, whereas for LTSM layers it reflects the amount  of nodes. \par}
-\end{doublespacing}
-\end{table}
-\egroup
-
-\clearpage
+\newpage
 \subsection{Model Evaluation}
@@
 When assessing performance in deep/machine-learning, it is of importance to realize that each performance metric may favor one approach over the other, simply and solely due to the mathematical nature in which both the metric and the model are defined \cite{gunawardana2009survey}.
-For this reason, we deemed it of importance to not merely evaluate performance based on one or two metrics.
-The adopted approach is rather to consider a conglomerate of different metrics, and evaluate performance based on the whole span of those.
-The utilized metrics constitute six well known and widely deployed metrics in the field of deep/machine-learning.
-All six metrics are constructed from the confusion matrix.
-The theoretical format of the confusion matrix is depicted as Figure \ref{fig:confusion}.
+For this reason, we consider a conglomerate of different metrics.
 
-\bigskip
-\bgroup
-\def\arraystretch{1.6}%  
-\begin{figure}[h]
-\caption{Confusion Matrix}
-\label{fig:confusion}
-\begin{tabular}{lll}
-                                        & True Positive          & True Negative          \\ \cline{2-3} 
-\multicolumn{1}{l|}{Predicted Positive} & \multicolumn{1}{l|}{a} & \multicolumn{1}{l|}{b} \\ \cline{2-3} 
-\multicolumn{1}{l|}{Predicted Negative} & \multicolumn{1}{l|}{c} & \multicolumn{1}{l|}{d} \\ \cline{2-3} 
-\end{tabular}
-\end{figure}
-\egroup
-\bigskip
+Mean Absolute Error, hereafter referred to as "MAE",  of a DNN is the first utilized performance metric, defined as Equation \ref{eq:mae},
 
-The six metrics include accuracy, sensitivity, specificity, positive predicted value hereafter referred to as "PPV, negative predicted value hereafter referred to as "NPV" and F1.
-Table \ref{table:metrics} depicts the mathematical composition of these performance metrics, by partly referring to confusion matrix depicted as Figure \ref{fig:confusion}.
-In substantive terms, accuracy can simply be understood as the proportion of correct classifications.
-Sensitivity is understood as the proportion true positives, whereas specificity is understood as the proportion of true negatives.
-PPV reflects the proportion of predicted positives that are correctly predicted as positive.
-NPV on the other hand reflects the proportion of predicted negatives that are correctly predicted to be negative.
-Lastly, F1-score is a function of both sensitivity and PPV, seeking balance between the latter two.
+\begin{equation}
+\label{eq:mae}
+\frac{1}{n} \sum^n_{i=1}|f(x_i)-y_i| 
+\end{equation}
+where $n$ refers to the amount of windows utilized for testing, $x_i$ to the predicted value for window $i$ and $y_i$ to the true label of window $i$.
+The MAE constitutes the most straightforward metric for the assessment in performance of a DNN, especially since the value can simply be interpreted as the average amount by which the prediction was off.
 
-\bgroup
-\def\arraystretch{1.8}%  
-\begin{table}[h]
-\caption{Utilized Performance Metrics}
-\label{table:metrics}
-\begin{tabular}{ll}
-\hline
-Accuracy:                       & \(\frac{\!\!\!\!\!\!\!\!\!\!\!\!\!\!a+d}{a+b+c+d}\) \\
-Sensitivity:                    & \(\frac{a}{a+c}\)                                   \\
-Specificity:                    & \(\frac{d}{b+d}\)                                   \\
-Positive Predicted Value (PPV): & \(\frac{a}{a+b}\)                                   \\
-Negative Predicted Value (NPV):       & \(\frac{d}{c+d}\)                                   \\
-F1-score:                     & \(\frac{2*Sensitivity*PPV}{Sensitivity+PPV}\)       \\ \hline
-\end{tabular}
-\end{table}
-\egroup
+Root Mean Squared Error, hereafter referred to as RMSE, is the second utilized performance metric, defined as Equation \ref{eq:rmse},
 
-For each of the three single-modular networks, as well as each of the three multi-modular network variants, these six metrics have been constructed and reported.
-The network that performed best across the range of these metrics was considered to be the superior performing network.
-In case of contradictory interpretations, a reference was made back to the mathematical definition and substantive interpretation of the previously delineated performance metrics.
-To summarize, with the described assessment approach it was aimed to gain insight into multiple dimension of network performance, resulting in a broad and complete assessment of performance altogether.
+\begin{equation}
+\label{eq:rmse}
+\sqrt{{\frac{1}{n} \sum^n_{i=1}|f(x_i)-y_i|}^2}
+\end{equation}
+where $n$ refers to the amount of windows utilized for testing, $x_i$ to the predicted value for window $i$ and $y_i$ to the true label of window $i$.The RMSE, which is strongly related to the MAE, differs in that it punishes big absolute differences more severely.
+
+Finally, the Pearson Correlation Coefficient, hereafter referred to as simply "correlation", constitutes the third utilized performance metric defined as Equation  \ref{eq:corr},
+
+\begin{equation}
+\label{eq:corr}
+\rho_{X,Y} = \frac{cov(X,Y)}{\sigma_{X} \sigma_{Y}}
+\end{equation}
+where $x$ refers to the predicted values for the test windows,  $y$ to the true labels of test windows and $\sigma_{X}\, \& \,\sigma_{Y}$ refer to the standard deviation of $x$ and $y$ respectively.
+Conceptually, correlation indicates the coherence between predictions and labels, hereby posing an alternative model performance metric.
 
@@
 \section{Results}
+Before illustrating results,  a short elaboration on the testing procedure will be provided.
+Windows of eight seconds each were cut, resulting in a total of 9474 windows over all respondents, i.e.
+on average about 351 windows per respondent.
+For each network for each respondent individually,  80\% of all windows have been used for training, 10\% for validation within the training process and 10\% for assessing performance of the trained DNN's.
+This results in an average of 35 windows for assessing DNN performance per respondent, i.e.
+a total of 969 windows in total.
+Partitioning windows into train-, validation- and testing -sets was done systematically by selecting every \textit{n-th} window, such that windows over the entire duration of the experiment were represented equally in each partition.
+
+The distribution of all 9474 window labels, aggregated for all respondents,  is depicted as Figure \ref{fig:labels}.
+It becomes readily apparent that distribution of the window labels displays a noticeably right-skewed tendency, with a median of 5.75 and a 12.75 90\% upper-bound, implying that higher workload windows are relatively uncommon within both train and test partitions.
+\vspace{0.2cm}
+
+\begin{figure}[h]
+\caption{Distribution Window Labels}
+\includegraphics[scale=0.42]{labels.png}
+\label{fig:labels}
+\floatfoot{\emph{Note:} The solid line represents the median, whereas the two dashed line represent the 10\% and 90\% quantiles respectively.}
+\end{figure}
+
+\subsection{Single-modular Network Performance}
+
+\newgeometry{margin=1.4cm}
+\begin{figure}
+\caption{Mean Absolute Error (MAE) per modality}
+\bigskip
+\includegraphics[scale=0.7]{mae_hist.png}
+\label{fig:mae_hist}
+\floatfoot{\emph{Note:} The solid line represents the medians, whereas the two dashed line represent the 10\% and 90\% quantiles respectively.}
+\end{figure}
+\restoregeometry
+
+\newgeometry{margin=1.1cm}
+\begin{figure}
+\caption{Mean Absolute Error (MAE) against label size}
+\bigskip
+\includegraphics[scale=0.67]{mae_scatter.png}
+\label{fig:mae_scatter}
+\end{figure}
+\restoregeometry
+
+\subsection{Multi-modular Network Performance}
+
 Results EEG networks 
@@
 
-\newgeometry{margin=1.4cm}
-\begin{figure}
-\caption{Mean Absolute Error (MAE) per modality}
-\bigskip
-\includegraphics[scale=0.7]{mae_hist.png}
-\label{fig:mae_hist}
-\end{figure}
-\restoregeometry
-
-\newpage
-
-\newgeometry{margin=1.1cm}
-\begin{figure}
-\caption{Mean Absolute Error (MAE) against label size}
-\bigskip
-\includegraphics[scale=0.67]{mae_scatter.png}
-\label{fig:mae_scatter}
-\end{figure}
-\restoregeometry
-
 \section{Limitations}
@@
    \item hardware failure?
+   \item The fact that we use TLX as labels.
 \end{itemize}

### 2021-04-13 pytorch/train.py

@@ -23,7 +23,7 @@ except ModuleNotFoundError:
 
 
 #Included participants
-participants = ["bci22",
+participants = ["bci10", "bci12", "bci13", "bci17", "bci21", "bci22",
                 "bci23", "bci24", "bci26", "bci27", "bci28", "bci29", "bci30", 
                 "bci31", "bci32", "bci33", "bci34", "bci35", "bci36", "bci37", 
                 "bci38", "bci39", "bci40", "bci41", "bci42", "bci43", "bci44"]
@@ -62,7 +62,7 @@ for modality in modalities:
 ################################### Multi-modality networks #################################
 #############################################################################################
 #############################################################################################
-"""
+
 for i in participants:
     
     #Select correct hpo file
@@ -72,24 +72,10 @@ for i in participants:
     loop_multi.MultiTrainLoop(participant = i,
                     batch_size = batch_size, hpo = hpo,
                     epochs = epochs, trainortest = "train")
-"""
 
 
 
 
 
-"""
-#TEMP
-#check amount of data for each person
-lengths = np.array([])
-for participant in participants:
-    path = "pipeline/prepared_data/"+participant+".pickle"
-    pydata =  dataprep.PytorchDataset(path = path,           #Creating PyTorch dataset
-                                      modality = "EEG")
-    padding_length = dataprep.PaddingLength(pydata) #Determining the longest window for later use
-    lengths = np.append(lengths, [padding_length])
-import matplotlib.pyplot as plt
-plt.plot(lengths)
-plt.show()
-print("ha;;p")
-"""
+
+

### 2021-04-13 results/descriptives/2.creat_figure.r

@@ -1,38 +1,0 @@
-######################################################
-################## 0. PREREQUISITES ##################
-######################################################
-#Setting seed
-set.seed(7931)
-
-#Loading libraries
-require(rstudioapi) #Utilized for automatically setting wd
-require(ggplot2)  #Utilized for plotting
-
-#Setting working directory
-setwd(dirname(getActiveDocumentContext()$path)) 
-
-#Loading data
-data <- readRDS("./data/data.rds")
-
-######################################################
-################# 2. DATA PREPARATION ################
-######################################################
-
-#Create ordinal age variable
-data$age_cat <- cut(data$age, breaks = c(14,19,24,29,34,39,44,49,54,59,64), labels = c("15-19","20-24","25-29","30-34","35-39","40-44","45-49","50-54","55-59","60-64"))
-
-#Drop unused factor levels
-data$gender <-  droplevels(data$gender)
-
-######################################################
-################### 3. CREATING PLOT #################
-######################################################
-
-#Creating plots
-#Histogram
-ggplot(data, aes(x = age_cat, fill=gender, color = gender))+
-  geom_histogram(alpha=0.5, stat = "count",position="identity")+
-  xlab("Age")+
-  ylab("Count")
-
-                 

### 2021-04-14 manuscript/manuscript.tex
Manuscript: Finished result section

@@
 \usepackage[capposition=top]{floatrow}
+\usepackage{showframe}
 
@@
 \bigskip
-\includegraphics[scale=0.7]{single_model_architecture}
+\includegraphics[scale=0.69]{single_model_architecture}
 \label{fig:singlearchitecture}
@@
 \bigskip
-\includegraphics[scale=0.7]{multi_model_architecture}
+\includegraphics[scale=0.69]{multi_model_architecture}
 \label{fig:multiarchitecture}
@@
 
-Mean Absolute Error, hereafter referred to as "MAE",  of a DNN is the first utilized performance metric, defined as Equation \ref{eq:mae},
+The Mean Absolute Error, hereafter referred to as "MAE",  of a DNN is the first utilized performance metric, defined as Equation \ref{eq:mae},
 
@@
 
-Root Mean Squared Error, hereafter referred to as RMSE, is the second utilized performance metric, defined as Equation \ref{eq:rmse},
+The Root Mean Squared Error, hereafter referred to as RMSE, is the second utilized performance metric, defined as Equation \ref{eq:rmse},
 
@@
 \label{eq:corr}
-\rho_{X,Y} = \frac{cov(X,Y)}{\sigma_{X} \sigma_{Y}}
+r_{X,Y} = \frac{cov(X,Y)}{\sigma_{X} \sigma_{Y}}
 \end{equation}
@@
 on average about 351 windows per respondent.
-For each network for each respondent individually,  80\% of all windows have been used for training, 10\% for validation within the training process and 10\% for assessing performance of the trained DNN's.
+For each network for each respondent individually,  80\% of all windows have been used for training, 10\% for validation within the training process and 10\% for the assessment of performance.
 This results in an average of 35 windows for assessing DNN performance per respondent, i.e.
@@
 Partitioning windows into train-, validation- and testing -sets was done systematically by selecting every \textit{n-th} window, such that windows over the entire duration of the experiment were represented equally in each partition.
+These partitions compromise exactly the same windows across the four networks.
 
 The distribution of all 9474 window labels, aggregated for all respondents,  is depicted as Figure \ref{fig:labels}.
-It becomes readily apparent that distribution of the window labels displays a noticeably right-skewed tendency, with a median of 5.75 and a 12.75 90\% upper-bound, implying that higher workload windows are relatively uncommon within both train and test partitions.
-\vspace{0.2cm}
+It becomes readily apparent that distribution of the window labels displays a noticeably right-skewed tendency, with a median of 5.75 and a 12.75 90\% upper-bound quantatile, implying that higher workload windows are relatively uncommon within both train and test partitions.
+\vspace{0.1cm}
 
@@
 \caption{Distribution Window Labels}
-\includegraphics[scale=0.42]{labels.png}
+\includegraphics[scale=0.39]{labels.png}
 \label{fig:labels}
@@
 
-\subsection{Single-modular Network Performance}
+\subsection{Deep Neural Network Performance}
+Depicted in Table \ref{table:results} are the performance metrics for each of the trained DNN's.
+The most conspicuous result that becomes apparent is that the multi-modality networks performs consistently worse on all metrics as compared with both the single-modular EEG and GSR networks.
 
-\newgeometry{margin=1.4cm}
-\begin{figure}
-\caption{Mean Absolute Error (MAE) per modality}
+\vspace{0.3cm}
+\bgroup
+\def\arraystretch{1.6}%  
+\begin{table}[h]
+\caption{Deep Neural Network performance metrics}
+\label{table:results}
+\begin{tabular}{lllll}
+\hline
+                                                                               & EEG\hspace{0.5cm} & PPG\hspace{0.5cm} & GSR\hspace{0.5cm} & Multi\hspace{0.5cm} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Mean Absolute Error\\ \hspace{1.2cm}(\textit{0-1 scale})\end{tabular} & 0.110 & 0.136 & 0.119 & 0.128  \\
+\begin{tabular}[c]{@{}l@{}}Mean Absolute Error\\ \hspace{0.25cm}(\textit{original 0-20 scale})\end{tabular} & 2.206 & 2.717 & 2.377 & 2.570 \\
+Root Mean Square Error                                                         & 0.154 & 0.180 & 0.159 & 0.167 \\
+Pearson Correlation                                                                    & 0.688 & 0.530 & 0.653 & 0.609 \\ \hline
+\end{tabular}
+\end{table}
+
+Performance in terms of MAE of the EEG networks is superior over all other networks, with $MAE = 0.110$ with a standard deviation of $\sigma = 0.154$.
+The DNN's demonstrating the next best performance are the GSR networks, closely pursuing the EGG networks,  and displaying $MAE = 0.119$ with a standard deviation of $\sigma = 0.159$.
+Surprisingly, the multi-modular networks check out on the third place, displaying $MAE = 0.128$ with a standard deviation of $\sigma = 0.167$.
+The PPG networks can clearly be considered the worst performing networks, displaying $MAE = 0.136$ with a standard deviation of $\sigma = 0.179$.
+
+A similar pattern can be observed when observing the RMSE.This is not surprising, given the RMSE is very similar to the MAE.
+The difference is that the RMSE values for all networks reside slightly higher, which is not surprising for the punishes high deviations more severely.
+
+The correlation between predictions and labels are indicative of a similar pattern as compared with the other metrics.
+Although patterns are similar, an interesting disparity is, however, that the differences across the four architectures is more substantial.
+The value for the EEG networks are observed to be $r=0.688$, which is interpretable as a rather strong correlation.
+Equally so, the GSR networks display a fairly strong correlation of $r=0.653$.
+Again, Both the multi and GSR networks are the least accurately performing, displaying a correlation of $r=0.609$ and $r=530$ respectively.
+
+A graphical visualization of the prediction errors for each of the four network architectures is depicted as Figure \ref{fig:mae_hist}.
+
+\vspace{0.3cm}
+\begin{figure}[h]
+\caption{Error per modality}
 \bigskip
-\includegraphics[scale=0.7]{mae_hist.png}
+\includegraphics[scale=0.6]{error_hist.png}
 \label{fig:mae_hist}
-\floatfoot{\emph{Note:} The solid line represents the medians, whereas the two dashed line represent the 10\% and 90\% quantiles respectively.}
+\floatfoot{\emph{Note:} The solid line represents the medians, whereas the two dashed line represent the 10\% and 90\% quantiles respectively. The displayed numbers are the values of the quantiles.}
 \end{figure}
-\restoregeometry
 
-\newgeometry{margin=1.1cm}
-\begin{figure}
-\caption{Mean Absolute Error (MAE) against label size}
-\bigskip
-\includegraphics[scale=0.67]{mae_scatter.png}
+In line with the previously delineated results, it becomes readily apparent that the distribution of the prediction errors for the EEG networks approximates the normal distribution most closely, as indicative by the strong accumulation around 0 error and relatively flat tails.
+Not surprisingly, the two worst performing DNN's, being the multi-modular and PPG networks, display much thicker tails, and are observed to have a less accumulation around the 0 error mark (i.e.
+visually "less-peaked").
+This is equally so demonstrated by the 10\% and 90\% quantiles, residing farthest from the median.
+All distributions are observed to be slightly left-skewed, as indicated firstly by shape and secondly by the fact that 10\% quantiles are farther removed from the median as compared with the 90\% quantiles.
+Despite that this left-leaning tendency is observable for all network architectures, it is most profound for the PPG and multi-modular networks.
+These previously delineated anomalies indicate that all networks are less accurate in predicting high-labeled windows, and that this seems to be more profound for the PPG and multi-modular networks.
+
+Figure \ref{fig:mae_scatter} helps explore this notion into more detail,  by plotting prediction error of each window against its label value,  in addition to their linear relationship and correlation coefficient.
+
+\vspace{0.3cm}
+\begin{figure}[h]
+\caption{Window Prediction Error as opposed to Window Label Value}
+\includegraphics[scale=0.64]{mae_scatter.png}
 \label{fig:mae_scatter}
+\floatfoot{\emph{Note:} The red lines represent the linear relationship between prediction error and label value. The values \textit{r} represent their Pearson Correlation Coefficient.}
 \end{figure}
-\restoregeometry
 
-\subsection{Multi-modular Network Performance}
+Firstly, it becomes immediately apparent that higher labeled windows are substantially less prevailing, as indicative by the thin spreading of dots for the higher labels, conform to the conclusion drawn from the earlier depicted Figure \ref{fig:labels}.
+Noteworthy is that, for each the four network architectures, a relationship can be observed between the height of the absolute value of the prediction error and the height of the label.
+This is indicative by the moderately ascending slope, as well as the correlation coefficients.
+Substantively, this implies that all network architectures are observed to be considerably less accurate when predicting high labeled windows.
+This tendency upholds the most for the multi-modular and PPG networks, with an observable correlation coefficients as high as $r=0.37$ for the multi-modular networks specifically.
+A, less severe, but still noteworthy relationship between prediction error and label size is observable for both the GSR and EEG architectures,  with a correlation coefficients of $r=0.24$ and $r=0.28$ respectively.
 
-Results EEG networks 
-\begin{itemize}
-\item Correlation predictions and labels: 0.68788.
-\item Mean asbsolute error: 0.11029.
-\item Mean absolute error on the original scale: 2.20586.
-\end{itemize}
-\bigskip
-
-Results PPG networks 
-\begin{itemize}
-\item Correlation predictions and labels: 0.52998.
-\item Mean asbsolute error: 0.13587.
-\item Mean absolute error on the original scale: 2.71747.
-\end{itemize}
-\bigskip
-
-Results GSR networks 
-\begin{itemize}
-\item Correlation predictions and labels: 0.65339.
-\item Mean asbsolute error: 0.11883.
-\item Mean absolute error on the original scale: 2.37665.
-\end{itemize}
-\bigskip
-
-Results Multi-Modality networks 
-\begin{itemize}
-\item Correlation predictions and labels: 0.60864.
-\item Mean asbsolute error: 0.12848.
-\item Mean absolute error on the original scale: 2.56964.
-\end{itemize}
-
-\section{Limitations}
+\section{Conclusion and Discussion}
+It can be concluded that the single-modular EEG networks consistently exhibit the best performance,  with a rather noteworthy difference on the correlations in particular.
+The single-modular GSR networks, although being worse as compared with the EEG networks, also were observed to exhibit fairly adequate performance.
+Most surprising is that the multi-modular networks performed substantially worse as the previously mentioned, especially as compared with the EEG networks.
+This was not expected, for one is enticed to expect that the network combining information from multiple modalities would yield more adequate performance as compared with networks solely using a single of these modalities.
+Apparently
 

### 2021-04-20 manuscript/manuscript.tex

--- 2021-04-13 manuscript/manuscript.tex
@@
 \usepackage[capposition=top]{floatrow}
+\usepackage{authblk}
 
@@
 
+%Frontpage specifications 
+\title{Predicting  Mental Workload: An Intermediate Fusion Deep Learning Approach}
+
+\author[1]{Bart-Jan Boverhof \thanks{b.boverhof@students.uu.nl}}
+\author[2]{Bernard P. Veldkamp\thanks{b.p.veldkamp@utwente.nl}}
+\affil[1]{\normalsize Faculty of Behavioral, Management and Social Sciences, University of Twente}
+\affil[2]{\normalsize Faculty of Social and Behavioural Sciences, Utrecht University}
+
+\renewcommand\Authands{ and }
+\date{\today}
+
 \begin{document}
 
-%Title page 
-\begin{titlepage}
-\begin{center}
-\LARGE{\textbf{The Realtime Assessment of Mental Workload by Means of Multiple Bio-Signals}}\\
-\vspace*{2\baselineskip}
-\Large{\textbf{Masterthesis Report}}\\
-Methodology and Statistics for the Behavioral, Biomedical and Social Sciences\\
-\vspace*{1\baselineskip}
-Utrecht University\\
-\vspace*{4\baselineskip}
-{Bart-Jan Boverhof, 6000142}\\
-\vspace*{1\baselineskip}
-{\textbf{Thesis Supervisor}}\\
-Prof.dr.ir. B.P. Veldkamp\\
-\vspace*{1\baselineskip}
-{\textbf{Date}}\\
-January 7, 2021\\
-\vspace*{1\baselineskip}
-\end{center}
-\end{titlepage}
+\maketitle
 
-%Introduction section
+\begin{abstract}
+Morbi tempor congue porta.
+Proin semper, leo vitae faucibus dictum, metus mauris lacinia lorem, ac congue leo felis eu turpis.
+Sed nec nunc pellentesque, gravida eros at, porttitor ipsum.
+Praesent consequat urna a lacus lobortis ultrices eget ac metus.
+In tempus hendrerit rhoncus.
+Mauris dignissim turpis id sollicitudin lacinia.
+Praesent libero tellus, fringilla nec ullamcorper at, ultrices id nulla.
+Phasellus placerat a tellus a malesuada.
+\end{abstract}
+
+\hspace*{3.6mm}\textit{Keywords:} lorem, ipsum, dolor, sit amet, lectus % Keywords
+
+\newpage
 \section{Introduction}
@@
 
-With the current research endeavor we explore the feasibility of an approach to workload assessment by means of multiple modalities simultaneously, hereafter referred to as "multi-modular approach".
+With the current research endeavor we explore the feasibility of an approach to workload assessment by means of multiple modalities simultaneously, hereafter referred to as "multimodal approach".
 We do so by combining data-streams stemming from three different modalities, being electroencephalography, photoplethysmography and galvanic skin response.
@@
 A deep learning approach towards modeling is adopted.
-A range of four different deep neural networks, hereafter referred to as "DNN's", are constructed and contrasted in performance: three of which are single-modular DNN's, i.e.
+A range of four different deep neural networks, hereafter referred to as "DNN's", are constructed and contrasted in performance: three of which are unimodal DNN's, i.e.
 networks each utilizing data from only a single modality.
 Thus,  one DNN solely utilizes the EEG modality,  one solely utilizes GSR and one solely utilizes PPG.
-The fourth network is a multi-modular network combining all three modalities into one.
-With this research we firstly sought to explore which modalities constitute the most adequate predictors of workload in an experimental setting, and secondly whether a multi-modular combination is preferable over the three simpler (but much less computationally demanding) single-modular DNN's.
+The fourth network is a multimodal network combining all three modalities into one.
+With this research we firstly sought to explore which modalities constitute the most adequate predictors of workload in an experimental setting, and secondly whether a multimodal combination is preferable over the three simpler (but much less computationally demanding) unimodal DNN's.
 This assessment will be propelled by contrasting network performance, however when drawing conclusions, considerations regarding computational costs will be taken into consideration as well.
@@
 The following section provides an overview of preceding research regarding the assessment of workload by means of physiological bio-signals, with a focus on deep learning approaches.
-Attention is predominantly placed upon the most feasible network architectures, in addition to a range of model optimization techniques and to the data fusion strategy for the multi-modular DNN.
+Attention is predominantly placed upon the most feasible network architectures, in addition to a range of model optimization techniques and to the data fusion strategy for the multimodal DNN.
 The final part of this section will be dedicated to hyperparameter optimization.
@@
 Both the deep and shallow ConvNets were found to reach at least similar, and in some regards better classification results as compared with the FBCSP baseline approach.
-Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, exhibiting an accuracy of 92.4 \% \cite{schirrmeister2017deep}.
+Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, exhibiting an accuracy of 92.4\% \cite{schirrmeister2017deep}.
 
@@
 Research by \citeA{biswas2019cornet} explored a deep learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
-Exceptional results were realized with a DNN, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
+Exceptional results were realized with a DNN, attaining an average accuracy of 96\% \cite{biswas2019cornet}.
 This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed by two LSTM layers.
 
-\subsubsection{Multi-modular Fusion Strategy}  
-When conducting a multi-modular deep learning approach,  information streams stemming from the different modalities are required to be combined, i.e.
+\subsubsection{Multimodal Fusion Strategy}  
+When conducting a multimodal deep learning approach,  information streams stemming from the different modalities are required to be combined, i.e.
 "fused", at a certain point in the network in order to ultimately result in a single prediction of workload.
@@
 
-Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modular deep-learning problems.
+Lastly, intermediate fusion is the most widely employed fusion strategy for multimodal deep-learning problems.
 Data streams are usually fused by a concatenation layer, joining the outputs of the separately defined network parts of each modality.
@@
 
-Indeed, when consulting the literature, one is prone to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep learning approaches.
+Indeed, when consulting the literature, one is prone to conclude that intermediate fusion strategies are the most prevailing for multimodal deep learning approaches.
 When taking an intermediate fusion approach, the higher-order part of the network needs to be designed and established, for which several previous research endeavors are considered.
-\citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers and two dense layers.
+\citeA{rastgoo2019automatic} utilized a multimodal ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers and two dense layers.
 A simpler approach is adopted by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers.
@@
 
-\subsubsection{Single-modular Network}
-All single-modular network architectures took inspiration from previously delineated research \cite{schirrmeister2017deep} \cite{dolmans2020perceived} \cite{sun2019hybrid} \cite{biswas2019cornet}.
+\subsubsection{Unimodal Network}
+All unimodal network architectures took inspiration from previously delineated research \cite{schirrmeister2017deep} \cite{dolmans2020perceived} \cite{sun2019hybrid} \cite{biswas2019cornet}.
 In contrast with most of these previous endeavors, we opted for a ConvNet-only approach, i.e.
@@
 
-The three single-modular DNN architectures are depicted alongside one another as Figure \ref{fig:singlearchitecture}.
-Each of the single-modular networks can be distinguished by two separate part, being the convolutional part and the prediction part.
+The three unimodal DNN architectures are depicted alongside one another as Figure \ref{fig:singlearchitecture}.
+Each of the unimodal networks can be distinguished by two separate part, being the convolutional part and the prediction part.
 The objective of the convolutional part is to extract features from the data.
@@
 For training, a total of 600 epochs have been made through the data for each network independently.
-All training and HPO of the single-modular networks has been done on a V100 GPU,  offered by the GPU cloud service Google Collab.
-Total running time for the single-modular networks was about four days, the most of which was absorbed by HPO.
+All training and HPO of the unimodal networks has been done on a V100 GPU,  offered by the GPU cloud service Google Collab.
+Total running time for the unimodal networks was about four days, the most of which was absorbed by HPO.
 
@@
 \begin{figure}
-\caption{The Three Single-modular Network Architectures}
+\caption{The Three Unimodal Network Architectures}
 \bigskip
-\includegraphics[scale=0.7]{single_model_architecture}
+\includegraphics[scale=0.69]{single_model_architecture}
 \label{fig:singlearchitecture}
@@
 \hline
-        & EEG-Net/Part  & GSR-Net/Part  & PPG-Net/Part  & Multi-Modular Head-Net     \\ \hline
- Single-Modular-Nets & Dense Out: 1 & Dense Out: 1 & Dense Out: 1 &   \\
+        & EEG-Net/Part  & GSR-Net/Part  & PPG-Net/Part  & Multimodal Head-Net     \\ \hline
+ Unimodal-Nets & Dense Out: 1 & Dense Out: 1 & Dense Out: 1 &   \\
         & Dense 1: \emph{hpo} & Dense 1: \emph{hpo} & Dense 1: \emph{hpo} &   \\
@@
         & Conv1: 25 & Conv1: 16 & Conv1: 16 &  \\         
-  Multi-Modular-Net & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense Out: 1  \\
+  Multimodal-Net & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense Out: 1  \\
         & Conv4: 200 & Conv4: 128 & Conv4: 128  &  Dense 3: \emph{hpo} \\ 
@@
 
-\subsubsection{Multi-modular Network}
-The network architecture utilized for the multi-modular approach was determined by combining the previously characterized single-modular networks with insights drawn from previous research, in particular \cite{han2020classification}.
-A visual representation of the multi-modular network is depicted as Figure \ref{fig:multiarchitecture}.
-An overview of the amount of utilized filters and neurons for each layer of the multi-modular network is provided in Table \ref{table:modelvariations}.
+\subsubsection{Multimodal Network} \label{section:multimodal}
+The network architecture utilized for the multimodal approach was determined by combining the previously characterized unimodal networks with insights drawn from previous research, in particular \cite{han2020classification}.
+A visual representation of the multimodal network is depicted as Figure \ref{fig:multiarchitecture}.
+An overview of the amount of utilized filters and neurons for each layer of the multimodal network is provided in Table \ref{table:modelvariations}.
 
-The network architecture for the single-modular parts of the network are separately defined entities of the multi-modular network, but are highly similar as compared with the previously delineated single-modular networks.
+The network architecture for the unimodal parts of the network are separately defined entities of the multimodal network, but are highly similar as compared with the previously delineated unimodal networks.
 An intermediate fusion strategy is adopted due to its highly flexible nature as compared with alternative fusion strategies.
 The output of all three distinct parts in the network were flattened, followed by a dense layer and RELU activation.
-Flattening was nescessary such that all inputs were represented in one-dimensional space, after which concatenation was possible.
+Flattening was necessary such that all inputs were represented in one-dimensional space, after which concatenation was possible.
 The prediction part, also referred to as "Head-Network", consists of three dense layers, alternated with dropout, batch normalization and RELU activation.
 
-Again, consistent with training, HPO was equally so done for each respondent individually, resulting in 27 optimized sets of parameters each of the 27 multi-modular networks.
+Again, consistent with training, HPO was equally so done for each respondent individually, resulting in 27 optimized sets of parameters each of the 27 multimodal networks.
 We optimized the learning rate, dropout rate and the amount of neurons for the first and second dense layers in 18 trials per network.
@@
 All training and HPO has been done on a Cloud TPU v2,  offered by the GPU cloud service Google Collab Pro.
-Total running time for the multi-modular networks was about 12 days, the most of which absorbed by HPO.
+Total running time for the multimodal networks was about 12 days, the most of which absorbed by HPO.
 
@@
 \begin{figure}
-\caption{The Multi-modular Network Architecture}
+\caption{The Multimodal Network Architecture}
 \bigskip
-\includegraphics[scale=0.7]{multi_model_architecture}
+\includegraphics[scale=0.69]{multi_model_architecture}
 \label{fig:multiarchitecture}
@@
 
-Mean Absolute Error, hereafter referred to as "MAE",  of a DNN is the first utilized performance metric, defined as Equation \ref{eq:mae},
+The Mean Absolute Error, hereafter referred to as "MAE",  of a DNN is the first utilized performance metric, defined as Equation \ref{eq:mae}
 
@@
 
-Root Mean Squared Error, hereafter referred to as RMSE, is the second utilized performance metric, defined as Equation \ref{eq:rmse},
+The Root Mean Squared Error, hereafter referred to as RMSE, is the second utilized performance metric, defined as Equation \ref{eq:rmse}
 
@@
 
-Finally, the Pearson Correlation Coefficient, hereafter referred to as simply "correlation", constitutes the third utilized performance metric defined as Equation  \ref{eq:corr},
+Finally, the Pearson Correlation Coefficient, hereafter referred to as simply "correlation", constitutes the third utilized performance metric defined as Equation  \ref{eq:corr}
 
@@
 \section{Results}
-Before illustrating results,  a short elaboration on the testing procedure will be provided.
-Windows of eight seconds each were cut, resulting in a total of 9474 windows over all respondents, i.e.
-on average about 351 windows per respondent.
-For each network for each respondent individually,  80\% of all windows have been used for training, 10\% for validation within the training process and 10\% for assessing performance of the trained DNN's.
-This results in an average of 35 windows for assessing DNN performance per respondent, i.e.
-a total of 969 windows in total.
+Before illustrating DNN results,  a short elaboration on the testing procedure will be conducted.
+The data streams constituting the entire length of the experiment were cut into windows of eight seconds, resulting in an average of roughly 351 windows per respondent.
+For each network for each respondent individually,  80\% of all windows have been used for training, 10\% for validation within the training process and 10\% for the assessment of performance.
+This resulted in an average of 35 windows for assessing DNN performance per respondent.
 Partitioning windows into train-, validation- and testing -sets was done systematically by selecting every \textit{n-th} window, such that windows over the entire duration of the experiment were represented equally in each partition.
+For each respondent, the same partitions were used across all four DNN's.
 
 The distribution of all 9474 window labels, aggregated for all respondents,  is depicted as Figure \ref{fig:labels}.
-It becomes readily apparent that distribution of the window labels displays a noticeably right-skewed tendency, with a median of 5.75 and a 12.75 90\% upper-bound, implying that higher workload windows are relatively uncommon within both train and test partitions.
-\vspace{0.2cm}
+It becomes readily apparent that distribution of the window labels displays a noticeably right-skewed tendency, with a median of 5.75 and an 90\% upper-bound quantatile of 12.75, implying that higher workload windows are relatively uncommon within all partitions.
+\vspace{0.1cm}
 
@@
 
-\subsection{Single-modular Network Performance}
+\subsection{Deep Neural Network Performance}
+Depicted in Table \ref{table:results} are the performance metrics for each of the four network architectures.
+The most conspicuous result that becomes apparent is that the multimodal architecture performs consistently worse on all metrics as compared with both the unimodal EEG and GSR networks.
 
-\newgeometry{margin=1.4cm}
-\begin{figure}
-\caption{Mean Absolute Error (MAE) per modality}
+\vspace{0.3cm}
+\bgroup
+\def\arraystretch{1.6}%  
+\begin{table}[h]
+\caption{Deep Neural Network Performance Metrics}
+\label{table:results}
+\begin{tabular}{lllll}
+\hline
+                                                                               & EEG\hspace{0.5cm} & PPG\hspace{0.5cm} & GSR\hspace{0.5cm} & Multi\hspace{0.5cm} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Mean Absolute Error\\ \hspace{1.2cm}(\textit{0-1 scale})\end{tabular} & 0.110 & 0.136 & 0.119 & 0.128  \\
+\begin{tabular}[c]{@{}l@{}}Mean Absolute Error\\ \hspace{0.25cm}(\textit{original 0-20 scale})\end{tabular} & 2.206 & 2.717 & 2.377 & 2.570 \\
+Root Mean Square Error                                                         & 0.154 & 0.180 & 0.159 & 0.167 \\
+Pearson Correlation                                                                    & 0.688 & 0.530 & 0.653 & 0.609 \\ \hline
+\end{tabular}
+\end{table}
+
+Performance in terms of MAE for the EEG architecture is highest of all other architectures, with $MAE = 0.110$ with a standard deviation, hereafter referred to as "\emph{sd}" of $\sigma = 0.154$.
+The architecture demonstrating the next highest MAE is the GSR architecture, displaying an $MAE = 0.119$ with an sd of $\sigma = 0.159$.
+The multimodal networks is observed to display an $MAE = 0.128$ with an sd of $\sigma = 0.167$.
+Lastly, the PPG networks exhibits the highest error of $MAE = 0.136$ with an sd of $\sigma = 0.179$.
+Results in terms of RMSE adhere to a similar pattern as MAE do, which is not surprising given that the RMSE and MAE are similar.
+The difference is that the RMSE values for all networks reside slightly higher, which is not surprising for the punishes high deviations more severely.
+The correlation between predictions and labels are indicative of a similar pattern as compared with the other metrics.
+However despite similarity, an interesting disparity is that the differences across the four architectures seems to be more substantial.
+The value for the EEG networks are observed to be $r=0.688$.
+Equally so, the GSR networks display a fairly strong correlation of $r=0.653$.
+Again, both the multimodal and GSR architectures are the least adequately performing in terms of correlation, displaying $r=0.609$ and $r=0.530$ respectively.
+
+An independent samples t-test was conducted to formally test differences in network performance.
+To be precise, we statistically tested the difference in absolute error per window across several pairs of architectures (two-sided with $\alpha = 0.05$).
+The absolute error for the unimodel EEG architecture was found to be significantly lower as compared with the multimodel architecture $t(1936)=-2.566, p=0.01$.
+We did not find a significant difference in absolute error between the GSR- and multimodal -architecture $t(1936)=-1.188, p=0.24$, and equally so no significant difference was found between the GSR- and multi- architectures $t(1936)=-1.463, p = 0.144$.
+Lastly, absolute error for the PPG architecture was found to be significantly lower as compared with the GSR architecture $t(1936)=-2.636 , p = 0.008$, but no difference was found between the GSR- and multimodal -architecture $t(1936)=-1.164 , p = 0.245$.
+
+To explore the difference in performance into more detail, a graphical visualization of the prediction errors for each of the four network architectures is depicted as Figure \ref{fig:mae_hist}.
+
+\vspace{0.2cm}
+\begin{figure}[h]
+\caption{Prediction Error per modality}
 \bigskip
-\includegraphics[scale=0.7]{mae_hist.png}
+\includegraphics[scale=0.44]{error_hist.png}
 \label{fig:mae_hist}
-\floatfoot{\emph{Note:} The solid line represents the medians, whereas the two dashed line represent the 10\% and 90\% quantiles respectively.}
+\floatfoot{\emph{Note:} The solid line represents the medians, whereas the two dashed line represent the 10\% and 90\% quantiles respectively.
+The displayed numbers are the values of the respective quantiles.}
 \end{figure}
-\restoregeometry
 
-\newgeometry{margin=1.1cm}
-\begin{figure}
-\caption{Mean Absolute Error (MAE) against label size}
-\bigskip
-\includegraphics[scale=0.67]{mae_scatter.png}
+In line with the previously presented performance metrics, it becomes readily apparent that the distribution of the prediction errors for the architecture that scored highest across all metrics, i.e.
+the EEG architecture, approximates the normal distribution most closely, as indicative by the strong accumulation around 0 error and relatively flat tails.
+The two worst performing architectures, i.e.
+multimodal and PPG, display much thicker tails, and are observed to have a less accumulation around the 0 error mark (i.e.
+visually "less-peaked").
+This is equally so demonstrated by the 10\% and 90\% quantiles, residing farthest from the median.
+All distributions are observed to be slightly left-skewed, as indicated firstly by shape and secondly by the fact that 10\% quantiles are farther removed from the median as compared with the 90\% quantiles.
+Despite that this left-leaning tendency is observable for all network architectures, it is most profound for the PPG and multimodal architectures.
+The left-leaning tendency of the distribution of predictions errors indicates that most error is due to under-prediction, i.e.
+predicting a label to be lower than it should have been.
+This notion is further investigated by means of Figure \ref{fig:mae_scatter}, plotting absolute prediction error of each window against its label value.
+
+\vspace{0.2cm}
+\begin{figure}[h]
+\caption{Absolute Window Prediction Error as opposed to Window Label Value}
+\includegraphics[scale=0.51]{mae_scatter.png}
 \label{fig:mae_scatter}
+\floatfoot{\emph{Note:} The red lines represent the linear relationship between absolute prediction error and label value.
+The values \textit{r} represent the Pearson Correlation between prediction errors and label values.}
 \end{figure}
-\restoregeometry
 
-\subsection{Multi-modular Network Performance}
+Firstly, it becomes immediately apparent that higher labeled windows are substantially less prevailing, as indicative by the thin spreading of dots for the higher labels, conform to the conclusion drawn from the earlier depicted Figure \ref{fig:labels}.
+Noteworthy is that for each of the four architectures a relationship can be observed between the height of the absolute value of the prediction error and the height of its label.
+This is indicated by the moderately ascending slope, as well as the moderately high and positive correlations.
+Substantively, this implies that all network architectures are observed to be considerably less accurate when predicting high labeled windows.
+This tendency upholds the most for the multimodal and PPG architectures, with an observable correlation coefficients as high as $r=0.37$ for the multimodal architecture specifically.
+A, less severe, but still noteworthy relationship between prediction error and label size is observable for both the GSR and EEG architectures,  with a correlation coefficients of $r=0.24$ and $r=0.28$ respectively.
 
-Results EEG networks 
-\begin{itemize}
-\item Correlation predictions and labels: 0.68788.
-\item Mean asbsolute error: 0.11029.
-\item Mean absolute error on the original scale: 2.20586.
-\end{itemize}
-\bigskip
+\newpage
+\section{Conclusion and Discussion}
+We found that the unimodal EEG architecture consistently scored best on all performance metrics,  with a rather sizable difference when considering correlations between predictions and labels.
+Rather unexpected is the inadequate performance of the multimodal architecture.
+One is enticed to expect that the architecture combining information from multiple modalities yields a multifaceted, hence richer, assessment of workload, and as a consequence attains more adequate performance.
+Indeed this is also to be distinguished from previous research, lending credence to the unexpected character of our results \cite{dolmans2020perceived} \cite{han2020classification} \cite{rastgoo2019automatic}.
+Furthermore, score on performance metrics for the GSR architecture are consistently lower as compared with the EEG architecture, but consistently higher as compared with the multimodal architecture.
+In terms of absolute errors, these differences were not found to be statistically significant, however.
+The unimodal PPG architecture was found to perform worst across the board.
 
-Results PPG networks 
-\begin{itemize}
-\item Correlation predictions and labels: 0.52998.
-\item Mean asbsolute error: 0.13587.
-\item Mean absolute error on the original scale: 2.71747.
-\end{itemize}
-\bigskip
+Although some differences in performance are distinguishable, one must recognize that these differences are of rather modest size.
+Some of the differences in absolute error, although being statistically significant, still differ virtually negligibly in terms of their absolute difference, as indicated by both MAE and RMSE.
+The statistical significance is particularly attributable to the vast amount of degrees of freedom with which was tested.
+Nevertheless, the fact that the multimodal architecture didn't outperform a single of the unimodel architectures deserves some further investigation.
 
-Results GSR networks 
-\begin{itemize}
-\item Correlation predictions and labels: 0.65339.
-\item Mean asbsolute error: 0.11883.
-\item Mean absolute error on the original scale: 2.37665.
-\end{itemize}
-\bigskip
+One imaginable train of thought is that the multimodal architecture should have outperformed at least some of the unimodal architectures, but this was stiffed by the head-network architecture.
+Despite some different head-networks were cross-compared, this was not done in a systematical manner, i.e.
+such as would be possible with HPO.
+We finally opted for a relatively shallow head-network, consisting of several fully connected dense layers.
+The reader might recall from Section \ref{section:multimodal} that HPO and training for the current multimodal architecture already demanded hefty computational resources, and thus considerable time.
+Utilizing a deeper head-network would increase the required computational resources and hence running time exceedingly more.
+Additionally, in spite of some previous research utilizing a relatively deep head-network, a rather shallow network was equally so proposed oftentimes for multimodal workload classification problems \cite{yin2017recognition}, \cite{han2020classification} \cite{rastgoo2019automatic}.
+Moreover, one could propose that that the performance of the multimodal architecture was stiffed by the poor performing unimodal PPG component.
+In order to scrutinize this, we optimized hyperparamaters and trained a multimodal architecture in exactly the same manner, except for omitting the PPG component altogether.
+This network did not perform better on any metric, and results were not reported as a consequence.
 
-Results Multi-Modality networks 
-\begin{itemize}
-\item Correlation predictions and labels: 0.60864.
-\item Mean asbsolute error: 0.12848.
-\item Mean absolute error on the original scale: 2.56964.
-\end{itemize}
+A contrary train of thought is that our case simply didn't benefit from a multimodal approach.
+A classical theorem in the fields of statistics and machine-learning alike is the, sometimes precarious, balance between model complexity and and simplicity.
+A model that is overly complex is in increased peril of overfitting, i.e.
+performing well on training data, but failing to generalize to the test data.
+A more parsimonious model is generally at less jeopardy to fall into this pitfall, however an overly simple model simply doesn't describe the data very well.
+It is not implausible to consider that this mechanism could, at least, partially rationalize why our relatively complex multimodal architecture performs worse as compared with at least one of the simpler unimodal architecture.
+The fact that we trained an individual network for each participant separately, inherently implying that training is not done on an extraordinary sizable amount of data, may lend credence to this explanation: training on insufficient data equally so increases the likelihood of overfitting.
 
-\section{Limitations}
+One is therefore inclined to reflect on the following: Even if a multimodal approach could result in a moderate improvement over unimodal approaches, would this justify the sheer addition in complexity,  the considerable increase in required computational resources and the necessity to possess a multitude of different physiological sensors?
+The answers to this question is naturally heavily dependent upon context, i.e.
+how precise need the network be for the task at hand and how much funding and time is available?
+It is not
+
+The two previously delineated opposite lines of argumentation can be distilled into recommendations for future research endeavors.
+Firstly, insights into the most appropriate network architecture of, in particular, the multimodal head-network is would be beneficial.
+Despite the range of different proposals to architectures with the purpose of workload classification by amongst others \citeA{yin2017recognition}, \citeA{han2020classification} \citeA{rastgoo2019automatic} and \citeA{dolmans2020perceived}, some rough outlines into what is prone to work under different circumstances would be highly beneficial.
 
@@
   \item  More HPO could have been done, to get even better performing models but we had limited computatioal power.   
-  \item This approach costs a lot of computational power to both train and do HPO. Especially since person-specific models are fitted. This upholds mostly for the multi-modal network.
+  \item This approach costs a lot of computational power to both train and do HPO. Especially since person-specific models are fitted. This upholds mostly for the multimodal network.
   \item Due to the sheer size of the trained model and the fact that models are trained person specific, storage sizes of the models are huge.
 This could be unpractical.
-This upholds mostly for the multi-modal network.
+This upholds mostly for the multimodal network.
   \item Possibly different window sizes per modality could lead to better results.

### 2021-04-26 0.manuscript/manuscript.tex
Repo restructure + updates readme files

--- 2021-04-20 manuscript/manuscript.tex
@@
 \graphicspath{ {./figures/} } %Defining image path
+\pagestyle{myheadings}
+\markright{A Deep Learning Approach to Mental Workload Prediction}
 
 %Frontpage specifications 
-\title{Predicting  Mental Workload: An Intermediate Fusion Deep Learning Approach}
+\title{Predicting  Mental Workload: A Multimodal Intermediate Fusion Deep Learning Approach}
 
 \author[1]{Bart-Jan Boverhof \thanks{b.boverhof@students.uu.nl}}
-\author[2]{Bernard P. Veldkamp\thanks{b.p.veldkamp@utwente.nl}}
-\affil[1]{\normalsize Faculty of Behavioral, Management and Social Sciences, University of Twente}
-\affil[2]{\normalsize Faculty of Social and Behavioural Sciences, Utrecht University}
+\author[2]{Bernard P. Veldkamp}
+\affil[1]{\normalsize Faculty of Social and Behavioural Sciences, Utrecht University}
+\affil[2]{\normalsize Faculty of Behavioral, Management and Social Sciences, University of Twente}
 
@@
 \begin{document}
-
 \maketitle
+\thispagestyle{empty}
 
@@
 
-\hspace*{3.6mm}\textit{Keywords:} lorem, ipsum, dolor, sit amet, lectus % Keywords
+\vspace{1cm}
+\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
+\textit{Keywords:} deep-learning, multimodal, mental workload, intermediate fusion, hyperparameter optimization (HPO), brain-computer Interface (\textit{BCI}),  electroencephalography (\textit{EEG}), galvanic skin response (\textit{GSR}), photoplethysmography (\textit{PPG})
+\end{minipage}
 
@@
 \end{equation}
-where $x$ refers to the predicted values for the test windows,  $y$ to the true labels of test windows and $\sigma_{X}\, \& \,\sigma_{Y}$ refer to the standard deviation of $x$ and $y$ respectively.
+where $x$ refers to the predicted values for the test windows,  $y$ to the true labels of test windows, $cov(X,Y)$ to their covariance, and $\sigma_{X}\, \& \,\sigma_{Y}$ refer to the standard deviation of $x$ and $y$ respectively.
 Conceptually, correlation indicates the coherence between predictions and labels, hereby posing an alternative model performance metric.
@@
 \newpage
-\section{Conclusion and Discussion}
-We found that the unimodal EEG architecture consistently scored best on all performance metrics,  with a rather sizable difference when considering correlations between predictions and labels.
-Rather unexpected is the inadequate performance of the multimodal architecture.
-One is enticed to expect that the architecture combining information from multiple modalities yields a multifaceted, hence richer, assessment of workload, and as a consequence attains more adequate performance.
-Indeed this is also to be distinguished from previous research, lending credence to the unexpected character of our results \cite{dolmans2020perceived} \cite{han2020classification} \cite{rastgoo2019automatic}.
-Furthermore, score on performance metrics for the GSR architecture are consistently lower as compared with the EEG architecture, but consistently higher as compared with the multimodal architecture.
-In terms of absolute errors, these differences were not found to be statistically significant, however.
-The unimodal PPG architecture was found to perform worst across the board.
+\section{Discussion \& Conclusion}
+\subsection{Discussion Results}
+We found the unimodal EEG architecture to consistently surpass the other architectures in terms of their scores on the performance metrics,  with a rather sizable difference in the correlations between predictions and labels.
+Although no statistically significant difference in absolute error was found between the unimodal EEG and GSR architectures, we did find evidence in favor of the unimodal EEG architecture significantly outperforming the multimodel architecture.
+Furthermore, the performance of GSR architecture was detected to be consistently worse as compared with the EEG architecture, but consistently better as compared with the multimodal architecture, however in terms of absolute error these differences were not found to be statistically significant.
+The unimodal PPG architecture was found to perform worst across the board, however in terms of absolute error this difference was not found to be statistically significant when evaluated against the multimodal architecture.
 
-Although some differences in performance are distinguishable, one must recognize that these differences are of rather modest size.
-Some of the differences in absolute error, although being statistically significant, still differ virtually negligibly in terms of their absolute difference, as indicated by both MAE and RMSE.
-The statistical significance is particularly attributable to the vast amount of degrees of freedom with which was tested.
-Nevertheless, the fact that the multimodal architecture didn't outperform a single of the unimodel architectures deserves some further investigation.
+Perhaps the most noteworthy result is that the unimodel EEG architecture outperformed the multimodal architecture.
+One is gravitated to believe that, since the architecture combining information from multiple modalities yields a multifaceted, hence richer, assessment of workload, performance would be more formidable.
+Indeed, this can be distinguished from previous research, lending credence to the unexpected character of our results \cite{dolmans2020perceived} \cite{han2020classification} \cite{rastgoo2019automatic} \cite{yin2017recognition}.
+We will aim to rationalize these results in the subsequent sections.
 
-One imaginable train of thought is that the multimodal architecture should have outperformed at least some of the unimodal architectures, but this was stiffed by the head-network architecture.
-Despite some different head-networks were cross-compared, this was not done in a systematical manner, i.e.
-such as would be possible with HPO.
-We finally opted for a relatively shallow head-network, consisting of several fully connected dense layers.
-The reader might recall from Section \ref{section:multimodal} that HPO and training for the current multimodal architecture already demanded hefty computational resources, and thus considerable time.
-Utilizing a deeper head-network would increase the required computational resources and hence running time exceedingly more.
-Additionally, in spite of some previous research utilizing a relatively deep head-network, a rather shallow network was equally so proposed oftentimes for multimodal workload classification problems \cite{yin2017recognition}, \cite{han2020classification} \cite{rastgoo2019automatic}.
-Moreover, one could propose that that the performance of the multimodal architecture was stiffed by the poor performing unimodal PPG component.
-In order to scrutinize this, we optimized hyperparamaters and trained a multimodal architecture in exactly the same manner, except for omitting the PPG component altogether.
-This network did not perform better on any metric, and results were not reported as a consequence.
+One imaginable train of thought constitutes that the multimodal architecture should have outperformed (at least some of) the unimodal architectures, but this was stiffed by the relatively simple head-network architecture.
+Despite that some different head-network architectures were considered, no systematical comparison was conducted to select the best performing architecture.
+We opted for a relatively shallow head-network architecture.
+However, the most important reason for opting for a relatively shallow head-network architecture was that a rather shallow network was found to be successful in many previous multimodal workload classification problems \cite{yin2017recognition}, \cite{han2020classification} \cite{rastgoo2019automatic}.
+Additionally, utilizing a deeper head-network would have substantially increased the computational expenses (which were already of quite considerable size) even further.
 
-A contrary train of thought is that our case simply didn't benefit from a multimodal approach.
-A classical theorem in the fields of statistics and machine-learning alike is the, sometimes precarious, balance between model complexity and and simplicity.
+Further investigation is therefore pursued along a contrary line of reasoning, in which we propose that our case simply didn't benefit from a multimodal approach.
+A classical theorem in the fields of statistics and machine-learning alike, is the oftentimes precarious balance between model complexity and simplicity.
 A model that is overly complex is in increased peril of overfitting, i.e.
-performing well on training data, but failing to generalize to the test data.
-A more parsimonious model is generally at less jeopardy to fall into this pitfall, however an overly simple model simply doesn't describe the data very well.
-It is not implausible to consider that this mechanism could, at least, partially rationalize why our relatively complex multimodal architecture performs worse as compared with at least one of the simpler unimodal architecture.
-The fact that we trained an individual network for each participant separately, inherently implying that training is not done on an extraordinary sizable amount of data, may lend credence to this explanation: training on insufficient data equally so increases the likelihood of overfitting.
+performing well on training data, but failing to generalize this adequate prediction towards the testing data.
+With a simpler model, one is generally at less jeopardy to step into this pitfall, however an overly simplistic model is simply inaccurate \cite{lever2016points}.
+It is not implausible that this mechanism could, at least partially, rationalize that our rather complex multimodal architecture performed worse as compared with the considerably more parsimonious unimodal architecture.
+Lending more credence to this justification is the fact that we trained an individual network for each participant, inherently implying that training is done on a relatively small amount of data: this equally so increases the risk of overfitting.
 
-One is therefore inclined to reflect on the following: Even if a multimodal approach could result in a moderate improvement over unimodal approaches, would this justify the sheer addition in complexity,  the considerable increase in required computational resources and the necessity to possess a multitude of different physiological sensors?
-The answers to this question is naturally heavily dependent upon context, i.e.
-how precise need the network be for the task at hand and how much funding and time is available?
-It is not
+Another noteworthy result was the delineated relationship between a window's absolute error and its respective label score (as was visualized by Figure \ref{fig:mae_scatter}), which indicated that all architectures tended to underpredict high labeled windows.
+A credible explanation for this anomaly is the relatively minor presence of high labeled windows in our data (as was visualized by Figure \ref{fig:labels}).
+Naturally, when a relatively small amount of high labeled windows, i.e.
+high workload windows, are present in the training data, the DNN doesn't adequately learn to predict such windows.
 
-The two previously delineated opposite lines of argumentation can be distilled into recommendations for future research endeavors.
-Firstly, insights into the most appropriate network architecture of, in particular, the multimodal head-network is would be beneficial.
-Despite the range of different proposals to architectures with the purpose of workload classification by amongst others \citeA{yin2017recognition}, \citeA{han2020classification} \citeA{rastgoo2019automatic} and \citeA{dolmans2020perceived}, some rough outlines into what is prone to work under different circumstances would be highly beneficial.
+Concluding the discussion section, one should note that, despite a difference in performance across architectures was observed,  these differences were of rather modest size.
+Some of the differences in absolute error, although being statistically significant, are still very small in terms of their absolute difference, as indicated by how close both MAE and RMSE scores were observed to be across architectures.
+The statistical significance of some of the conducted t-tests can particularly be attributed to the vast amount of degrees of freedom with which was tested.
+We therefore suggest to reflect on the following: in opposite to our finding, suppose that if a multimodal approach could result in a moderate improvement over an unimodal approach.
+Would this justify the sheer addition in complexity,  the considerable increment in computational expenditure and the necessity to invest in a multitude of different physiological sensors?
+In other words, isn't the already particularly adequately performing unimodal EEG approach sufficient for most task at hand?
+The answers to this question is naturally heavily context dependent, and should be considered in a case-specific manner.
 
-\begin{itemize}
-  \item  More HPO could have been done, to get even better performing models but we had limited computatioal power.   
-  \item This approach costs a lot of computational power to both train and do HPO. Especially since person-specific models are fitted. This upholds mostly for the multimodal network.
-  \item Due to the sheer size of the trained model and the fact that models are trained person specific, storage sizes of the models are huge.
-This could be unpractical.
-This upholds mostly for the multimodal network.
-  \item Possibly different window sizes per modality could lead to better results.
-* Insert some of the sources here that suggest different window sizes per modality* .
-This was beyond the scope of this project.
-   \item How generizable is this to other situations for the same person (since things such as PPG are context dependent (like for example regarding how one ate).
-   \item Long runtimes,  even when testing. This upholds only for the multi network. The reason is likely the sheer size of these networks, which for some persons are blown up due to device lagging. 
-   \item hardware failure?
-   \item The fact that we use TLX as labels.
-\end{itemize}
+\subsection{Limitations \& Future Research Recommendations}
+More research is necessary to be able to answer the question concluding the previous section.
+Can the fact that we didn't find the multimodel architecture to perform superiourly,  in opposite to previous research, be attributed to the too shallow (head-network) DNN architecure?
+If yes,  what would be an appropriate architecture?
+Or is the current multimodal approach to complex for the data at hand, resulting in overfitting?
+An effective technique with which to answers these questions is HPO.
+With HPO, different network architectures can be contrasted, with the objective of systematically finding the best performing architecture.
+In the current study we did optimize several hyperparamaters, however the architecture in itself was set in stone.
+The reason for doing so were both restrictions in available time and computational power.
+A recommendation for future research is therefore to further investigate the most suitable DNN architecture for multimodal approaches.
+
+As was delineated before, another noteworthy result was the underprediction  of high labeled windows, most likely due to their relative absence in training data.
+This absence naturally stems from the fact that respondents refrained from providing extremely high answers towards the items of the NASA-TLX questionnaire, which were utilized for labeling.
+Alternative labeling should therefore be considered in future research endeavors.
+Ideally, one would want to contrast various labeling strategies with one another, and derive those most suitable for the task at hand.
+Again, due to restrictions in available time and computational power, this lay outside the scope of the current research.
+Potentially interesting alternatives approaches to labeling could for example include a standardized version of the NASA-TLX, or an objective difficulty score of the task at hand as proposed by \citeA{dolmans2020perceived}, or lastly, an extensive combination of personal information such as big-five personality scale, sex, age, etc.
+as proposed by \citeA{sun2019hybrid}.
+
+Finally, as was elaborated on before, the ultimate goal of this line of research is obtain trained networks with which workload assessment can be done in simulational scenario's, with the objective of training its participants.
+In order to acknowledge the different character of physiological data across participants, a separate network for each individual was trained.
+However, apart from between person differences in physiological data, differences between occasions could equally so prevail.
+An example of such a circumstantial difference could entail that a person has a higher baseline stress level in one occasion over the other, which could imply that a personally trained DNN is not generalizable to another occasion.
+Other of such imaginable circumstantial factors that could interfere with physiological signals includes food consumption before the simulation and room temperature.
+Further research is required in order to assess the generelizability of a single personally trained DNN across different occasions, and is suggested as a consequence.
+
+\subsection{Conclusion}
+We embarked on a multimodal deep learning approach to workload prediction, by combining three physiological sensors, being EEG, GSR and PPG, into a single deep neural network.
+An intermediate fusion approach was adopted towards the construction of the multimodal architecture.
+The performance of this approach was contrasted with three unimodal approaches, each utilizing one of the previously delineated modalities.
+It was found that all architectures performed rather adequately.
+A difference in performance was observable however: most notably it was found that the unimodal EEG architecture outperformed the multimodal architecture.
+Several explanations were proposed for this anomaly, which were distilled into various recommendations for future research.
+Future work will ideally investigate upon the most appropriate network architecture for multimodal approaches,  the feasibility of different labeling strategies and the cross-occasional generelization of individually trained networks.
 

### 2021-04-26 3.pytorch/loop_multi.py

@@ -22,7 +22,7 @@ from torch.nn.utils.rnn import pad_sequence
 import numpy as np
 
 try: #Importing network
-    import dataprep, networks
+    import utility, networks
 except ModuleNotFoundError:
     wd = os.getcwd()
     print("Error: please make sure that working directory is set as '~/Masterthesis'")
@@ -46,22 +46,22 @@ def MultiTrainLoop(participant, hpo, epochs, trainortest, batch_size):
     #Create PyTorch dataset definition class
     path = "pipeline/prepared_data/"+participant+".pickle"
                                         
-    eegdat =  dataprep.PytorchDataset(path = path,       #Creating PyTorch dataset
+    eegdat =  utility.PytorchDataset(path = path,       #Creating PyTorch dataset
                                        modality = "EEG")
-    ppgdat =  dataprep.PytorchDataset(path = path,       #Creating PyTorch dataset
+    ppgdat =  utility.PytorchDataset(path = path,       #Creating PyTorch dataset
                                       modality = "PPG")
-    gsrdat =  dataprep.PytorchDataset(path = path,       #Creating PyTorch dataset
+    gsrdat =  utility.PytorchDataset(path = path,       #Creating PyTorch dataset
                                       modality = "GSR")
 
     print(participant)
 
-    padinglength_eeg = dataprep.PaddingLength(eegdat) #Determining the longest window for later use
-    padinglength_ppg = dataprep.PaddingLength(ppgdat) #Determining the longest window for later use
-    padinglength_gsr = dataprep.PaddingLength(gsrdat) #Determining the longest window for later use
+    padinglength_eeg = utility.PaddingLength(eegdat) #Determining the longest window for later use
+    padinglength_ppg = utility.PaddingLength(ppgdat) #Determining the longest window for later use
+    padinglength_gsr = utility.PaddingLength(gsrdat) #Determining the longest window for later use
 
-    dataprep.BatchTransformationEEG.transfer([padinglength_eeg, "EEG"]) #Transfer max padding length & modality vars to BatchTransfor class               
-    dataprep.BatchTransformationPPG.transfer([padinglength_ppg, "PPG"]) #Transfer max padding length & modality vars to BatchTransfor class
-    dataprep.BatchTransformationGSR.transfer([padinglength_gsr, "GSR"]) #Transfer max padding length & modality vars to BatchTransfor class
[…]

### 2021-04-26 3.pytorch/train.py

@@ -15,7 +15,7 @@ import pickle
 
 #Import local files
 try:
-    import loop_single, loop_multi, dataprep
+    import loop_single, loop_multi, utility
 except ModuleNotFoundError:
     wd = os.getcwd()
     print("Error: please make sure that working directory is set as '~/Masterthesis'.")

### 2021-04-26 pipeline/transformer.py
d

@@ -1,0 +1,299 @@
+"""
+@Author: Thomas de Groot
+@Modified by: Bart-Jan Boverhof
+@Description: Creates pandas dataframes based on the desired markers.
+"""
+
+#### Prerequisites ####
+#Importing packages
+import pyxdf
+import pandas as pd
+import torch
+from matplotlib import pyplot
+import numpy as np 
+
+
+def load_data(filename):
+    """
+    Purpose: 
+        Load the data streams from the xdf file
+    Arguments:
+        filename: Path of the respective .xdf file
+    """
+
+    print("""
+         __
+ _(\    |@@|
+(__/\__ \--/ __
+   \___|----|  |   __
+       \ }{ /\ )_ / _
+       /\__/\ \__O (__
+      (--/\--)    \__/
+      _)(  )(_
+     `---''---`     
+   transforming...
+    """)
+
+    streams, _ = pyxdf.load_xdf(filename)
+
+
+    return streams
+
+
+
+def create_windows(streams, events, 
+                   start_margin, end_margin, 
+                   window_size, window_overlap, window_exact, 
+                   labels, role, participant):
+    """
+    Purpose:
+        Use the marker stream to create windows and summarize these in a pandas df
+        Additionally, within this function the labels are appended to this df
+    Arguments:
+        streams:        streams loaded from the .xdf file       
+        events:         experimental events to create windows from 
+        start_margin:   number of seconds to cut from the start of each block
+        end_margin:     number of seconds to cut from the end of each block
+        window_size:    windows size in seconds
+        window_overlap: window overlap in seconds
+        window_exaxt:   whether or not smaller windows then window_size are used
+        labels:         labels df object 
+        role:           experimental role of the data type (Engineer /  Operations / Tactical)
+    Return:
+        dataframe containing:
+            ROWS:
+                all cutted windows
+            COLS:
+                index: window index
+                durations: window durations
+                start: start timecode window
+                task: task difficulty (1, 2, 3,)
+                tries: number of tries to cut the window
+                window: window index per task (thus seperate index for each task)
+                workload: workload assessment lable
+    """
+
+    #Windows result object 
+    result = pd.DataFrame()
+    tries = {}
+
+    #Create labels df 
+    pfilter = labels["Username"] == participant
+    labels = labels[pfilter]
+    rolefilter = labels["Role"] == role
+    labels = labels[rolefilter]
+    counter = 0 #Counter for attributing labels to windows df 
+    
[…]

### 2021-04-26 pipeline/transformer.py
Repo restructure + updates readme files

@@ -1,299 +1,0 @@
-"""
-@Author: Thomas de Groot
-@Modified by: Bart-Jan Boverhof
-@Description: Creates pandas dataframes based on the desired markers.
-"""
-
-#### Prerequisites ####
-#Importing packages
-import pyxdf
-import pandas as pd
-import torch
-from matplotlib import pyplot
-import numpy as np 
-
-
-def load_data(filename):
-    """
-    Purpose: 
-        Load the data streams from the xdf file
-    Arguments:
-        filename: Path of the respective .xdf file
-    """
-
-    print("""
-         __
- _(\    |@@|
-(__/\__ \--/ __
-   \___|----|  |   __
-       \ }{ /\ )_ / _
-       /\__/\ \__O (__
-      (--/\--)    \__/
-      _)(  )(_
-     `---''---`     
-   transforming...
-    """)
-
-    streams, _ = pyxdf.load_xdf(filename)
-
-
-    return streams
-
-
-
-def create_windows(streams, events, 
-                   start_margin, end_margin, 
-                   window_size, window_overlap, window_exact, 
-                   labels, role, participant):
-    """
-    Purpose:
-        Use the marker stream to create windows and summarize these in a pandas df
-        Additionally, within this function the labels are appended to this df
-    Arguments:
-        streams:        streams loaded from the .xdf file       
-        events:         experimental events to create windows from 
-        start_margin:   number of seconds to cut from the start of each block
-        end_margin:     number of seconds to cut from the end of each block
-        window_size:    windows size in seconds
-        window_overlap: window overlap in seconds
-        window_exaxt:   whether or not smaller windows then window_size are used
-        labels:         labels df object 
-        role:           experimental role of the data type (Engineer /  Operations / Tactical)
-    Return:
-        dataframe containing:
-            ROWS:
-                all cutted windows
-            COLS:
-                index: window index
-                durations: window durations
-                start: start timecode window
-                task: task difficulty (1, 2, 3,)
-                tries: number of tries to cut the window
-                window: window index per task (thus seperate index for each task)
-                workload: workload assessment lable
-    """
-
-    #Windows result object 
-    result = pd.DataFrame()
-    tries = {}
-
-    #Create labels df 
-    pfilter = labels["Username"] == participant
-    labels = labels[pfilter]
-    rolefilter = labels["Role"] == role
-    labels = labels[rolefilter]
-    counter = 0 #Counter for attributing labels to windows df 
-    
[…]

### 2021-05-08 0.manuscript/manuscript.tex
Finishes manuscript

--- 2021-04-14 manuscript/manuscript.tex
@@
-\documentclass[12pt]{article}
+\documentclass[fleqn,11pt]{paper}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{apacite}
+\renewcommand{\doiprefix}{}
+\newcommand{\doi}[1]{https://doi.org/#1}
 
-%Required packages
-\usepackage[utf8]{inputenc}
-\usepackage{apacite}
-\usepackage{caption} 
-\usepackage{setspace}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[textwidth=160mm, textheight=210mm, hmarginratio=1:1]{geometry}
-\usepackage{geometry}
-\usepackage[capposition=top]{floatrow}
-\usepackage{showframe}
+\title{Physiological sensor based prediction of mental workload: A multimodal deep learning approach}
 
-%Prerequisite statements
-\DeclareCaptionLabelSeparator*{spaced}{\\[2ex]} %Declare the caption and title seperator spacing
-\captionsetup[table]{,textfont=it,format=plain,justification=justified,
-  singlelinecheck=false,labelsep=spaced,skip=2ex} %Setting up caption for table titles
- \captionsetup[figure]{,textfont=it,format=plain,justification=justified,
-  singlelinecheck=false,labelsep=spaced,skip=2ex} %Setting up caption for figure titles
-\captionsetup{labelfont={bf}} %Bold label font for tables
-\onehalfspacing %Document line spacing
-\pagestyle{myheadings} %Heading style
-\graphicspath{ {./figures/} } %Defining image path
+\author[1]{Bart-Jan Boverhof \thanks{b.boverhof@students.uu.nl}}
+\affil[1]{\normalsize Faculty of Social and Behavioural Sciences, Utrecht University}
+
+\begin{abstract}
+The assessment of mental workload by means of physiological sensors has gained in popularity in recent years.
+We utilized three physiological sensors from which mental workload was predicted, being electroencephalography, photoplethysmography and galvanic skin response.
+Deep learning poses a promising, yet novel, approach towards the modeling of such sensory data.
+Four deep neural network architectures were created and contrasted in their performance.
+Three out of four were specified to predict workload based on on a single of the aforementioned physiological sensors, whilst the fourth architecture was a joint neural network combining all physiological signals into a single model.
+In this study we aimed to identify 1) which physiological sensor constitutes the most adequate predictor of mental workload, and 2) whether a joint approach utilizing multiple sensors is preferable over the approaches utilizing just one.
+Altogether the electroencephalography-only architecture was found to perform best, closely followed by the galvanic skin response-only architecture,  both displaying a mean absolute error of 0.110 and 0.119 (scaled on 0-1) respectively.
+Against expectations, the joint approach was outperformed by both aforementioned architectures, displaying a mean absolute error of 0.128 (equally so scaled on 0-1).
+The photoplethysmography-only architecture was found to perform worst, displaying a mean absolute error of 0.136.
+In the discussion section we presented several explanations that help rationalize this anomaly, one being due to an imperfect model architecture for the joint neural network, and another being due to overfitting resulting from a limited amount of data.
+Regardless of the unexpected character of this result, we still recognize that differences in performance were of rather modest size: all four neural network architectures performed fairly adequately.
+\end{abstract}
 
 \begin{document}
+\begin{titlepage}
+\vspace{10mm}
 
-%Title page 
-\begin{titlepage}
-\begin{center}
-\LARGE{\textbf{The Realtime Assessment of Mental Workload by Means of Multiple Bio-Signals}}\\
-\vspace*{2\baselineskip}
-\Large{\textbf{Masterthesis Report}}\\
-Methodology and Statistics for the Behavioral, Biomedical and Social Sciences\\
-\vspace*{1\baselineskip}
-Utrecht University\\
-\vspace*{4\baselineskip}
-{Bart-Jan Boverhof, 6000142}\\
-\vspace*{1\baselineskip}
-{\textbf{Thesis Supervisor}}\\
-Prof.dr.ir. B.P. Veldkamp\\
-\vspace*{1\baselineskip}
-{\textbf{Date}}\\
-January 7, 2021\\
-\vspace*{1\baselineskip}
-\end{center}
+\begin{large}
+{\setlength{\parindent}{0cm}
+Methodology and Statistics for the Behavioural, Biomedical and Social Sciences
+}
+\newline Utrecht University, the Netherlands
+\vspace{18mm}
+\newline MSc Thesis Bart-Jan Boverhof (6000142)
+\newline Physiological sensor based prediction of mental workload: A multimodal deep learning approach
+\newline May 2021
+\vspace{18mm}
+\newline Supervisor:
+\newline Prof. Dr. Ir. Bernard Veldkamp
+\vspace{10mm}
+\newline Second grader:
+\newline Prof. Dr. Ir René Eijkemans
+\vspace{10mm}
+\newline Preferred journal of publication: Frontiers in Neuroscience
+\end{large}
 \end{titlepage}
 
-%Introduction section
+\flushbottom
+\maketitle
+% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
+%
+%  Click the title above to edit the author information and abstract
+%
+\thispagestyle{empty}
+
 \section{Introduction}
 The topic of mental workload is a widely studied phenomenon across a variety of different fields, amongst others the field of ergonomics \cite{young2015state}, human factors \cite{pretorius2007development} and cognitive neurosciences \cite{shuggi2017mental}.
-A commonly utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon one whilst one carries out a particular task.
-As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is lacking, for it defines workload solely as a phenomenon external to the individual.
-Workload, however, requires to be recognized as a person-specific construct, for the amount of perceived workload ushered by a given task may vary substantially across individuals.
-\cite{de1996measurement}.
+A commonly utilized definition of mental workload, hereafter referred to as simply "workload", is the demand placed upon one whilst carrying out a particular task.
+As rightfully pointed out by \citeA{de1996measurement}, the aforementioned definition is incomplete, for it defines workload solely as a phenomenon external to the individual.
+Workload, however, requires to be recognized as a person-specific construct, for the amount of perceived workload ushered by a given task may vary substantially between individuals \cite{de1996measurement}.
 
-A commonly employed method for the assessment of workload is the well established NASA-Task Load Index questionnaire, hereafter referred to as "NASA-TLX".
-This method inquires into the amount of perceived workload,  embodying six different dimensions \cite{hart2006nasa}.
-Due to practical considerations such an assessment is usually conducted post-experiment, which can in certain situations be deemed suboptimal.
-Consider for example an experiment in which it is aimed to assess the perceived workload of a pilot in flight.
-An insightful  approach towards such an experiment would be to measure the degree of perceived workload during different phases of the flight, such that can be determined which specific manoeuvres tend to cause an increase in perceived workload.
-However,  a questionnaire-based assessment such as the NASA-TLX can only be administrated after the flight is concluded.
-In such a situation, utilizing a post-experiment assessment well after the action took place is prone to generate biases.
-One example of such a bias is the observer-bias, dictating that participants of an experiment tend to overexaggerate the treatment effect, i.e.
-the amount of perceived workload in our case, when having to report it post-experiment \cite{mahtani2018catalogue}.
+A commonly employed method for the assessment of workload in an experimental setting is the well established NASA-Task Load Index questionnaire, hereafter referred to as \enquote{NASA-TLX}.
+This method embodies several dimensions, jointly inquiring into the amount of perceived workload \cite{hart2006nasa}.
+However, due to the ever-increasing availability in computing power characterizing recent times, a novel approach to workload assessment has gained in popularity.
+This promising approach constitutes the use of physiological sensors, worn throughout the entire duration of the experiment.
+An approach like this poses the advantage that the development of perceived workload may be monitored throughout the entire experiment, enabling the possibility to precisely monitor the impact of a specific task on a participant's level of workload.
+Another advantage is that the method may be personalized, which could simply be done by creating and training an individual model for each participant.
+By doing this, the person-specific character that is inherent to workload is acknowledged, the importance of which was stressed in the opening paragraph of this paper.
 
-An alternative approach to the assessment of workload is to collect physiological bio-signals during the experiment, and utilize these inputs to predict the degree of experienced workload.
-A considerable advantage of such an approach is that it renders possible to cater the method towards the individual,  hereby acknowledging the between-personal perceptual differences inherent to workload, the importance of which was discussed in the first paragraph of this paper and stressed by \citeA{de1996measurement}.
-But taking a physiological bio-signal-approach poses more advantages: e.g.
-one may utilize multiple complementary bio-signals, each stemming from a different physiological source simultaneously \cite{ramachandram2017deep}.
-Doing so poses the theoretical potential of yielding a rich and multifaceted assessment of a mental construct such as workload.
-In addition, with such an approach one may select a variety of the most suitable physiological bio-signals, hereafter referred to as "modalities",  and combine these information streams in order to yield a multifaceted prediction.
+With the current research we explore the feasibility of an approach towards workload assessment by means of various physiological sensors, hereafter referred to as \enquote{modalities}.
+The three utilized modalities are electroencephalography (EEG), photoplethysmography (PPG) and galvanic skin response (GSR).
+EEG is a technique that monitors electrical activity in the brain, and is often utilized in the assessment of workload \cite{berka2005evaluation, craik2019deep}.
+EEG is found to be amongst the most adequately performing techniques for this task \cite{hogervorst2014combining}.
+GSR is a technique that measures electrical conductance of the skin, and equally so is a widely adopted method for workload assessment \cite{nourbakhsh2012using, zhou2015dynamic}.
+Lastly, also heart-rate is a widely utilized indicator of workload, mostly obtained through PPG \cite{zhang2018evaluating,jimenez2018using}.
 
-With the current research endeavor we explore the feasibility of an approach to workload assessment by means of multiple modalities simultaneously, hereafter referred to as "multi-modular approach".
-We do so by combining data-streams stemming from three different modalities, being electroencephalography, photoplethysmography and galvanic skin response.
-Electroencephalography,  hereafter referred to as "EEG", is often utilized in the assessment of workload \cite{craik2019deep} \cite{berka2005evaluation} and found to be amongst the most adequately performing techniques within the field \cite{hogervorst2014combining}.
-Galvanic skin response, hereafter referred to as "GSR", equally so is a widely adopted approach towards workload assessment \cite{nourbakhsh2012using} \cite{zhou2015dynamic}.
-Lastly, heart-rate is a widely recognized indicator of workload, mostly obtained through photoplethysmography, hereafter referred to as "PPG" \cite{zhang2018evaluating} \cite{jimenez2018using}.
+In this project we opted for a deep learning approach towards workload prediction.
+A range of four different deep neural network architectures, hereafter referred to as \enquote{DNN's} or simply \enquote{networks},  are constructed and contrasted in their performance.
+Among these are three unimodal DNN's, i.e.
+networks each utilizing only a single modality.
+Thus,  one network solely utilizes the EEG modality,  one solely utilizes the GSR modality and one solely utilizes the PPG modality.
+The fourth is a multimodal network, i.e.
+combining all three aforementioned modalities into a single architecture.
+The main advantage of taking a deep learning approach specifically resides in its flexibility.
+Fitting a model that combines multiple modalities can be done in different, relatively straightforward, ways when taking a deep learning approach \cite{ramachandram2017deep}.
+We expect the multimodal approach to results in better performance as compared with the unimodal approaches, for predictions are based on richer composite of information.
+This expectation is indeed in line with previous research, which reported a multimodal approach to perform superiorly \cite{dolmans2020perceived, han2020classification,rastgoo2019automatic, yin2017recognition}.
 
-A deep learning approach towards modeling is adopted.
-A range of four different deep neural networks, hereafter referred to as "DNN's", are constructed and contrasted in performance: three of which are single-modular DNN's, i.e.
-networks each utilizing data from only a single modality.
-Thus,  one DNN solely utilizes the EEG modality,  one solely utilizes GSR and one solely utilizes PPG.
-The fourth network is a multi-modular network combining all three modalities into one.
-With this research we firstly sought to explore which modalities constitute the most adequate predictors of workload in an experimental setting, and secondly whether a multi-modular combination is preferable over the three simpler (but much less computationally demanding) single-modular DNN's.
-This assessment will be propelled by contrasting network performance, however when drawing conclusions, considerations regarding computational costs will be taken into consideration as well.
-All networks were constructed in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}.
+With this research we 1) seek to explore which individual modality constitutes the most adequate predictor of workload when taking a deep learning approach, and 2) whether a multimodal network architecture is preferable over the three simpler (but much less computationally demanding) unimodal architectures.
+This comparison will mainly be propelled by contrasting network performance, however when drawing conclusions, considerations regarding computational costs will also be taken into consideration.
+With this research we aim to deepen the knowledge of taking a deep learning approach towards workload prediction with physiological sensors in an experimental setting, which as of yet, is still a novel and fairly understudied topic.
 
 %Method section
-\newpage
+\vspace{10mm}
 \section{Data \& Methods}
+\subsection{Related Work} \label{sec:related}
+The following section provides an overview of preceding research on the assessment of workload by means of various physiological sensors, with a focus on deep learning approaches.
+Attention is predominantly placed upon network architectures and hyperparameter optimization.
+In this section we will solely describe previous work: an in depth description of our adopted modeling approach follows in Section \ref{section:DNN}.
 
-\subsection{Data}
-The subsequent section will provide an overview of the utilized data.
-Attention is placed upon the experimental setup, the description of the respondents, the utilized devices for data collection and the synchronization process.
+\subsubsection*{EEG Network Architecture}
+An overview of the complete literature EEG applications with deep learning was presented by \citeA{craik2019deep}, who reported 16\% of all publications to constitute workload assessment.
+The lion's share of these publications utilized either a deep belief network or convolutional neural network (ConvNet).
+\citeA{tabar2016novel} proposed a ConvNet and stacked auto-encoder (SAE) hybrid approach towards workload classification with EEG.
+Their proposed network constituted two different parts.
+Firstly, raw EEG data was fed into a single convolutional layer, with the objective of extracting features.
+Secondly, the the extracted features fed into the SAE part of the network,  which encompassed a stack of dense-layers designed to ultimately result in a classification of workload.
+An accuracy of 90\% was acquired with this architecture \cite{tabar2016novel}.
+A similar approach was proposed by \citeA{schirrmeister2017deep}, who contrasted different DNN architectures in their ability to adequately decode EEG signals.
+Several ConvNet architectures were contrasted against the baseline method for EEG decoding, filter bank common spatial pattern (FBCSP).
+A deep ConvNet, a shallow ConvNet, a deep-shallow hybrid ConvNet and a residual ConvNet were contrasted with the FBCSP baseline method.
+Both the deep and shallow ConvNets were found to reach at least similar, and in some regards better classification results as compared with the FBCSP baseline approach.
+Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, exhibiting a classification accuracy of 92.4\% \cite{schirrmeister2017deep}.
 
-\subsubsection{Experimental Setup}
-The experimental setting in which data collection befell is the open-source spaceship video-game Empty Epsilon, in which partakers carry out tasks on a virtual spaceship bridge \cite{daid2016empty}.
-This experiment was instituted by the Brain Computer Interfaces testbed, hosted by the University of Twente and carried out in cooperation with Thales group Hengelo.
-The experiment constituted three different segments, in each of which the respondent had to carry out tasks.
-These tasks were designed to evoke varying degrees of workload.
-Each segment consisted of six small sessions, lasting roughly five to ten minutes.
-These sessions varied in difficulty, including two easy, two intermediate and two hard sessions per segment.
-Within each segment, the order in which the sessions were presented was randomized.
-Between every three sessions, respondents were given a short two minute break.
-A schematic overview of the experimental structure is depicted as Figure \ref{fig:experimental}.
+\subsubsection*{GSR Network Architecture}
+\citeA{sun2019hybrid} explored various deep-learning approaches towards the classification of emotional states with GSR.
+Despite that this application differs from workload prediction, inspiration may still be drawn from their utilized architecture.
+Various models were explored, amongst others a support vector machine, a ConvNet and a long-short-term-memory (LSTM) network.
+In addition to these, a hybrid ConvNet-LSTM approach was explored as well.
+This hybrid approach constituted four convolutional blocks followed by a single LSTM layer, and was found to perform best with an accuracy of 74\% \cite{sun2019hybrid}.
+\citeA{dolmans2020perceived} contrasted several physiological signals in their ability to predict workload, each of which by taking a deep learning approach.
+One of these modalities constituted GSR, for which a ConvNet-LSTM hybrid network architecture was utilized to predict workload.
+The performance of this DNN was contrasted with a network consisting solely of fully connected dense layers.
+Conform with the previously mentioned findings by  \citeA{sun2019hybrid}, the ConvNet-LSTM hybrid architecture was found to perform best, displaying an absolute difference between predicted and true label of 0.180 (scaled on 0-1).
+This network architecture incorporated two convolutional blocks, followed by two LSTM layers \cite{dolmans2020perceived}.
 
-After each of the 18 sessions, respondents were asked to fill out the NASA-TLX, resulting in 18 filled in questionnaires per respondent.
-Each questionnaire consists out of 6 questions, inquiring upon the degree to which the respondent experienced workload during the preceding session.
-The mean of a subset of four of these items have been utilized to label the data for training purposes.
-Two items were not incorporated into the scale, for they inquired into physical demand specifically, which given the experiment took place on a computer whilst sitting behind a desk was considered to be a redundant factor.
-Each item, and hence the newly constructed scale, ranges from 0-20, wherein 0 reflects low workload and 20 reflects high workload.
+\subsubsection*{PPG Network Architecture}
+Research by \citeA{biswas2019cornet} explored a PPG deep learning approach, in which their objective was to perform both bio-metric identification and obtain heart rate information.
+Again, despite that this research doesn't constitute workload prediction or classification, inspiration may still be drawn from the employed network architecture.
+An exceptional performance of 96\% accuracy was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed by two LSTM layers \cite{biswas2019cornet}.
+\citeA{dolmans2020perceived} also explored a deep-learning PPG approach to workload prediction.
+A ConvNet constituting two convolutional blocks was found to perform best out of all contrasted PPG architectures, displaying an absolute difference between predicted and true label of 0.1969 (scaled on 0-1).
+
+\subsubsection*{Multimodal Fusion Strategy}  
+When creating a DNN that combines multiple modalities into a single network,  the information streams that stem from the different subparts of the network (each corresponding to one of the modalities) are required to be combined, i.e.
+\enquote{fused}, at a given point in the network.
+This is necessary in order to ultimately end up with a single prediction of workload.
+Fusion can be done conforming several strategies, out of which three strategies as proposed by \citeA{ramachandram2017deep} are considered.
+
+Firstly, early fusion constitutes an approach that fuses data sources before being fed into the network.
+Early fusing usually proves to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate.
+In addition, when taking an early fusion approach, the assumption of conditional independence is made implicitly.
+This assumption is oftentimes unrealistic in practice, for data stemming from different modalities are expected to be correlated \cite{ramachandram2017deep}.
+Secondly, late fusion refers to the process of aggregating the decisions of multiple separate networks, each constructed for every modality separately.
+When the data sources stemming from the various modalities happen to be either correlated or different in their dimensionality, late fusion is oftentimes a more feasible approach as opposed to early fusion \cite{ramachandram2017deep}.
+Lastly, intermediate fusion is the most widely employed fusion strategy for multimodal networks.
+Data streams are usually fused by a concatenation layer, joining the outputs of the separately defined network parts of each modality.
+This results in a single joint deep neural network.
+Several higher-order layers are usually defined in between the concatenation layer and the ultimate prediction layer.
+The depth of the fusion, i.e.
+the specified number of higher-order layers, may be chosen by the researcher, posing intermediate fusion to be the most flexible and therefore the most widely adopted fusion strategy \cite{ramachandram2017deep}.
+
+Indeed when consulting the literature, it becomes apparent that intermediate fusion is the most prevailing strategy for multimodal DNN architectures.
+As mentioned before, when taking an intermediate fusion approach, the higher-order part of the network is required to be designed by the researcher.
+\citeA{rastgoo2019automatic} utilized a multimodal ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers and two dense layers.
+A simpler approach is adopted by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers.
+Lastly, \citeA{dolmans2020perceived} took a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.
+
+\subsubsection*{Auxiliary Layers in a DNN Architecture}
+At the core of a DNN are the aforementioned types of layers, such as convolutional, LSTM and dense layers.
+Such layers are often accompanied with auxiliary layers in order to ensure network stability.
+The first type of layers often used in network architectures are batch normalization layers, which have the objective improving network stability.
+It is beneficial to incorporate a batch normalization layer subsequent to a convolutional layer, but before feeding into the activation layer \cite{ioffe2015batch}.
+For a deep dive into batch normalization, we refer the reader to \citeA{ioffe2015batch}.
+All previously considered network architectures made use of batch normalization layers \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid, tabar2016novel}.
+
+Pooling layers are commonly employed in ConvNets, usually succeeding a convolutional layer with the purpose of reducing dimensionality.
+The objective of such layers are to down-sample features into a more compact space, hereby only retaining essential information, and thus omitting redundant information.
+For a more extensive elaboration on pooling we refer the reader to \citeA{lecun2015deep}.
+All previously considered network architectures utilize max-pooling layers, usually specified subsequent to the activation layer \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid, tabar2016novel}.
+
+The incorporation of dropout layers was initially proposed by \citeA{srivastava2014dropout}.
+Dropout layers drop a randomly-selected number of neurons and their connections throughout the training process.
+More specifically, within each full training run through the data, i.e.
+each \enquote{epoch}, a different randomly selected set of neurons are fixed to be inactive.
+Doing so helps to reduce overfitting, particularly for complex network architectures \cite{srivastava2014dropout}.
+Most of the previously considered network architectures make use of dropout layers \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid}.
+
+\subsubsection*{Hyperparameter Optimization}
+Hyperparameter optimization (HPO) is a technique that optimizes network hyperparameters, such as for example learning rate and dropout rate.
+Substantial advancements in DNN performance have been attained by utilizing HPO, especially in the case of ConvNets \cite{bergstra2012random}.
+In theory, one could optimize the entire DNN architecture, including the number of neurons/filters in dense/convolutional layers, the number of layers in general, whether to use certain layers, etc.
+There is, however, a strong relationship between the amount of parameters to be optimized and the computational resources required to do so: optimizing many hyperparameters will inflate computational costs substantially.
+The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyperparameters may be sampled, and optimization can be performed \cite{akiba2019optuna}.
+
+\subsection{Data} \label{sec:data}
+The subsequent section provides a description of the utilized data and its collection process.
+Attention is placed upon the experimental setup, the description of the respondents, the utilized devices for data collection, the synchronization process and the data preprocessing approach.
+
+\subsubsection*{Experimental Setup \& Data Labeling Strategy}
+The experimental setting in which our data was collected is the open-source spaceship video-game Empty Epsilon, in which partakers carried out tasks on a virtual spaceship bridge \cite{daid2016empty}.
+This experiment was instituted by the Brain Computer Interfaces Testbed \footnote{https://bmslab.utwente.nl/} hosted by the University of Twente and carried out in cooperation with Thales Group\footnote{https://www.thalesgroup.com/en/countries/europe/netherlands} Hengelo, the Netherlands.
+The experiment was divided into a total of 15 tasks, differing in difficulty and hence designed to evoke varying degrees of workload.
+The total duration of the experiment was roughly three hours.
+
+Respondents were asked to fill out the NASA-TLX questionnaire after each of the fifteen task, inquiring into the amount workload perceived during the respective task.
+Each questionnaire consisted out of six items.
+The mean of a subset of four of these items were utilized for labeling of the data.
+Two items were not incorporated into the scale, for they inquired into the perceived physical demands.
+Since the experiment took place on a computer whilst participants sat behind a desk, we chose to not incorporate such items.
+Each item, and hence the newly constructed scale, ranges from 0-20, wherein 0 reflects the lowest possible level workload and 20 reflects the highest possible level workload.
 In order to encourage numerical stability, label scores were normalized to reside in-between 0-1.
 
-\begin{figure}
-\caption{Schematic Depiction of the Experimental Setup}
-\bigskip
-\includegraphics[scale=0.35]{experimental_setup}
-\label{fig:experimental}
-\bigskip
-\end{figure}
+\subsubsection*{Participants}
+After having to omit seven participants due to hardware failure, 27 respondents remained in the final analysis.
+18 participants were female whereas nine were male.
+The average age and its standard deviation were $\mu =26$ and $\sigma = 10.31$ respectively.
+The participants were students recruited from the University of Twente situated in the Netherlands, as well as several employees of Thales Group Hengelo, equally so situated in the Netherlands.
 
-The first segment emulated a scenario in which hostile spaceships approached the respondent's spaceship.
-The respondent was required to quickly respond by defusing the hostiles in order to survive.
-The increment in difficulty caused the process of defusing hostile spaceships to become more challenging, hereby aiming to cause an increase in workload.
-The second segment emulated a scenario in which the respondent had to navigate their spaceship trough space, gathering as many way-points as possible.
-Obstacles around which the respondent had to navigate carefully, as well as hostile spaceships the respondent had to decimate, were introduced in the higher difficulty sessions.
-The third and final segment emulated a machine room, in which respondents had to control the power based on randomly generated requests.
-In the increased difficulty settings, variables that could overheat the spaceship were introduced, demanding the respondent to multi-task and aiming to increase workload as a consequence.
+\subsubsection*{Devices and Synchronization}
+The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
+This device was worn on the wrist, whilst signals were communicated wirelessly via Bluetooth.
+An ear-clip was utilized for measuring PPG, which was automatically converted to heart-rate.
+Skin conductivity, or GSR, was measured by two electrodes attached to the fingers.
+EEG measurement was conducted with the Muse 2 multi-sensor headband, equally so whilst communicating signals wirelessly via Bluetooth.
+The Shimmer3 GSR+ measured on a sampling rate of 256 Hz, whereas the Muse 2 measured at a sampling rate of 220 Hz.
 
-\subsubsection{Participants}
-After having to omit 7 participants due to hardware failure, 27 respondents were included in the final analysis.
-18 participants are female whereas 9 are male.
-The mean age and standard deviation are $\mu =26, \sigma = 10.31$ respectively.
-The participants are students recruited from the University of Twente, as well as several employees of Thales group Hengelo.
-
-\subsubsection{Devices and Synchronization}
-The Shimmer3 GSR+ sensor was used for both PPG and GSR measurements.
-This device is worn on the wrist.
-Signals are communicated wirelessly via Bluetooth.
-An ear-clip is utilized for measuring PPG.
-The Shimmer3 GSR+ automatically converts measured PPG signals to heart-rate.
-Skin conductivity, or GSR, is measured by two electrodes attached to the fingers \cite{shimmer}.
-EEG measurement was conducted with the Muse 2, which is a commercially offered multi-sensor headband that provides feedback on brain activity \cite{muse}.
-The Muse 2 headband constitutes five sensors, each monitoring a different brainwave frequency.
-
-The Shimmer3 GSR+ measures signals on a sampling rate of 256 Hz, whereas the Muse 2 measures at a sampling rate of 220 Hz.
-Given that multiple devices are utilized, data streams are required to be properly synchronized.
+Given that multiple devices were utilized, data streams were required to be properly synchronized.
 This was accomplished by means of an application called Lab-Streaming Layer, hereafter referred to as "LSL", developed by \citeA{kothe2018lab}.
@@
 
-\subsection{Related Work} 
-The following section provides an overview of preceding research regarding the assessment of workload by means of physiological bio-signals, with a focus on deep learning approaches.
-Attention is predominantly placed upon the most feasible network architectures, in addition to a range of model optimization techniques and to the data fusion strategy for the multi-modular DNN.
-The final part of this section will be dedicated to hyperparameter optimization.
+\subsubsection*{Data Preprocessing \& Partitioning}
+For each participant, the EEG, PPG and GSR data streams were cut into windows of eight seconds, resulting in an average of roughly 351 windows per respondent.
+80\% of all windows have been used for training, 10\% for validation within the training process and 10\% for the testing of network performance.
+The partitioning of the windows into training, validation and testing sets was done systematically by selecting every \textit{n-th} window, such that windows over the entire duration of the experiment were represented equally in each partition.
+Exactly the same partitions were utilized in the training, validation and testing procedure across the four architectures to ensure a fair comparison.
 
-\subsubsection{Electroencephalography (EEG)}
-An overview of the complete literature on EEG applications with deep-learning was presented by \citeA{craik2019deep}, who reported a total of 16 \% of all publications to consider workload assessment specifically.
-The lion's share of these publications utilized either a deep belief networks or convolutional neural network, hereafter referred to as "ConvNet".
-One of these approaches is encouraged by the authors consequently \cite{craik2019deep}.
+\subsection{Network Architectures \& Training} \label{section:DNN}
+Individuals tend to respond differently towards high workload situations: for some workload manifests itself mostly through an increase in heart rate detected through PPG, whereas for others it manifests as an increase in skin conductivity detected through GSR.
+To account for such between-person differences, we trained an individual DNN for each participant.
+Since a total of four architectures are contrasted for 27 respondents, this resulted in a total of 108 trained networks.
+Equally so, HPO was conducted for each person individually, resulting in 108 sets of optimized hyperparameters.
+All networks were constructed in Python, by utilizing the deep-learning toolbox PyTorch \cite{paszke2017automatic}.
 
-\citeA{tabar2016novel} proposed a hybrid of a ConvNet with a stacked auto-encoder network, hereafter referred to as "SAE network".
-Inputs were specified to feed into the convolutional-part with the objective of learning extracting features.
-The output of this part was subsequently specified to feed into the SAE part of the network,  which encompasses a stack of dense-layers, designed specifically as an input layer, six hidden layers and an output layer.
-A classification accuracy of 90 \% was acquired with this network \cite{tabar2016novel}.
+\subsubsection*{Unimodal Network Architectures}
+All unimodal architectures drew inspiration from aforementioned research \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid}.
+We opted for a ConvNet architecture for all three unimodal network architectures.
 
-Research by \citeA{schirrmeister2017deep} contrasted the performance of several ConvNets against the widely utilized baseline method for EEG classification, filter bank common spatial pattern, hereafter referred to as "FBCSP".
-A deep ConvNet, a shallow ConvNet, a deep-shallow hybrid ConvNet and a residual ConvNet were contrasted with an FBCSP.
-Both the deep and shallow ConvNets were found to reach at least similar, and in some regards better classification results as compared with the FBCSP baseline approach.
-Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, exhibiting an accuracy of 92.4 \% \cite{schirrmeister2017deep}.
-
-\subsubsection{Galvanic Skin Response (GSR)}
-\citeA{sun2019hybrid} explored the most suitable approach to the classification of several emotional states with GSR.
-Various models were explored, amongst others a support vector machine, a ConvNet and a long-short-term-memory, hereafter referred to as "LSTM", network.
-Additionally, the feasibility of a hybrid DNN, combining both the ConvNet and LSTM approaches, was explored.
-This aforementioned hybrid model was found to perform best, exhibiting an accuracy of 74\% \cite{sun2019hybrid}.
-
-\citeA{dolmans2020perceived} took, amongst other approaches to workload prediction,  a GSR approach, and designed a variant based on the previously delineated CovNet-LSTM structure.
-The performance of this model was contrasted with a network consisting solely of fully connected dense layers.
-Conform with findings by  \citeA{sun2019hybrid}, the hybrid model was found to perform best, displaying an absolute difference between predicted and true label of 0.197 (scaled on 0-1).
-The model architecture as utilized deployed two convolutional max-pooling blocks and two LSTM layers \cite{dolmans2020perceived}.
-
-\subsubsection{Photoplethysmography (PPG)}
-Research by \citeA{biswas2019cornet} explored a deep learning approach towards PPG classification, with the objective to perform both bio-metric identification and obtain heart rate information.
-Exceptional results were realized with a DNN, attaining an average accuracy of 96 \% \cite{biswas2019cornet}.
-This performance was realized with a ConvNet-LSTM hybrid, incorporating two convolutional max-pooling blocks followed by two LSTM layers.
-
-\subsubsection{Multi-modular Fusion Strategy}  
-When conducting a multi-modular deep learning approach,  information streams stemming from the different modalities are required to be combined, i.e.
-"fused", at a certain point in the network in order to ultimately result in a single prediction of workload.
-Fusion can be done conforming several strategies.
-Three strategies as proposed by \citeA{ramachandram2017deep} have been considered.
-
-Early, or data-level, fusion constitutes an approach that fuses data sources before being fed into the network.
-Early fusing is usually proven to be quite challenging, residing in the fact that data streams stemming from different modalities often differ in their dimensionality and sampling rate.
-In addition, when taking an early fusion approach, the oversimplified assumption of conditional independence is made implicitly.
-This assumption is unrealistic in nature, for data stemming from different modalities are expected to be correlated in practice \cite{ramachandram2017deep}.
-
-Late, or decision-level, fusion refers to the process of aggregating the decisions of multiple separate networks, each applied towards every modality separately.
-In case the data sources stemming from the various modalities are either correlated or ultimately differ in their dimensionality, late fusion is often a more feasible approach as opposed to early fusion \cite{ramachandram2017deep}.
-
-Lastly, intermediate fusion is the most widely employed fusion strategy for multi-modular deep-learning problems.
-Data streams are usually fused by a concatenation layer, joining the outputs of the separately defined network parts of each modality.
-This results in a single joint deep neural network.
-Several "higher-order layers" are usually defined in between the concatenation layer and the ultimate classification.
-The depth of the fusion, i.e.
-the specified number of higher-order layers, can be chosen conform to the specific circumstances, posing intermediate fusion to be the most flexible and therefore the most widely adopted fusion strategy \cite{ramachandram2017deep}.
-
-Indeed, when consulting the literature, one is prone to conclude that intermediate fusion strategies are the most prevailing for multi-modular deep learning approaches.
-When taking an intermediate fusion approach, the higher-order part of the network needs to be designed and established, for which several previous research endeavors are considered.
-\citeA{rastgoo2019automatic} utilized a multi-modular ConvNet approach, and fused the modalities by concatenation, followed with two LTSM layers and two dense layers.
-A simpler approach is adopted by \citeA{han2020classification}, who utilized an intermediate fusion approach solely consisting of several fully connected dense layers.
-Lastly, \citeA{dolmans2020perceived} took a relatively deep intermediate fusion approach, consisting of two dense layers, two convolutional layers followed by another two dense layers.
-
-\subsubsection{Model Optimization Strategies}
-The technique of batch normalization was initialized by \citeA{ioffe2015batch}, and is widely utilized in DNN's with the objective of stabilization.
-Especially ConvNets benefit from this technique.
-It is beneficial to incorporate a batch normalization layer subsequent to a convolutional layer, but before feeding into the activation function \cite{ioffe2015batch}.
-All previously delineated networks architectures utilize batch normalization layers, in most cases specified subsequent to each convolutional layer \cite{dolmans2020perceived} \cite{tabar2016novel} \cite{schirrmeister2017deep} \cite{biswas2019cornet} \cite{sun2019hybrid}.
-
-Pooling layers are commonly employed in ConvNets, usually succeeding a convolutional layer with the purpose of reducing dimensionality.
-The objective of such layers are to down-sample features into a more compact space, hereby only retaining indispensable information.
-For a more extensive elaboration on pooling, please consult \citeA{lecun2015deep}.
-All previously delineated networks architectures utilize max-pooling layers, usually specified subsequent to the activation layer \cite{dolmans2020perceived} \cite{tabar2016novel} \cite{schirrmeister2017deep} \cite{biswas2019cornet} \cite{sun2019hybrid}.
-
-\subsubsection{Hyper Parameter Optimization}
-Hyper parameter optimization, hereafter referred to as "HPO", is a technique that can be utilized to optimize network hyper-parameters, such as learning rate and dropout rate.
-In theory, one could optimize the entire DNN architecture, including the number of neurons/filters in (convolutional) layers, the number of layers in general, whether to use certain layers etc.
-There is, however, a strong relationship between the amount of parameters to be optimized and the computational resources required to do so, in where many parameters to optimize tends to inflate computational costs by a substantial amount.
-Substantial advancements in DNN performance have been attained by utilizing HPO, especially for ConvNets \cite{bergstra2012random}.
-The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyper-parameters can be sampled and optimization can be performed \cite{akiba2019optuna}.
-\bigskip
-
-\subsection{Deep Neural Network Architectures \& Training} \label{section:DNN}
-Before elaborating on the chosen DNN architectures, we will firstly touch upon several universal truths for all networks.
-Given the person-specific character inherent to physiological data,  networks for each respondent have been trained independently.
-Despite this, all network architectures across persons are similar, except for the specified hyperparamaters: these were optimized for each of the four networks and for each respondents individually as well.
-As a consequence, four DNN's are trained for each of the 27 respondents separately, resulting in a total of 108 trained networks, each one utilizing one of 108 sets of optimized hyperparamaters.
-All networks were
-
-\subsubsection{Single-modular Network}
-All single-modular network architectures took inspiration from previously delineated research \cite{schirrmeister2017deep} \cite{dolmans2020perceived} \cite{sun2019hybrid} \cite{biswas2019cornet}.
-In contrast with most of these previous endeavors, we opted for a ConvNet-only approach, i.e.
-without LSTM-layers, for the objective of the current research is not of a time-series-forecasting-kind.
-An experimental scenario wherein the course of actions over the duration of the experiment always unfold in a similar manner are inclined to benefit from acknowledging this time-series-like nature, hence benefiting from LSTM.
-An example of such a scenario would be a pilot in flight: whilst workload arousing phenomena that occur during a flight could differ across takes, the general chronological structure of the scenario always adheres to a similar blueprint.
-I.e., starting with ascend, likely to arouse a peak in workload, and closing with touch down, equally so likely to arouse a peak in workload.
-Our experimental scenario doesn't adhere to such a set in stone unfolding, for the order in which the scenario's with variable difficulty were presented was entirely randomized.
-Hence, for there is no chronologically consistent development of the experimental scenario, we opted for a ConvNet approach without opting to learn from the development over time, thus without LSTM-layers.
-
-The three single-modular DNN architectures are depicted alongside one another as Figure \ref{fig:singlearchitecture}.
-Each of the single-modular networks can be distinguished by two separate part, being the convolutional part and the prediction part.
-The objective of the convolutional part is to extract features from the data.
-For each network, this part consists of four convolutional blocks, each compromising a convolutional layer, a batch normalization layer, the Exponential Linear Unit, hereafter referred to as "ELU", activation function, and a max-pooling layer respectively.
-The prediction part compromises a flatten-layer,  with the objective of representing all input into one dimensional shape, followed by a dropout layer, a dense layer, a Rectified linear activation, hereafter referred to as "RELU", closed by another dense layer.
+The three unimodal DNN architectures are depicted alongside one another in Figure \ref{fig:singlearchitecture}.
+Each of the unimodal networks may be distinguished by two separate parts, being the convolutional part and the prediction part.
+The objective of the convolutional part is to extract features from the data, and consists of four convolutional blocks, each constituting a convolutional layer, a batch normalization layer, the Exponential Linear Unit (ELU) activation function, and a max-pooling layer respectively.
+The objective of the prediction part is to predict the amount of perceived workload,  i.e.
+ultimately resulting in a single prediction of the label.
+The prediction part constitutes a flatten-layer,  with the objective of representing all input into one dimensional shape, followed by a dropout layer, a dense layer, a Rectified Linear (RELU) activation function closed by another dense layer.
 An overview of the amount of utilized filters / neurons for each layer of each network is provided in Table \ref{table:modelvariations}.
 
-Consistent with training, HPO was equally so done for each respondent individually, resulting in 27 optimized sets of parameters for the EEG networks, 27 for the PPG networks and 27 for the GSR networks.We optimized the learning rate, dropout rate and the amount of neurons for the first dense layer in 50 trials per network.
-For training, a total of 600 epochs have been made through the data for each network independently.
-All training and HPO of the single-modular networks has been done on a V100 GPU,  offered by the GPU cloud service Google Collab.
-Total running time for the single-modular networks was about four days, the most of which was absorbed by HPO.
+\vspace{7mm}
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.50]{single_model_architecture}
+\caption{Unimodal Network Architectures.
+Each network constitutes a convolutional part of four convolutional blocks, and a classification part of two fully connected dense layers.
+}\label{fig:singlearchitecture}
+\end{figure}
 
-\newgeometry{margin=2cm}
-\begin{figure}
-\caption{The Three Single-modular Network Architectures}
-\bigskip
-\includegraphics[scale=0.69]{single_model_architecture}
-\label{fig:singlearchitecture}
-\floatfoot{\emph{Note:} Each network constitutes a convolutional part of four convolutional blocks, and a classification part of two fully connected dense layers. }
-\end{figure}
-\restoregeometry
+\newpage
+We optimized the hyperparamater for learning rate, dropout rate and the amount of neurons for the first dense layer (\enquote{Dense1} in Figure \ref{fig:singlearchitecture}).
+This was managed in a total of 50 trials per network.
+With respect to network training, a total of 600 epochs have been made through the data for each network specifically.
+All HPO and training of the unimodal networks was done on a V100 GPU,  offered by the GPU cloud service Google Collab.
+Total running time for the unimodal networks was about 96 hours, the most of which was absorbed by HPO.
 
-\newgeometry{margin=1.6cm}
+\vspace{7mm}
 \bgroup
-\def\arraystretch{1.6}%  
+\def\arraystretch{1.4}  
 \begin{table}[h]
-\caption{Network Sizes}
+\begin{center}
+\caption{Amount of neurons and filters that each respective layer outputs. }
 \label{table:modelvariations}
@@
 \hline
-        & EEG-Net/Part  & GSR-Net/Part  & PPG-Net/Part  & Multi-Modular Head-Net     \\ \hline
- Single-Modular-Nets & Dense Out: 1 & Dense Out: 1 & Dense Out: 1 &   \\
-        & Dense 1: \emph{hpo} & Dense 1: \emph{hpo} & Dense 1: \emph{hpo} &   \\
+        & EEG-Net/Part  & GSR-Net/Part  & PPG-Net/Part  & Multimodal Head-Net     \\ \hline
+ Unimodal-Nets & Dense Out: 1 & Dense Out: 1 & Dense Out: 1 &   \\
+        & Dense 1: \emph{hpo} & Dense1: \emph{hpo} & Dense1: \emph{hpo} &   \\
         \vspace{1.5ex}        
-        & Drop out: \emph{hpo} & Drop out: \emph{hpo} & Drop out: \emph{hpo} &   \\
+        & Dropout: \emph{hpo} & Dropout: \emph{hpo} & Dropout: \emph{hpo} &   \\
         & Conv4: 200 & Conv4: 128 & Conv4: 128 &    \\ 
@@
         & Conv2 50 & Conv2: 32 & Conv2: 32 &    \\ 
-        \vspace{3ex}
-        & Conv1: 25 & Conv1: 16 & Conv1: 16 &  \\         
-  Multi-Modular-Net & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense 1: \emph{input} & Dense Out: 1  \\
-        & Conv4: 200 & Conv4: 128 & Conv4: 128  &  Dense 3: \emph{hpo} \\ 
-        & Conv3: 100 & Conv3: 64 & Conv3: 64 & Dense 2: \emph{hpo}  \\ 
-        & Conv2 50 & Conv2: 32 & Conv2: 32 & Drop out: \emph{hpo}    \\ 
-        \vspace{3ex}
+        \vspace{1mm}
         & Conv1: 25 & Conv1: 16 & Conv1: 16 &  \\      \hline      
+  Multimodal-Net & Dense EEG1: \emph{input} & Dense PPG1: \emph{input} & Dense GSR1: \emph{input} & Dense Out: 1  \\
+        & Conv EEG4: 200 & Conv PPG4: 128 & Conv GSR4: 128  &  Dense3: \emph{hpo} \\ 
+        & Conv EEG3: 100 & Conv PPG3: 64 & Conv GSR3: 64 & Dense2: \emph{hpo}  \\ 
+        & Conv EEG2 50 & Conv PPG2: 32 & Conv GSR2: 32 & Dropout: \emph{hpo}    \\ 
+        & Conv EEG1: 25 & Conv PPG1: 16 & Conv GSR1: 16 &    \\   \hline
 \end{tabular}
-\vspace{2ex}
-\begin{doublespacing}
+\end{center}
+\raggedright \emph{ \newline For all convolutional layers, the depicted numbers reflect the amount of filters that are outputted by the respective layer, whereas for dense layers it reflects the amount of nodes outputted by the respective layer.\textit{\enquote{Input}} refers layers wherein the number of outputting nodes equals the number of inputting nodes.} \par
+\end{table}
 
-\floatfoot{\textit{Notes:} For all convolutional layers the depicted number reflects the amount of utilized filters, whereas for dense layers it reflects the amount  of nodes.
-All depicted values are the amount of filters/nodes that a respective layer outputs.
-\textit{input} refers to fully connected dense layers, wherein the number of outputting nodes equals the number of inputting nodes.
-\textit{Hpo} implies that the value for the respective layer was optimized (see first paragraph of section \ref{section:DNN})}
+\subsubsection*{Multimodal Network Architectures} \label{section:multimodal}
+The multimodal network architecture was determined by combining the previously characterized unimodal architectures into a single architecture.
+These separate network parts were joined by a head-network, the architecture of which drew inspiration from aforementioned research by \citeA{han2020classification}.
+A visual representation of the multimodal network is depicted in Figure \ref{fig:multiarchitecture}.
+An overview of the amount of utilized filters and neurons is provided in Table \ref{table:modelvariations}.
 
-\end{doublespacing}
-\end{table}
-\egroup
-\restoregeometry
+The feature extraction part of the multimodal network architecture is highly similar to the separate unimodel architectures.
+The seperate unimodal parts were combined by means of an intermediate fusion strategy, due to its highly flexible nature as compared with alternative fusion strategies (See: Section \ref{sec:related}).
+The outputs of the three distinct subparts were flattened, followed by a dense layer and RELU activation.
+Flattening was necessary such that all inputs were represented into one-dimensional space, after which concatenation rendered possible.
+The prediction part, also referred to as "Head-Network", consists of three dense layers, alternated with a dropout layer, batch normalization layers and RELU activation layers.
 
-\subsubsection{Multi-modular Network}
-The network architecture utilized for the multi-modular approach was determined by combining the previously characterized single-modular networks with insights drawn from previous research, in particular \cite{han2020classification}.
-A visual representation of the multi-modular network is depicted as Figure \ref{fig:multiarchitecture}.
-An overview of the amount of utilized filters and neurons for each layer of the multi-modular network is provided in Table \ref{table:modelvariations}.
-
-The network architecture for the single-modular parts of the network are separately defined entities of the multi-modular network, but are highly similar as compared with the previously delineated single-modular networks.
-An intermediate fusion strategy is adopted due to its highly flexible nature as compared with alternative fusion strategies.
-The output of all three distinct parts in the network were flattened, followed by a dense layer and RELU activation.
-Flattening was nescessary such that all inputs were represented in one-dimensional space, after which concatenation was possible.
-The prediction part, also referred to as "Head-Network", consists of three dense layers, alternated with dropout, batch normalization and RELU activation.
-
-Again, consistent with training, HPO was equally so done for each respondent individually, resulting in 27 optimized sets of parameters each of the 27 multi-modular networks.
-We optimized the learning rate, dropout rate and the amount of neurons for the first and second dense layers in 18 trials per network.
+We optimized the hyperparameter for learning rate, dropout rate and the amount of neurons for the first and second dense layers in 18 trials per network.
 For training, a total of 250 epochs have been made through the data for each network independently.
 All training and HPO has been done on a Cloud TPU v2,  offered by the GPU cloud service Google Collab Pro.
-Total running time for the multi-modular networks was about 12 days, the most of which absorbed by HPO.
+Total running time for the multimodal networks was about 7 days, the most of which absorbed by HPO.
 
-\newgeometry{margin=2cm}
-\begin{figure}
-\caption{The Multi-modular Network Architecture}
-\bigskip
-\includegraphics[scale=0.69]{multi_model_architecture}
-\label{fig:multiarchitecture}
-\floatfoot{\emph{Note:} The network constitutes a convolutional part of four convolutional blocks for each of distinct parts of the networks.
-All three distinct parts were flatenned, after which concatenation was possible.
-The prediction part of the network constitutes several dense layers.}
+\vspace{6mm}
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.50]{multi_model_architecture}
+\caption{Multimodal Network Architecture.
+The network constitutes a convolutional part of four convolutional blocks for each of distinct network parts.
+All three distinct parts were flattened and concatenated subsequently.
+The prediction part of the network constitutes several dense layers.}\label{fig:multiarchitecture}
 \end{figure}
-\restoregeometry
 
-\newpage
-\subsection{Model Evaluation}
-The performance of the networks has been assessed and contrasted by means of several performance metrics.
-When assessing performance in deep/machine-learning, it is of importance to realize that each performance metric may favor one approach over the other, simply and solely due to the mathematical nature in which both the metric and the model are defined \cite{gunawardana2009survey}.
-For this reason, we consider a conglomerate of different metrics.
+\subsection{Network Performance Evaluation}
+For each of the four investigated network architectures, the predictions of all 27 individually trained network were aggregated, after which performance was assessed by means of the following three performance metrics.
 
-The Mean Absolute Error, hereafter referred to as "MAE",  of a DNN is the first utilized performance metric, defined as Equation \ref{eq:mae},
+The Mean Absolute Error, hereafter referred to as "MAE",  is the first utilized performance metric, defined as:
 
-\begin{equation}
-\label{eq:mae}
-\frac{1}{n} \sum^n_{i=1}|f(x_i)-y_i| 
-\end{equation}
-where $n$ refers to the amount of windows utilized for testing, $x_i$ to the predicted value for window $i$ and $y_i$ to the true label of window $i$.
-The MAE constitutes the most straightforward metric for the assessment in performance of a DNN, especially since the value can simply be interpreted as the average amount by which the prediction was off.
+$$\frac{1}{n} \sum^n_{i=1}|f(x_i)-y_i|$$
+where $n$ refers to the total amount of testing windows, $f(x_i)$ to the predicted value for window $i$ and $y_i$ to the true label of window $i$.
+The MAE constitutes the most straightforward metric for DNN performance assessment, for its value can simply be interpreted as the average misprediction.
 
-The Root Mean Squared Error, hereafter referred to as RMSE, is the second utilized performance metric, defined as Equation \ref{eq:rmse},
+The Root Mean Squared Error, hereafter referred to as "RMSE", is the second utilized performance metric, defined as:
 
-\begin{equation}
-\label{eq:rmse}
-\sqrt{{\frac{1}{n} \sum^n_{i=1}|f(x_i)-y_i|}^2}
-\end{equation}
-where $n$ refers to the amount of windows utilized for testing, $x_i$ to the predicted value for window $i$ and $y_i$ to the true label of window $i$.The RMSE, which is strongly related to the MAE, differs in that it punishes big absolute differences more severely.
+$$\sqrt{{\frac{1}{n} \sum^n_{i=1} \Big( f(x_i)-y_i} \Big) ^2}$$
+where $n$ refers to the amount of testing windows, $f(x_i)$ to the predicted value for window $i$ and $y_i$ to the true label of window $i$.
+The RMSE is closely related to the MAE, differing in that it tends to punish big differences more severely.
 
-Finally, the Pearson Correlation Coefficient, hereafter referred to as simply "correlation", constitutes the third utilized performance metric defined as Equation  \ref{eq:corr},
+Finally, Pearson's correlation coefficient, hereafter referred to as simply "correlation", constitutes the third utilized performance metric, defined as:
 
-\begin{equation}
-\label{eq:corr}
-r_{X,Y} = \frac{cov(X,Y)}{\sigma_{X} \sigma_{Y}}
-\end{equation}
-where $x$ refers to the predicted values for the test windows,  $y$ to the true labels of test windows and $\sigma_{X}\, \& \,\sigma_{Y}$ refer to the standard deviation of $x$ and $y$ respectively.
-Conceptually, correlation indicates the coherence between predictions and labels, hereby posing an alternative model performance metric.
+$$r_{X,Y} = \frac{cov(X,Y)}{\sigma_{X} \sigma_{Y}}$$
+where $X$ refers to the predicted test windows,  $Y$ to the true labels of the test windows, $cov(X,Y)$ to their covariance and $\sigma_{X}$ and $\sigma_{Y}$ to the standard deviation of $x$ and $y$ respectively.
+Conceptually, correlation can be interpreted as the strength of the linear relationship between predictions and their labels, thus providing an indication of network performance.
 
-\newpage
+\vspace{8mm}
 \section{Results}
-Before illustrating results,  a short elaboration on the testing procedure will be provided.
-Windows of eight seconds each were cut, resulting in a total of 9474 windows over all respondents, i.e.
-on average about 351 windows per respondent.
-For each network for each respondent individually,  80\% of all windows have been used for training, 10\% for validation within the training process and 10\% for the assessment of performance.
-This results in an average of 35 windows for assessing DNN performance per respondent, i.e.
-a total of 969 windows in total.
-Partitioning windows into train-, validation- and testing -sets was done systematically by selecting every \textit{n-th} window, such that windows over the entire duration of the experiment were represented equally in each partition.
-These partitions compromise exactly the same windows across the four networks.
+Before addressing network performance, a description of all window labels is depicted in Figure \ref{fig:labels}.
+This constitutes an aggregation of the labels of all windows over all participants, resulting in a total of 9474 depicted window labels.
+It becomes readily apparent that the distribution of the window labels displays a noticeably right-skewed tendency, with a median of 5.75 and an 90\% upper-bound quantatile of 12.75.
+This implies that there is a considerable underrepresentation of high workload windows.
 
-The distribution of all 9474 window labels, aggregated for all respondents,  is depicted as Figure \ref{fig:labels}.
-It becomes readily apparent that distribution of the window labels displays a noticeably right-skewed tendency, with a median of 5.75 and a 12.75 90\% upper-bound quantatile, implying that higher workload windows are relatively uncommon within both train and test partitions.
-\vspace{0.1cm}
-
+\vspace{3mm}
 \begin{figure}[h]
-\caption{Distribution Window Labels}
-\includegraphics[scale=0.39]{labels.png}
-\label{fig:labels}
-\floatfoot{\emph{Note:} The solid line represents the median, whereas the two dashed line represent the 10\% and 90\% quantiles respectively.}
+\centering
+\includegraphics[scale=0.45]{labels.png}
+\caption{Distribution window labels.
+The solid line represents the median, whereas the two dashed line and their displayed values represent the 10\% and 90\% quantiles respectively.
+}\label{fig:labels}
 \end{figure}
@@
 \subsection{Deep Neural Network Performance}
-Depicted in Table \ref{table:results} are the performance metrics for each of the trained DNN's.
-The most conspicuous result that becomes apparent is that the multi-modality networks performs consistently worse on all metrics as compared with both the single-modular EEG and GSR networks.
+Depicted in Table \ref{table:results} are the performance metrics for each of the four network architectures.
+The most remarkable result is the relatively bad performance of the multimodal architecture.
+Both the unimodal EEG and GSR architectures score consistently higher on all metrics.
 
-\vspace{0.3cm}
+Performance in terms of MAE is most favorable for the EEG architecture, closely followed by the GSR architecture.
+The multimodal architecture performs worse as compared with the aforementioned architectures, ultimately followed by the PPG architecture which performed worst.
+Results in terms of RMSE adhere to a similar pattern, which is not surprising given that the RMSE and MAE are closely related.
+RMSE values are consistently higher as compared with MAE, which can be attributed to the tendency of the RMSE to punish strong deviations more severely.
+The correlation between predictions and labels are indicative of a similar pattern, in which the EEG architecture scores best, followed by the GSR, multimodal and PPG -architectures respectively Despite consistency in this pattern, an interesting disparity is that the differences in terms of correlation between the architectures are more substantial.
+In addition to the aforementioned results, we also assessed network performance on the training data, with the objective of gaining insight into overfitting.
+Table \ref{table:appendix} in Appendix \ref{sec:appendix} depicts the performance metrics of the networks as deployed on the training data.
+It becomes apparent that the unimodal architectures perform substantially better on the training data, whereas the multimodal architecture performs slightly better on the training data.
+
+\vspace{7mm}
 \bgroup
-\def\arraystretch{1.6}%  
+\def\arraystretch{1.4}  
 \begin{table}[h]
-\caption{Deep Neural Network performance metrics}
-\label{table:results}
+\begin{center}
+\caption{Deep Neural Network Performance Metrics} \label{table:results}
 \begin{tabular}{lllll}
 \hline
-                                                                               & EEG\hspace{0.5cm} & PPG\hspace{0.5cm} & GSR\hspace{0.5cm} & Multi\hspace{0.5cm} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Mean Absolute Error\\ \hspace{1.2cm}(\textit{0-1 scale})\end{tabular} & 0.110 & 0.136 & 0.119 & 0.128  \\
-\begin{tabular}[c]{@{}l@{}}Mean Absolute Error\\ \hspace{0.25cm}(\textit{original 0-20 scale})\end{tabular} & 2.206 & 2.717 & 2.377 & 2.570 \\
-Root Mean Square Error                                                         & 0.154 & 0.180 & 0.159 & 0.167 \\
-Pearson Correlation                                                                    & 0.688 & 0.530 & 0.653 & 0.609 \\ \hline
+ &
+  \begin{tabular}[c]{@{}l@{}}MAE (sd) \\ 0-1 scale\end{tabular} &
+  \begin{tabular}[c]{@{}l@{}}MAE (sd) \\ 0-20 scale\end{tabular} &
+  \begin{tabular}[c]{@{}l@{}}RMSE \\ 0-1 Scale\end{tabular} &
+  \begin{tabular}[c]{@{}l@{}}Pearson's\\ Correlation\end{tabular} \\ \hline
+EEG        & 0.110 \,\,(0.15) & \,\,2.206 \,\,(3.08) & \,\,0.154 & 0.688 \\
+PPG        & 0.136 \,\,0.18) & \,\,2.717 \,\,(3.59) & \,\,0.180 & 0.530 \\
+GSR        & 0.119 \,\,(0.16) & \,\,2.377 \,\,3.18) & \,\,0.159 & 0.653 \\
+Multimodal & 0.128 \,\,(0.17) & \,\,2.570 \,\,(3.33) & \,\,0.167 & 0.609 \\ \hline
 \end{tabular}
+\end{center}
+\raggedright{ \emph{\newline Values between parentheses are standard deviations.
+MAE refers to Mean Average Error.
+RMSE refers to Root Mean Square Error.
+The depicted values are the averages of all individually trained networks.}}
 \end{table}
+\vspace{7mm}
 
-Performance in terms of MAE of the EEG networks is superior over all other networks, with $MAE = 0.110$ with a standard deviation of $\sigma = 0.154$.
-The DNN's demonstrating the next best performance are the GSR networks, closely pursuing the EGG networks,  and displaying $MAE = 0.119$ with a standard deviation of $\sigma = 0.159$.
-Surprisingly, the multi-modular networks check out on the third place, displaying $MAE = 0.128$ with a standard deviation of $\sigma = 0.167$.
-The PPG networks can clearly be considered the worst performing networks, displaying $MAE = 0.136$ with a standard deviation of $\sigma = 0.179$.
+An independent samples t-test was conducted to formally test differences in terms of absolute (window) error across various pairs of architectures.  The absolute error of a window $i$ is defined as:
 
-A similar pattern can be observed when observing the RMSE.This is not surprising, given the RMSE is very similar to the MAE.
-The difference is that the RMSE values for all networks reside slightly higher, which is not surprising for the punishes high deviations more severely.
+$$|f(x_i)-y_i|$$
+where $f(x_i)$ represents the predicted value for window $i$ and $y_i$ represents its true label.
+Testing was done two-sided with $\alpha = 0.05$.
+Mean absolute error values per architecture are not reported, for they can be discerned from Table \ref{table:results}.
+The absolute error for the unimodel EEG architecture was found to be significantly lower as compared with the multimodel architecture $t(1936)=-2.566, p=0.01$.
+No significant difference in terms of absolute error between the EEG- and GSR -architectures was found $t(1936)=-1.188, p=0.24$, and equally so no significant difference was found between the GSR- and multimodal -architectures $t(1936)=-1.463, p = 0.144$.
+Lastly, absolute error for the GSR architecture was found to be significantly lower as compared with the PPG architecture $t(1936)=-2.636 , p = 0.008$, but no significant difference was found between the GSR- and multimodal -architecture $t(1936)=-1.164 , p = 0.245$.
 
-The correlation between predictions and labels are indicative of a similar pattern as compared with the other metrics.
-Although patterns are similar, an interesting disparity is, however, that the differences across the four architectures is more substantial.
-The value for the EEG networks are observed to be $r=0.688$, which is interpretable as a rather strong correlation.
-Equally so, the GSR networks display a fairly strong correlation of $r=0.653$.
-Again, Both the multi and GSR networks are the least accurately performing, displaying a correlation of $r=0.609$ and $r=530$ respectively.
+To explore performance differences across architectures into more detail, a graphical visualization of the distribution of window prediction errors per architecture are depicted in Figure \ref{fig:mae_hist}.
 
-A graphical visualization of the prediction errors for each of the four network architectures is depicted as Figure \ref{fig:mae_hist}.
+\vspace{7mm}
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.56]{error_hist.png}
+\vspace{2mm}
+\caption{Distribution of window prediction error per network architecture.
+The solid lines represent the median, whereas the dashed lines represent the 10\% and 90\% quantiles respectively.
+} \label{fig:mae_hist}
+\end{figure}
+\vspace{7mm}
 
-\vspace{0.3cm}
-\begin{figure}[h]
-\caption{Error per modality}
-\bigskip
-\includegraphics[scale=0.6]{error_hist.png}
-\label{fig:mae_hist}
-\floatfoot{\emph{Note:} The solid line represents the medians, whereas the two dashed line represent the 10\% and 90\% quantiles respectively. The displayed numbers are the values of the quantiles.}
-\end{figure}
-
-In line with the previously delineated results, it becomes readily apparent that the distribution of the prediction errors for the EEG networks approximates the normal distribution most closely, as indicative by the strong accumulation around 0 error and relatively flat tails.
-Not surprisingly, the two worst performing DNN's, being the multi-modular and PPG networks, display much thicker tails, and are observed to have a less accumulation around the 0 error mark (i.e.
+In line with the previously presented performance metrics, it becomes readily apparent that the distribution of the prediction errors for the architecture that scored highest across all metrics, i.e.
+the EEG architecture, approximates the normal distribution most closely.
+This may be derived by the strong accumulation around 0 error (i.e.
+visually "peaked") and the relatively flat tails.
+The two worst performing architectures, i.e.
+multimodal- and PPG -architectures, display relatively thick tails, and are observed to have less strong accumulation around the 0 error mark (i.e.
 visually "less-peaked").
@@
 All distributions are observed to be slightly left-skewed, as indicated firstly by shape and secondly by the fact that 10\% quantiles are farther removed from the median as compared with the 90\% quantiles.
-Despite that this left-leaning tendency is observable for all network architectures, it is most profound for the PPG and multi-modular networks.
-These previously delineated anomalies indicate that all networks are less accurate in predicting high-labeled windows, and that this seems to be more profound for the PPG and multi-modular networks.
+Despite that this left-leaning tendency is observable for all network architectures, it is most profound for the PPG and multimodal architectures.
 
-Figure \ref{fig:mae_scatter} helps explore this notion into more detail,  by plotting prediction error of each window against its label value,  in addition to their linear relationship and correlation coefficient.
+\newpage
+We further explore the results by means of a graphical visualization of absolute window prediction error against label value. This relationship is defined by Figure \ref{fig:mae_scatter}.
 
-\vspace{0.3cm}
+\vspace{7mm}
 \begin{figure}[h]
-\caption{Window Prediction Error as opposed to Window Label Value}
-\includegraphics[scale=0.64]{mae_scatter.png}
-\label{fig:mae_scatter}
-\floatfoot{\emph{Note:} The red lines represent the linear relationship between prediction error and label value. The values \textit{r} represent their Pearson Correlation Coefficient.}
+\centering
+\includegraphics[scale=0.5]{mae_scatter.png}
+\caption{Relationship of absolute window prediction error opposed to window label value.
+The red lines represent the linear relationship between absolute prediction error and label value.
+The values \textit{r} represent the Pearson's Correlation coefficient between prediction errors and label values.} \label{fig:mae_scatter}
 \end{figure}
+\vspace{7mm}
 
-Firstly, it becomes immediately apparent that higher labeled windows are substantially less prevailing, as indicative by the thin spreading of dots for the higher labels, conform to the conclusion drawn from the earlier depicted Figure \ref{fig:labels}.
-Noteworthy is that, for each the four network architectures, a relationship can be observed between the height of the absolute value of the prediction error and the height of the label.
-This is indicative by the moderately ascending slope, as well as the correlation coefficients.
-Substantively, this implies that all network architectures are observed to be considerably less accurate when predicting high labeled windows.
-This tendency upholds the most for the multi-modular and PPG networks, with an observable correlation coefficients as high as $r=0.37$ for the multi-modular networks specifically.
-A, less severe, but still noteworthy relationship between prediction error and label size is observable for both the GSR and EEG architectures,  with a correlation coefficients of $r=0.24$ and $r=0.28$ respectively.
+It becomes apparent from Figure \ref{fig:mae_scatter}} that higher labeled windows are substantially less prevailing, as indicated by the thin spreading of dots at the right hand side of the figures,  This is conform to the conclusion drawn from the earlier depicted Figure \ref{fig:labels}.
+Most noteworthy is that for each of the four architectures, a linear relationship between the height of the absolute window prediction error and its respective label is observed.
+This is indicated by both the moderately ascending slope and the moderately high (positive) correlations coefficients $r$.
+Substantively, this implies that all network architectures are considerably less accurate in predicting high labeled windows.
+This tendency is strongest for the multimodal architecture.
+For both the EEG- and GSR -architectures, this linear relationship is observed to be weaker, although still of noteworthy size.
 
-\section{Conclusion and Discussion}
-It can be concluded that the single-modular EEG networks consistently exhibit the best performance,  with a rather noteworthy difference on the correlations in particular.
-The single-modular GSR networks, although being worse as compared with the EEG networks, also were observed to exhibit fairly adequate performance.
-Most surprising is that the multi-modular networks performed substantially worse as the previously mentioned, especially as compared with the EEG networks.
-This was not expected, for one is enticed to expect that the network combining information from multiple modalities would yield more adequate performance as compared with networks solely using a single of these modalities.
-Apparently
+\newpage
+\section{Discussion \& Conclusion}
+We found the unimodal EEG architecture to perform best on all performance metrics,  with a rather sizable difference in the correlations between predictions and labels.
+In terms of absolute window prediction error, statistical evidence was found in favor of the unimodal EEG architecture outperforming the multimodel architecture, but not so in favor of the EEG architecture outperforming the GSR architectures.
+Performance of the GSR architecture was detected to be worse on all metrics as compared with the EEG architecture, but better on all metrics as compared with the multimodal architecture.
+These differences were, however, not found to be statistically significant in terms of absolute window prediction error.
+The unimodal PPG architecture was found to perform worst across the board.
+In terms of absolute window prediction error, this difference was found to be statistically significant when evaluated against the EEG- and GSR -architectures.
+When applied on the training data, network performance was substantially improved, indicative of overfitting.
+This especially held true for the singlemodal architectures.
+Lastly, a moderate relationship was observed between absolute prediction error and label size, implying that all network architectures performed worse on higher labeled windows.
+This deviation was strongest for the two worst performing architectures, i.e.
+the multimodal and PPG.
 
-\begin{itemize}
-  \item  More HPO could have been done, to get even better performing models but we had limited computatioal power.   
-  \item This approach costs a lot of computational power to both train and do HPO. Especially since person-specific models are fitted. This upholds mostly for the multi-modal network.
-  \item Due to the sheer size of the trained model and the fact that models are trained person specific, storage sizes of the models are huge.
-This could be unpractical.
-This upholds mostly for the multi-modal network.
-  \item Possibly different window sizes per modality could lead to better results.
-* Insert some of the sources here that suggest different window sizes per modality* .
-This was beyond the scope of this project.
-   \item How generizable is this to other situations for the same person (since things such as PPG are context dependent (like for example regarding how one ate).
-   \item Long runtimes,  even when testing. This upholds only for the multi network. The reason is likely the sheer size of these networks, which for some persons are blown up due to device lagging. 
-   \item hardware failure?
-   \item The fact that we use TLX as labels.
-\end{itemize}
+\subsection{Discussion}
+Perhaps the most noteworthy of all aforementioned results is that the unimodel EEG architecture outperformed the multimodal architecture.
+As argued in the introduction, the opposite was expected: given that the predictions of a multimodal architecture rest on a richer conglomerate of information, better performance is expected.
+Lending credence to this this inclination is previous research that found a multimodal architecture to perform superiourly \cite{dolmans2020perceived, han2020classification, rastgoo2019automatic, yin2017recognition}.
+In the subsequent sections we aim to rationalize our results.
+
+One reason could be the network architecture.
+Conform to  \citeA{han2020classification}, a shallow head network architecture was adopted, solely consisting of several fully connected dense layers.
+Further investigation into various alternative head network architectures could have resulted in a more adequately performing network,  but would have increased the computational expenses considerably.
+
+Besides this, an important consideration in the fields of statistics and machine-learning alike, is the oftentimes precarious balance between model complexity and simplicity.
+A model that is overly complex is in increased peril of overfitting, i.e.
+performing well on training data, but failing to generalize to testing data \cite{lever2016points}.
+Overfitting can especially be anticipated when training a relatively complex DNN on a small amount of data \cite{feng2019using,aggarwal2018neural}.
+As was argued before,  our case required personally trained networks due to the person-specific nature that is inherent to physiological data, resulting in a small amount of training data per DNN.
+Strong evidence in favor of overfitting was found for the unimodal architectures, posing that these network architectures were too complex to be trained on a small amount of data.
+Surprisingly, the even more complex multiodal architecture did only produce moderate overfitting.
+However despite this, it should be acknowledged that the core of the multimodal architecture is a composite of the overly complex unimodal architectures, which likely contributed to its relatively inadequate performance.
+
+Another noteworthy result was the expounded relationship between a window's absolute error and its respective label score (as was visualized by Figure \ref{fig:mae_scatter}).
+It was visualized that all four architectures were consistently less accurate in predicting high labeled windows.
+A credible explanation for this is the relatively minor presence of high labeled windows in our data (as was visualized by Figure \ref{fig:labels}).
+Naturally, when a relatively small amount of high labeled windows are present in the training data, the network doesn't adequately learn to predict such windows.
+
+Finally, despite that a comparison of absolute window prediction error across several architectures was found to be statistically significant, all differences in terms of MAE and RMSE were rather small.
+The statistical significance of some of the conducted t-tests can particularly be attributed to the vast amount of degrees of freedom with which was tested.
+We therefore reflect on the following: in opposite to our finding, suppose that a multimodal approach would have entailed a moderate improvement in performance over an unimodal approach.
+Would this justify the addition in complexity,  the considerable increment in computational expenditure and the necessity to invest in a multitude of different physiological sensors?
+In other words, isn't the already adequately performing, and much less complex unimodal EEG approach sufficient for most tasks at hand?
+The answer to this question is context dependent, and should be reconsidered in each case specifically.
+
+\subsection{Limitations \& Future Research Recommendations}
+Additional research is necessary in order to find more optimal DNN architectures for small data scenario's such as the current.
+More specifically, 1) which network architectures are able to minimize overfitting and 2) which network architecture is most suitable for a multimodal approach.
+An effective approach to investigate this is by means of HPO.
+Apart from only optimizing hyperparamaters, a network architecture in its entirety can be optimized.
+In the current study we optimized several hyperparamaters, however the architecture in itself was pre-specified.
+A recommendation for future research is therefore to further investigate upon an appropriate architecture for both the unimodal and multimodal approaches
+
+As expounded on before, all architectures were found to be less precise in predicting high labeled windows, attributable to the fact that such windows were relatively uncommon in our data.
+This could stem from either 1) the fact that respondents refrained from indicating high workload on the NASA-TLX items utilized for labeling, or 2) respondents simply did not experience high workload throughout the experiment.
+Alternative labeling approaches may be suited to address the first point.
+Ideally, one would want to contrast various labeling strategies with one another, such that the most suitable labels for the task at hand may be utilized.
+Potentially interesting alternatives approaches to labeling are for example a standardized version of the NASA-TLX, or an objective difficulty score for each task, as was proposed by \citeA{dolmans2020perceived}.
+The second point could be addressed by designing the simulational scenario such high workload envoking segments are prevalent throughout the entire scenario.
+One could assess this by pretesting, and increasing the difficulty in certain segments if need be.
+
+Finally, as was elaborated on before, the ultimate goal of this line of research is to obtain trained networks utilizable for workload assessment in a simulational setting.
+The personal differences that are inherent to physiological data were acknowledged by utilizing an individual network for each participant.
+However apart from such between-personal differences, physiological data might be characterized by between-occasional differences as well.
+To give an example, PPG measurement is dependent upon various occasional factors such as amongst others the amount of emitted surrounding light, body position, cardiovascular stresses, etc.
+\cite{lemay2014application}.
+Further research is required in order to assess the generelizability of a personally trained network to different occasions.
+
+\subsection{Conclusion}
+We took three unimodal and one multimodal approach to workload prediction by means of physiological sensors.
+The performance of the unimodal EEG-, GSR-, and PPG -architectures were assessed in order to determine the most suitable modality for workload prediction.
+In addition, an architecture combining all aforementioned modalities was proposed and assessed in terms of performance.
+It was found that all architectures performed rather adequately.
+A difference in performance was observable however: most notably it was found that the unimodal EEG architecture performed best.
+Surprisingly, we found a multimodal approach to be unjustified, however several explanations were considered that could potentially refute this.
+The implications of the current research is another step in the exploration of multimodal deep learning approaches towards workload prediction.
+Future research in this field will ideally investigate upon 1) network architectures that prevent substantial overfitting in a small dataset scenario,  2) an appropriate architecture for a multimodal approach in a small dataset scenario, 3) the feasibility of different labeling strategies and 4) the cross-occasional generelization of individually trained networks.
 
@@
 
+\newpage
+\appendix
+\section{Appendix} \label{sec:appendix}
+\subsection*{Performance on Training Data}
+\setcounter{table}{0}    
+\counterwithin{table}{section}
+
+\vspace{15mm}
+\bgroup
+\def\arraystretch{1.6}%  
+\begin{table}[h]
+\begin{center}
+\caption{Deep neural network performance metrics on training data}
+\label{table:appendix}
+\begin{tabular}{lllll}
+\hline
+ &
+  \begin{tabular}[c]{@{}l@{}}MAE (sd) \\ 0-1 scale\end{tabular} &
+  \begin{tabular}[c]{@{}l@{}}MAE (sd) \\ 0-20 scale\end{tabular} &
+  \begin{tabular}[c]{@{}l@{}}RMSE (sd) \\ 0-1 Scale\end{tabular} &
+  Correlation \\ \hline
+EEG        & 0.038 \,\,(0.06) & \,\,0.761 \,\,(1.14) & \,\,0.070 & 0.944 \\
+PPG        & 0.077 \,\,(0.11) & \,\,1.541 \,\,(2.28) & \,\,0.114 & 0.838 \\
+GSR        & 0.085 \,\,(0.12) & \,\,1.700 \,\,(2.43) & \,\,0.122 & 0.813 \\
+Multimodal & 0.116 \,\,(0.16) & \,\,2.331 \,\,(3.11) & \,\,0.156 & 0.670 \\ \hline
+\end{tabular}
+\end{center}
+{\raggedright \emph{ \newline Values between parentheses are standard deviations. Mae refers to Mean Average Error. RMSE refers to Root Mean Square Error. } \par}
+\end{table}
+\vspace{3mm}
+
 \end{document}

### 2021-05-08 1.pipeline/main.py

@@ -14,7 +14,7 @@ import csv
 import torch
 
 #Setting working directory 
-os.chdir("pipeline")
+os.chdir("1.pipeline")
 
 try: #Importing from subfile
     from transformer import transformer

### 2021-05-08 4.results/results.py

@@ -16,9 +16,38 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import scipy
 from scipy.stats import t
+import csv
 
+def Descriptives():
+    """
+    Purpose:
+        Calculates and print several demographic descriptive information
+    """    
+    
+    #Open data
+    with open("4.results/descriptives/Demographics.csv") as csvfile:
+        data = pd.read_csv(csvfile)
 
-def Performance(modality):
+        #Remove participants that were not included in the final analysis
+        participants = ["bci 10", "bci 12", "bci 13", "bci 17", "bci 21", "bci 22",
+                "bci 23", "bci 24", "bci 26", "bci 27", "bci 28", "bci 29", "bci 30", 
+                "bci 31", "bci 32", "bci 33", "bci 34", "bci 35", "bci 36", "bci 37", 
+                "bci 38", "bci 39", "bci 40", "bci 41", "bci 42", "bci 43", "bci 44"]
+        participants = pd.DataFrame(participants)
+        participants = participants.rename(columns = {0:"User full name"})
+        data = data[data["User full name"].isin(participants["User full name"])]
+
+        #Print desriptives
+        print("---------------------------------------------------")
+        print("The total number of cases is N = "+str(len(data)))
+        print("---------------------------------------------------")
+        print("Number of Females = "+str(data["What is your gender?"].value_counts()["Female"]))
+        print("Number of Males = "+str(data["What is your gender?"].value_counts()["Male"]))
+        print("---------------------------------------------------")
+        print("Mean Age = "+str(round(sum(data['What is your age?<span class="boundaries"></span>']) / len(data))))
+        print("Standard Deviation Age = "+str(round(np.std(data['What is your age?<span class="boundaries"></span>']),1)))
+
+def Performance(modality, data):
     """
     Purpose:
         Calculates and print several performance statistics
@@ -32,8 +61,11 @@ def Performance(modality):
 
 
     #Open results
-    results = pickle.load(open("results/predictions/"+modality+".pickle", "rb"))  
-    
+    if data == "test":
[…]

### 2021-05-13 0.manuscript/manuscript.tex
Final version thesis

@@
 
-\title{Physiological sensor based prediction of mental workload: A multimodal deep learning approach}
+\title{Physiological sensor based mental workload assessment: A multimodal deep learning approach}
 
@@
 \begin{abstract}
-The assessment of mental workload by means of physiological sensors has gained in popularity in recent years.
-We utilized three physiological sensors from which mental workload was predicted, being electroencephalography, photoplethysmography and galvanic skin response.
+The approach of using physiological sensors for the assessment of mental workload has gained in popularity in recent years.
+We utilized three physiological sensors in predicting mental workload, being electroencephalography (EEG), photoplethysmography (PPG) and galvanic skin response (GSR).
 Deep learning poses a promising, yet novel, approach towards the modeling of such sensory data.
@@
 Three out of four were specified to predict workload based on on a single of the aforementioned physiological sensors, whilst the fourth architecture was a joint neural network combining all physiological signals into a single model.
-In this study we aimed to identify 1) which physiological sensor constitutes the most adequate predictor of mental workload, and 2) whether a joint approach utilizing multiple sensors is preferable over the approaches utilizing just one.
-Altogether the electroencephalography-only architecture was found to perform best, closely followed by the galvanic skin response-only architecture,  both displaying a mean absolute error of 0.110 and 0.119 (scaled on 0-1) respectively.
-Against expectations, the joint approach was outperformed by both aforementioned architectures, displaying a mean absolute error of 0.128 (equally so scaled on 0-1).
-The photoplethysmography-only architecture was found to perform worst, displaying a mean absolute error of 0.136.
-In the discussion section we presented several explanations that help rationalize this anomaly, one being due to an imperfect model architecture for the joint neural network, and another being due to overfitting resulting from a limited amount of data.
-Regardless of the unexpected character of this result, we still recognize that differences in performance were of rather modest size: all four neural network architectures performed fairly adequately.
+In this study we investigated 1) which physiological sensor individually constitutes the most adequate predictor of mental workload, and 2) whether an approach utilizing multiple sensors simultaneously (i.e.
+multimodal) is preferable over the approaches utilizing just one.
+Altogether the EEG-only architecture was found to perform best displaying a mean absolute error of 0.110.
+We thus conclude that EEG may be considered the most adequate predictor of workload.
+A mean absolute error of 0.119 was found for the GSR-only architecture.
+Against expectations, the multimodal approach was outperformed by both aforementioned architectures, displaying a mean absolute error of 0.128.
+The PPG-only architecture was found to perform worst, displaying a mean absolute error of 0.136.
+We posed several explanations that help rationalize why the multimodal architecture was found to perform suboptimal, one being an imperfect model architecture, and another being overfitting as resulting from a limited amount of data.
+Regardless, we demonstrated that the differences in performance across the four network architectures were rather small, i.e.
+all four neural network architectures performed adequately.
 \end{abstract}
@@
 
-\begin{large}
+\begin{Large}
 {\setlength{\parindent}{0cm}
@@
 }
+\vspace{2mm}
 \newline Utrecht University, the Netherlands
@@
 \newline MSc Thesis Bart-Jan Boverhof (6000142)
+\vspace{2mm}
 \newline Physiological sensor based prediction of mental workload: A multimodal deep learning approach
+\vspace{2mm}
 \newline May 2021
@@
 \newline Supervisor:
+\vspace{1mm}
 \newline Prof. Dr. Ir. Bernard Veldkamp
@@
 \newline Second grader:
+\vspace{1mm}
 \newline Prof. Dr. Ir René Eijkemans
@@
 \newline Preferred journal of publication: Frontiers in Neuroscience
-\end{large}
+\vspace{1mm}
+\newline Word count: 5603
+\end{Large}
 \end{titlepage}
@@
 This method embodies several dimensions, jointly inquiring into the amount of perceived workload \cite{hart2006nasa}.
-However, due to the ever-increasing availability in computing power characterizing recent times, a novel approach to workload assessment has gained in popularity.
+Recently, a novel approach has gained in popularity, however.
 This promising approach constitutes the use of physiological sensors, worn throughout the entire duration of the experiment.
-An approach like this poses the advantage that the development of perceived workload may be monitored throughout the entire experiment, enabling the possibility to precisely monitor the impact of a specific task on a participant's level of workload.
+The advantage of this approach, is that the development of perceived workload may be monitored throughout the entire experiment, enabling the possibility to precisely monitor the impact of a specific task on a participant's level of workload.
 Another advantage is that the method may be personalized, which could simply be done by creating and training an individual model for each participant.
@@
 The three utilized modalities are electroencephalography (EEG), photoplethysmography (PPG) and galvanic skin response (GSR).
-EEG is a technique that monitors electrical activity in the brain, and is often utilized in the assessment of workload \cite{berka2005evaluation, craik2019deep}.
-EEG is found to be amongst the most adequately performing techniques for this task \cite{hogervorst2014combining}.
-GSR is a technique that measures electrical conductance of the skin, and equally so is a widely adopted method for workload assessment \cite{nourbakhsh2012using, zhou2015dynamic}.
+EEG is a technique that monitors electrical activity in the brain, and is often utilized in the assessment of workload \cite{berka2005evaluation, craik2019deep, hogervorst2014combining}.
+GSR is a technique that measures electrical conductance of the skin, and equally so is a widely adopted approach to workload assessment \cite{nourbakhsh2012using, zhou2015dynamic}.
 Lastly, also heart-rate is a widely utilized indicator of workload, mostly obtained through PPG \cite{zhang2018evaluating,jimenez2018using}.
 
-In this project we opted for a deep learning approach towards workload prediction.
+In this project we opted for a deep learning approach towards modeling.
 A range of four different deep neural network architectures, hereafter referred to as \enquote{DNN's} or simply \enquote{networks},  are constructed and contrasted in their performance.
-Among these are three unimodal DNN's, i.e.
-networks each utilizing only a single modality.
-Thus,  one network solely utilizes the EEG modality,  one solely utilizes the GSR modality and one solely utilizes the PPG modality.
-The fourth is a multimodal network, i.e.
-combining all three aforementioned modalities into a single architecture.
-The main advantage of taking a deep learning approach specifically resides in its flexibility.
-Fitting a model that combines multiple modalities can be done in different, relatively straightforward, ways when taking a deep learning approach \cite{ramachandram2017deep}.
-We expect the multimodal approach to results in better performance as compared with the unimodal approaches, for predictions are based on richer composite of information.
+Among these are three unimodal DNN architectures, each utilizing only a single modality.
+Thus,  one architecture solely utilizes the EEG modality,  one solely utilizes the GSR modality and one solely utilizes the PPG modality.
+The fourth is a multimodal architecture, combining all three aforementioned modalities into a single framework.
+The main advantage of taking a deep learning approach resides its flexibility: designing a network architecture that combines multiple modalities may be done in a relatively straightforward manner \cite{ramachandram2017deep}.
+
+With this research we 1) seek to explore which individual modality constitutes the most adequate predictor of workload when taking a deep learning approach, and 2) whether a multimodal DNN architecture is preferable over the three simpler (but much less computationally demanding) unimodal network architectures.
+With regards to the first point, only a single study was found that contrasted several modalities in their ability to predict workload.
+\citeA{hogervorst2014combining} contrasted multiple modalities, and reported EEG to be the best performing.We therefore carefully hypothesize the EEG modality to be the most adequate predictor of workload.
+With regards to the second point, we expect the multimodal approach to attain better performance as compared with the unimodal approaches, for predictions are based on richer composite of information.
 This expectation is indeed in line with previous research, which reported a multimodal approach to perform superiorly \cite{dolmans2020perceived, han2020classification,rastgoo2019automatic, yin2017recognition}.
-
-With this research we 1) seek to explore which individual modality constitutes the most adequate predictor of workload when taking a deep learning approach, and 2) whether a multimodal network architecture is preferable over the three simpler (but much less computationally demanding) unimodal architectures.
-This comparison will mainly be propelled by contrasting network performance, however when drawing conclusions, considerations regarding computational costs will also be taken into consideration.
-With this research we aim to deepen the knowledge of taking a deep learning approach towards workload prediction with physiological sensors in an experimental setting, which as of yet, is still a novel and fairly understudied topic.
+Taking a deep learning approach such as ours may still be considered a novel, yet promising, approach to workload assessment.
+Due to the novelty of this approach, a deepening of the body of knowledge is necessary, which is something we aim to contribute to with this study.
 
@@
 \subsubsection*{EEG Network Architecture}
-An overview of the complete literature EEG applications with deep learning was presented by \citeA{craik2019deep}, who reported 16\% of all publications to constitute workload assessment.
-The lion's share of these publications utilized either a deep belief network or convolutional neural network (ConvNet).
+An overview of the complete literature on EEG applications with deep learning was presented by \citeA{craik2019deep}, who reported 16\% of all publications to constitute workload assessment.
 \citeA{tabar2016novel} proposed a ConvNet and stacked auto-encoder (SAE) hybrid approach towards workload classification with EEG.
@@
 Firstly, raw EEG data was fed into a single convolutional layer, with the objective of extracting features.
-Secondly, the the extracted features fed into the SAE part of the network,  which encompassed a stack of dense-layers designed to ultimately result in a classification of workload.
+Secondly, the extracted features were fed into the SAE part of the network,  which encompassed a stack of dense-layers designed to ultimately result in a classification of workload.
 An accuracy of 90\% was acquired with this architecture \cite{tabar2016novel}.
@@
 A deep ConvNet, a shallow ConvNet, a deep-shallow hybrid ConvNet and a residual ConvNet were contrasted with the FBCSP baseline method.
-Both the deep and shallow ConvNets were found to reach at least similar, and in some regards better classification results as compared with the FBCSP baseline approach.
+Both the deep and shallow ConvNets were found to reach at least similar, and in some regards better, classification results as compared with the FBCSP baseline approach.
 Altogether, a deep ConvNet with four convolutional-max-pooling blocks was found to perform best, exhibiting a classification accuracy of 92.4\% \cite{schirrmeister2017deep}.
@@
 In addition to these, a hybrid ConvNet-LSTM approach was explored as well.
-This hybrid approach constituted four convolutional blocks followed by a single LSTM layer, and was found to perform best with an accuracy of 74\% \cite{sun2019hybrid}.
+This hybrid approach constituted four convolutional blocks, followed by a single LSTM layer, and was found to perform best with an accuracy of 74\% \cite{sun2019hybrid}.
 \citeA{dolmans2020perceived} contrasted several physiological signals in their ability to predict workload, each of which by taking a deep learning approach.
@@
 \subsubsection*{Multimodal Fusion Strategy}  
-When creating a DNN that combines multiple modalities into a single network,  the information streams that stem from the different subparts of the network (each corresponding to one of the modalities) are required to be combined, i.e.
+When creating a DNN that combines multiple modalities into a single architecture,  the information streams that stem from the different subparts of the network (each corresponding to one of the modalities) are required to be combined, i.e.
 \enquote{fused}, at a given point in the network.
@@
 Secondly, late fusion refers to the process of aggregating the decisions of multiple separate networks, each constructed for every modality separately.
-When the data sources stemming from the various modalities happen to be either correlated or different in their dimensionality, late fusion is oftentimes a more feasible approach as opposed to early fusion \cite{ramachandram2017deep}.
+When the data sources stemming from the various modalities happen to be either correlated, or different in dimensionality, late fusion is oftentimes a more feasible approach as opposed to early fusion \cite{ramachandram2017deep}.
 Lastly, intermediate fusion is the most widely employed fusion strategy for multimodal networks.
@@
 \subsubsection*{Auxiliary Layers in a DNN Architecture}
-At the core of a DNN are the aforementioned types of layers, such as convolutional, LSTM and dense layers.
-Such layers are often accompanied with auxiliary layers in order to ensure network stability.
-The first type of layers often used in network architectures are batch normalization layers, which have the objective improving network stability.
+At the core of a DNN are the previously mentioned types of layers, such as convolutional, LSTM and dense layers.
+Such layers are oftentimes accompanied with auxiliary layers.
+The first type of layers often used in network architectures are batch normalization layers, which have the objective of improving network stability.
 It is beneficial to incorporate a batch normalization layer subsequent to a convolutional layer, but before feeding into the activation layer \cite{ioffe2015batch}.
@@
 For a more extensive elaboration on pooling we refer the reader to \citeA{lecun2015deep}.
-All previously considered network architectures utilize max-pooling layers, usually specified subsequent to the activation layer \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid, tabar2016novel}.
+All previously considered network architectures utilized max-pooling layers, usually specified subsequent to the activation layer \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid, tabar2016novel}.
 
-The incorporation of dropout layers was initially proposed by \citeA{srivastava2014dropout}.
+The incorporation of dropout was initially proposed by \citeA{srivastava2014dropout}.
 Dropout layers drop a randomly-selected number of neurons and their connections throughout the training process.
@@
 Doing so helps to reduce overfitting, particularly for complex network architectures \cite{srivastava2014dropout}.
-Most of the previously considered network architectures make use of dropout layers \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid}.
+Most of the previously considered network architectures made use of dropout layers \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid}.
 
 \subsubsection*{Hyperparameter Optimization}
-Hyperparameter optimization (HPO) is a technique that optimizes network hyperparameters, such as for example learning rate and dropout rate.
+Hyperparameter optimization (HPO) is a technique that can optimize various DNN hyperparameters, such as for example learning rate and dropout rate.
 Substantial advancements in DNN performance have been attained by utilizing HPO, especially in the case of ConvNets \cite{bergstra2012random}.
-In theory, one could optimize the entire DNN architecture, including the number of neurons/filters in dense/convolutional layers, the number of layers in general, whether to use certain layers, etc.
+In theory, one could optimize the entire DNN architecture, including the amount of neurons/filters in dense/convolutional layers, the number of layers in general, whether to use certain layers, etc.
 There is, however, a strong relationship between the amount of parameters to be optimized and the computational resources required to do so: optimizing many hyperparameters will inflate computational costs substantially.
-The Optuna toolbox provides a method for creating a parameter search space, from which values for the hyperparameters may be sampled, and optimization can be performed \cite{akiba2019optuna}.
+The Optuna toolbox provides a method for creating a parameter search space, out of which values for the hyperparameters may be sampled \cite{akiba2019optuna}.
 
@@
 The experimental setting in which our data was collected is the open-source spaceship video-game Empty Epsilon, in which partakers carried out tasks on a virtual spaceship bridge \cite{daid2016empty}.
-This experiment was instituted by the Brain Computer Interfaces Testbed \footnote{https://bmslab.utwente.nl/} hosted by the University of Twente and carried out in cooperation with Thales Group\footnote{https://www.thalesgroup.com/en/countries/europe/netherlands} Hengelo, the Netherlands.
-The experiment was divided into a total of 15 tasks, differing in difficulty and hence designed to evoke varying degrees of workload.
+This experiment was instituted by the Brain Computer Interfaces Testbed\footnote{https://bmslab.utwente.nl/} hosted by the University of Twente and carried out in cooperation with Thales Group Hengelo, the Netherlands\footnote{https://www.thalesgroup.com/en/countries/europe/netherlands}.
+The experiment constituted 15 tasks, differing in difficulty and hence designed to evoke varying degrees of workload.
 The total duration of the experiment was roughly three hours.
 
-Respondents were asked to fill out the NASA-TLX questionnaire after each of the fifteen task, inquiring into the amount workload perceived during the respective task.
+Respondents were asked to fill out the NASA-TLX questionnaire after each of the 15 task, inquiring into the amount workload perceived during the respective task.
 Each questionnaire consisted out of six items.
@@
 Since the experiment took place on a computer whilst participants sat behind a desk, we chose to not incorporate such items.
-Each item, and hence the newly constructed scale, ranges from 0-20, wherein 0 reflects the lowest possible level workload and 20 reflects the highest possible level workload.
+Each item, and hence the newly constructed scale, ranges from 0-20, wherein 0 reflects the lowest possible level of workload and 20 reflects the highest possible level of workload.
 In order to encourage numerical stability, label scores were normalized to reside in-between 0-1.
@@
 For each participant, the EEG, PPG and GSR data streams were cut into windows of eight seconds, resulting in an average of roughly 351 windows per respondent.
-80\% of all windows have been used for training, 10\% for validation within the training process and 10\% for the testing of network performance.
+80\% of the windows have been used for training, 10\% for validation within the training process and 10\% for testing final network performance.
 The partitioning of the windows into training, validation and testing sets was done systematically by selecting every \textit{n-th} window, such that windows over the entire duration of the experiment were represented equally in each partition.
-Exactly the same partitions were utilized in the training, validation and testing procedure across the four architectures to ensure a fair comparison.
+Exactly the same partitions were utilized in the training, validation and testing procedure across the four architectures, in order to ensure a fair comparison.
 
 \subsection{Network Architectures \& Training} \label{section:DNN}
-Individuals tend to respond differently towards high workload situations: for some workload manifests itself mostly through an increase in heart rate detected through PPG, whereas for others it manifests as an increase in skin conductivity detected through GSR.
-To account for such between-person differences, we trained an individual DNN for each participant.
-Since a total of four architectures are contrasted for 27 respondents, this resulted in a total of 108 trained networks.
+As was shortly elaborated on in the introduction, an advantage of our approach is that an individual network may be trained for every participant separately.
+This is helpful, since individuals tend to respond differently towards high workload situations: for some, workload manifests itself mostly through an increase in heart rate detected through PPG, whereas for others, it mainly manifests as an increase in skin conductivity detected through GSR.
+Since a total of four architectures are contrasted for 27 participants, this resulted in a total of 108 trained networks.
 Equally so, HPO was conducted for each person individually, resulting in 108 sets of optimized hyperparameters.
@@
 All unimodal architectures drew inspiration from aforementioned research \cite{biswas2019cornet, dolmans2020perceived, schirrmeister2017deep, sun2019hybrid}.
-We opted for a ConvNet architecture for all three unimodal network architectures.
+We opted for a ConvNet architecture for all three unimodal approaches.
 
@@
 Each of the unimodal networks may be distinguished by two separate parts, being the convolutional part and the prediction part.
-The objective of the convolutional part is to extract features from the data, and consists of four convolutional blocks, each constituting a convolutional layer, a batch normalization layer, the Exponential Linear Unit (ELU) activation function, and a max-pooling layer respectively.
+The objective of the convolutional part is to extract features from the data, and consists of four convolutional blocks.
+Each convolutional block consists of a convolutional layer, a batch normalization layer, the Exponential Linear Unit (ELU) activation function, and a max-pooling layer respectively.
 The objective of the prediction part is to predict the amount of perceived workload,  i.e.
 ultimately resulting in a single prediction of the label.
-The prediction part constitutes a flatten-layer,  with the objective of representing all input into one dimensional shape, followed by a dropout layer, a dense layer, a Rectified Linear (RELU) activation function closed by another dense layer.
-An overview of the amount of utilized filters / neurons for each layer of each network is provided in Table \ref{table:modelvariations}.
+The prediction part constitutes a flatten-layer,  with the objective of representing all input into one dimensional shape, followed by a dropout layer, a dense layer, a Rectified Linear (RELU) activation function, closed by another dense layer.
+An overview of the amount of utilized filters / neurons for each layer of each architecture is provided in Table \ref{table:modelvariations}.
 
@@
 \includegraphics[scale=0.50]{single_model_architecture}
-\caption{Unimodal Network Architectures.
-Each network constitutes a convolutional part of four convolutional blocks, and a classification part of two fully connected dense layers.
+\caption{Unimodal network architectures.
+Each network architecture constitutes a convolutional part of four convolutional blocks, and a classification part of two fully connected dense layers.
 }\label{fig:singlearchitecture}
@@
 \newpage
-We optimized the hyperparamater for learning rate, dropout rate and the amount of neurons for the first dense layer (\enquote{Dense1} in Figure \ref{fig:singlearchitecture}).
+We optimized the hyperparamaters learning rate, dropout rate and the amount of neurons for the first dense layer (\enquote{Dense1} in Figure \ref{fig:singlearchitecture}).
 This was managed in a total of 50 trials per network.
@@
 \subsubsection*{Multimodal Network Architectures} \label{section:multimodal}
-The multimodal network architecture was determined by combining the previously characterized unimodal architectures into a single architecture.
+The multimodal network architecture was designed by combining the previously characterized unimodal architectures into a single architecture.
 These separate network parts were joined by a head-network, the architecture of which drew inspiration from aforementioned research by \citeA{han2020classification}.
 A visual representation of the multimodal network is depicted in Figure \ref{fig:multiarchitecture}.
-An overview of the amount of utilized filters and neurons is provided in Table \ref{table:modelvariations}.
+An overview of the amount of utilized filters and neurons per layer is provided in Table \ref{table:modelvariations}.
 
 The feature extraction part of the multimodal network architecture is highly similar to the separate unimodel architectures.
-The seperate unimodal parts were combined by means of an intermediate fusion strategy, due to its highly flexible nature as compared with alternative fusion strategies (See: Section \ref{sec:related}).
-The outputs of the three distinct subparts were flattened, followed by a dense layer and RELU activation.
-Flattening was necessary such that all inputs were represented into one-dimensional space, after which concatenation rendered possible.
-The prediction part, also referred to as "Head-Network", consists of three dense layers, alternated with a dropout layer, batch normalization layers and RELU activation layers.
+We opted for an intermediate fusion strategy, due to its highly flexible nature as compared with alternative fusion strategies (See: Section \ref{sec:related}).
+The outputs of the three distinct subparts were flattened, followed by a dense layer and RELU activation funtion.
+Flattening was necessary such that all inputs were represented into one-dimensional space, after which concatenation becomes possible.
+The prediction part, also referred to as "head-network", consists of three dense layers, alternated with a dropout layer, batch normalization layers and RELU activation layers.
 
-We optimized the hyperparameter for learning rate, dropout rate and the amount of neurons for the first and second dense layers in 18 trials per network.
+We optimized the hyperparameters learning rate, dropout rate and the amount of neurons for the first and second dense layers in 18 trials per network.
 For training, a total of 250 epochs have been made through the data for each network independently.
 All training and HPO has been done on a Cloud TPU v2,  offered by the GPU cloud service Google Collab Pro.
-Total running time for the multimodal networks was about 7 days, the most of which absorbed by HPO.
+Total running time for the multimodal networks was about 120 hours, the most of which absorbed by HPO.
 
@@
 \includegraphics[scale=0.50]{multi_model_architecture}
-\caption{Multimodal Network Architecture.
-The network constitutes a convolutional part of four convolutional blocks for each of distinct network parts.
-All three distinct parts were flattened and concatenated subsequently.
+\caption{Multimodal network architecture.
+The network constitutes a convolutional part of four convolutional blocks for each of three subparts.
+All three distinct parts were flattened and concatenated.
 The prediction part of the network constitutes several dense layers.}\label{fig:multiarchitecture}
@@
 \subsection{Network Performance Evaluation}
-For each of the four investigated network architectures, the predictions of all 27 individually trained network were aggregated, after which performance was assessed by means of the following three performance metrics.
+As the reader might recall from Section \ref{section:DNN} we opted for individually tailored DNN's, trained for each respondent separately.
+Hence, for each of the the four contrasted architectures, the predictions of all personally trained network were aggregated, after which performance was assessed by means of the following three performance metrics.
 
@@
 \section{Results}
-Before addressing network performance, a description of all window labels is depicted in Figure \ref{fig:labels}.
-This constitutes an aggregation of the labels of all windows over all participants, resulting in a total of 9474 depicted window labels.
-It becomes readily apparent that the distribution of the window labels displays a noticeably right-skewed tendency, with a median of 5.75 and an 90\% upper-bound quantatile of 12.75.
-This implies that there is a considerable underrepresentation of high workload windows.
+Before addressing network performance, we firstly present a description of all window labels as depicted in Figure \ref{fig:labels}.
+Displayed is an aggregation of the window labels of all participants, resulting in a total of 9474.
+It is immediately noticeable that the distribution displays a right-skewed tendency, with a median of 0.29 and an 90\% upper-bound quantile of 0.64.
+This demonstrates that there is a considerable underrepresentation of high workload windows in our data, the implication of which will be addressed in a subsequent section.
 
@@
 \centering
-\includegraphics[scale=0.45]{labels.png}
-\caption{Distribution window labels.
-The solid line represents the median, whereas the two dashed line and their displayed values represent the 10\% and 90\% quantiles respectively.
-}\label{fig:labels}
+\includegraphics[scale=0.5]{labels.png}
+\caption{Distribution of the aggregate of all window labels. The solid line represents the median, whereas the two dashed lines represent the 10\% and 90\% quantiles respectively. }\label{fig:labels}
 \end{figure}
 
-\subsection{Deep Neural Network Performance}
-Depicted in Table \ref{table:results} are the performance metrics for each of the four network architectures.
-The most remarkable result is the relatively bad performance of the multimodal architecture.
-Both the unimodal EEG and GSR architectures score consistently higher on all metrics.
+\subsection{Results: Performance Metrics}
+Depicted in Table \ref{table:results} are the performance metrics of all four network architectures.
+Most striking is the performance of the multimodal architecture, scoring consistently worse across all metrics when compared with the unimodal EEG and GSR architectures.
 
 Performance in terms of MAE is most favorable for the EEG architecture, closely followed by the GSR architecture.
-The multimodal architecture performs worse as compared with the aforementioned architectures, ultimately followed by the PPG architecture which performed worst.
-Results in terms of RMSE adhere to a similar pattern, which is not surprising given that the RMSE and MAE are closely related.
+The multimodal architecture performs worse than the aforementioned, ultimately followed by the PPG architecture, which scored worst in terms of MAE.
+Results in terms of RMSE adheres to a similar pattern, which is not surprising, given that the RMSE and MAE are closely related.
 RMSE values are consistently higher as compared with MAE, which can be attributed to the tendency of the RMSE to punish strong deviations more severely.
-The correlation between predictions and labels are indicative of a similar pattern, in which the EEG architecture scores best, followed by the GSR, multimodal and PPG -architectures respectively Despite consistency in this pattern, an interesting disparity is that the differences in terms of correlation between the architectures are more substantial.
-In addition to the aforementioned results, we also assessed network performance on the training data, with the objective of gaining insight into overfitting.
-Table \ref{table:appendix} in Appendix \ref{sec:appendix} depicts the performance metrics of the networks as deployed on the training data.
-It becomes apparent that the unimodal architectures perform substantially better on the training data, whereas the multimodal architecture performs slightly better on the training data.
+The correlation between predictions and labels are indicative of a similar pattern, in which the EEG architecture scores best, followed by the GSR, multimodal and PPG architectures respectively.
+Despite the consistency in this pattern, an interesting disparity is that the differences in terms of correlation across the four architectures are more substantial.
+In addition to the aforementioned results, we also assess network performance on the training data, with which we attempt to gain insight into the potential occurrence of overfitting.
+Table \ref{table:appendix} in Appendix \ref{sec:appendix} presents the performance of the four network architectures, but now employed on the training data.
+It becomes apparent that the unimodal architectures perform better by a substantial margin on the training data: both MAE and RMSE values are considerably lower, whereas the correlation between predictions and labels are considerably higher.
+This is indicative of rather substantial overfitting.
+This tendency, although much less profound, is also observable for the multimodal architecture.
 
@@
 \end{center}
-\raggedright{ \emph{\newline Values between parentheses are standard deviations.
-MAE refers to Mean Average Error.
-RMSE refers to Root Mean Square Error.
-The depicted values are the averages of all individually trained networks.}}
+\raggedright{ \emph{\newline Values between parentheses are standard deviations. MAE refers to Mean Average Error. RMSE refers to Root Mean Square Error. }}
 \end{table}
@@
 
-An independent samples t-test was conducted to formally test differences in terms of absolute (window) error across various pairs of architectures.  The absolute error of a window $i$ is defined as:
+In order to formally contrast performance across various network architectures (as employed on the training data), we conduct several independent sample t-tests, with which we test differences in absolute (window) prediction error.
+The absolute prediction error is the same as mean absolute error (MAE), except for that it is not averaged per architecture.
+Testing is done two-sided with $\alpha = 0.05$.
+The average absolute prediction error per architecture (i.e.
+MAE) is not repeated alongside the statistical tests, for they are already displayed in Table \ref{table:results}.
+Absolute prediction errors of the unimodel EEG architecture were found to be significantly lower as compared with those of the multimodel architecture $t(1936)=-2.566, p=0.01$.
+No significant difference in terms of absolute prediction error between the EEG and GSR architectures were found $t(1936)=-1.188, p=0.24$, and equally so, no significant differences between the GSR and multimodal architectures were found $t(1936)=-1.463, p = 0.144$.
+Lastly, absolute prediction errors of the GSR architecture were found to be significantly lower as compared with the PPG architecture $t(1936)=-2.636 , p = 0.008$, but no significant differences between the GSR and multimodal architecture were found $t(1936)=-1.164 , p = 0.245$.
 
-$$|f(x_i)-y_i|$$
-where $f(x_i)$ represents the predicted value for window $i$ and $y_i$ represents its true label.
-Testing was done two-sided with $\alpha = 0.05$.
-Mean absolute error values per architecture are not reported, for they can be discerned from Table \ref{table:results}.
-The absolute error for the unimodel EEG architecture was found to be significantly lower as compared with the multimodel architecture $t(1936)=-2.566, p=0.01$.
-No significant difference in terms of absolute error between the EEG- and GSR -architectures was found $t(1936)=-1.188, p=0.24$, and equally so no significant difference was found between the GSR- and multimodal -architectures $t(1936)=-1.463, p = 0.144$.
-Lastly, absolute error for the GSR architecture was found to be significantly lower as compared with the PPG architecture $t(1936)=-2.636 , p = 0.008$, but no significant difference was found between the GSR- and multimodal -architecture $t(1936)=-1.164 , p = 0.245$.
-
-To explore performance differences across architectures into more detail, a graphical visualization of the distribution of window prediction errors per architecture are depicted in Figure \ref{fig:mae_hist}.
+\subsection{Results: Further Exploration}
+To further explore the differences in performance, a graphical visualization of the distribution of window prediction errors per architecture are depicted in Figure \ref{fig:mae_hist}.
 
@@
 \end{figure}
-\vspace{7mm}
+\vspace{4mm}
 
-In line with the previously presented performance metrics, it becomes readily apparent that the distribution of the prediction errors for the architecture that scored highest across all metrics, i.e.
-the EEG architecture, approximates the normal distribution most closely.
-This may be derived by the strong accumulation around 0 error (i.e.
+In line with the previously discussed performance metrics, it becomes readily apparent that the distribution of the prediction errors for the architecture that scored best across all metrics, i.e.
+the EEG architecture, approximates the most narrowly shaped normal distribution.
+This may be derived by the strong accumulation around the zero error mark (i.e.
 visually "peaked") and the relatively flat tails.
 The two worst performing architectures, i.e.
-multimodal- and PPG -architectures, display relatively thick tails, and are observed to have less strong accumulation around the 0 error mark (i.e.
+the multimodal and PPG architectures, display relatively thick tails, and are observed to have less strong accumulation around the 0 error mark (i.e.
 visually "less-peaked").
 This is equally so demonstrated by the 10\% and 90\% quantiles, residing farthest from the median.
-All distributions are observed to be slightly left-skewed, as indicated firstly by shape and secondly by the fact that 10\% quantiles are farther removed from the median as compared with the 90\% quantiles.
+All distributions are observed to be slightly left-skewed, as indicated firstly by shape and secondly by the fact that 10\% quantiles are farther removed from zero as compared with the 90\% quantiles.
 Despite that this left-leaning tendency is observable for all network architectures, it is most profound for the PPG and multimodal architectures.
 
-\newpage
-We further explore the results by means of a graphical visualization of absolute window prediction error against label value. This relationship is defined by Figure \ref{fig:mae_scatter}.
+We further explore our results by means of a graphical visualization of absolute (window) prediction error contrasted against window label value.
+This relationship is depicted in Figure \ref{fig:mae_scatter}.
 
-\vspace{7mm}
 \begin{figure}[h]
@@
 \includegraphics[scale=0.5]{mae_scatter.png}
-\caption{Relationship of absolute window prediction error opposed to window label value.
-The red lines represent the linear relationship between absolute prediction error and label value.
-The values \textit{r} represent the Pearson's Correlation coefficient between prediction errors and label values.} \label{fig:mae_scatter}
+\caption{Relationship between absolute window prediction error and window label value.
+The lines represent the linear relationships between absolute prediction errors and label values.
+The values \textit{r} represent the Pearson's correlation coefficients as captured by the lines.} \label{fig:mae_scatter}
 \end{figure}
@@
 
-It becomes apparent from Figure \ref{fig:mae_scatter}} that higher labeled windows are substantially less prevailing, as indicated by the thin spreading of dots at the right hand side of the figures,  This is conform to the conclusion drawn from the earlier depicted Figure \ref{fig:labels}.
-Most noteworthy is that for each of the four architectures, a linear relationship between the height of the absolute window prediction error and its respective label is observed.
-This is indicated by both the moderately ascending slope and the moderately high (positive) correlations coefficients $r$.
-Substantively, this implies that all network architectures are considerably less accurate in predicting high labeled windows.
+\newpage
+It becomes apparent from Figure \ref{fig:mae_scatter}}, that higher labeled windows are substantially less prevailing, as indicated by the thin spreading of dots at the right hand side of the plots.
+This is conform to the conclusion drawn from the earlier depicted Figure \ref{fig:labels}.
+Most noteworthy is that for all architectures, a moderately high linear relationship between absolute window prediction error and the respective label size can be observed.
+This is indicated by both the moderately ascending slopes, and the moderately high (and positive) correlation coefficients $r$.
+Substantively, this implies that all network architectures are considerably less accurate when predicting high labeled windows.
 This tendency is strongest for the multimodal architecture.
-For both the EEG- and GSR -architectures, this linear relationship is observed to be weaker, although still of noteworthy size.
+For both the EEG and GSR architectures, this linear relationship is observed to be weaker, although still of a noteworthy magnitude.
+\vspace{5mm}
 
-\newpage
 \section{Discussion \& Conclusion}
-We found the unimodal EEG architecture to perform best on all performance metrics,  with a rather sizable difference in the correlations between predictions and labels.
-In terms of absolute window prediction error, statistical evidence was found in favor of the unimodal EEG architecture outperforming the multimodel architecture, but not so in favor of the EEG architecture outperforming the GSR architectures.
-Performance of the GSR architecture was detected to be worse on all metrics as compared with the EEG architecture, but better on all metrics as compared with the multimodal architecture.
-These differences were, however, not found to be statistically significant in terms of absolute window prediction error.
-The unimodal PPG architecture was found to perform worst across the board.
-In terms of absolute window prediction error, this difference was found to be statistically significant when evaluated against the EEG- and GSR -architectures.
-When applied on the training data, network performance was substantially improved, indicative of overfitting.
-This especially held true for the singlemodal architectures.
-Lastly, a moderate relationship was observed between absolute prediction error and label size, implying that all network architectures performed worse on higher labeled windows.
-This deviation was strongest for the two worst performing architectures, i.e.
-the multimodal and PPG.
+The unimodal EEG architecture was found to consistently perform best across all performance metrics.
+The second best performance was attained by the unimodal GSR architecture, followed by the multimodal architecture, and lastly, the unimodal PPG architecture.
+For various pairs of architectures, we formally tested differences in terms of their absolute prediction errors.
+Statistical evidence indicated that the unimodal EEG architecture significantly outperformed the multimodel architecture.
+In addition, we presented statistical evidence indicating that both the unimodal EEG and unimodal GSR architectures, outperformed the unimodal PPG architecture.
+In order to explore the extent to which our networks suffered from overfitting, we applied them towards the training data.
+These results demonstrated rather substantial overfitting, particularly so for the three unimodal architectures.
+Lastly, we illustrated the linear relationship between absolute window prediction errors and label sizes.
+This relationship was found to be moderately high across all architectures, indicating that they performed worse in predicting higher labeled windows.
+This tendency was found to be strongest for the two worst performing architectures, i.e.
+the multimodal and unimodal PPG architectures.
 
 \subsection{Discussion}
-Perhaps the most noteworthy of all aforementioned results is that the unimodel EEG architecture outperformed the multimodal architecture.
-As argued in the introduction, the opposite was expected: given that the predictions of a multimodal architecture rest on a richer conglomerate of information, better performance is expected.
-Lending credence to this this inclination is previous research that found a multimodal architecture to perform superiourly \cite{dolmans2020perceived, han2020classification, rastgoo2019automatic, yin2017recognition}.
-In the subsequent sections we aim to rationalize our results.
+Out of all three unimodal architectures, the EEG architecture was found to perform best.
+The EEG modality may thus be considered the most adequate predictor of workload.
+This confirms the first expectation we posed in the introduction, and is conform to previous research by \cite{hogervorst2014combining}.
+In addition to this, perhaps the most noteworthy result is that the multimodal architecture was outperformed by the unimodal EEG architecture.
+As posed in the introduction, we hypothesized the contrary.
+This expecation was partly based on a number of preceding studies, which consistently found a multimodal architecture to perform superiourly \cite{dolmans2020perceived, han2020classification, rastgoo2019automatic, yin2017recognition}.
+In the subsequent section we aim to rationalize this result.
 
-One reason could be the network architecture.
+Part of the reason could be the network architecture.
 Conform to  \citeA{han2020classification}, a shallow head network architecture was adopted, solely consisting of several fully connected dense layers.
-Further investigation into various alternative head network architectures could have resulted in a more adequately performing network,  but would have increased the computational expenses considerably.
-
-Besides this, an important consideration in the fields of statistics and machine-learning alike, is the oftentimes precarious balance between model complexity and simplicity.
+However, as was reported upon in Section \ref{sec:related}, some other studies opted for a fundamentally different design philosophy \cite{dolmans2020perceived, rastgoo2019automatic}.
+Further investigation into alternative head network architectures could have resulted in a more adequately performing network,  but would have increased the computational expenses considerably.
+Besides this, an important consideration is the oftentimes precarious balance between model complexity and simplicity.
 A model that is overly complex is in increased peril of overfitting, i.e.
 performing well on training data, but failing to generalize to testing data \cite{lever2016points}.
-Overfitting can especially be anticipated when training a relatively complex DNN on a small amount of data \cite{feng2019using,aggarwal2018neural}.
-As was argued before,  our case required personally trained networks due to the person-specific nature that is inherent to physiological data, resulting in a small amount of training data per DNN.
-Strong evidence in favor of overfitting was found for the unimodal architectures, posing that these network architectures were too complex to be trained on a small amount of data.
-Surprisingly, the even more complex multiodal architecture did only produce moderate overfitting.
-However despite this, it should be acknowledged that the core of the multimodal architecture is a composite of the overly complex unimodal architectures, which likely contributed to its relatively inadequate performance.
+Overfitting can especially be anticipated when training a relatively complex DNN on a small amount of data \cite{aggarwal2018neural, feng2019using}.
+As was expounded upon in Section \ref{section:DNN}, we opted for personally trained networks.
+A consequence of this is that we trained on small amounts of data.
+Indeed, strong evidence in favor of overfitting was found for the unimodal architectures, indicating that these networks were too complex to be trained on such small amounts of data.
+Surprisingly, the even more complex multiodal architecture only displayed minor overfitting.
+Despite this, it should be acknowledged that the core of the multimodal architecture is a composite of the, apparently overly complex, unimodal architectures, which most likely contributed to its relatively inadequate performance.
+These insights are distilled into various future research recommendations, presented in the later Section \ref{sec:future}.
 
-Another noteworthy result was the expounded relationship between a window's absolute error and its respective label score (as was visualized by Figure \ref{fig:mae_scatter}).
-It was visualized that all four architectures were consistently less accurate in predicting high labeled windows.
-A credible explanation for this is the relatively minor presence of high labeled windows in our data (as was visualized by Figure \ref{fig:labels}).
-Naturally, when a relatively small amount of high labeled windows are present in the training data, the network doesn't adequately learn to predict such windows.
+Another noteworthy result was the illustrated linear relationship between absolute prediction errors and their respective label scores (as visualized in Figure \ref{fig:mae_scatter}).
+It was demonstrated that all four architectures were consistently less accurate in predicting high labeled windows.
+A credible explanation for this is the relatively minor presence of high labeled windows in our data (as visualized in Figure \ref{fig:labels}).
+Naturally, when a relatively small amount of high labeled windows are present in the training set, a DNN is unable to adequately learn to predict such windows.
+Again, various strategies to handle this are proposed in Section \ref{sec:future}.
 
-Finally, despite that a comparison of absolute window prediction error across several architectures was found to be statistically significant, all differences in terms of MAE and RMSE were rather small.
-The statistical significance of some of the conducted t-tests can particularly be attributed to the vast amount of degrees of freedom with which was tested.
-We therefore reflect on the following: in opposite to our finding, suppose that a multimodal approach would have entailed a moderate improvement in performance over an unimodal approach.
+Finally, despite that several comparisons of absolute prediction errors across architectures were found to be statistically significant, all differences in terms of MAE and RMSE were rather small absolutely speaking.
+The statistical significance of several of the conducted t-tests may particularly be attributed to the vast amount of degrees of freedom with which was tested.
+We therefore recognize that the performance of most of our architectures were rather close, and reflect on the following: in opposite to our finding, suppose that a multimodal approach would have lead to a small improvement in performance over the unimodal approaches.
 Would this justify the addition in complexity,  the considerable increment in computational expenditure and the necessity to invest in a multitude of different physiological sensors?
 In other words, isn't the already adequately performing, and much less complex unimodal EEG approach sufficient for most tasks at hand?
-The answer to this question is context dependent, and should be reconsidered in each case specifically.
+The answer to these questions is heavily dependent upon context.
 
-\subsection{Limitations \& Future Research Recommendations}
-Additional research is necessary in order to find more optimal DNN architectures for small data scenario's such as the current.
-More specifically, 1) which network architectures are able to minimize overfitting and 2) which network architecture is most suitable for a multimodal approach.
-An effective approach to investigate this is by means of HPO.
-Apart from only optimizing hyperparamaters, a network architecture in its entirety can be optimized.
-In the current study we optimized several hyperparamaters, however the architecture in itself was pre-specified.
-A recommendation for future research is therefore to further investigate upon an appropriate architecture for both the unimodal and multimodal approaches
+\subsection{Limitations \& Future Research Recommendations} \label{sec:future}
+Additional research is necessary to gain insight into optimally performing network architectures for small data scenario's such as the current.
+More specifically,  further insights are required into 1) which network architectures are able to minimize overfitting and 2) which network architecture is most suitable for a multimodal approach.
+An effective technique with which this can be investigated is HPO, since apart from optimizing hyperparamaters, a network architecture in its entirety can be optimized.
+Thus, a recommendation for future research is to gain more insight into which type of DNN architectures are suitable for small dataset scenarios.
 
-As expounded on before, all architectures were found to be less precise in predicting high labeled windows, attributable to the fact that such windows were relatively uncommon in our data.
-This could stem from either 1) the fact that respondents refrained from indicating high workload on the NASA-TLX items utilized for labeling, or 2) respondents simply did not experience high workload throughout the experiment.
-Alternative labeling approaches may be suited to address the first point.
-Ideally, one would want to contrast various labeling strategies with one another, such that the most suitable labels for the task at hand may be utilized.
-Potentially interesting alternatives approaches to labeling are for example a standardized version of the NASA-TLX, or an objective difficulty score for each task, as was proposed by \citeA{dolmans2020perceived}.
-The second point could be addressed by designing the simulational scenario such high workload envoking segments are prevalent throughout the entire scenario.
-One could assess this by pretesting, and increasing the difficulty in certain segments if need be.
+As became apparent, all architectures were found to be less precise in predicting high labeled windows, attributable to the fact that such windows were relatively uncommon in our data.
+In theory, the absence of high labeled windows could result from two factors.
+Firstly, participants could have refrained from reporting high workload on the NASA-TLX items that were utilized for labeling.
+Alternative labeling approaches may be compared in order to address this.
+Ideally, one would want to contrast various labeling strategies, such that the best performing can be adopted.
+Examples of alternatives labeling approaches are a standardized version of the NASA-TLX, or an objective difficulty score for each task, as was proposed by \citeA{dolmans2020perceived}.
+Secondly, it might be that participants simply did not experience high workload throughout the experiment.
+The may be addressed by designing the experiment such high workload tasks are prevalent.
+Pretesting might help to ensure this.
 
-Finally, as was elaborated on before, the ultimate goal of this line of research is to obtain trained networks utilizable for workload assessment in a simulational setting.
-The personal differences that are inherent to physiological data were acknowledged by utilizing an individual network for each participant.
+Finally, as was discussed before, the personal differences that are inherent to physiological data were acknowledged by using individually trained networks.
 However apart from such between-personal differences, physiological data might be characterized by between-occasional differences as well.
-To give an example, PPG measurement is dependent upon various occasional factors such as amongst others the amount of emitted surrounding light, body position, cardiovascular stresses, etc.
+To give an example, PPG measurement is dependent upon various occasional factors, such as amongst others the amount of emitted surrounding light, body position, cardiovascular stresses, etc.
 \cite{lemay2014application}.
-Further research is required in order to assess the generelizability of a personally trained network to different occasions.
+Even for the same person, these contextual factors may differ across occasions, potentially endangering the generalizability of the trained networks.
+Further research is necessary in order to determine the robustness of personally trained networks at different occasions.
 
 \subsection{Conclusion}
-We took three unimodal and one multimodal approach to workload prediction by means of physiological sensors.
-The performance of the unimodal EEG-, GSR-, and PPG -architectures were assessed in order to determine the most suitable modality for workload prediction.
-In addition, an architecture combining all aforementioned modalities was proposed and assessed in terms of performance.
-It was found that all architectures performed rather adequately.
-A difference in performance was observable however: most notably it was found that the unimodal EEG architecture performed best.
-Surprisingly, we found a multimodal approach to be unjustified, however several explanations were considered that could potentially refute this.
-The implications of the current research is another step in the exploration of multimodal deep learning approaches towards workload prediction.
-Future research in this field will ideally investigate upon 1) network architectures that prevent substantial overfitting in a small dataset scenario,  2) an appropriate architecture for a multimodal approach in a small dataset scenario, 3) the feasibility of different labeling strategies and 4) the cross-occasional generelization of individually trained networks.
+The current research adds to the body of knowledge on deep learning based workload assessment.
+We contrasted various approaches to workload prediction by means of several physiological sensors.
+Four network architectures were contrasted in performance, including a unimodal EEG architecture, a unimodal GSR architecture, a unimodal PPG architecture and a multimodal architecture.
+In the introduction we posed two key research goals.
+Firstly, with this research we sought to explore which modality constitutes the most adequate predictor of workload.
+This was expected to be the EEG modality.
+Altough all modalities were found to perform rather satisfactory, we conclude that indeed the EEG modality constitutes the most adequate predictor of workload (opposed to PPG and GSR).
+Secondly, with this research we sought to determine whether a multimodal network architecture was preferable over three simpler unimodal architectures.
+Based on our results a multimodal approach was unjustified, however several explanations were considered that could potentially refute this finding.
+Further research is therefore necessary.
+This future research will ideally investigate upon 1) network architectures that prevent substantial overfitting in a small dataset scenario,  2) an appropriate architecture for a multimodal approach in a small dataset scenario, 3) the feasibility of different labeling strategies and 4) the extent to which personally trained networks can be generalized towards different occasions.
 

### 2021-05-13 4.results/results.py

@@ -115,7 +115,7 @@ def HistGrid():
 
     #Plot
     ax1.hist(x, bins = 70, color = "#0092cb")
-    ax1.set_title("EEG-Networks", fontsize = 10, fontstyle = "italic") 
+    ax1.set_title("EEG Architecture", fontsize = 10, fontstyle = "italic") 
     ax1.vlines((lowerbound, median, upperbound), 0, 71, colors= "darkslategray", linestyles= ("dashed", "solid", "dashed"))
     ax1.text(lowerbound-0.05, 60, round(lowerbound,2), horizontalalignment='right', verticalalignment='center', 
             color = "black", fontstyle = "italic", fontsize = 10)
@@ -139,7 +139,7 @@ def HistGrid():
 
     #Plot
     ax2.hist(x, bins = 70, color = "#0092cb")
-    ax2.set_title("PPG-Networks", fontsize = 10, fontstyle = "italic") 
+    ax2.set_title("PPG Architecture", fontsize = 10, fontstyle = "italic") 
     ax2.vlines((lowerbound, median, upperbound), 0, 68, colors= "darkslategray", linestyles= ("dashed", "solid", "dashed"))
     ax2.text(lowerbound-0.05, 60, round(lowerbound,2), horizontalalignment='right', verticalalignment='center', 
             color = "black", fontstyle = "italic", fontsize = 10)
@@ -162,7 +162,7 @@ def HistGrid():
 
     #Plot
     ax3.hist(x, bins = 70, color = "#0092cb")
-    ax3.set_title("GSR-Networks", fontsize = 10, fontstyle = "italic") 
+    ax3.set_title("GSR Architecture", fontsize = 10, fontstyle = "italic") 
     ax3.vlines((lowerbound, median, upperbound), 0, 69, colors= "darkslategray", linestyles= ("dashed", "solid", "dashed"))
     ax3.set(ylabel='Count', xlabel = 'Prediction Error')
     ax3.text(lowerbound-0.05, 60, round(lowerbound,2), horizontalalignment='right', verticalalignment='center', 
@@ -186,7 +186,7 @@ def HistGrid():
 
     #Plot
     ax4.hist(x, bins = 70, color = "#0092cb")
-    ax4.set_title("Multi-Modular Networks", fontsize = 10, fontstyle = "italic") 
+    ax4.set_title("Multimodal Architecture", fontsize = 10, fontstyle = "italic") 
[…]
